### 2014-06-10 R/read_network.Rmd
first commit

Title
========================================================

This is an R Markdown document. Markdown is a simple formatting syntax for authoring web pages (click the **Help** toolbar button for more details on using R Markdown).

When you click the **Knit HTML** button a web page will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r}
summary(cars)
```

You can also embed plots, for example:

```{r fig.width=7, fig.height=6}
plot(cars)
```

### 2014-06-10 analysis/context_permeability.Rmd
first commit

```{r message=FALSE}
source("../R/experiment_utils.R")
```

Context Permeability Convergence Results
========================================

In this analysis, we analyse the context permeability model in terms of 
convergence. This is, the percentage of times a simulation has converged to 
total consensus and how many agent encounters were needed for this to happen.

# Convergence for K-Regular Networks #
In this analysis we look at the convergence to consensus for simulations that use 
regular networks only. We will analyse two things: the *percentage of convergence to total consensus* and the *number of encounters* necessary to achieve concensus.

We first load the data related to convergence to consensus. In this first dataset, we can find a single boolean variable {1,0} that tells us wheather or not consensus was achieved. 
```{r results='asis',message=FALSE}
#Read the Parameters for this experiment
params <- read.exp.parameters(param_file_name="../data/regular_networks/param-space_2014-05-30_16:47:53experiment:0_.csv")

#read the adata related to consensus was achieved before 
require(data.table)
convergence_data <- fread("../data/regular_networks/consensus_achieved.csv")
convergence_data <- as.data.frame(convergence_data)[,-ncol(convergence_data)]
convergence_data <- merge(convergence_data, params, by="cfg.id")
```
We can now create a table to display the percentage of convergences to total 
consensus **for each value of k and number of networks**.

```{r message=FALSE}
require(reshape)
require(tables)

#filter some things out
fcdata <- melt.data.frame(convergence_data,id.vars=c("cfg.id","run","num.networks","network.0.k"), measure.vars=c("consensus-achieved"))

#I can also cast to obtain multiple values like summary 
#this will be useful later for the table with the number of encounters
#convergence_table <- cast(fcdata, num.networks~network.0.k~value, sum)

#convergence_table

fcdata_table <- aggregate(data=fcdata, fcdata$value~num.networks + fcdata$network.0.k, FUN=sum)
colnames(fcdata_table) <- c("num.networks", "k", "value")

 #create a pretty table for latex
latex_table <- tabular(cast(fcdata_table, num.networks~k, value="value"))

```

```{r results='asis'}
html(latex_table)

#I can also save this table to a file for later reference
latex(latex_table,file="tex/regular_convergence.tex", booktabs=T, )
```

This table shows the percentage of simulation runs that converged to total consensus over 100 
independent runs.

# Number of Encounters for K-Regular Networks 
Now we analise the number of encouters necessary to achieve consensus. Or the total number of encounters that 
were performed if consensus was not achieved. **The maximum number of simulation cycles is 2000.** The maximum
number of encounters is thus limited by the maximum number of simulation cycles (and in consequense steps). The 
data for the encounters contains the following variables.
```{r}
encounter_data <- fread("../data/regular_networks/num_encounters.csv")
encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
head(encounter_data)
```
To get the information for how many networks were in the simulation and what was the k value we 
can merge the data like we have done previously. 
```{r}
encounter_data <- merge(encounter_data, params, by="cfg.id")
```

We now filter some of the variables out.
```{r message=FALSE}
#filter some things out
fedata <- melt.data.frame(encounter_data,id.vars=c("cfg.id","run","num.networks","network.0.k"), measure.vars=c("total-encounters"))
head(fedata)

#filter encounter data include only num networks > 3
fedata_net1 <- fedata[fedata$num.networks>2 & fedata$network.0.k <= 5,]

fedata_net10 <- fedata[fedata$num.networks>2 & fedata$network.0.k > 5,]

#create a table with avg and sd
cast_fedata_table <- cast(data=fedata, formula=network.0.k~num.networks, c(mean, sd))

fedata_table_full <- tabular(cast_fedata_table)

```

Create the tables
```{r results='asis',message=FALSE}
#to print the table created with tabular

html(fedata_table_full)

#print this to a file to use in the paper

Hmisc::latex(fedata_table_full, file="tex/regular_encounters_full.tex",booktabs=T)
```

Now to observe the distribution of the number of encounters, necessary to achieve consensus, we look at the box plots for **k = {1,2,3,4,5}** and **k = {10,20,30,40,50}** respectively. We look at **configurations with a number of networks > 3** since less networks require more connectivity to allow consensus to be reached 100% of the time.

```{r}
plot <- plot.exp.box(data=fedata_net1,x_factor=as.factor(fedata_net1$num.networks), data_y=fedata_net1$value, fill_factor=as.factor(fedata_net1$network.0.k),fill_label="K", x_label="Number of Networks", y_label="Number of Encounters")

plot

plot <- plot.exp.box(data=fedata_net10,x_factor=as.factor(fedata_net10$num.networks), data_y=fedata_net10$value, fill_factor=as.factor(fedata_net10$network.0.k),fill_label="K", x_label="Number of Networks", y_label="Number of Encounters")

plot
```

To try to answer the question "why do some outliers show up in the data" (simulation runs that took more time than the typical run), I look at the outlier from the configuration **(networks=3, k = 10)**. What I'm trying to find is weather the network structure is the same from the other runs.

```{r}
source("../R/read_network.R")

network_data <- fread("../data/regular_networks/networks.csv")

#get outlier
outlier <- fedata_net10[fedata_net10$value > 30000 & fedata_net10$network.0.k == 10,]
normal <- fedata_net10[fedata_net10$value < 3000 & fedata_net10$network.0.k == 10,]

#get outlier network
network_outlier_data <- network_data[network_data$"cfg.id" == outlier$"cfg.id" & network_data$"run" == outlier$"run", ]
outlier_net <- read.composite.network(network_data=network_outlier_data)

fdata <- fedata_net10[fedata_net10$"network.0.k" == 10 & fedata_net10$"num.networks" == 3 & fedata_net10$value < 5000,]#filter the data
plot <- plot.exp.box(data=fdata,x_factor=as.factor(fdata$num.networks), data_y=fdata$value, fill_factor=as.factor(fdata$network.0.k),fill_label="K", x_label="Number of Networks", y_label="Number of Encounters")

plot

normal <- normal[2,] #choose one possible configuration (not an outlier)
normal

network_normal_data <- network_data[network_data$"cfg.id" == normal$"cfg.id" & network_data$"run" == normal$"run", ]
normal_net <- read.composite.network(network_data=network_normal_data)

#outlier network properties
outlier_net_props <- read.composite.properties(outlier_net)
normal_net_props <- read.composite.properties(normal_net)

```

```{r}
outlier_net_props
normal_net_props
```
There is no significant differences between the network from the outlier simulation run and one case from a normal run. 
This suggests that this can be a property of the game itself (see plots bellow) and some "event" leads the convergence to be slower than those of the rest of the runs. My hypothesis is that the agents reach a state from which converging towards consensus is significantly harder. This needs further analysis. One idea is to look at difference between the observations (agent memory) for both opinions throughout the simulation.

Another idea is to look at the sate of the agents and their location in the underlying networks. If networks contain some sort of self-reinforcing structures, this can cause the convergence to be slowed. Daniel Villatoro found these structures in models such as scale-free networks (see [http://dl.acm.org/citation.cfm?id=2451250](here)). Self-reinforcing structures are subgraphs that converge to consensus, and due to its structure (and the nature of the consensus game), lead the agents in that subgroup to reinforce one another. Breaking these consensus groups can be particularly difficult even if the whole society has converged to a different opinion value.

```{r}
opinion_data <- read.opinion.progress("../data/regular_networks/opinion_progress.csv")
#filter opinion to outlier run and normal run
outlier_run <- opinion_data[opinion_data$"cfg.id" == outlier$"cfg.id" & opinion_data$"run" == outlier$"run",]
normal_run <- opinion_data[opinion_data$"cfg.id" == normal$"cfg.id" & opinion_data$"run" == normal$"run",]

```

```{r}
plot_run_outlier <- plot_opinion(opinion_data=outlier_run)
plot_run_normal <- plot_opinion(opinion_data=normal_run)

plot_run_normal + labs(title = "Normal Run")
plot_run_outlier + labs(title = "Outlier Run")
```

# Convergence for Scale-Free Networks #
We now perform the same analysis for an homogenous scale-free configuration (scale-free networks in all the layers). 
To create the scale-free networks, we used the Barabasi-Albert model in which the networks are expanded by preferential 
attachment. The networks have an additional parameter d which dictates how many connections are added each time a new node 
is added to the network. We varied this parameter and considered the values ** d = {1,2,3,4,5} **.

We first look at the number of convergences to total consensus in 100 simulation runs. 
```{r results='asis',message=FALSE}
#Read the Parameters for this experiment
params <- read.exp.parameters(param_file_name="../data/scale-free_networks/param-space_2014-05-30_18:38:14experiment:1_.csv")

#read the adata related to consensus was achieved before 
require(data.table)
convergence_data <- fread("../data/scale-free_networks/consensus_achieved.csv")
convergence_data <- as.data.frame(convergence_data)[,-ncol(convergence_data)]
convergence_data <- merge(convergence_data, params, by="cfg.id")
```

We can now create a table to display the percentage of convergences to total 
consensus **for each value of d and number of networks**.

```{r}
require(reshape)
require(tables)

#filter some things out
fcdata <- melt.data.frame(convergence_data,id.vars=c("cfg.id","run","num.networks","network.0.d"), measure.vars=c("consensus-achieved"))

#I can also cast to obtain multiple values like summary 
#this will be useful later for the table with the number of encounters
#convergence_table <- cast(fcdata, num.networks~network.0.k~value, sum)

#convergence_table

fcdata_table <- aggregate(data=fcdata, fcdata$value~num.networks + fcdata$network.0.d, FUN=sum)
colnames(fcdata_table) <- c("num.networks", "d", "value")

 #create a pretty table for latex
latex_table <- tabular(cast(fcdata_table, num.networks~d, value="value"))

```

```{r results='asis'}
html(latex_table)

#I can also save this table to a file for later reference
latex(latex_table,file="tex/scale-free_convergence.tex", booktabs=T, )
```

# Number of Encounters for Scale-Free Networks #
Now we analise the number of encouters necessary to achieve consensus. Or the total number of encounters that 
were performed if consensus was not achieved. The data for the encounters contains the following variables.
```{r}
encounter_data <- fread("../data/scale-free_networks/num_encounters.csv")
encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
head(encounter_data)
```
To get the information for how many networks were in the simulation and what was the **d** value, we 
can merge the data like we have done previously. 
```{r}
encounter_data <- merge(encounter_data, params, by="cfg.id")
```

We now filter some of the variables out.
```{r message=FALSE}
#filter some things out
fedata <- melt.data.frame(encounter_data,id.vars=c("cfg.id","run","num.networks","network.0.d"), measure.vars=c("total-encounters"))
head(fedata)

#create a table with avg and sd
cast_fedata_table <- cast(data=fedata, formula=network.0.d~num.networks, c(mean, sd))

fedata_table_full <- tabular(cast_fedata_table)

```

Create the tables
```{r results='asis',message=FALSE}
#to print the table created with tabular

html(fedata_table_full)

#print this to a file to use in the paper

Hmisc::latex(fedata_table_full, file="tex/scale-free_encounters_full.tex",booktabs=T)
```

Now to observe the distribution of the number of encounters, necessary to achieve consensus, we look at the box plots for **d = {1,2,3,4,5}**. We look at **configurations with a number of networks > 3** since less networks require more connectivity to allow consensus to be reached 100% of the time.

```{r}
plot <- plot.exp.box(data=fedata,x_factor=as.factor(fedata$num.networks), data_y=fedata$value, fill_factor=as.factor(fedata$network.0.d),fill_label="d", x_label="Number of Networks", y_label="Number of Encounters")

plot

```

Focusing on the runs where the **number of encounters was < 2000** (some outliers are not present, see previous plots for that)

```{r}
fedata <- fedata[fedata$"num.networks" >= 3 & fedata$"network.0.d" > 1 & fedata$"value" < 10000, ]
plot <- plot.exp.box(data=fedata,x_factor=as.factor(fedata$num.networks), data_y=fedata$value, fill_factor=as.factor(fedata$network.0.d),fill_label="d", x_label="Number of Networks", y_label="Number of Encounters")

plot

```

# Convergence for Heterogeneous Configuration (K-Regular Network + Scale-free Network) #
Now we analyse what happens when we use an heterogenous configuration, this is, each layer in the model uses different 
network models. In a first experiment, we use a K-Regular network for one layer and a Scale-free network for the other. 
```{r results='asis',message=FALSE}
#Read the Parameters for this experiment
params <- read.exp.parameters(param_file_name="../data/scale-free_regular/param-space_2014-05-30_18:40:41experiment:2_.csv")

#read the adata related to consensus was achieved before 
require(data.table)
convergence_data <- fread("../data/scale-free_regular/consensus_achieved.csv")
convergence_data <- as.data.frame(convergence_data)[,-ncol(convergence_data)]
convergence_data <- merge(convergence_data, params, by="cfg.id")
```

We can now create a table to display the percentage of convergences to total 
consensus **for each value of k and d**. The **number of networks** in this experiment is allways **2**.

```{r message=FALSE}
require(reshape)
require(tables)

#filter some things out
fcdata <- melt.data.frame(convergence_data,id.vars=c("cfg.id","run","network.0.k","network.1.d"), measure.vars=c("consensus-achieved"))

#convergence_table

fcdata_table <- aggregate(data=fcdata, fcdata$value~network.1.d + fcdata$network.0.k, FUN=sum)
colnames(fcdata_table) <- c("d", "k", "value")

 #create a pretty table for latex
latex_table <- tabular(cast(fcdata_table, d~k, value="value"))

```

```{r results='asis'}
html(latex_table)

#I can also save this table to a file for later reference
latex(latex_table,file="tex/regular_scale-free_convergence.tex", booktabs=T, )
```

This table shows the percentage of simulation runs that converged to total consensus over 100 
independent runs.

# Number of Encounters for Heterogeneous Configuration (K-Regular Network + Scale-free Network) #
In this section, we analise the number of encouters necessary to achieve consensus with this heterogenous setup.
The data for the encounters contains the following variables.
```{r}
encounter_data <- fread("../data/scale-free_regular/num_encounters.csv")
encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
head(encounter_data)
```
To get the information for the d and k values we can merge the data with the parameter space
```{r}
encounter_data <- merge(encounter_data, params, by="cfg.id")
```

We now filter some of the variables out.
```{r message=FALSE}
#filter some things out
fedata <- melt.data.frame(encounter_data,id.vars=c("cfg.id","run","network.0.k","network.1.d"), measure.vars=c("total-encounters"))
head(fedata)

#filter encounter data include only num networks > 3
fedata_net1 <- fedata[fedata$network.0.k <= 5,]

fedata_net10 <- fedata[fedata$network.0.k > 5,]

#create a table with avg and sd
cast_fedata_table <- cast(data=fedata, formula=network.0.k~network.1.d, c(mean, sd))

fedata_table_full <- tabular(cast_fedata_table)

```

Create the tables
```{r results='asis',message=FALSE}
#to print the table created with tabular

html(fedata_table_full)

#print this to a file to use in the paper

Hmisc::latex(fedata_table_full, file="tex/regular_scale-free_encounters_full.tex",booktabs=T)
```

Now to observe the distribution of the number of encounters, necessary to achieve consensus, we look at the box plots for **k = {1,2,3,4,5}** and **k = {10,20,30,40,50}** respectively.

```{r}
plot <- plot.exp.box(data=fedata_net1,x_factor=as.factor(fedata_net1$network.1.d), data_y=fedata_net1$value, fill_factor=as.factor(fedata_net1$network.0.k),fill_label="K", x_label="D", y_label="Number of Encounters")

plot

plot <- plot.exp.box(data=fedata_net10,x_factor=as.factor(fedata_net10$network.1.d), data_y=fedata_net10$value, fill_factor=as.factor(fedata_net10$network.0.k),fill_label="K", x_label="D", y_label="Number of Encounters")

plot
```

Focusing now on the best performing configurations and on the runs that produced a convergence in less than 50000 encounters, the distribution of the number of encounters is as follows.

```{r}
fedata_net10 <- fedata_net10[fedata_net10$"network.1.d" > 1 & fedata_net10$value <= 10000,]

plot <- plot.exp.box(data=fedata_net10,x_factor=as.factor(fedata_net10$network.1.d), data_y=fedata_net10$value, fill_factor=as.factor(fedata_net10$network.0.k),fill_label="K", x_label="D", y_label="Number of Encounters")

plot

```

# Heterogeneous Network Properties #
In this section we analyse the properties of this heterogenous setup. This is, what happens when you mix 
k-regular networks with a scale-free network.

```{r}
source("../R/read_network.R")
network_data <- fread("../data/scale-free_regular/networks.csv")
#filter the data, we just need the data from one simulation run
network_data <- network_data[network_data$"cfg.id" == fedata_net10[1,]$"cfg.id" & network_data$"run" == fedata_net10[1,]$"run",]

k_regular_network <- read.single.network(data=network_data, layer=0)
scale_free_network <- read.single.network(data=network_data, layer=1)
combined_network <- k_regular_network + scale_free_network

```

We combine a 10-Regular and a Scale-free network from the previous experiment (D = 2) by merging the overllaping edges. 
```{r fig.width=15, results='asis'}
network1 <- k_regular_network
network2 <- scale_free_network

color1 <- "#7D9C9F"
color2 <- "#B1B1B1"
color_over <- "#FF003F"

E(network1)$color <- color1
E(network2)$color <- color2

el1 <- apply(get.edgelist(network1), 1, paste, collapse="-")
el2 <- apply(get.edgelist(network2), 1, paste, collapse="-")
elc <- apply(get.edgelist(combined_network), 1, paste, collapse="-")

E(combined_network)$color <- ifelse((elc %in% el1) & (elc %in% el2), color_over, ifelse((elc %in% el1), color1, color2))

par(mfrow=c(1,3))
plot(network1,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="10-Regular Network")
plot(network2,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="Scale-Free with D = 2")
plot(combined_network,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="Combined Networks")
```

We now plot the degree distribution using a log scale. We do this for the **10-Regular** Network, the **Scale-Free Network with d = 2**, and the combined network.

```{r fig.width=15}
par(mfrow=c(1,3))
plot.degree.distribution(network=k_regular_network, "10-Regular Network")
plot.degree.distribution(network=scale_free_network, "Scale-Free Network with D = 2")
plot.degree.distribution(network=combined_network, "Combined network")
```

# Regular / Scale-Free / Scale-Free Configuration #
We look at a final heterogeneous configuration. In this experiment we used 1 K-Regular network and 2 Scale-Free Networks 
with varying k and d parameters. To analyse the convergence and number of encounters to achieve consensus, we consider 
homogenous parameter configurations for scale-free networks (the same value of d for both networks).

## CONVERGENCE FOR REG/SF/SF ##

```{r results='asis',message=FALSE}
#Read the Parameters for this experiment
params <- read.exp.parameters(param_file_name="../data/scale-free_scale-free_regular/param-space_2014-05-30_18:43:13experiment:2_.csv")

#read the adata related to consensus was achieved before 
require(data.table)
convergence_data <- fread("../data/scale-free_scale-free_regular/consensus_achieved.csv")
convergence_data <- as.data.frame(convergence_data)[,-ncol(convergence_data)]
convergence_data <- merge(convergence_data, params, by="cfg.id")
```

We can now create a table to display the percentage of convergences to total 
consensus **for each value of k and d**. The **number of networks** in this experiment is allways **2**.

```{r message=FALSE}
require(reshape)
require(tables)

#filter some things out
fcdata <- melt.data.frame(convergence_data,id.vars=c("cfg.id","run","network.0.k","network.1.d", "network.2.d"), measure.vars=c("consensus-achieved"))

#filter the data and get the data for homogenous d configurations (network.1.d == network.2.d)
fcdata <- fcdata[fcdata$"network.1.d" == fcdata$"network.2.d",]

#convergence_table

fcdata_table <- aggregate(data=fcdata, fcdata$value~network.1.d + fcdata$network.0.k, FUN=sum)
colnames(fcdata_table) <- c("d", "k", "value")

 #create a pretty table for latex
latex_table <- tabular(cast(fcdata_table, d~k, value="value"))

```

```{r results='asis'}
html(latex_table)

#I can also save this table to a file for later reference
latex(latex_table,file="tex/regular_scale-free_scale-free_convergence.tex", booktabs=T, )
```

This table shows the percentage of simulation runs that converged to total consensus over 100 
independent runs.

# Number of Encounters for REG/SF/SF #
In this section, we analise the number of encouters necessary to achieve consensus with this heterogenous setup.
The data for the encounters contains the following variables.
```{r}
encounter_data <- fread("../data/scale-free_scale-free_regular/num_encounters.csv")
encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
head(encounter_data)
```
To get the information for the d and k values we can merge the data with the parameter space
```{r}
encounter_data <- merge(encounter_data, params, by="cfg.id")
```

We now filter some of the variables out.
```{r message=FALSE}
#filter some things out
fedata <- melt.data.frame(encounter_data,id.vars=c("cfg.id","run","network.0.k","network.1.d","network.2.d"), measure.vars=c("total-encounters"))
head(fedata)

#filter the data and get the data for homogenous d configurations (network.1.d == network.2.d)
fedata <- fedata[fedata$"network.1.d" == fedata$"network.2.d",]

#filter encounter data include only num networks > 3
fedata_net1 <- fedata[fedata$network.0.k <= 5,]

fedata_net10 <- fedata[fedata$network.0.k > 5,]

#create a table with avg and sd
cast_fedata_table <- cast(data=fedata, formula=network.0.k~network.1.d, c(mean, sd))

fedata_table_full <- tabular(cast_fedata_table)

```

Create the tables
```{r results='asis',message=FALSE}
#to print the table created with tabular

html(fedata_table_full)

#print this to a file to use in the paper

Hmisc::latex(fedata_table_full, file="tex/regular_scale-free_scale_free_encounters_full.tex",booktabs=T)
```

Now to observe the distribution of the number of encounters, necessary to achieve consensus, we look at the box plots for **k = {1,2,3,4,5}** and **k = {10,20,30,40,50}** respectively.

```{r}
plot <- plot.exp.box(data=fedata_net1,x_factor=as.factor(fedata_net1$network.1.d), data_y=fedata_net1$value, fill_factor=as.factor(fedata_net1$network.0.k),fill_label="K", x_label="D", y_label="Number of Encounters")

plot

plot <- plot.exp.box(data=fedata_net10,x_factor=as.factor(fedata_net10$network.1.d), data_y=fedata_net10$value, fill_factor=as.factor(fedata_net10$network.0.k),fill_label="K", x_label="D", y_label="Number of Encounters")

plot
```

Focusing now on the best performing configurations and on the runs that produced a convergence in less than 50000 encounters, the distribution of the number of encounters is as follows.

```{r}
fedata_net10 <- fedata_net10[fedata_net10$"network.1.d" > 1 & fedata_net10$value <= 10000,]

plot <- plot.exp.box(data=fedata_net10,x_factor=as.factor(fedata_net10$network.1.d), data_y=fedata_net10$value, fill_factor=as.factor(fedata_net10$network.0.k),fill_label="K", x_label="D", y_label="Number of Encounters")

plot

```

### 2014-06-10 analysis/model_validation.Rmd
first commit

```{r}
library(knitr)
```

Consensus in Multiple Social Networks - Summary Report
======================================================
This document is intended as a reproducible report for the results 
for our simulation model of _consensus_ in multiple _social networks_. In this model, we
use multiple social networks to represent different social relations in which agents engage possibly at the same time.
We consider the following network models.

* _Barabasi-Albert_ scale-free networks.
* _Gilbert_ Random graphs.
* _Watts & Strogatz_ small-world networks.
* _K-Regular_ Networks (which do not display complex properties but are useful to investigate the effects of connectivity and clustering in our simulations)

We conducted investigations in 3 different model variations. We use ifferent models to generate random complex social networks in which agents interact. In the first from now on called _**Context Permeability**_ model, agents interact in multiple social networks at the same time. In the second model called _**Context Switching**_ model, agents interact in multiple social networks but only in one network at a time. We use a switching probability parameter to model the time agents spend on each social network. Finally we consider a modification of the context switching model 
and add a segregation mechanism, we called this model the _**Context Switching with Segregation**_ model. In this model agents switch between the multiple networks based on the _switching probability parameter_ and a new parameter called _tolerance_. Each network has a _tolerance_ value associated with it. This determines the ratio of neighbors with opposing opinion values that an agent tolerates on that network. For each agent, uppon completing an interaction with a neighbour in the current social network, if the neighborhood of the current agent is above the tolerance value set for the network, it immediately switches to another network. If the neighbourhood is within the tolerance threshold, the agent decides to switch or to stay based on the _switching probability_ set for the network.

# Model and Script Testing#
In this section I **analyse a few model runs** and **confirm if the measures that are being considered 
are working correctly**. It is generally a good practice to confirm if what you expect to 
be measured is actually being measured, and if the model is behaving correctly. I will also use this section to test different plots, libraries and data transformations that can be used in a more detailed analysis.

## Opinion Progression ##
One of the measurements made is the number of agents with each opinion value. So we load the following data
from the simulation with a single network using a _Barabasi-Albert_ scale-free network model.

```{r}
params <- read.csv("../data/model_validation/ba-scale-free-network/param-space_2014-04-08_12:34:57experiment:0_.csv", header=TRUE, sep=";")

#remove empty column at the end
params<- params[,-ncol(params)] 
params<-(t(params))
colnames(params) <- c("Parameter Value")
```

The parameters used for this model test are the following:

```{r results='asis',message=FALSE} 
library(stargazer)
stargazer(params, title="Simulation Parameters", type="html", align=FALSE)
```

For instance, just for the sake of observing if the opinion progression is behaving correctly
lets observe the first run of this small experiment: 
```{r}
opinion_progress <- read.csv("../data/model_validation/ba-scale-free-network/opinion_progress.csv", sep=";")
op_run <- opinion_progress[opinion_progress$run == 1,]
```

From here we can plot the number of agents for each opinion value on each simulation step:
```{r fig.width=13}
library(ggplot2)
library(reshape2)

#reshape data so it is easier to plot
r_op_data <- melt(op_run, id=(c("step")), measure.vars=(c("num.opinion.0","num.opinion.1")))
names(r_op_data)<- c("step", "opinion", "value")

plot <- ggplot(data = r_op_data, aes(x = r_op_data$step, y = r_op_data$value , color=r_op_data$opinion))
plot <- plot + geom_line() + geom_point(size=0)
plot <- plot + labs(x = "Simulation Step", y = "Number of Agents")
#plot <- scale_fill_discrete(name="Opinion",
 #                        breaks=c("num.opinion.0", "num.opinion.1"),
  #                       labels=c("Opinion Value 1", "Opinion Value 2"))
plot <- plot + labs(title = "Opinions")
plot <- plot + theme_bw()
plot <- plot + theme(legend.title=element_blank())
plot

```
We can see that for this run, consensus was not achieved. The required consensus was _1.0_ and 
the model converged to _0.8_ of consensus. It remained stable until _2000_ steps passed (maximum number of steps allowed).

## Social Network Analysis ##
To test some network analysis measures we will load the Scale-Free network from the data and take 
some measures using the _igraph_ library.

```{r}
library(igraph)
```

```{r}
networks <- read.csv("../data/model_validation/ba-scale-free-network/networks.csv", sep=";", quote="")
```

The network data has information about how the agents are connected for each simulation run. We have performed 
multiple runs so lets retrieve the network for the first run.

We are just interested in the list of links between nodes, we don't want the configuration id nor the step 
in which the network snapshot was taken so we trim the data accordingly. We also filter the data to retrieve the
first run only.

```{r}
library(igraph)
networksData <- as.data.frame(networks)
network <- networks[networks$run == 1, ]
#only the edge list
network <- network[,4:5]

#load the edge list into an igraph object
graph <- graph.data.frame(d=network, directed=FALSE, vertices=NULL)
```

We can print the network loaded for instance to check if it is properly constructed:
```{r}
plot(graph,vertex.size = 1, vertex.label=NA, layout =   layout.kamada.kawai)
```
We can also plot the label and node size based on the node degree. While we test this, lets also 
test a new script that does what we previously defined above. 
```{r}
source(file="../R/read_network.R")

#test the read network script, it loads the run 1 layer 0
#this simple test only has one layer (1 network) anyway
graph <- read.network(networks,1,0)

V(graph)$degree <- degree(graph,mode=c("all"))
V(graph)$label.cex <- 1.5 * V(graph)$degree / max(V(graph)$degree)+ .4
V(graph)$size <- 10 * V(graph)$degree / max(V(graph)$degree)+ 3
V(graph)$frame.color <- NA
plot(graph, vertex.label=NA, layout = layout.kamada.kawai, vertex.color="Gray")
```

### Some Measures

Average path length of network for run 1:

```{r}
average.path.length(graph, directed=FALSE)
```

Network clustering coefficient
```{r}
transitivity(graph, type=c("globalundirected"))
```
The clustering coefficient is _0_ because the _scale-free_ network does not produce any triangles between its vertices. We used a model that adds only one link each time a node is added to the network. This produces a _forest_ a network composed by _tree_ structures. In our experiments, we also consider _BA_ networks with more than _1_ link added at a time. This produces networks with a higher clustering coefficient.

Finally, we look at the degree distribution. I plot the degree distribution on the log scale and we can see that the the  distribution demonstrate the power law (characteristic from scale-free networks generated with the Barabasi-Albert model).

```{r}

distribution<- degree(graph, V(graph),mode = c("all"))

hist(log(distribution + 1), main = "Log Degree Distribution", col = "green")

```

### 2014-06-10 analysis/network_properties.Rmd
first commit

Context Permeability Investigations
===================================
We now investigate the first variation of the multi-network simulation model we called _Context Permeability_.
We first investigate how different network topologies affect the convergence to consensus.  We change the network 
models and the number of networks in which each agent interacts. Obviously, in this mode, adding more networks means
adding more connections. We show that what is important is not the number of connections but rather the properties they 
display when they are merged.

# Convergence to Consensus with Regular Networks #
We first investigate how the convergence is affected by regular networks. We use a _K-Regular_ network model 
in which each agent has the same number of connections. The number of connections is controlled by parameter _k_. Each agent has _2*k_ connections. This structure is not very realistic if we compare it with real network structures. Nonetheless, this investigation is useful for two reasons. The first is that we can investigate the influence of connectivity in the convergence to consensus. The second is that these models of interaction can be used outside the 
social simulation domain, nothing prohibits multi-agent systems to use these as models of interaction, we might even want to construct highly clustered networks of agents. Given this, it is valuable to know how the system responds to such structures.

### Network Generation ###
Each network is generated by placing the nodes in a ring and connecting each node to its next _k-neighbours_. 
The initial order of the nodes in the ring is randomised so that we can have multiple instances of k-regular networks in which agents have different neighbourhoods.

### Multiple k-regular networks ###
We generate multiple _k-regular_ networks and agents are allowed to interact in any one of them. The number of nodes is the same in all the networks. Given that the networks are randomised, neighbourshoods may or may not overlap. What this means is that adding more regular networks is not the same as creating a k-regular network with twice the number of connections. As we will see, the overlapping different k-regular networks changes the original regular properties. Overlapping regular structures can result in the creation of shortcuts between neighbourhoods that would not be created by the regular network generation model.

In this first experiment we performed experiment with _k-regular_ networks with different _k_ values. We also varied the number of concomitant networks as follows:

```{r results='asis',echo=FALSE}
source("../R/experiment_utils.R")

#shows the k values explored and the number of networks
params <- read.exp.parameters("../data/regular_networks/param-space_2014-05-30_16:47:53experiment:0_.csv")
params <- params[,c("cfg.id","num.networks","network.0.k")]

k_values <- as.data.frame(unique(params[,"network.0.k"]))
colnames(k_values) <- c("k values")
num_networks <- as.data.frame(unique(params[,"num.networks"]))
colnames(num_networks) <- c("number of networks")

require(stargazer)
stargazer(t(k_values), type="html", summary = FALSE)
stargazer(t(num_networks), type="html", summary = FALSE)

#clean up the environment, I justneed the params for later
gc()
```

First, we load the network data from the regular network experiment. 
This is somehow a large file so we use the `bigmemory` package which 
is more efficient in terms of memory management.
```{r message=FALSE}
source("../R/network.utils.R")
require(bigmemory)
network_data <- read.big.matrix(filename="../data/regular_networks/networks.csv", header=T, sep=";")
```

Before a more detailed analysis lets consider an example. Lets consider 
the scenario where we have _2 networks_ with _k = 10_. We retrieve the 
networks from the first run and make some measurements.

```{r}
#extract networks for num networks = 2 and k = 10 as an example
cfg <- params[params$"num.network" == 2 & params$"network.0.k" == 10,][[1]]

#use the configuration id to filter the data
network1 <- read.big.network.layer(data=network_data,cfg=cfg,run=1, layer=0)

network2 <- read.big.network.layer(data=network_data,cfg=cfg,run=1, layer=1)

#combine the 2 networks
combined_network <- network1 + network2

#some measures

#clustering
network1$cc <- transitivity(network1, type=c("globalundirected")) 
network2$cc <- transitivity(network2, type=c("globalundirected")) 
combined_network$cc <- transitivity(combined_network, type=c("globalundirected"))

#average path length
network1$apl <- average.path.length(network1, directed=FALSE)
network2$apl <- average.path.length(network2, directed=FALSE)
combined_network$apl <- average.path.length(combined_network, directed=FALSE)

net1 <- c(length(V(network1)), length(E(network1)),network1$cc, network1$apl)
net2 <- c(length(V(network2)), length(E(network2)),network2$cc, network2$apl)
combnet <- c(length(V(combined_network)), length(E(combined_network)),combined_network$cc,combined_network$apl)
netprop.table <- as.data.frame(rbind(net1,net2,combnet))
colnames(netprop.table)<- c("Number of Nodes","Number of Edges","Clustering Coefficient", "Average Path Length")
rownames(netprop.table) <- c("K-Regular 1", "K-Regular 2", "Combined")
```

For this configuration we have two networks in which the agent can interact. In the next figure you can see
the two _k-regular_ networks with _k = 10_ followed by the network that results from merging these two structures. 
The networks are drawn using the _Kamada-Kawai_ Layout which "regards the desirable "geometric" (Euclidean) distance between two vertices in the drawing as the "graph theoretic"" distance between them in the corresponding graph.
```{r fig.width=15, results='asis'}
color1 <- "#7D9C9F"
color2 <- "#B1B1B1"
color_over <- "#FF003F"

E(network1)$color <- color1
E(network2)$color <- color2

el1 <- apply(get.edgelist(network1), 1, paste, collapse="-")
el2 <- apply(get.edgelist(network2), 1, paste, collapse="-")
elc <- apply(get.edgelist(combined_network), 1, paste, collapse="-")

E(combined_network)$color <- ifelse((elc %in% el1) & (elc %in% el2), color_over, ifelse((elc %in% el1), color1, color2))

par(mfrow=c(1,3))
plot(network1,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="10-Regular 1")
plot(network2,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="10-Regular 2")
plot(combined_network,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="Combined 10-Regulars")

stargazer(netprop.table, type="html", summary = FALSE)

#clean up the mess
gc()
```
We can see by the results of the layout that the distance between nodes in the network has decreased, this is confirmed by the decreased average path length of the combined networks. To illustrate our previous point that this is not the same as having a k-regular network with twice the size lets retrieve the setup with 1 k-regular network with _k = 20_.

```{r results='asis'}
#now lets select a network with twice the k value
#extract networks for num networks = 2 and k = 10 as an example
cfg <- params[params$"num.network" == 1 & params$"network.0.k" == 20,][[1]]

#use the configuration id to filter the data
network_k_20 <- read.big.network.layer(data=network_data,cfg=cfg,run=1, layer=0)

par(mfrow=c(1,1))
plot(network_k_20,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="K-Regular with K=20")
```

As you can see in the following table, while the clustering coefficient of a _20-Regular_ network is approximately the same as the _10-Regulars_, it is higher than this particular combination of regular networks, the average path length also decreases 
as there are more connections between the nodes.

```{r results='asis'}
network_k_20$cc <- transitivity(network_k_20, type=c("globalundirected")) 
network_k_20$apl <- average.path.length(network_k_20, directed=FALSE)

network_k_20.props <- c(length(V(network_k_20)),
                        length(E(network_k_20)),
                        network_k_20$cc,
                        network_k_20$apl)

netprop.table <- as.data.frame(rbind(net1,net2,combnet,network_k_20.props))

colnames(netprop.table)<- c("Number of Nodes","Number of Edges","Clustering Coefficient", "Average Path Length")
rownames(netprop.table) <- c("10-Regular 1", "10-Regular 2", "Combined 10-Regulars", "20-Regular Network")

require(stargazer)
stargazer(netprop.table, type="html", summary = FALSE)
```

This is not always the case, as we will show, since the nodes are subjected to random permutations to create different instances of _K-Regular_ networks, we can have different overlaps that create different network topologies. 
Obviously, this is not the only difference. From a modelling perspective, different networks can display different properties as well, we can assign different tolerances or trust depending on the network the agent is interacting in.

#### Merging K-Regular Networks: overlapping ####
We will now investigate, what kind of properties we can get from merging _K-Regular_ networks. We do this 
empirically by taking the network instances used in the simulation and analysing the distribution of clustering coefficient and average path length for the different configurations where we consider multiple networks (from 1 to 5 in this case).

```{r}
#Collect the network data and create a data table to hold the network properties
props <- NULL
num_networks <- c(1,2,3,4,5)
k_values <- seq(10,50,10) 
runs <- sort(unique(network_data[,"run"]))

require(BBmisc)#for progress bar
pb <- makeProgressBar(min=0, max=(length(num_networks)*length(k_values)*length(runs)), label="network analysis")

  #pre-alocate a matrix for the network properties
  props <- matrix(nrow=(length(num_networks)*length(k_values)*length(runs))-1, ncol=7)
  i <- 1

for(n in num_networks){
  #reads the properties for all the k-regular networks with the given k and num_networks

  for(k in k_values){
    cfg <- params[params$"num.network" == n & params$"network.0.k" == k,][[1]]
    for(r in runs){

        fn_net <- mwhich(x=network_data, cols=c("run","cfg.id"), vals=list(r,cfg),comps=list("eq"))
        f_network_data <- network_data[fn_net,c("node1","node2")]
        network <- read.network(ndata=f_network_data)

        network$properties <- cbind(k,n,r,measure.network(network))
        colnames(network$properties)[1:3] <- c("k","networks","run")

        #append the properties to the current matrix
        props[i,] <- network$properties
        i <- i + 1

        #some progress feddback
        pb$inc(1,paste("reading n=",n,"k=",k,"and run=",r,"\n"))
    }
    gc()
  } 
}
pb$kill()

colnames(props) <- colnames(network$properties)

#clean up
rm(pb)
gc()
```

Creating boxplots to observe the average path length and the clustering coefficient, we can see that these values don't varie much 
within each configuration. Within K-Regular networks we can thus assume certain property values for specific combinations of networks.

```{r}
props <- as.data.frame(props)

require(ggplot2)

#create box plots
net_props <- props[props$networks > 2,]

plot <- plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"average-path-length",fill=as.factor(net_props$k)) ) 
plot <- plot + geom_boxplot()
plot <- plot + labs(fill="K", y="Average Path Length", x="Number of Networks")
plot

net_props <- props[props$networks > 0,]

plot <- plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"clustering-coefficient",fill=as.factor(net_props$k)) ) 
plot <- plot + geom_boxplot()
plot <- plot + labs(fill="K", y="Clustering Coefficient", x="Number of Networks")
plot 
```

We now plot the average value of **average path length** and **clustering coefficient** for a total of 100 K-Regular Networks. We analyse the properties of networks with different levels of **K**. The **number of networks** refers to the number of networks in which the agents
interacted at the same time. As we describe above, these are built merging the networks and suppressing the overllaping edges
between nodes.

```{r}
#aggregate run data by k and networks
require(reshape2)

apl_data <- melt(props, id=c("k","networks","run"),measure.vars=c("average-path-length"))
clustering_data <- melt(props, id=c("k","networks","run"),measure.vars=c("clustering-coefficient"))

average_apl_data <- dcast(apl_data, k + networks ~ variable, mean)
average_clustering_data <- dcast(clustering_data, k + networks ~ variable, mean)

#plot average path length
net_props <- average_apl_data

plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"average-path-length",))

plot <- plot +  geom_point(aes(shape=as.factor(net_props$k), color=as.factor(net_props$k)),size = 3.5)

plot <- plot +  geom_line(aes(color=as.factor(net_props$k), group=as.factor(net_props$k), linetype=as.factor(net_props$k)),size=1)

plot <- plot + labs(color="K", shape="K", linetype="K", y="Average Path Length", x="Number of Networks")
plot

#clean up
rm(apl_data,average_apl_data)
gc()
```

```{r}
#lets plot the clustering coefficient
net_props <- average_clustering_data

plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"clustering-coefficient",))

plot <- plot +  geom_point(aes(shape=as.factor(net_props$k), color=as.factor(net_props$k)),size = 3.5)

plot <- plot +  geom_line(aes(color=as.factor(net_props$k), group=as.factor(net_props$k), linetype=as.factor(net_props$k)),size=1)

plot <- plot + labs(color="K", shape="K", linetype="K", y="Clustering Coefficient", x="Number of Networks")
plot

#clean up
rm(clustering_data,average_clustering_data,props, net_props,plot)
gc()
```

In the previous plots we can see that as we increase the number of overllaping networks, the clustering coefficient also increases. The average path lenth decreases as a result from overllapings that create shortcuts between different points in the network.

The different behaviour for k = {10,20} and k = {30,40,50} can be explained by the fact that networks are overlapped in a random fashion, as such, 
by overlapping networks with less connectivity makes so that our composite networks have shortcuts between different points without the end points of these shortcuts being clustered together. This obviously changes as we add increase k towards 50, which is the configuration where the networks are fully connected.

### 2014-06-10 R/analyse_opinion_progress.R

@@ -1,0 +1,30 @@
+# opinion_progress <- read.csv("~/Dropbox/PhD/experiments/Context Permeability/data/model_validation/ba-scale-free-network/opinion_progress.csv", sep=";")
+# get one run 
+# op_run <- opinion_progress[opinion_progress$run == 1,]
+#
+# install rcharts
+#require(devtools)
+#install_github('rCharts', 'ramnathv')
+
+library(rCharts)
+require(reshape2)
+
+opinion_progress <- read.csv("~/Dropbox/PhD/experiments/Context Permeability/data/model_validation/ba-scale-free-network/opinion_progress.csv", sep=";")
+op_run <- opinion_progress[opinion_progress$run == 1,]
+
+#reshapes the data to be ploted
+reshaped_op_data <- melt(op_run, id=(c("step")), measure.vars=(c("num.opinion.0","num.opinion.1")))
+x1 <- xPlot(value ~ step, group = "variable", data = reshaped_op_data, type = "line-dotted")
+
+
+opinion_progress <- read.csv("~/Dropbox/PhD/experiments/Context Permeability/data/model_validation/ba-scale-free-network/opinion_progress.csv", sep=";")
+op_run <- opinion_progress[opinion_progress$run == 1,]
+
+#reshapes the data to be ploted
+reshaped_op_data <- melt(op_run, id=(c("step")), measure.vars=(c("num.opinion.0","num.opinion.1")))
+
+m1 <- mPlot(x = op_run$step, y = c(op_run$num.opinion.0, op_run$num.opinion.1), type = "Line", data = op_run)
+m1$set(pointSize = 0, lineWidth = 1)
+m1$show('inline', include_assets = TRUE, cdn = TRUE)
+
+

### 2014-06-10 R/experiment_utils.R

@@ -1,0 +1,75 @@
+#*******************************************************************************
+# Reads a parameter file (normaly each experiment has an associated
+# Parameter Space File) with all the parameter values used.
+#
+#@param param_file_name: a string with the filename / path to the parameter file
+#*******************************************************************************
+read.exp.parameters <- function(param_file_name){
+  params <- read.csv(param_file_name, header=TRUE, sep=";")
+  #remove empty column at the end
+  params<- params[,-ncol(params)]
+  return(params)
+}
+
+
+#*******************************************************************************
+# Takes a a previously read parameter table and 
+# prints it using the stargazer library. 
+# 
+# This is useful mainly to generate reports. 
+# Note: for printing in knitr use "results='asis',message=FALSE" 
+# in the chunk options
+#
+# @param parameters: a previously loaded parameter table
+#*******************************************************************************
+print.exp.parameters <- function(parameters){
+  require(stargazer)
+
+  stargazer(params, title="Simulation Parameters", type="html", align=FALSE, summary = FALSE)
+}
+
+require(ggplot2)
+plot.exp.box <- function(data,
+                         x_factor,
+                         data_y,
+                         fill_factor,
+                         fill_label,
+                         y_label,
+                         x_label){
+  .e <- environment()
+  plot <- ggplot(aes(y=data_y,x=x_factor,fill=fill_factor), data=data, environment=.e)  
+  plot <- plot + geom_boxplot()
+  plot <- plot + labs(fill=fill_label, y=y_label, x=x_label)
+  return(plot) 
+}
+
+#***********************************************************************
+# RETURNS A LINE PLOT WITH THE OPINION PROGRESSION FOR A PARTICULAR 
+# CONFIGURATION / RUN
+#
+#***********************************************************************
+plot_opinion <- function(opinion_data){
+  op_run <- as.data.frame(opinion_data)
+  r_op_data <- melt(op_run, id=(c("step")), measure.vars=(c("num.opinion.0","num.opinion.1")))
+  names(r_op_data)<- c("step", "opinion", "value")
+  
+  .e <- environment()
+  
+  plot <- ggplot(data = r_op_data, aes(x = r_op_data$step, y = r_op_data$value , color=r_op_data$opinion,), environment=.e)
+  plot <- plot + geom_line() + geom_point(size=0)
[…]

### 2014-06-10 R/network.utils.R

@@ -1,0 +1,128 @@
+#' Reads a complete network based on the data, the configuration
+#' and the current run. 
+#' 
+#' 
+#' @description This takes a matrix constructed using the bigmemory package and
+#' subsets it based on the configuration id, the run and the layer. This was design for our 
+#' experiments in which, for each simulation, we can have more than one layer of networks. 
+#' the function \code{read.big.network} merges all the layers (edges are not duplicated). This function 
+#' filters the data using an additional column called 'layer'
+#' 
+#' Note: this is to be used with the package \code{bigmemory}.
+#' 
+#' requires that the data has the column names:
+#' - cfg.id
+#' - run
+#' - node1 
+#' - node2
+#' - layer
+#' 
+#' node1 and node2 are used as the edge list. 
+#' 
+#' @param data the network data with the above columns
+#' @param cfg an integer with the configuration id for the network we wan't to read
+#' @param run an integer with the current run
+#' @param layer a layer number, it must be between 0 and the maximum number of layers for the filtered
+#' data (filtered by cfg and run)
+#' 
+#' 
+#' 
+#' @examples
+#' require(bigmemory)
+#' network_data <- read.big.matrix(filename="../data/regular_networks/networks.csv", header=T, sep=";")
+#' network <- read.big.network(data=network_data, cfg=1, run=1, layer=0)
+#' 
+read.big.network.layer <- function(data, cfg, run, layer){
+  
+  #filter data by configuration, run, and layer 
+  fn_net <- mwhich(x=data, cols=c("run","cfg.id","layer"), vals=list(run,cfg,layer),comps=list("eq"))
+  
+  #filter data, we just need the edge list
+  f_data <- data[fn_net,c("node1","node2")]
+  
+  network <- read.network(f_data)
+  
+  return(network)
+}
+
+#' Reads a complete network based on the data, the configuration
+#' and the current run. The difference between this method and the others
+#' is that the network data is subset inside the function based on the 
+#' cfg id value and the run. \code{read.network} for instance, requires 
+#' an edge list (a data frame with two columns). 
+#' 
+#' Note: this is to be used with the package \code{bigmemory}.
+#' 
+#' requires that the data has the column names:
+#' - cfg.id
+#' - run
+#' - node1 
+#' - node2
+#' 
+#' node1 and node2 are used as the edge list. 
+#' 
+#' @param data the network data with the above columns
[…]

### 2014-06-10 R/parallel_example.R

@@ -1,0 +1,52 @@
+library(parallel)
+
+## Number of workers (R processes) to use:
+numWorkers <- 8
+
+
+
+measure_parallel <- function(cfg,r){
+  data <- network_data
+  network <- read.big.network(data,cfg,r)
+  properties <- measure.network(network)
+  properties <- cbind(r,properties)
+  return(properties)
+}
+
+props <- NULL
+num_networks <- c(1,2,3,4,5)
+k_values <- seq(10,50,10) 
+runs <- sort(unique(network_data[,"run"]))
+
+require(BBmisc)#for progress bar
+pb <- makeProgressBar(min=0, max=(length(num_networks)*length(k_values)), label="network analysis")
+
+#pre-alocate a matrix for the network properties
+props <- matrix(nrow=(length(num_networks)*length(k_values)*length(runs))-1, ncol=7)
+i <- 0
+
+
+for(n in num_networks){
+  #reads the properties for all the k-regular networks with the given k and num_networks 
+  for(k in k_values){
+    cfg <- params[params$"num.network" == n & params$"network.0.k" == k,][[1]]
+    
+    properties <- mcmapply(cfg=cfg, r=runs, measure_parallel, mc.cores = numWorkers)
+    properties <- t(properties)
+    
+      
+    props[(i+1):(i+100),] <- cbind(k,n,properties)
+    i <- i + 100  
+    #some progress feddback
+    pb$inc(1,paste("reading n=",n,"k=",k,"\n"))
+    gc()
+  } 
+}
+pb$kill()
+
+colnames(props)<-c("k","networks","run","nodes","edges","clustering-coefficient","average-path-length")
+
+#clean up
+rm(pb)
+gc()
+

### 2014-06-10 R/read_network.R

@@ -1,0 +1,290 @@
+library(igraph)
+
+
+#********************************************************************
+# READS NETWORK DATA AND RETURNS AN ARRAY OF IGRAPH INSTANCES
+#
+# network csv data
+#
+# returns a list with all the igraph objects, you can access it with
+# the  [[]] operator
+#********************************************************************
+read.network <- function(network_data, layer){
+  
+  num_networks <- max(network_data[ ,network_data$"run"])
+  
+  networkv <- vector("list",num_networks)
+  
+  #create the networks
+  for(r in 1:num_networks){
+    graph <- read_network(network_data,r,layer)
+    networkv[[(r)]] <- graph
+  }
+  return(networkv)
+}
+
+#******************************************************
+# In the context permeability simulations networks are 
+# written to a file at the end of each simulation run
+# this function READS A NETWORK FOR A PARTICULAR RUN
+#
+# @param networkData data for the network with a field 
+# "run for each network"
+# @param run the run number from which we want the 
+# network.
+#
+#
+# this assunes the networkData has columns for 
+# run, node1, node2 where run is the current run the 
+# network belongs to, node1 and node2 are ids of nodes
+# representing an undirected edge.
+#
+#*******************************************************
+read.network <- function(network_data, run, layer){
+  networks <- as.data.frame(network_data)
+  
+  #create the networks
+  network <- networks[networks$"run" == run & networks$"layer" == layer, ]
+  
+  #no network found for that layer
+  if(nrow(network) == 0)
+    stop(paste("No network found for layer",toString(layer)))
+  
+  #only the edge list
+  network <- network[,c("node1","node2")] 
+  #load the edge list into an igraph object
+  graph <- graph.data.frame(d=network, directed=FALSE, vertices=NULL)
+    
+  return(graph)
+}
+
+#********************************************************
+# READS A SINGLE NETWORK, THIS REQUIRES THE DATA TO BE
+# FILTERED TO INCLUDE THE DATA OF THE NETWORKS FOR A SINGLE
+# RUN
+#
+# THE LAYER IS THE NETWORK WE WANT TO READ
+#********************************************************
+read.single.network <- function(data, layer){
+  networks <- as.data.frame(data)
+  network <- networks[networks$"layer" == layer, ]
+  if(nrow(network) == 0)
+    stop(paste("No network found for layer",toString(layer)))
+  network <- network[,c("node1","node2")] 
[…]

### 2014-06-10 analysis/network_properties.Rmd
network properties fixed

@@
 #Collect the network data and create a data table to hold the network properties
+require(parallel)
+
+## Number of workers (R processes) to use:
+numWorkers <- 8
+
+measure_parallel <- function(cfg,r){
+  data <- network_data
+  network <- read.big.network(data,cfg,r)
+  properties <- measure.network(network)
+  properties <- cbind(r,properties)
+  return(properties)
+}
+
 props <- NULL
 num_networks <- c(1,2,3,4,5)
-k_values <- seq(10,50,10) 
+k_values <- c(1:5,seq(10,50,10))
 runs <- sort(unique(network_data[,"run"]))
@@
 require(BBmisc)#for progress bar
-pb <- makeProgressBar(min=0, max=(length(num_networks)*length(k_values)*length(runs)), label="network analysis")
+pb <- makeProgressBar(min=0, max=(length(num_networks)*length(k_values)), label="network analysis")
 
 #pre-alocate a matrix for the network properties
-  props <- matrix(nrow=(length(num_networks)*length(k_values)*length(runs))-1, ncol=7)
-  i <- 1
+props <- matrix(nrow=(length(num_networks)*length(k_values)*length(runs)), ncol=7)
+i <- 0
 
@@
   #reads the properties for all the k-regular networks with the given k and num_networks 
-
   for(k in k_values){
     cfg <- params[params$"num.network" == n & params$"network.0.k" == k,][[1]]
-    for(r in runs){
 
-        fn_net <- mwhich(x=network_data, cols=c("run","cfg.id"), vals=list(r,cfg),comps=list("eq"))
-        f_network_data <- network_data[fn_net,c("node1","node2")]
-        network <- read.network(ndata=f_network_data)
+    properties <- mcmapply(cfg=cfg, r=runs, measure_parallel, mc.cores = numWorkers)
+    properties <- t(properties)
 
-        network$properties <- cbind(k,n,r,measure.network(network))
-        colnames(network$properties)[1:3] <- c("k","networks","run")
-
-        #append the properties to the current matrix
-        props[i,] <- network$properties
-        i <- i + 1
-
+    props[(i+1):(i+100),] <- cbind(k,n,properties)
+    i <- i + 100  
     #some progress feddback
-        pb$inc(1,paste("reading n=",n,"k=",k,"and run=",r,"\n"))
-    }
+    pb$inc(1,paste("reading n=",n,"k=",k,"\n"))
     gc()
@@
 
-colnames(props) <- colnames(network$properties)
+colnames(props)<-c("k","networks","run","nodes","edges","clustering-coefficient","average-path-length")
 

### 2014-06-10 R/parallel_example.R

@@ -1,9 +1,7 @@
-library(parallel)
+require(parallel)
 
 ## Number of workers (R processes) to use:
 numWorkers <- 8
-
-
 
 measure_parallel <- function(cfg,r){
   data <- network_data

### 2014-06-10 analysis/network_properties.Rmd
network properties fixed, analysis divided between k=1:5 and k = 10..50

@@
-Context Permeability Investigations
-===================================
+Context Permeability Investigations: Network Properties
+=======================================================
 We now investigate the first variation of the multi-network simulation model we called _Context Permeability_.
-We first investigate how different network topologies affect the convergence to consensus.  We change the network 
-models and the number of networks in which each agent interacts. Obviously, in this mode, adding more networks means
-adding more connections. We show that what is important is not the number of connections but rather the properties they 
-display when they are merged.
+We first investigate the properties of different network topologies that we then use in our model. We change the network 
+models and the number of networks in which each agent interacts. Obviously, adding more networks means
+adding more connections. We show that what is important is not exactly the number of connections but rather the properties the 
+networks display when they are merged.
 
-# Convergence to Consensus with Regular Networks #
-We first investigate how the convergence is affected by regular networks. We use a _K-Regular_ network model 
-in which each agent has the same number of connections.
+# Properties for K-Regular Networks #
+We first investigate the properties of regular networks. We use a _K-Regular_ network model 
+in which each node has the same number of connections.
 The number of connections is controlled by parameter _k_.
@@
 The first is that we can investigate the influence of connectivity in the convergence to consensus.
-The second is that these models of interaction can be used outside the
-social simulation domain, nothing prohibits multi-agent systems to use these as models of interaction, we might even want to construct highly clustered networks of agents.
+The second is that these models of interaction can be used outside the social simulation domain, nothing prohibits multi-agent systems to use these as models of interaction, we might even want to construct highly clustered networks of agents.
 Given this, it is valuable to know how the system responds to such structures.
@@
 
-In this first experiment we performed experiment with _k-regular_ networks with different _k_ values. We also varied the number of concomitant networks as follows:
+In a first experiment we performed experiment with _k-regular_ networks with different _k_ values. We also varied the number of concomitant networks as follows:
 
@@
 
-First, we load the network data from the regular network experiment. 
-This is somehow a large file so we use the `bigmemory` package which 
+We load the network data from the regular networks experiment with the `bigmemory` package which 
 is more efficient in terms of memory management.
@@
 
-#create box plots
-net_props <- props[props$networks > 2,]
+#create average path length box plots for k = 1,2,3,4,5
+net_props <- props[props$k <= 5,]
 
@@
 
-net_props <- props[props$networks > 0,]
+#create average path length box plots for k = 10, 20,30,40,50
+net_props <- props[props$k > 5,]
+
+plot <- plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"average-path-length",fill=as.factor(net_props$k)) ) 
+plot <- plot + geom_boxplot()
+plot <- plot + labs(fill="K", y="Average Path Length", x="Number of Networks")
+plot
+
+#create clustering coefficient box plots for k = 1,2,3,4,5
+net_props <- props[props$k <= 5,]
+
+plot <- plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"clustering-coefficient",fill=as.factor(net_props$k)) ) 
+plot <- plot + geom_boxplot()
+plot <- plot + labs(fill="K", y="Clustering Coefficient", x="Number of Networks")
+plot
+
+#create clustering coefficient box plots for k = 10,20,30,40,50
+net_props <- props[props$k > 5,]
 
@@
 
-#plot average path length
-net_props <- average_apl_data
+#plot average path length for k = 1,2,3,4,5
+net_props <- average_apl_data[average_apl_data$"k" <= 5,]
+plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"average-path-length",)) 
+plot <- plot +  geom_point(aes(shape=as.factor(net_props$k), color=as.factor(net_props$k)),size = 3.5)
+plot <- plot +  geom_line(aes(color=as.factor(net_props$k), group=as.factor(net_props$k), linetype=as.factor(net_props$k)),size=1)   
+plot <- plot + labs(color="K", shape="K", linetype="K", y="Average Path Length", x="Number of Networks")
+plot
 
+#plot for k = 10,20,30,40,50
+net_props <- average_apl_data[average_apl_data$"k" >5,]
 plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"average-path-length",)) 
-
 plot <- plot +  geom_point(aes(shape=as.factor(net_props$k), color=as.factor(net_props$k)),size = 3.5)
-
 plot <- plot +  geom_line(aes(color=as.factor(net_props$k), group=as.factor(net_props$k), linetype=as.factor(net_props$k)),size=1)   
-
 plot <- plot + labs(color="K", shape="K", linetype="K", y="Average Path Length", x="Number of Networks")
@@
 ```{r}
-#lets plot the clustering coefficient
-net_props <- average_clustering_data
+#plot for k = 1,2,3,4,5
+net_props <- average_clustering_data[average_clustering_data$"k" <= 5, ]
 
 plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"clustering-coefficient",)) 
+plot <- plot +  geom_point(aes(shape=as.factor(net_props$k), color=as.factor(net_props$k)),size = 3.5)
+plot <- plot +  geom_line(aes(color=as.factor(net_props$k), group=as.factor(net_props$k), linetype=as.factor(net_props$k)),size=1)   
+plot <- plot + labs(color="K", shape="K", linetype="K", y="Clustering Coefficient", x="Number of Networks")
+plot
 
+#plot for k = 10,20,30,40,50
+net_props <- average_clustering_data[average_clustering_data$"k" > 5, ]
+
+plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"clustering-coefficient",)) 
 plot <- plot +  geom_point(aes(shape=as.factor(net_props$k), color=as.factor(net_props$k)),size = 3.5)
-
 plot <- plot +  geom_line(aes(color=as.factor(net_props$k), group=as.factor(net_props$k), linetype=as.factor(net_props$k)),size=1)   
-
 plot <- plot + labs(color="K", shape="K", linetype="K", y="Clustering Coefficient", x="Number of Networks")

### 2014-06-23 analysis/context_permeability.Rmd
context switching added

@@
 #Read the Parameters for this experiment
-params <- read.exp.parameters(param_file_name="../data/regular_networks/param-space_2014-05-30_16:47:53experiment:0_.csv")
+params <- read.exp.parameters(param_file_name="../data/context_permeability/regular_networks/param-space_2014-05-30_16:47:53experiment:0_.csv")
 
@@
 require(data.table)
-convergence_data <- fread("../data/regular_networks/consensus_achieved.csv")
+convergence_data <- fread("../data/context_permeability/regular_networks/consensus_achieved.csv")
 convergence_data <- as.data.frame(convergence_data)[,-ncol(convergence_data)]
@@
 ```{r}
-encounter_data <- fread("../data/regular_networks/num_encounters.csv")
+encounter_data <- fread("../data/context_permeability/regular_networks/num_encounters.csv")
 encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
@@
 
-network_data <- fread("../data/regular_networks/networks.csv")
+network_data <- fread("../data/context_permeability/regular_networks/networks.csv")
 
@@
 ```{r}
-opinion_data <- read.opinion.progress("../data/regular_networks/opinion_progress.csv")
+opinion_data <- read.opinion.progress("../data/context_permeability/regular_networks/opinion_progress.csv")
 #filter opinion to outlier run and normal run
@@
 #Read the Parameters for this experiment
-params <- read.exp.parameters(param_file_name="../data/scale-free_networks/param-space_2014-05-30_18:38:14experiment:1_.csv")
+params <- read.exp.parameters(param_file_name="../data/context_permeability/scale-free_networks/param-space_2014-05-30_18:38:14experiment:1_.csv")
 
@@
 require(data.table)
-convergence_data <- fread("../data/scale-free_networks/consensus_achieved.csv")
+convergence_data <- fread("../data/context_permeability/scale-free_networks/consensus_achieved.csv")
 convergence_data <- as.data.frame(convergence_data)[,-ncol(convergence_data)]
@@
 ```{r}
-encounter_data <- fread("../data/scale-free_networks/num_encounters.csv")
+encounter_data <- fread("../data/context_permeability/scale-free_networks/num_encounters.csv")
 encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
@@
 #Read the Parameters for this experiment
-params <- read.exp.parameters(param_file_name="../data/scale-free_regular/param-space_2014-05-30_18:40:41experiment:2_.csv")
+params <- read.exp.parameters(param_file_name="../data/context_permeability/scale-free_regular/param-space_2014-05-30_18:40:41experiment:2_.csv")
 
@@
 require(data.table)
-convergence_data <- fread("../data/scale-free_regular/consensus_achieved.csv")
+convergence_data <- fread("../data/context_permeability/scale-free_regular/consensus_achieved.csv")
 convergence_data <- as.data.frame(convergence_data)[,-ncol(convergence_data)]
@@
 ```{r}
-encounter_data <- fread("../data/scale-free_regular/num_encounters.csv")
+encounter_data <- fread("../data/context_permeability/scale-free_regular/num_encounters.csv")
 encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
@@
 source("../R/read_network.R")
-network_data <- fread("../data/scale-free_regular/networks.csv")
+network_data <- fread("../data/context_permeability/scale-free_regular/networks.csv")
 #filter the data, we just need the data from one simulation run
@@
 #Read the Parameters for this experiment
-params <- read.exp.parameters(param_file_name="../data/scale-free_scale-free_regular/param-space_2014-05-30_18:43:13experiment:2_.csv")
+params <- read.exp.parameters(param_file_name="../data/context_permeability/scale-free_scale-free_regular/param-space_2014-05-30_18:43:13experiment:2_.csv")
 
@@
 require(data.table)
-convergence_data <- fread("../data/scale-free_scale-free_regular/consensus_achieved.csv")
+convergence_data <- fread("../data/context_permeability/scale-free_scale-free_regular/consensus_achieved.csv")
 convergence_data <- as.data.frame(convergence_data)[,-ncol(convergence_data)]
@@
 ```{r}
-encounter_data <- fread("../data/scale-free_scale-free_regular/num_encounters.csv")
+encounter_data <- fread("../data/context_permeability/scale-free_scale-free_regular/num_encounters.csv")
 encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]

### 2014-06-23 analysis/network_properties.Rmd
context switching added

@@
 #shows the k values explored and the number of networks
-params <- read.exp.parameters("../data/regular_networks/param-space_2014-05-30_16:47:53experiment:0_.csv")
+params <- read.exp.parameters("../data/context_permeability/regular_networks/param-space_2014-05-30_16:47:53experiment:0_.csv")
 params <- params[,c("cfg.id","num.networks","network.0.k")]
@@
 require(bigmemory)
-network_data <- read.big.matrix(filename="../data/regular_networks/networks.csv", header=T, sep=";")
+network_data <- read.big.matrix(filename="../data/context_permeability/regular_networks/networks.csv", header=T, sep=";")
 ```

### 2014-06-23 R/experiment_utils.R

@@ -73,3 +73,69 @@ read.opinion.progress <- function(filename){
   return(opinion_data)
 }
 
+plot_persp_span <- function(x,y,data_matrix,breaks,xlab,ylab,zlab, pallete="YlOrBr"){ 
+    z<- data_matrix
+    nrz <- nrow(z)
+    ncz <- ncol(z)
+    
+    jet.colors <- colorRampPalette(brewer.pal(n=9, name=pallete))
+
+    nbcol <- 9
+    color <- jet.colors(nbcol)
+    
+    #range normalization function
+    normal.range <- function(x){
+      (x-min(x))/(max(x)-min(x))
+    }
+    
+    #normalized breaks
+    normbreaks <- normal.range(unique(breaks))
+
+    zfacet <- z[-1, -1] + z[-1, -ncz] + z[-nrz, -1] + z[-nrz, -ncz]
+    # Recode facet z-values into color indices
+    facetcol <- cut(zfacet, breaks=normbreaks*max(zfacet))
+  
+  
+    persp_plot <- persp(x, y, z,expand=1, ylab=ylab, xlab=xlab, zlab=zlab,ticktype="detailed", col=color[facetcol], phi=45, theta=135,  cex=2)
+    return(persp_plot)
+}
+
+
+
+#'Takes the aggregated data for the number of encounters containing 3 columns ("cs0", "cs1", and "value")
+#'and returns a contour plot. The contour lines and filling are based on the breaks which are also supplied.
+#'The cusom breaks are the values for which the user desires a contour line. 
+#'
+#'@param data a data frame with 3 columns:
+#'cs0 - the switching probability for network 0
+#'cs1 - the switching probability for network 1
+#'value - the value we are plotting
+#'
+#'@param brks the breaks for wich we want the contour lines
+#'
+#'@param the title for the colourband guide which goes with the filling 
+#'(the colour filling is also constructed based on the breaks)
+#'
+#'
+create_contour_span <- function(span,brks,guide_title){
+  require(ggplot2)
+  require(RColorBrewer)
+  require(directlabels)
+  
+  jet.colors <- colorRampPalette(brewer.pal(n=9, name="YlOrBr"))  
+  nbcol <- 9
+  color <- jet.colors(nbcol)
+  
+  #I have to do this otherwise ggplot cant find the variables in this function environmnet
+  .e <- environment()
+  
[…]

### 2014-06-23 analysis/context_switching.Rmd
Context Switching Added

Context Switching
=================

In this set of experiments we analyse a new multi-context model with a binary opinion dynamics game. In this case, the difference between the context switching model and the context permeability one is that agents no longer interact in the multiple  networks at the same time (being able to select any neighbour at a given simulation step) but rather become active in one network at a time. Agents are also able to switch to a different network at the end of each interaction with a partner. The agent switches based on a probability associated with the current network in which it is currently active.

First, we look at the influece of the new parameter in the convergence to consensus. **We span the switching probability parameter between the values 0 and 1 with intervals of 0.05**. We do this for **2** networks with **k-regular and scale-free topologies**.

We then freeze the switching probabilities and vary the number of networks. We compare the results with the context permeability in terms of percentage of convergences to consensus and average number of encounters.

##Switching Probability Span##
We set the number of networks for 2 and span the switching probabilities for each network between 0 and 1 in intervals of 0.05.

###2 10-Regular Networks###
```{r load-parameters}
#load some utilities
source("../R/experiment_utils.R")

#Read the Parameters for this experiment
params <- read.exp.parameters(param_file_name="../data/context_switching/switching_span/2 10-regular networks/param-space_2014-06-17_15:44:50experiment:10_.csv")

#read data for number of encounters

require(data.table)

encounter_data <- fread("../data/context_switching/switching_span/2 10-regular networks/num_encounters.csv")
encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
head(encounter_data)

#merge with configuration context switching values
require(reshape2)
encounter_data <- merge(encounter_data, params[,c("cfg.id","network.0.cs","network.1.cs")], by="cfg.id")
head(encounter_data)

#melt data to use cast
melted_encounters <- melt(encounter_data,id.vars=c("cfg.id","run","network.0.cs","network.1.cs"), measure.vars=c("total-encounters"))
head(melted_encounters)

#aggregate encounter data 
agg_encounters <- aggregate(melted_encounters$value,by=list(melted_encounters$network.0.cs,melted_encounters$network.1.cs),mean)
colnames(agg_encounters) <- c("cs0","cs1","value")

#create a contour plot to visualize the data

#breaks in the contour
brks <- c(0,5000,10000, seq(20000,200000, by=50000),max(agg_encounters$"value"))
guide_title <- "Average Encounters"

encouters_contour <- create_contour_span(span = agg_encounters, brks = brks, guide_title = guide_title)
encouters_contour
gc()
```

```{r fig.width=16, message=FALSE}
#reshape the data to display average number of encounters
encounter_table <- dcast(data=melted_encounters, network.0.cs~network.1.cs, mean)

#average encounters as a matrix
encounter_matrix <- as.matrix(encounter_table[,-1])
colnames(encounter_matrix) <- c()

xlab<-"\n\nSwitching for Network 1"
ylab<-"\n\nSwitching for Network 2"
zlab<-"\n\n\n Avg. Encounters"

par(mfrow=c(1,3))
plot_persp_span(x = seq(0,1,0.05), y = seq(0,1,0.05),data_matrix = encounter_matrix, breaks=log(c(1:10)),xlab=xlab,ylab=ylab,zlab = zlab)
plot_persp_span(x = seq(0.2,1,0.05), y = seq(0.2,1,0.05),data_matrix = encounter_matrix[-c(1:4),-c(1:4)], breaks=log(c(1:10)),xlab=xlab,ylab=ylab,zlab = zlab)
plot_persp_span(x = seq(0.4,1,0.05), y = seq(0.4,1,0.05),data_matrix = encounter_matrix[-c(1:8),-c(1:8)], breaks=log(c(1:10)),xlab=xlab,ylab=ylab,zlab = zlab)
gc()
```

```{r fig.width=10}
par(mfrow=c(1,1))
plot_persp_span(x = seq(0,1,0.05), y = seq(0,1,0.05),data_matrix = log(encounter_matrix), breaks=log(c(1:10)),xlab=xlab,ylab=ylab,zlab=zlab,pallete="PRGn")
```
**Note** I don't need custom breaks, its simpler to apply a logarithm to a set of n numbers, normalize them inside the plotting function and multiply this by the maximum value in the dataset, this will get the effect I'm looking for in both the filling and contour lines.

###2 Scale-Free Networks with D=1###

###1 10-Regular + 1 Scale-Free with D=1###

### 2014-06-28 analysis/context_permeability.Rmd
updated with lattest analysis

@@
-```{r message=FALSE}
-source("../R/experiment_utils.R")
-```
-
 Context Permeability Convergence Results
@@
 ```{r results='asis',message=FALSE}
+source("../R/experiment_utils.R")
+
 #Read the Parameters for this experiment
@@
 ```{r message=FALSE}
-require(reshape)
-require(tables)
+
+require(reshape2)
 
 #filter some things out
-fcdata <- melt.data.frame(convergence_data,id.vars=c("cfg.id","run","num.networks","network.0.k"), measure.vars=c("consensus-achieved"))
+fcdata <- melt(convergence_data,id.vars=c("cfg.id","run","num.networks","network.0.k"), measure.vars=c("consensus-achieved"))
 
@@
 
-fcdata_table <- aggregate(data=fcdata, fcdata$value~num.networks + fcdata$network.0.k, FUN=sum)
+fcdata_table <- aggregate(data=fcdata, fcdata$value~fcdata$num.networks + fcdata$network.0.k, FUN=sum)
 colnames(fcdata_table) <- c("num.networks", "k", "value")
 
+require(reshape)
  #create a pretty table for latex
-latex_table <- tabular(cast(fcdata_table, num.networks~k, value="value"))
+table <- cast(fcdata, num.networks~network.0.k, sum)
+
+require(tables)
+latex_table <- tabular.cast_df(table)
 
@@
 #I can also save this table to a file for later reference
-latex(latex_table,file="tex/regular_convergence.tex", booktabs=T, )
+Hmisc::latex(latex_table, file="tex/regular_convergence.tex",booktabs=T)
 ```
@@
 ```{r message=FALSE}
+
 #filter some things out
-fedata <- melt.data.frame(encounter_data,id.vars=c("cfg.id","run","num.networks","network.0.k"), measure.vars=c("total-encounters"))
+fedata <- melt(encounter_data,id.vars=c("cfg.id","run","num.networks","network.0.k"), measure.vars=c("total-encounters"))
 head(fedata)
@@
 
+require(reshape)
 #create a table with avg and sd
@@
 
-fedata_table_full <- tabular(cast_fedata_table)
-
+fedata_table_full <- tabular.cast_df(cast_fedata_table)
 ```
@@
 Now to observe the distribution of the number of encounters, necessary to achieve consensus, we look at the box plots for **k = {1,2,3,4,5}** and **k = {10,20,30,40,50}** respectively.
-We look at **configurations with a number of networks > 3** since less networks require more connectivity to allow consensus to be reached 100% of the time.
+We look at **configurations with a number of networks > 3** since less networks tab1 <- tabular(Heading()*RowFactor(rowFactor2, spacing = 1,
+                        levelnames = c("rowLabel1", "rowLabel2"))*
+                Heading()*RowFactor(rowFactor1, 
+                        levelnames = c("b1", "b2")) ~ 
+                Heading()*Factor(colFactor2, 
+                        levelnames = c("colLabel1", "colLabel2") )*
+                Heading()*Factor(colFactor1, 
+                        levelnames = c("a1", "a2"))*
+                Heading()*(x)*Heading()*(mean), 
+        data = mydf)require more connectivity to allow consensus to be reached 100% of the time.
 

### 2014-06-28 analysis/context_switching.Rmd
updated with lattest analysis

@@
 
-###2 10-Regular Networks###
+The analysis for each context switching probability span is as follows: 
 ```{r load-parameters}
+analyse_contour <- function(paramfile, encountersfile, net1label, net2label){
   #load some utilities
@@
 #Read the Parameters for this experiment
-params <- read.exp.parameters(param_file_name="../data/context_switching/switching_span/2 10-regular networks/param-space_2014-06-17_15:44:50experiment:10_.csv")
+params <- read.exp.parameters(param_file_name=paramfile)
 
@@
 
-encounter_data <- fread("../data/context_switching/switching_span/2 10-regular networks/num_encounters.csv")
+encounter_data <- fread(encountersfile)
 encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
@@
 
-encouters_contour <- create_contour_span(span = agg_encounters, brks = brks, guide_title = guide_title)
-encouters_contour
+encouters_contour <- create_contour_span(span = agg_encounters, brks = brks, guide_title = guide_title,xlab=net1label, ylab=net2label)
+pdf(paste("./pdf/",output_prefix,"_switching_contour.pdf"), width=7, height=5)
+par(mfrow=c(1,1))
+print(encouters_contour)
+
+dev.off() 
+print(encouters_contour)
 gc()
-```
+}
 
-```{r fig.width=16, message=FALSE}
+analyse_persp <- function(paramfile, encountersfile,output_prefix,net1label,net2label){
+    #load some utilities
+source("../R/experiment_utils.R")
+
+#Read the Parameters for this experiment
+params <- read.exp.parameters(param_file_name=paramfile)
+
+#read data for number of encounters
+
+require(data.table)
+
+encounter_data <- fread(encountersfile)
+encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
+head(encounter_data)
+
+#merge with configuration context switching values
+require(reshape2)
+encounter_data <- merge(encounter_data, params[,c("cfg.id","network.0.cs","network.1.cs")], by="cfg.id")
+head(encounter_data)
+
+#melt data to use cast
+melted_encounters <- melt(encounter_data,id.vars=c("cfg.id","run","network.0.cs","network.1.cs"), measure.vars=c("total-encounters"))
+head(melted_encounters)
   #reshape the data to display average number of encounters
@@
 
-xlab<-"\n\nSwitching for Network 1"
-ylab<-"\n\nSwitching for Network 2"
+xlab<- net1label
+ylab<- net2label
 zlab<-"\n\n\n Avg. Encounters"
 
+pdf(paste("./pdf/",output_prefix,"_switching_persp.pdf"), width=15, height=5)
 par(mfrow=c(1,3))
 plot_persp_span(x = seq(0,1,0.05), y = seq(0,1,0.05),data_matrix = encounter_matrix, breaks=log(c(1:10)),xlab=xlab,ylab=ylab,zlab = zlab)
+
 plot_persp_span(x = seq(0.2,1,0.05), y = seq(0.2,1,0.05),data_matrix = encounter_matrix[-c(1:4),-c(1:4)], breaks=log(c(1:10)),xlab=xlab,ylab=ylab,zlab = zlab)
+
 plot_persp_span(x = seq(0.4,1,0.05), y = seq(0.4,1,0.05),data_matrix = encounter_matrix[-c(1:8),-c(1:8)], breaks=log(c(1:10)),xlab=xlab,ylab=ylab,zlab = zlab)
-gc()
+
+dev.off() 
+par(mfrow=c(1,3))
+plot_persp_span(x = seq(0,1,0.05), y = seq(0,1,0.05),data_matrix = encounter_matrix, breaks=log(c(1:10)),xlab=xlab,ylab=ylab,zlab = zlab)
+
+plot_persp_span(x = seq(0.2,1,0.05), y = seq(0.2,1,0.05),data_matrix = encounter_matrix[-c(1:4),-c(1:4)], breaks=log(c(1:10)),xlab=xlab,ylab=ylab,zlab = zlab)
+
+plot_persp_span(x = seq(0.4,1,0.05), y = seq(0.4,1,0.05),data_matrix = encounter_matrix[-c(1:8),-c(1:8)], breaks=log(c(1:10)),xlab=xlab,ylab=ylab,zlab = zlab)
+
+zlab<-"\n\n\n Log(Avg. Encounters)"
+pdf(paste("./pdf/",output_prefix,"_switching_log_persp.pdf"), width=5, height=5)
+plot_persp_span(x = seq(0,1,0.05), y = seq(0,1,0.05),data_matrix = log(encounter_matrix), breaks=log(c(1:10)),xlab=xlab,ylab=ylab,zlab=zlab,pallete="PRGn")
+dev.off()
+plot_persp_span(x = seq(0,1,0.05), y = seq(0,1,0.05),data_matrix = log(encounter_matrix), breaks=log(c(1:10)),xlab=xlab,ylab=ylab,zlab=zlab,pallete="PRGn")
+}
 ```
 
-```{r fig.width=10}
-par(mfrow=c(1,1))
-plot_persp_span(x = seq(0,1,0.05), y = seq(0,1,0.05),data_matrix = log(encounter_matrix), breaks=log(c(1:10)),xlab=xlab,ylab=ylab,zlab=zlab,pallete="PRGn")
+###2 10-Regular Networks###
+```{r}
+params <- "../data/context_switching/switching_span/2 10-regular networks/param-space_2014-06-17_15:44:50experiment:10_.csv"
+encounters <- "../data/context_switching/switching_span/2 10-regular networks/num_encounters.csv"
+
+output_prefix <- "context_switching_2_10_regular"
+
+net1label <- "\n\nSwitching for Network 1 \n regular network, k=10"
+net2label <- "\n\nSwitching for Network 2 \n regular network, k=10"
+
+analyse_contour(params, encounters,net1label,net2label)
 ```
-**Note** I don't need custom breaks, its simpler to apply a logarithm to a set of n numbers, normalize them inside the plotting function and multiply this by the maximum value in the dataset, this will get the effect I'm looking for in both the filling and contour lines.
+
+```{r fig.width=15}
+analyse_persp(params, encounters,output_prefix,net1label,net2label)
+```
+
+**Note** I don't need custom breaks for the **persp plots**, its simpler to apply a logarithm to a set of n numbers, normalize them inside the plotting function, and multiply this by the maximum value in the dataset, this gets me the effect I'm looking for both the filling and contour lines.
+
+###2 30-Regular Networks###
+```{r}
+params <- "../data/context_switching/switching_span/2 30-regular networks/param-space_2014-06-20_20:25:18experiment:10_.csv"
+encounters <- "../data/context_switching/switching_span/2 30-regular networks/num_encounters.csv"
+output_prefix <- "context_switching_2_30_regular"
+
+net1label <- "\n\nSwitching for Network 1 \n regular network, k=30"
+net2label <- "\n\nSwitching for Network 2 \n regular network, k=30"
+
+analyse_contour(params, encounters,net1label,net2label)
+```
+As we can see, increasing the connectivity of the agents makes so that the switching probability values are no longer as important to the speed of convergence to total concensus.
+The clustering coefficient for the merged networks is significantly higher for k = 30 than for k = 10.
+This is especially true for a number of networks = 2 (see [network properties](http://rpubs.com/davidelnunes/socsim_network_properties)).
+The average path length is also lower for k=30 although this difference is not as drastic (for 2 networks) as in the clustering coefficient.
+
+```{r fig.width=15}
+analyse_persp(params, encounters,output_prefix,net1label,net2label)
+```
 
 ###2 Scale-Free Networks with D=1###
+```{r}
+params <- "../data/context_switching/switching_span/2 scale-free networks d=1/param-space_2014-06-17_15:58:29experiment:11_.csv"
+encounters <- "../data/context_switching/switching_span/2 scale-free networks d=1/num_encounters.csv"
+output_prefix <- "context_switching_2_sf_d1"
+
+net1label <- "\n\nSwitching for Network 1 \n scale-free network, d=1"
+net2label <- "\n\nSwitching for Network 2 \n scale-free network, d=1"
+
+analyse_contour(params, encounters,net1label,net2label)
+```
+
+```{r fig.width=15}
+analyse_persp(params, encounters,output_prefix,net1label,net2label)
+```
+
+###2 Scale-Free Networks with D=5###
+```{r}
+params <- "../data/context_switching/switching_span/2 scale-free networks d=5/param-space_2014-06-25_11:38:56experiment:11_.csv"
+encounters <- "../data/context_switching/switching_span/2 scale-free networks d=5/num_encounters.csv"
+output_prefix <- "context_switching_2_sf_d5"
+
+net1label <- "\n\nSwitching for Network 1 \n scale-free network, d=5"
+net2label <- "\n\nSwitching for Network 2 \n scale-free network, d=5"
+
+analyse_contour(params, encounters,net1label,net2label)
+```
+With 2 scale-free networks with **d=5**, similarly to the 2 k-regular networks, switching is less important to achieve faster consensus.
+The main difference is that the number of edges is nowhere near the number of edges of 30-regular networks for 100 agents.
+With the 30-regular networks we generate 30 edges per agent (a total of 3000 edges since we have 100 agents).
+With the scale-free, with each agent we add 5 edges, which gives us a total of 500 edges.
+So this effect is not related to the connectivity of the agents but rather to the properties of the underlying structure.
+The clustering coefficient for d=1 for instance is 0--the network is basically a forest (a set of tree graphs)--, with d=5 this is no longer the case.
+For d=1 the average path length of scale-frees is already lower than a regular network with k within the values [1,5].
+```{r fig.width=15}
+analyse_persp(params, encounters,output_prefix,net1label,net2label)
+```
 
 ###1 10-Regular + 1 Scale-Free with D=1###
+In this experiment, network 1 has a 10-Regular Topology while network 2 has a scale-free topology with d=1. 
+```{r}
+params <- "../data/context_switching/switching_span/scale-free d=1 k-regular k=10/param-space_2014-06-17_16:06:26experiment:12_.csv"
+encounters <- "../data/context_switching/switching_span/scale-free d=1 k-regular k=10/num_encounters.csv"
+
+output_prefix <- "context_switching_1_10regular_1_scale-free_d1"
+
+net1label <- "\n\nSwitching for Network 1 \n regular network, k=10"
+net2label <- "\n\nSwitching for Network 2 \n scale-free network, d=1"
+
+analyse_contour(params, encounters,net1label,net2label)
+```
+
+```{r fig.width=15}
+analyse_persp(params, encounters,output_prefix,net1label,net2label)
+```
+
+###2 10-Regular Networks with 300 Agents###
+
+In the previous experiments we use 100 agents. This time, we use 300 agents to see the effect
+of context switching with slightly diferent network properties. The scale should not be important here
+but rather the conectivity pattern. I hypothesise that what influences the results the most with k-regular 
+networks is **the proportion of connections (given by 2k) versus the number of agents in the network**.
+
+```{r}
+params <- "../data/context_switching/switching_span/2 10-regular networks 300 agents/param-space_2014-06-23_23:48:11experiment:10_.csv"
+encounters <- "../data/context_switching/switching_span/2 10-regular networks 300 agents/num_encounters.csv"
+
+output_prefix <- "context_switching_2_10regular_300agents"
+
+net1label <- "\n\nSwitching for Network 1 \n regular network, k=10, 300 agents"
+net2label <- "\n\nSwitching for Network 1 \n regular network, k=10, 300 agents"
+
+analyse_contour(params, encounters,net1label,net2label)
+```
+We can observe that lower connectivity also means that **the lower the switching probability the more important simetry is--if the network topologies are the same for both networks**.
+It is the same for scale-free networks with d = 1.
+```{r fig.width=15}
+analyse_persp(params, encounters,output_prefix,net1label,net2label)
+```
+
+### 2 30-Regular Networks 300 Agents ###
+We can see that the results for k = 30 and 300 agents are qualitatively similar to the results for k=10 and 100 agents. 
+```{r}
+params <- "../data/context_switching/switching_span/2 30-regular networks 300 agents/param-space_2014-06-24_01:00:58experiment:10_.csv"
+encounters <- "../data/context_switching/switching_span/2 30-regular networks 300 agents/num_encounters.csv"
+
+output_prefix <- "context_switching_2_30regular_300agents"
+
+net1label <- "\n\nSwitching for Network 1 \n regular network, k=30, 300 agents"
+net2label <- "\n\nSwitching for Network 1 \n regular network, k=30, 300 agents"
+
+analyse_contour(params, encounters,net1label,net2label)
+```
+
+```{r fig.width=15}
+analyse_persp(params, encounters,output_prefix,net1label,net2label)
+```
+
+# Results for Multiple-Networks and Comparison with Context Permeability #
+
+## Comparison for K-Regular Networks ##
+```{r}
+#**************************************************************************
+#   read encounter results for context permeability (for comparison)
+#**************************************************************************
+params <- "../data/context_permeability/regular_networks/param-space_2014-05-30_16:47:53experiment:0_.csv"
+encounters <- "../data/context_permeability/regular_networks/num_encounters.csv"
+
+params <- read.exp.parameters(param_file_name=params)
+
+require(data.table)
+
+encounter_data <- fread(encounters)
+encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
+#merge with configuration context switching values
+require(reshape2)
+encounter_data <- merge(encounter_data, params[,c("cfg.id","network.0.k","num.networks")], by="cfg.id")
+head(encounter_data)
+#melt data to use cast
+melted_encounters <- melt(encounter_data,id.vars=c("cfg.id","run","network.0.k","num.networks"), measure.vars=c("total-encounters"))
+head(melted_encounters)
+permeability_encounters <- melted_encounters
+
+#***************************************************************
+#   read encounter results for context switching
+#***************************************************************
+params <- "../data/context_switching/multiple_networks/regular_networks/param-space_2014-06-22_00:33:19experiment:10_.csv"
+
+encounters <- "../data/context_switching/multiple_networks/regular_networks/num_encounters.csv"
+
+params <- read.exp.parameters(param_file_name=params)
+
+require(data.table)
+
+encounter_data <- fread(encounters)
+encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
+head(encounter_data)
+
+#merge with configuration context switching values
+require(reshape2)
+encounter_data <- merge(encounter_data, params[,c("cfg.id","network.0.cs","network.0.k","num.networks")], by="cfg.id")
+head(encounter_data)
+
+#melt data to use cast
+melted_encounters <- melt(encounter_data,id.vars=c("cfg.id","run","network.0.cs","network.0.k","num.networks"), measure.vars=c("total-encounters"))
+head(melted_encounters)
+
+for(n in 2:5){
+  #plot for 2 networks
+  current_encounters<-melted_encounters[melted_encounters$"num.networks" == n,]
+  perm_encounters<-permeability_encounters[permeability_encounters$"num.networks" == n,]
+
+  plot_data <- dcast(current_encounters, network.0.k + network.0.cs ~ variable, mean)
+  colnames(plot_data) <- c("k","cs","avg-encounters")
+
+  perm_data <- dcast(perm_encounters, network.0.k ~ variable, mean)
+  colnames(perm_data) <- c("k","avg-encounters")
+
+  plot <- NULL
+
+  plot <- ggplot(plot_data, aes(x=as.factor(plot_data$k), y=plot_data$"avg-encounters")) 
+  plot <- plot +  geom_point(aes(shape=as.factor(plot_data$cs), color=as.factor(plot_data$cs)),size = 3.5)
+  plot <- plot +  geom_line(aes(color=as.factor(plot_data$cs), group=as.factor(plot_data$cs), linetype=as.factor(plot_data$cs)),size=1)   
+  #add line for permeability baseline
+  plot <- plot + geom_point(data=perm_data, aes(x=as.factor(perm_data$k), y=perm_data$"avg-encounters", shape="permeability", color="permeability"),size = 3.5)
+  plot <- plot + geom_line(data=perm_data, aes(x=as.factor(perm_data$k), y=perm_data$"avg-encounters", group="Permeability", linetype="permeability", color="permeability"),size=1)
+
+  plot <- plot + labs(color="CS", shape="CS", linetype="CS", y="Average Encounters", x="K",
+                       title=paste("K-Regular Networks With Number of Networks =",n))
+
+  print(plot)
+
+}
+gc()
+
+for(cs in c(0.25,0.5,0.75)){
+  #plot for 2 networks
+  current_encounters<-melted_encounters[melted_encounters$"network.0.cs" == cs,]
+  #perm_encounters<-permeability_encounters[permeability_encounters$"num.networks" > 1,]
+
+  plot_data <- dcast(current_encounters, network.0.k + num.networks ~ variable, mean)
+  colnames(plot_data) <- c("k","num-networks","avg-encounters")
+
+  #gets too messy with permeability data 
+  #perm_data <- dcast(perm_encounters, network.0.k + num.networks ~ variable, mean)
+  #colnames(perm_data) <- c("k","num-networks", "avg-encounters")
+
+  plot <- ggplot(plot_data, aes(x=as.factor(plot_data$k), y=plot_data$"avg-encounters")) 
+  plot <- plot +  geom_point(aes(shape=as.factor(plot_data$"num-networks"), color=as.factor(plot_data$"num-networks")),size = 3.5)
+  plot <- plot +  geom_line(aes(color=as.factor(plot_data$"num-networks"), group=as.factor(plot_data$"num-networks"), linetype=as.factor(plot_data$"num-networks")),size=1)
+
+  #add line for permeability
+  #plot <- plot +  geom_point(data=perm_data, aes(x=as.factor(perm_data$k), y=perm_data$"avg-encounters", shape="permeability", color=as.factor(perm_data$"num-networks")),size = 3.5)
+  #plot +  geom_line(data=perm_data, aes(x=as.factor(perm_data$k), y=perm_data$"avg-encounters",group=as.factor(perm_data$"num-networks"),linetype=as.factor(plot_data$"num-networks"),color=as.factor(perm_data$"num-networks")),size=1)
+
+  plot <- plot + labs(color="Num. Networks", shape="Num. Networks", linetype="Num. Networks", y="Average Encounters", x="K",
+                      title=paste("K-Regular Networks With CS =",cs))
+
+   print(plot)
+}
+gc()
+
+```

### 2014-06-28 analysis/network_properties.Rmd
updated with lattest analysis

@@
 This obviously changes as we add increase k towards 50, which is the configuration where the networks are fully connected.
+
+# Properties for Scale-Free Networks #
+We now look at the properties we get when we merge scale-free networks with different values of **D** (number of edges added with preferential attachement each time a new node is added to the network).
+
+```{r}
+#shows the d values explored and the number of networks
+params <- read.exp.parameters("../data/context_permeability/scale-free_networks/param-space_2014-05-30_18:38:14experiment:1_.csv")
+params <- params[,c("cfg.id","num.networks","network.0.d")]
+
+#read the network data
+require(bigmemory)
+network_data <- read.big.matrix(filename="../data/context_permeability/scale-free_networks/networks.csv", header=T, sep=";")
+
+#Collect the network data and create a data table to hold the network properties
+require(parallel)
+
+## Number of workers (R processes) to use:
+numWorkers <- 8
+
+measure_parallel <- function(cfg,r){
+  data <- network_data
+  network <- read.big.network(data,cfg,r)
+  properties <- measure.network(network)
+  properties <- cbind(r,properties)
+  return(properties)
+}
+
+props <- NULL
+num_networks <- c(1,2,3,4,5)
+d_values <- c(1,2,3,4,5)
+runs <- sort(unique(network_data[,"run"]))
+
+require(BBmisc)#for progress bar
+pb <- makeProgressBar(min=0, max=(length(num_networks)*length(d_values)), label="network analysis")
+
+#pre-alocate a matrix for the network properties
+props <- matrix(nrow=(length(num_networks)*length(d_values)*length(runs)), ncol=7)
+i <- 0
+
+for(n in num_networks){
+  #reads the properties for all the k-regular networks with the given k and num_networks 
+  for(d in d_values){
+    cfg <- params[params$"num.network" == n & params$"network.0.d" == d,][[1]]
+
+    properties <- mcmapply(cfg=cfg, r=runs, measure_parallel, mc.cores = numWorkers)
+    properties <- t(properties)
+
+    props[(i+1):(i+100),] <- cbind(d,n,properties)
+    i <- i + 100  
+    #some progress feddback
+    pb$inc(1,paste("reading n=",n,"d=",d,"\n"))
+    gc()
+  } 
+}
+pb$kill()
+
+colnames(props)<-c("d","networks","run","nodes","edges","clustering-coefficient","average-path-length")
+
+#clean up
+rm(pb)
+gc()
+
+```
+
+Creating boxplots to observe the average path length and the clustering coefficient, we can see that these values don't varie much within each configuration with the exception of the configuration: **d=1 networks=1**.
+This happens because the generative process is stochastic by nature and thus depends on the preferential attachement node selection.
+Within scale-free networks we can thus assume certain property values for specific combinations of networks much like what happens with the k-regular networks.
+
+```{r}
+props <- as.data.frame(props)
+
+require(ggplot2)
+
+#create average path length box plots for d = 1,2,3,4,5
+net_props <- props
+
+plot <- plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"average-path-length",fill=as.factor(net_props$d)) ) 
+plot <- plot + geom_boxplot()
+plot <- plot + labs(fill="D", y="Average Path Length", x="Number of Networks")
+plot
+
+#create clustering coefficient box plots for d = 1,2,3,4,5
+
+plot <- plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"clustering-coefficient",fill=as.factor(net_props$d)) ) 
+plot <- plot + geom_boxplot()
+plot <- plot + labs(fill="D", y="Clustering Coefficient", x="Number of Networks")
+plot 
+```
+
+We now plot the average value of **average path length** and **clustering coefficient** for a total of 100 Scale-Free Networks. We analyse the properties of networks with different levels of **D**.
+
+```{r}
+#aggregate run data by k and networks
+require(reshape2)
+
+apl_data <- melt(props, id=c("d","networks","run"),measure.vars=c("average-path-length"))
+clustering_data <- melt(props, id=c("d","networks","run"),measure.vars=c("clustering-coefficient"))
+
+average_apl_data <- dcast(apl_data, d + networks ~ variable, mean)
+average_clustering_data <- dcast(clustering_data, d + networks ~ variable, mean)
+
+#plot average path length for d = 1,2,3,4,5
+net_props <- average_apl_data
+plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"average-path-length",)) 
+plot <- plot +  geom_point(aes(shape=as.factor(net_props$d), color=as.factor(net_props$d)),size = 3.5)
+plot <- plot +  geom_line(aes(color=as.factor(net_props$d), group=as.factor(net_props$d), linetype=as.factor(net_props$d)),size=1)   
+plot <- plot + labs(color="D", shape="D", linetype="D", y="Average Path Length", x="Number of Networks")
+plot
+
+#clean up
+rm(apl_data,average_apl_data)
+gc()
+```
+
+```{r}
+#plot for D = 1,2,3,4,5
+net_props <- average_clustering_data
+
+plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"clustering-coefficient",)) 
+plot <- plot +  geom_point(aes(shape=as.factor(net_props$d), color=as.factor(net_props$d)),size = 3.5)
+plot <- plot +  geom_line(aes(color=as.factor(net_props$d), group=as.factor(net_props$d), linetype=as.factor(net_props$d)),size=1)   
+plot <- plot + labs(color="D", shape="D", linetype="D", y="Clustering Coefficient", x="Number of Networks")
+plot
+
+#clean up
+rm(clustering_data,average_clustering_data,props, net_props,plot)
+gc()
+```

### 2014-06-28 R/experiment_utils.R

@@ -1,3 +1,8 @@
+#range normalization function
+normal.range <- function(x){
+  (x-min(x))/(max(x)-min(x))
+}
+
 #*******************************************************************************
 # Reads a parameter file (normaly each experiment has an associated
 # Parameter Space File) with all the parameter values used.
@@ -83,10 +88,7 @@ plot_persp_span <- function(x,y,data_matrix,breaks,xlab,ylab,zlab, pallete="YlOr
     nbcol <- 9
     color <- jet.colors(nbcol)
     
-    #range normalization function
-    normal.range <- function(x){
-      (x-min(x))/(max(x)-min(x))
-    }
+   
     
     #normalized breaks
     normbreaks <- normal.range(unique(breaks))
@@ -117,7 +119,7 @@ plot_persp_span <- function(x,y,data_matrix,breaks,xlab,ylab,zlab, pallete="YlOr
 #'(the colour filling is also constructed based on the breaks)
 #'
 #'
-create_contour_span <- function(span,brks,guide_title){
+create_contour_span <- function(span,brks,guide_title,xlab,ylab){
   require(ggplot2)
   require(RColorBrewer)
   require(directlabels)
@@ -134,8 +136,112 @@ create_contour_span <- function(span,brks,guide_title){
   v <- v + geom_tile(aes(fill = span$"value"),breaks=brks) + scale_fill_gradientn(colours=color)
   v <- v + guides(fill = guide_colorbar(barwidth = 0.5, barheight = 20, title = guide_title))
   v <- v + stat_contour(aes(colour = ..level..), breaks=brks) + scale_colour_gradient(low = "black", high ="black")
-  v <- v + labs(x="Switching probability from network 1", y="Switching probability from network 2")
+  v <- v + labs(x=xlab, y=ylab)
   
   plot <- direct.label(v,method="top.pieces")
   return(plot)
 }
+
+
+tabular.cast_df <- function(xx,...)
+{
+  # a bunch of assumptions that must be met for this function to work:
+  if(!require(reshape)) stop("The {reshape} package must be installed for this function to work")
+  if(!require(tables)) stop("The {tables} package must be installed for this function to work")
+  if(! any(class(xx) == "cast_df")) stop("This function only works for cast_df objects")
+  # xx is a casted object
+  
+  m_xx <- melt(xx)
+  rdimnames_xx <- attr(xx, "rdimnames")
[…]

### 2014-06-28 doc/main.tex
paper added in docs folder

\documentclass[preprint,number]{elsarticle}
\usepackage[utf8]{inputenc}
\usepackage{multirow}

\begin{document}
\begin{frontmatter}

\author[ul]{Davide Nunes\corref{cor1}}
\ead{davide.nunes@di.fc.ul.pt}
\author[ul]{Luis Antunes}
\ead{xarax@di.fc.ul.pt}

\cortext[cor1]{Corresponding author}

\address[ul]{Group of Studies in Social Simulation (GUESS), Laboratory of Agent Modelling, University of Lisbon, 1749-016 Lisbon, Portugal}
\title{Modelling Structured Societies: a Multi-relational Approach to Context Permeability}

\begin{abstract}
The structure of social relations is fundamental for the construction of plausible simulation scenarios. It shapes the way actors interact and create their identity within overlapping social contexts. Each actor interacts in multiple contexts located within relations that constitute their social space. We present a modelling approach to construct structured agent societies with multiple concomitant social networks. We study the notion of context permeability using a consensus game in which agents try to achieve global consensus. We design and analyse models of permeability with three model different configurations. In the first model agents interact concurrently in multiple social networks. The second model uses a context switching mechanism that adds temporal dynamics to agent interaction. They switch between the different networks spending more or less time in each network. Finally we use a strategic neighbourhood selection by segregation that acts as a regulatory mechanism in the societal self-organisation process to achieve consensus. We compare each model and analyse the influence of different social topologies in the speed of convergence to global consensus.
%TODO abstract: brief strong conclusion
\end{abstract}

\begin{keyword}
Social Simulation and Modelling \sep Agent Societies \sep Consensus \sep Context \sep Social Networks
\end{keyword}

\end{frontmatter}
\newpage
%********************************************
%				INTRODUCTION
%********************************************
\section{Introduction and Related Work}
\label{sec:introduction}
%Social simulation view oever consensus
\noindent In social simulation, studying models of consensus formation helps us to investigate real-world phenomena. This can be done not only by constructing data-driven simulation but also with the help of abstract models that permit the assembly of \textit{what-if-scenarios}. Examples of real-world target phenomena in this domain include: the joint assessments of social policies or, in the context of economics and politics, \textit{the voting problem}. Herbert Simon investigated this last problem in an early model described in~\cite{Simon1954}.

Formal opinion dynamics models provide an understanding if not an analysis of opinion formation processes.  An early formulation of these models was designed to comprehend complex phenomena found empirically in groups \cite{French1956}. In particular, the work on consensus building in the context of decision-making was first studied by DeGroot \cite{Degroot74} and Lehrer \cite{Lehrer1975}. Empirical studies of opinion formation in large populations have methodological limitations, as such, we use simulation, in particular Multi-Agent Simulation (MAS), as a methodological framework to study such phenomena in a larger scale. Most opinion dynamics simulation models are based either on binary opinions \cite{Galam1997,Antunes2009} or on opinions with continuous values \cite{Deffuant2000,Deffuant2002}. In these models, agents update their opinions either under social influence or according to their own experience. For a detailed analysis over some opinion dynamics model analytical and simulation results, refer to \cite{Hegselmann2002}.

In agent-based opinion dynamics models, agent interactions are guided by social space abstractions. In some models, dimensionality is irrelevant. Typically, all agents can participate in interactions with all other agents. Axelrod, takes a different approach in his model of dissemination of culture \cite{Axelrod1997} and represents agents in a bi-dimensional grid which provides the structure that shapes how they interact. In Weisbuch's bounded confidence model with social networks \cite{Weisbuch2004}, the agents are bound by network structures. A first definition for these types of bounded confidence models was given in \cite{Krause1997}.

%position, most agent-based models don't take into account  social relations and this is important
In real-world scenarios, actors engage in a multitude of social relations different in kind and quality. Most simulation models don't explore social space designs that take into account the differentiation between coexisting social networks. Modelling multiple concomitant relations was an idea pioneered by Peter Albin in \cite{Albin1975} but without significant further development. The complex social structures that result from interacting in these different dimensions form the basis for the formation of social identity \cite{Roccas2002,Ellemers2002}.

%A broader view over consensus formation
\subsection{On Consensus}
Opinion dynamics models try to study under which circumstances convergence to consensus can be achieved. These agent-based models can have broader applications outside social simulation. In distributed systems in general, consensus is a means by which processes agree on some data value that is needed during computation, typically, this agreement is the result of a negotiation process often with the aid of a mediator. In human societies, social conventions emerge to deal with coordination and subsequently with cooperation problems \cite{Lewis1969}, these conventions are regularities of behaviour that can turn normative with time due to their being persistent solutions to such problems. Moreover, conventions typically originate from the necessity to resolve conflict. Mult-Agent Systems (MAS) can also benefit from being capable of produce emergent conventions as they might need to coordinate or cooperate in order to solve different problems \cite{Delgado2002}.

The decentralised nature of these models of consensus is highly desirable for problems where dynamic control is needed. In these scenarios, creating conventions before hand (off-line) or developing a central control mechanism for generating them can be a difficult and intractable task. MAS can be designed to update their values and strategies based on this local information. Consequently, the guarantee of achieving a global consensus and the efficiency of convergence towards it has been a natural concerns in the design of local interaction behaviours. Shoham and Tennenholtz compared several strategy update rules in %paper urbano

%TODO this was the last thing I wrote

. This explains the interest on the design of
emergent conventions through a co-learning process [13]: individual agents occasionally meet and observe each
other, and they may .

%TODO present the literature related to norms and consensus and motivate the problem

%TODO distributed systems need consensus to perform reliable sets of actions (tolerance to faults etc) such as transations
%Agents that co-exist need to coordinate to perform certain tasks or choose appropriate strategies, science a particular behaviour can 
%have an impact on the each agent not only on the environment, and even when agents have an impact on the environment, this is reflected
%in the performance of other agents that co-habit the same environment.

%TODO as in human societies, consensus is not an intentional end result but rather an emergent process which arises 
%without a central authority

%TODO see Emergent Conventions and the Structure of Multi{Agent Systems
%TODO see On the synhesis of useful social laws for artificial agent societies

In the field of Distributed Artificial Intelligence (DAI) in general and in Multi-Agent Systems (MAS) in particular, achieving a global agreement on some strategy, convention or norm is fundamental 
\cite{Delgado2002}

%Objective of this paper
This paper is aimed at extending the line of research regarding the representation of social spaces by modelling these with explicit multiple networks.

%****************************************
%			PAPER STRUCTURE
%****************************************
\subsection{Paper Structure}
This paper is organised as follows. In the next section we define our modelling approach that uses multiple social networks. We describe our game of consensus and introduce multiple model variations designed to study the notion of context permeability and the process of consensus formation. Section \ref{sec:experimental-setup} describes the experimental set-up for our series of experiments. Finally, in section \ref{sec:results-discussion}, we discuss our results and compare the different simulation models.

\section{Experimental Setup}
\label{sec:experimental-setup}

\section{Results and Discussion}
\label{sec:results-discussion}

\section*{References}
\bibliographystyle{elsarticle-num}
\bibliography{main}

\end{document}

### 2014-08-18 analysis/context_permeability.Rmd
pre-proof-read version of the paper added; some correlation analysis added; other old analysis corrected

--- 2014-06-23 analysis/context_permeability.Rmd
@@
 
+We will start by loading the dependencies for this report.
+```{r}
+source("../R/read_network.R")
+source("../R/experiment_utils.R")
+
+library(data.table)
+library(reshape2)
+library(reshape)
+library(tables)
+
+library(ggplot2)
+#to display ggplot2 plots in a grid layout
+library(gridExtra)
+```
+
 # Convergence for K-Regular Networks #
@@
 ```{r results='asis',message=FALSE}
-#Read the Parameters for this experiment
-params <- read.exp.parameters(param_file_name="../data/context_permeability/regular_networks/param-space_2014-05-30_16:47:53experiment:0_.csv")
+
+#read the convergence data
+params <- read.exp.parameters(param_file_name="../data/context_permeability/regular_networks/convergence/param-space_2014-08-01_00:09:09experiment:0_.csv")
 
 #read the adata related to consensus was achieved before
-require(data.table)
-convergence_data <- fread("../data/context_permeability/regular_networks/consensus_achieved.csv")
+
+convergence_data <- fread("../data/context_permeability/regular_networks/convergence/consensus_achieved.csv")
 convergence_data <- as.data.frame(convergence_data)[,-ncol(convergence_data)]
 convergence_data <- merge(convergence_data, params, by="cfg.id")
+
+convergence_data <- melt(convergence_data,id.vars=c("cfg.id","run","num.networks","network.0.k"), measure.vars=c("consensus-achieved"))
+
+convergence_data <- aggregate(data=convergence_data, convergence_data$value~convergence_data$num.networks + convergence_data$network.0.k, FUN=function(x) sum(x)/length(x))
+
+colnames(convergence_data) <- c("networks", "k", "convergence")
+head(convergence_data)
+
+table <- cast(convergence_data, networks~k, value="convergence")
+latex_table <- tabular.cast_df(table)
 ```
@@
 
-```{r message=FALSE}
-require(reshape)
-require(tables)
-
-#filter some things out
-fcdata <- melt.data.frame(convergence_data,id.vars=c("cfg.id","run","num.networks","network.0.k"), measure.vars=c("consensus-achieved"))
-
-#I can also cast to obtain multiple values like summary 
-#this will be useful later for the table with the number of encounters
-#convergence_table <- cast(fcdata, num.networks~network.0.k~value, sum)
-
-#convergence_table
-
-fcdata_table <- aggregate(data=fcdata, fcdata$value~num.networks + fcdata$network.0.k, FUN=sum)
-colnames(fcdata_table) <- c("num.networks", "k", "value")
-
- #create a pretty table for latex
-latex_table <- tabular(cast(fcdata_table, num.networks~k, value="value"))
-
-```
-
 ```{r results='asis'}
@@
 
-#I can also save this table to a file for later reference
-latex(latex_table,file="tex/regular_convergence.tex", booktabs=T, )
+#save this table to a file for later reference
+Hmisc::latex(latex_table, file="tex/regular_convergence.tex",booktabs=T)
 ```
 
-This table shows the percentage of simulation runs that converged to total consensus over 100 
-independent runs.
+This table shows the convergence ratio to total consensus for 3000 independent runs.
 
@@
 ```{r}
+params <- read.exp.parameters(param_file_name="../data/context_permeability/regular_networks/param-space_2014-07-23_11:40:44experiment:0_.csv")
+
 encounter_data <- fread("../data/context_permeability/regular_networks/num_encounters.csv")
@@
 ```{r message=FALSE}
-#filter some things out
-fedata <- melt.data.frame(encounter_data,id.vars=c("cfg.id","run","num.networks","network.0.k"), measure.vars=c("total-encounters"))
+#filter some columns that are not needed and convert to melted format
+fedata <- melt(encounter_data,id.vars=c("cfg.id","run","num.networks","network.0.k"), measure.vars=c("total-encounters"))
 head(fedata)
 
-#filter encounter data include only num networks > 3
+#divide data in two partitions k<=5 and k>5
 fedata_net1 <- fedata[fedata$num.networks>2 & fedata$network.0.k <= 5,]
-
 fedata_net10 <- fedata[fedata$num.networks>2 & fedata$network.0.k > 5,]
 
-#create a table with avg and sd
+#create a table with avg and stdev
 cast_fedata_table <- cast(data=fedata, formula=network.0.k~num.networks, c(mean, sd))
-
-fedata_table_full <- tabular(cast_fedata_table)
-
+fedata_table_full <- tabular.cast_df(cast_fedata_table)
 ```
 
-Create the tables
+Display the table in HTML for the knitr report and save it to a file.
 ```{r results='asis',message=FALSE}
 #to print the table created with tabular
-
 html(fedata_table_full)
@@
 #print this to a file to use in the paper
-
 Hmisc::latex(fedata_table_full, file="tex/regular_encounters_full.tex",booktabs=T)
@@
 Now to observe the distribution of the number of encounters, necessary to achieve consensus, we look at the box plots for **k = {1,2,3,4,5}** and **k = {10,20,30,40,50}** respectively.
-We look at **configurations with a number of networks > 3** since less networks require more connectivity to allow consensus to be reached 100% of the time.
-
+We look at **configurations with a number of networks >= 3** since less networks lead to much worse results.
+As we have seen in the previous convergence results.
 ```{r}
@@
 
+#print to pdf
+pdf(paste("./pdf/","context_permeability_encounters_kregular_12345.pdf"), width=7, height=5)
+plot
+dev.off()
+
 plot <- plot.exp.box(data=fedata_net10,x_factor=as.factor(fedata_net10$num.networks), data_y=fedata_net10$value, fill_factor=as.factor(fedata_net10$network.0.k),fill_label="K", x_label="Number of Networks", y_label="Number of Encounters")
@@
 plot
+
+pdf(paste("./pdf/","context_permeability_encounters_kregular_1020304050.pdf"), width=7, height=5)
+plot
+dev.off()
+
 ```
@@
 What I'm trying to find is weather the network structure is the same from the other runs.
-
 ```{r}
-source("../R/read_network.R")
-
 network_data <- fread("../data/context_permeability/regular_networks/networks.csv")
@@
 
+#print to pdf
+pdf(paste("./pdf/","context_permeability_encounters_kregular_k10_outlier.pdf"), width=7, height=5)
+plot
+dev.off()
+
 normal <- normal[2,] #choose one possible configuration (not an outlier)
@@
 normal_net_props <- read.composite.properties(normal_net)
-
 ```
@@
 opinion_data <- read.opinion.progress("../data/context_permeability/regular_networks/opinion_progress.csv")
+
 #filter opinion to outlier run and normal run
@@
 plot_run_outlier + labs(title = "Outlier Run")
+
+#print to pdf
+pdf(paste("./pdf/","context_permeability_simrun_kregular_k10_normal.pdf"), width=7, height=5)
+plot_run_normal + labs(title = "Normal Run")
+dev.off()
+
+pdf(paste("./pdf/","context_permeability_simrun_kregular_k10_outlier.pdf"), width=7, height=5)
+plot_run_outlier + labs(title = "Outlier Run")
+dev.off()
+```
+
+We now look at the average difference between the memory of opinions seen.
+This is abs(number of opinion 1 seen - number of opinion 2 seen).
+We also look at the variance of this difference between the 100 agents.
+```{r}
+#check the opinion memory difference for the outlier and the normal run
+plot.op.diff <- function(current_run){
+
+  average_data <- melt(current_run, id=(c("step")), measure.vars=(c("avg-op-diff")))
+
+  .e <- environment()
+
+  average_plot <- ggplot(data = average_data, aes(x = average_data$step, y = average_data$value), environment=.e)
+  average_plot <- average_plot + geom_line() + geom_point(size=0)
+  average_plot <- average_plot + labs(x = "Simulation Step", y = "Average Memory Difference")
+
+  #average_plot <- average_plot + labs(title = "Average Opinion Memory Difference")
+  average_plot <- average_plot + theme_bw()
+  average_plot <- average_plot + theme(legend.title=element_blank())
+
+  #plot variance
+
+  variance_data <- melt(current_run, id=(c("step")), measure.vars=(c("variance-op-diff")))
+
+  variance_plot <- ggplot(data = variance_data, aes(x = variance_data$step, y = variance_data$value), environment=.e)
+  variance_plot <- variance_plot + geom_line() + geom_point(size=0)
+  variance_plot <- variance_plot + labs(x = "Simulation Step", y = "Variance of Opinion Memory Difference")
+
+  #variance_plot <- variance_plot + labs(title = "Variance of Opinion Memory Difference")
+  variance_plot <- variance_plot + theme_bw()
+  variance_plot <- variance_plot + theme(legend.title=element_blank())
+
+  grid.arrange(average_plot, variance_plot, ncol=2)
+}
+```
+
+Bellow we can see the average difference between opinion memory 
+in the first ten steps (which was when the simulation converged for the "normal" run).
+```{r}
+current_run <- normal_run
+current_run <- current_run[current_run$"step" <= 10,]
+
+plot.op.diff(current_run)
+
+pdf(paste("./pdf/","cp-regular-normal-run-memory-diff.pdf"), width=15, height=5)
+plot.op.diff(current_run)
+dev.off()
+
+```
+
+For the outlier run we get the following results.
+We can see that the average difference in the opinion memory rises more quickly for the normal run than it does in the outlier run.
+The values of opinion memory and the position of the agents in the network is such that the convergence is slower but steady towards total consensus.
+```{r}
+current_run <- outlier_run
+current_run <- current_run[current_run$"step" <= 10,]
+plot.op.diff(current_run)
+
+pdf(paste("./pdf/","cp-regular-outlier-run-memory-diff.pdf"), width=15, height=5)
+plot.op.diff(current_run)
+dev.off()
+```
+
+In the outlier run the variance for the opinion difference is also quite low from **step 0 to 25**, this  indicates that while opinion memory difference is increasing on average, there is no significant difference between agents in terms of their counters.
+**There is no particular group of agents that is more strongly inclined to one particular opinion.** From this point on, the memory difference variance grows exponentialy --this corresponds to the point where one opinion won over the other and convergence towards consensus begins.
+
+```{r}
+current_run <- outlier_run
+current_run <- current_run[current_run$"step" <= 100,]
+plot.op.diff(current_run)
+
+pdf(paste("./pdf/","cp-regular-outlier-0-100-memory-diff.pdf"), width=15, height=5)
+plot.op.diff(current_run)
+dev.off()
+```
+
+```{r}
+
+current_run <- outlier_run
+plot.op.diff(current_run)
+
+pdf(paste("./pdf/","cp-regular-outlier-fullrun-memory-diff.pdf"), width=15, height=5)
+plot.op.diff(current_run)
+dev.off()
+
 ```
@@
 
-We first look at the number of convergences to total consensus in 100 simulation runs. 
+We first look at the convergence ratio in 3000 independent simulation runs. 
 ```{r results='asis',message=FALSE}
 #Read the Parameters for this experiment
-params <- read.exp.parameters(param_file_name="../data/context_permeability/scale-free_networks/param-space_2014-05-30_18:38:14experiment:1_.csv")
+params <- read.exp.parameters(param_file_name="../data/context_permeability/scale-free_networks/convergence/param-space_2014-08-01_00:47:12experiment:0_.csv")
 
 #read the adata related to consensus was achieved before 
-require(data.table)
-convergence_data <- fread("../data/context_permeability/scale-free_networks/consensus_achieved.csv")
+library(data.table)
+convergence_data <- fread("../data/context_permeability/scale-free_networks/convergence/consensus_achieved.csv")
 convergence_data <- as.data.frame(convergence_data)[,-ncol(convergence_data)]
@@
 ```{r}
-require(reshape)
-require(tables)
 
@@
 
-fcdata_table <- aggregate(data=fcdata, fcdata$value~num.networks + fcdata$network.0.d, FUN=sum)
+fcdata_table <- aggregate(data=fcdata, fcdata$value~num.networks + fcdata$network.0.d, FUN=function(x) sum(x)/length(x))
 colnames(fcdata_table) <- c("num.networks", "d", "value")
@@
 ```{r}
+params <- read.exp.parameters(param_file_name="../data/context_permeability/scale-free_networks/param-space_2014-05-30_18:38:14experiment:1_.csv")
+
 encounter_data <- fread("../data/context_permeability/scale-free_networks/num_encounters.csv")
@@
 Now to observe the distribution of the number of encounters, necessary to achieve consensus, we look at the box plots for **d = {1,2,3,4,5}**.
-We look at **configurations with a number of networks > 3** since less networks require more connectivity to allow consensus to be reached 100% of the time.
+We look at **configurations with a number of networks >= 3** which shows the best results in terms of convergence.
 
@@
 plot
+
+#print to pdf
+pdf(paste("./pdf/","context_permeability_encounters_sf.pdf"), width=7, height=5)
+plot
+dev.off()
 
@@
 
+#print to pdf
+pdf(paste("./pdf/","context_permeability_encounters_sf_best.pdf"), width=7, height=5)
 plot
+dev.off()
 
@@
 #Read the Parameters for this experiment
-params <- read.exp.parameters(param_file_name="../data/context_permeability/scale-free_regular/param-space_2014-05-30_18:40:41experiment:2_.csv")
+params <- read.exp.parameters(param_file_name="../data/context_permeability/scale-free_regular/convergence/param-space_2014-08-01_11:57:13experiment:2_.csv")
 
 #read the adata related to consensus was achieved before
-require(data.table)
+
 convergence_data <- fread("../data/context_permeability/scale-free_regular/consensus_achieved.csv")
@@
 ```{r message=FALSE}
-require(reshape)
-require(tables)
 
@@
 
-fcdata_table <- aggregate(data=fcdata, fcdata$value~network.1.d + fcdata$network.0.k, FUN=sum)
+fcdata_table <- aggregate(data=fcdata, fcdata$value~network.1.d + fcdata$network.0.k, FUN=function(x) sum(x)/length(x))
 colnames(fcdata_table) <- c("d", "k", "value")
@@
 
-This table shows the percentage of simulation runs that converged to total consensus over 100 
-independent runs.
+This table shows the ratio convergence to total consensus over 3000 simulation runs.
 
@@
 ```{r}
+params <- read.exp.parameters(param_file_name="../data/context_permeability/scale-free_regular/param-space_2014-05-30_18:40:41experiment:2_.csv")
 encounter_data <- fread("../data/context_permeability/scale-free_regular/num_encounters.csv")
@@
 fedata_table_full <- tabular(cast_fedata_table)
-
 ```
@@
 
+#print to pdf
+pdf(paste("./pdf/","context_permeability_encounters_sfreg_k12345.pdf"), width=7, height=5)
+plot
+dev.off()
+
 plot <- plot.exp.box(data=fedata_net10,x_factor=as.factor(fedata_net10$network.1.d), data_y=fedata_net10$value, fill_factor=as.factor(fedata_net10$network.0.k),fill_label="K", x_label="D", y_label="Number of Encounters")
@@
 plot
+
+#print to pdf
+pdf(paste("./pdf/","context_permeability_encounters_sfreg_k1020304050.pdf"), width=7, height=5)
+plot
+dev.off()
 ```
@@
 
+#print to pdf
+pdf(paste("./pdf/","context_permeability_encounters_sfreg_k1020304050_best.pdf"), width=7, height=5)
+plot
+dev.off()
 ```
@@
 ```{r}
-source("../R/read_network.R")
 network_data <- fread("../data/context_permeability/scale-free_regular/networks.csv")
@@
 combined_network <- k_regular_network + scale_free_network
-
 ```
@@
 plot(combined_network,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="Combined Networks")
+
+#print to pdf
+pdf(paste("./pdf/","network_properties_10regular_2scale-free.pdf"), width=15, height=5)
+par(mfrow=c(1,3))
+plot(network1,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="10-Regular Network")
+plot(network2,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="Scale-Free with D = 2")
+plot(combined_network,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="Combined Networks")
+dev.off()
 ```
@@
 plot.degree.distribution(network=combined_network, "Combined network")
+
+pdf(paste("./pdf/","network_properties_10regular_2scale-free_degree_dist.pdf"), width=15, height=5)
+par(mfrow=c(1,3))
+plot.degree.distribution(network=k_regular_network, "10-Regular Network")
+plot.degree.distribution(network=scale_free_network, "Scale-Free Network with D = 2")
+plot.degree.distribution(network=combined_network, "Combined network")
+dev.off()
 ```
@@
 ## CONVERGENCE FOR REG/SF/SF ##
-
 ```{r results='asis',message=FALSE}
@@
 #read the adata related to consensus was achieved before 
-require(data.table)
 convergence_data <- fread("../data/context_permeability/scale-free_scale-free_regular/consensus_achieved.csv")
@@
 ```{r message=FALSE}
-require(reshape)
-require(tables)
-
 #filter some things out
@@
 
-fcdata_table <- aggregate(data=fcdata, fcdata$value~network.1.d + fcdata$network.0.k, FUN=sum)
+fcdata_table <- aggregate(data=fcdata, fcdata$value~network.1.d + fcdata$network.0.k, FUN=function(x) sum(x)/length(x))
 colnames(fcdata_table) <- c("d", "k", "value")
 
- #create a pretty table for latex
+ #create a table for latex
 latex_table <- tabular(cast(fcdata_table, d~k, value="value"))
-
 ```
 
+Display the table in html and print it to a file:
 ```{r results='asis'}
@@
 
-This table shows the percentage of simulation runs that converged to total consensus over 100 
-independent runs.
+This table shows the convergence ratio to total consensus over 100 simulation runs.
 
@@
 
-#filter encounter data include only num networks > 3
+#split the data into two partitions k<=5 and k>5
 fedata_net1 <- fedata[fedata$network.0.k <= 5,]
-
 fedata_net10 <- fedata[fedata$network.0.k > 5,]
@@
 cast_fedata_table <- cast(data=fedata, formula=network.0.k~network.1.d, c(mean, sd))
-
 fedata_table_full <- tabular(cast_fedata_table)
-
 ```
 
-Create the tables
+Create the tables:
 ```{r results='asis',message=FALSE}
 #to print the table created with tabular
-
 html(fedata_table_full)
@@
 #print this to a file to use in the paper
-
 Hmisc::latex(fedata_table_full, file="tex/regular_scale-free_scale_free_encounters_full.tex",booktabs=T)
@@
 
+#print to pdf
+pdf(paste("./pdf/","context_permeability_encounters_reg_sf_sf_k12345.pdf"), width=7, height=5)
+plot
+dev.off()
+
 plot <- plot.exp.box(data=fedata_net10,x_factor=as.factor(fedata_net10$network.1.d), data_y=fedata_net10$value, fill_factor=as.factor(fedata_net10$network.0.k),fill_label="K", x_label="D", y_label="Number of Encounters")
@@
 plot
+
+pdf(paste("./pdf/","context_permeability_encounters_reg_sf_sf_k1020304050.pdf"), width=7, height=5)
+plot
+dev.off()
 ```
@@
 Focusing now on the best performing configurations and on the runs that produced a convergence in less than 50000 encounters, the distribution of the number of encounters is as follows. 
-
 ```{r}
@@
 
+pdf(paste("./pdf/","context_permeability_encounters_reg_sf_sf_best.pdf"), width=7, height=5)
+plot
+dev.off()
 ```

### 2014-08-18 analysis/context_segregation.Rmd
pre-proof-read version of the paper added; some correlation analysis added; other old analysis corrected

Context Segregation
===================
In this set of experiments, we analyse the impact of a new parameter called context tolerance in the convergence to consensus. 
In the previous experiments agents switched between networks using a __*switching probability*__. In the model of *context segregation*, agents switchich using a *segregation criteria* first--**based on a tolerance threshold**--and the same *switching probability* as follows.

At the end of each interaction an agent computes the *ratio of agents with an opposing opinion values* in its current neighbourhood. If this ratio is greater than the *threshold* defined for the current network, the agent switches to a different network immediately; if not, the agent switches using the *switching probability*.

Load the dependencies for this report.
```{r}
source("../R/experiment_utils.R")

library(data.table)
library(reshape2)
library(ggplot2)
```

# Exploring the Tolerance Threshold Span #
To explore the effect of adding the context threshold to the previous model of context switching, we fixed the **switching probability values in the values {0.25, 0.5, 0.75}** and varied the **context threshold from 0 to 1 in intervals of 0.05**.

## Tolerance Threshold Span for Regular Networks ##
In these experiments we wanted to observe the effect of the context tolerance parameter with scale-free networks. We used *2 networks*. We tested configurations with **switching probability set to 0.25 and 0.75** and **2 k-regular networks with k=5,10,30**. We adjusted the connectivity to observe the effect of the different in the clustering coefficient (and average path length although the difference in clustering coefficient for two networks is more prominent--see [network properties experiment](http://rpubs.com/davidelnunes/socsim_network_properties)).

```{r}
contour_analysis <- function(prop_name,prop_value,cs_values,encounter_data,brks){
  for(cs in cs_values){
    col <- paste("network.0.",prop_name, sep = "")
    current_data <- encounter_data[encounter_data[col] == prop_value & encounter_data$"network.0.cs" == cs,]
    melted_encounters <- melt(current_data,id.vars=c("cfg.id","run","network.0.ct","network.1.ct","network.0.cs",col), measure.vars=c("total-encounters"))

    #aggregate encounter data
    agg_encounters <- aggregate(melted_encounters$value,by=list(melted_encounters$network.0.ct,melted_encounters$network.1.ct),mean)
    colnames(agg_encounters) <- c("ct0","ct1","value")

    #breaks in the contour
    guide_title <- "Average Encounters"
    net1label <- paste("\n\nTolerance for Network 1 \n Regular Network, ",prop_name,"=",prop_value,sep="") 
    net2label <- paste("\n\nTolerance for Network 2 \n Regular Network, ",prop_name,"=",prop_value,sep="")

    encouters_contour <- create_tolerance_contour_span(span = agg_encounters, brks = brks, guide_title = guide_title,xlab=net1label, ylab=net2label)

    print(encouters_contour)
  }
}

```

# Opinion Segregation #
```{r}
#Read the Parameters for this experiment
params <- read.exp.parameters(param_file_name="../data/context_segregation/regular_networks/param-space_2014-07-25_19:46:42experiment:20_.csv")

#read data for number of encounters
encounter_data <- fread("../data/context_segregation/regular_networks/num_encounters.csv")
encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]

#merge with configuration context switching values
encounter_data <- merge(encounter_data, params[,c("cfg.id","network.0.ct","network.1.ct","network.0.cs","network.0.k")], by="cfg.id")
head(encounter_data)
```
### Regular Network with K = 5 ###

```{r}
csvalues <- c(0.25,0.5,0.75)
contour_analysis(prop_name = "k",prop_value = 5, cs_values = csvalues, encounter_data = encounter_data, brks=c(30000,50000,70000,100000,120000,180000))
```

```{r}
csvalues <- c(0.25,0.5,0.75)
contour_analysis(prop_name = "k",prop_value = 10, cs_values = csvalues, encounter_data = encounter_data, brks=c(10000,20000,40000,120000))

```

```{r}
csvalues <- c(0.25,0.5,0.75)
contour_analysis(prop_name = "k",prop_value = 30, cs_values = csvalues, encounter_data = encounter_data, brks=c(2000,4000,10000,70000))
```

```{r}
#we don't need the persp plots here for now
#reshape the data to display average number of encounters
#encounter_table <- dcast(data=melted_encounters, network.0.ct~network.1.ct, mean)

#average encounters as a matrix
#encounter_matrix <- as.matrix(encounter_table[,-1])
#colnames(encounter_matrix) <- c()

#xlab<- net1label
#ylab<- net2label
#zlab<-"\n\n\n Avg. Encounters"
#plot_persp_span(x = seq(0,1,0.05), y = seq(0,1,0.05),data_matrix = encounter_matrix, breaks=log(c(1:10)),xlab=xlab,ylab=ylab,zlab = zlab)
```

## Scale-Free Networks ##
```{r}
#Read the Parameters for this experiment
params <- read.exp.parameters(param_file_name="../data/context_segregation/scale-free_networks/param-space_2014-06-30_01:40:06experiment:20_.csv")

#read data for number of encounters
encounter_data <- fread("../data/context_segregation/scale-free_networks/num_encounters.csv")
encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
head(encounter_data)

#merge with configuration context switching values
encounter_data <- merge(encounter_data, params[,c("cfg.id","network.0.ct","network.1.ct","network.0.cs","network.0.d")], by="cfg.id")
head(encounter_data)

```
### D = 1 ###
```{r}
csvalues <- c(0.25,0.75)
contour_analysis(prop_name = "d",prop_value = 1, cs_values = csvalues, encounter_data = encounter_data, brks=c(104000,110000,120000))
```

### D = 5 ###
```{r}
csvalues <- c(0.25,0.75)
contour_analysis(prop_name = "d",prop_value = 5, cs_values = csvalues, encounter_data = encounter_data, brks=c(3000,5000,10000,20000))
```

# Conformism Segregation #
In this model we did the opposite of segregation from opposite opinions, the agents switch to avoid conformism. If the number of agents
with the same opinion rises above the tolerance threshold the agents switch to another context.

## K-Regular Networks ##
```{r}
#Read the Parameters for this experiment
params <- read.exp.parameters(param_file_name="../data/context_segregation_conformism/regular_networks/param-space_2014-07-23_20:20:09experiment:50_.csv")

#read data for number of encounters
encounter_data <- fread("../data/context_segregation_conformism/regular_networks/num_encounters.csv")
encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
head(encounter_data)

#merge with configuration context switching values
encounter_data <- merge(encounter_data, params[,c("cfg.id","network.0.ct","network.1.ct","network.0.cs","network.0.k")], by="cfg.id")
head(encounter_data)
```

### K = 5 ###
```{r}
csvalues <- c(0.25,0.5,0.75)
contour_analysis(prop_name = "k",prop_value = 5, cs_values = csvalues, encounter_data = encounter_data, brks=c(5000,10000,15000))
```

### K = 10 ###
```{r}
csvalues <- c(0.25,0.5,0.75)
contour_analysis(prop_name = "k",prop_value = 10, cs_values = csvalues, encounter_data = encounter_data, brks=c(5000,10000,15000))
```

### K = 30 ###
```{r}
csvalues <- c(0.25,0.5,0.75)
contour_analysis(prop_name = "k",prop_value = 30, cs_values = csvalues, encounter_data = encounter_data, brks=c(1500,1800,2000))
```

## Scale-Free Networks ##
```{r}
#Read the Parameters for this experiment
params <- read.exp.parameters(param_file_name="../data/context_segregation_conformism/scale-free_networks/param-space_2014-07-24_14:56:15experiment:51_.csv")

#read data for number of encounters
encounter_data <- fread("../data/context_segregation_conformism/scale-free_networks/num_encounters.csv")
encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
head(encounter_data)

#merge with configuration context switching values
encounter_data <- merge(encounter_data, params[,c("cfg.id","network.0.ct","network.1.ct","network.0.cs","network.0.d")], by="cfg.id")
head(encounter_data)

```
### D = 1 ###
```{r}
csvalues <- c(0.25,0.5,0.75)
contour_analysis(prop_name = "d",prop_value = 1, cs_values = csvalues, encounter_data = encounter_data, brks=c(20000,40000,50000,70000))
```

### D = 5 ###
```{r}
csvalues <- c(0.25,0.5,0.75)
contour_analysis(prop_name = "d",prop_value = 5, cs_values = csvalues, encounter_data = encounter_data, brks=c(2000,3000))
```

# Analysis with Multiple Networks #
We now look at the influence of multiple network by "freezing" the value of tolerance in an optimal configuration --in terms of speed of convergence. We compare the effects of having multiple networks 
for switching values of **0.25, 0.5 and 0.75**.

```{r}
params <- "../data/context_segregation/multiple-networks/regular-networks/param-space_2014-07-27_18:49:08experiment:20_.csv"

encounters <- "../data/context_segregation/multiple-networks/regular-networks/num_encounters.csv"

params <- read.exp.parameters(param_file_name=params)

encounter_data <- fread(encounters)
encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
head(encounter_data)

#merge with configuration context switching values
encounter_data <- merge(encounter_data, params[,c("cfg.id","network.0.cs","network.0.k","num.networks")], by="cfg.id")
head(encounter_data)

#melt data to use cast
melted_encounters <- melt(encounter_data,id.vars=c("cfg.id","run","network.0.cs","network.0.k","num.networks"), measure.vars=c("total-encounters"))
head(melted_encounters)
```

##K-regular networks with k = 5##
```{r}
for(cs in c(0.25,0.75)){
  #plot for 2 networks
  current_encounters<-melted_encounters[melted_encounters$"network.0.cs" == cs,]

  plot_data <- dcast(current_encounters, network.0.k + num.networks ~ variable, mean)
  colnames(plot_data) <- c("k","num-networks","avg-encounters")

  plot <- ggplot(plot_data, aes(x=as.factor(plot_data$k), y=plot_data$"avg-encounters")) 
  plot <- plot +  geom_point(aes(shape=as.factor(plot_data$"num-networks"), color=as.factor(plot_data$"num-networks")),size = 3.5)
  plot <- plot +  geom_line(aes(color=as.factor(plot_data$"num-networks"), group=as.factor(plot_data$"num-networks"), linetype=as.factor(plot_data$"num-networks")),size=1)

  plot <- plot + labs(color="Num. Networks", shape="Num. Networks", linetype="Num. Networks", y="Average Encounters", x="K",
                      title=paste("K-Regular Networks With CS =",cs))

   print(plot)
}

```

##Context Switching with Conformism Segregation##
```{r}
params <- "../data/context_segregation_conformism/multiple-networks/regular-networks/param-space_2014-07-27_18:51:59experiment:20_.csv"

encounters <- "../data/context_segregation_conformism/multiple-networks/regular-networks/num_encounters.csv"

params <- read.exp.parameters(param_file_name=params)

encounter_data <- fread(encounters)
encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
head(encounter_data)

#merge with configuration context switching values
encounter_data <- merge(encounter_data, params[,c("cfg.id","network.0.cs","network.0.k","num.networks")], by="cfg.id")
head(encounter_data)

#melt data to use cast
melted_encounters <- melt(encounter_data,id.vars=c("cfg.id","run","network.0.cs","network.0.k","num.networks"), measure.vars=c("total-encounters"))
head(melted_encounters)
```

```{r}

for(cs in c(0.25,0.5,0.75)){
  #plot for 2 networks
  current_encounters<-melted_encounters[melted_encounters$"network.0.cs" == cs,]

  plot_data <- dcast(current_encounters, network.0.k + num.networks ~ variable, mean)
  colnames(plot_data) <- c("k","num-networks","avg-encounters")

  plot <- ggplot(plot_data, aes(x=as.factor(plot_data$k), y=plot_data$"avg-encounters")) 
  plot <- plot +  geom_point(aes(shape=as.factor(plot_data$"num-networks"), color=as.factor(plot_data$"num-networks")),size = 3.5)
  plot <- plot +  geom_line(aes(color=as.factor(plot_data$"num-networks"), group=as.factor(plot_data$"num-networks"), linetype=as.factor(plot_data$"num-networks")),size=1)

  plot <- plot + labs(color="Num. Networks", shape="Num. Networks", linetype="Num. Networks", y="Average Encounters", x="K",
                      title=paste("K-Regular Networks With CS =",cs))

   print(plot)
}

```

##Context Switching with Segregation and Selective Switching##
In this model, agents keep a record of how many times they have switched from each network. The **switch to** a particular network based with a probability inversely proportional to the number of times they have switched from that network **using segregation**.

```{r}
params <- "../data/context_segregation_selective/multiple-networks/regular-networks/param-space_2014-07-27_18:58:16experiment:20_.csv"

encounters <- "../data/context_segregation_selective/multiple-networks/regular-networks/num_encounters.csv"

params <- read.exp.parameters(param_file_name=params)

encounter_data <- fread(encounters)
encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
head(encounter_data)

#merge with configuration context switching values
encounter_data <- merge(encounter_data, params[,c("cfg.id","network.0.cs","network.0.k","num.networks")], by="cfg.id")
head(encounter_data)

#melt data to use cast
melted_encounters <- melt(encounter_data,id.vars=c("cfg.id","run","network.0.cs","network.0.k","num.networks"), measure.vars=c("total-encounters"))
head(melted_encounters)
```

```{r}
for(cs in c(0.25,0.5,0.75)){
  #plot for 2 networks
  current_encounters<-melted_encounters[melted_encounters$"network.0.cs" == cs,]

  plot_data <- dcast(current_encounters, network.0.k + num.networks ~ variable, mean)
  colnames(plot_data) <- c("k","num-networks","avg-encounters")

  plot <- ggplot(plot_data, aes(x=as.factor(plot_data$k), y=plot_data$"avg-encounters")) 
  plot <- plot +  geom_point(aes(shape=as.factor(plot_data$"num-networks"), color=as.factor(plot_data$"num-networks")),size = 3.5)
  plot <- plot +  geom_line(aes(color=as.factor(plot_data$"num-networks"), group=as.factor(plot_data$"num-networks"), linetype=as.factor(plot_data$"num-networks")),size=1)

  plot <- plot + labs(color="Num. Networks", shape="Num. Networks", linetype="Num. Networks", y="Average Encounters", x="K",
                      title=paste("K-Regular Networks With CS =",cs))

   print(plot)
}

```

### 2014-08-18 analysis/context_segregation_selective.Rmd
pre-proof-read version of the paper added; some correlation analysis added; other old analysis corrected

Context Segregation With Selective Neighbourhoods
=================================================

```{r}
contour_analysis <- function(prop_name,prop_value,cs_values,encounter_data,brks){
  for(cs in cs_values){
    col <- paste("network.0.",prop_name, sep = "")
    current_data <- encounter_data[encounter_data[col] == prop_value & encounter_data$"network.0.cs" == cs,]
    melted_encounters <- melt(current_data,id.vars=c("cfg.id","run","network.0.ct","network.1.ct","network.0.cs",col), measure.vars=c("total-encounters"))

    #aggregate encounter data
    agg_encounters <- aggregate(melted_encounters$value,by=list(melted_encounters$network.0.ct,melted_encounters$network.1.ct),mean)
    colnames(agg_encounters) <- c("ct0","ct1","value")

    #breaks in the contour
    guide_title <- "Average Encounters"
    net1label <- paste("\n\nTolerance for Network 1 \n Regular Network, ",prop_name,"=",prop_value,sep="") 
    net2label <- paste("\n\nTolerance for Network 2 \n Regular Network, ",prop_name,"=",prop_value,sep="")

    encouters_contour <- create_tolerance_contour_span(span = agg_encounters, brks = brks, guide_title = guide_title,xlab=net1label, ylab=net2label)

    print(encouters_contour)
  }
}

```

# Opinion Segregation #
```{r}
#load some utilities
source("../R/experiment_utils.R")
#Read the Parameters for this experiment
params <- read.exp.parameters(param_file_name="../data/context_segregation_selective/regular_networks/regular_networks_5/param-space_2014-07-26_16:13:32experiment:20_.csv")

#read data for number of encounters

require(data.table)

encounter_data <- fread("../data/context_segregation_selective/regular_networks/regular_networks_5/num_encounters.csv")
encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
head(encounter_data)

#merge with configuration context switching values
require(reshape2)
encounter_data <- merge(encounter_data, params[,c("cfg.id","network.0.ct","network.1.ct","network.0.cs","network.0.k")], by="cfg.id")
head(encounter_data)
```
### Regular Network with K = 5 ###

```{r}
csvalues <- c(0.25,0.75)
contour_analysis(prop_name = "k",prop_value = 5, cs_values = csvalues, encounter_data = encounter_data, brks=c(30000,50000,70000,100000,120000,180000))
```

### Regular Networks with K = 10 ###
```{r}
#Read the Parameters for this experiment
params <- read.exp.parameters(param_file_name="../data/context_segregation_selective/regular_networks/regular_networks_10/param-space_2014-07-26_21:24:37experiment:20_.csv")

#read data for number of encounters

require(data.table)

encounter_data <- fread("../data/context_segregation_selective/regular_networks/regular_networks_10/num_encounters.csv")
encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
head(encounter_data)

#merge with configuration context switching values
require(reshape2)
encounter_data <- merge(encounter_data, params[,c("cfg.id","network.0.ct","network.1.ct","network.0.cs","network.0.k")], by="cfg.id")
head(encounter_data)
```

```{r}
csvalues <- c(0.25,0.75)
contour_analysis(prop_name = "k",prop_value = 10, cs_values = csvalues, encounter_data = encounter_data, brks=c(10000,20000,40000,120000))

```

### 2014-08-18 analysis/context_switching.Rmd
pre-proof-read version of the paper added; some correlation analysis added; other old analysis corrected

@@
 =================
-
 In this set of experiments we analyse a new multi-context model with a binary opinion dynamics game.
@@
 
-We then freeze the switching probabilities and vary the number of networks.
-We compare the results with the context permeability in terms of percentage of convergences to consensus and average number of encounters.
+We then freeze the switching probabilities and vary the number of networks. We compare the results with the context permeability in terms of average number of encounters to achieve consensus.
+
+We will start by loading the dependencies for this report.
+```{r}
+source("../R/experiment_utils.R")
+
+library(data.table)
+library(reshape2)
+library(ggplot2)
+
+```
 
@@
 
-The analysis for each context switching probability span is as follows: 
+We will use the following procedures to construct the contour plots and perspective "3D" plots.
 ```{r load-parameters}
 analyse_contour <- function(paramfile, encountersfile, net1label, net2label){
-  #load some utilities
-source("../R/experiment_utils.R")
-
   #Read the Parameters for this experiment
@@
   #read data for number of encounters
-
-require(data.table)
-
   encounter_data <- fread(encountersfile)
   encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
-head(encounter_data)
 
   #merge with configuration context switching values
-require(reshape2)
   encounter_data <- merge(encounter_data, params[,c("cfg.id","network.0.cs","network.1.cs")], by="cfg.id")
-head(encounter_data)
 
@@
   melted_encounters <- melt(encounter_data,id.vars=c("cfg.id","run","network.0.cs","network.1.cs"), measure.vars=c("total-encounters"))
-head(melted_encounters)
 
@@
 }
+```
 
+```{r}
 analyse_persp <- function(paramfile, encountersfile,output_prefix,net1label,net2label){
-    #load some utilities
-source("../R/experiment_utils.R")
-
   #Read the Parameters for this experiment
@@
   #read data for number of encounters
-
-require(data.table)
-
   encounter_data <- fread(encountersfile)
   encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
-head(encounter_data)
 
   #merge with configuration context switching values 
-require(reshape2)
   encounter_data <- merge(encounter_data, params[,c("cfg.id","network.0.cs","network.1.cs")], by="cfg.id")
-head(encounter_data)
 
@@
   melted_encounters <- melt(encounter_data,id.vars=c("cfg.id","run","network.0.cs","network.1.cs"), measure.vars=c("total-encounters"))
-head(melted_encounters)
+
   #reshape the data to display average number of encounters
@@
 }
+
 ```
@@
 
-**Note** I don't need custom breaks for the **persp plots**, its simpler to apply a logarithm to a set of n numbers, normalize them inside the plotting function, and multiply this by the maximum value in the dataset, this gets me the effect I'm looking for both the filling and contour lines.
+**Note** I don't need custom breaks for some **persp plots**, its simpler to apply a logarithm to a set of n numbers, normalize them inside the plotting function, and multiply this by the maximum value in the dataset, this gets me the effect I'm looking for both the filling and contour lines.
 
@@
 
+### Scale-Free Network with D=5 and Scale-free Network with D=1 ###
+
+```{r}
+params <- "../data/context_switching/switching_span/scale-free d=1 scale-free d=5/param-space_2014-07-22_20:33:49experiment:12_.csv"
+encounters <- "../data/context_switching/switching_span/scale-free d=1 scale-free d=5/num_encounters.csv"
+output_prefix <- "context_switching_sf_d5_d1"
+
+net1label <- "\n\nSwitching for Network 1 \n scale-free network, d=5"
+net2label <- "\n\nSwitching for Network 2 \n scale-free network, d=1"
+
+analyse_contour(params, encounters,net1label,net2label)
+```
+
+```{r fig.width=15}
+analyse_persp(params, encounters,output_prefix,net1label,net2label)
+```
+
 ###1 10-Regular + 1 Scale-Free with D=1###
@@
 
-analyse_contour(params, encounters,net1label,net2label)
+analyse_contour(params,encounters,net1label,net2label)
 ```
@@
 #**************************************************************************
-params <- "../data/context_permeability/regular_networks/param-space_2014-05-30_16:47:53experiment:0_.csv"
+params <- "../data/context_permeability/regular_networks/param-space_2014-07-23_11:40:44experiment:0_.csv"
 encounters <- "../data/context_permeability/regular_networks/num_encounters.csv"
@@
 
-require(data.table)
-
 encounter_data <- fread(encounters)
@@
 #merge with configuration context switching values
-require(reshape2)
 encounter_data <- merge(encounter_data, params[,c("cfg.id","network.0.k","num.networks")], by="cfg.id")
@@
 permeability_encounters <- melted_encounters
+```
 
+Now we get the data for the k-regular networks with homogenous values of switching probability (the same probability in all the networks). --We have seen previously that for less connected networks 
+simetry helps with the convergence: as such we take 0.25 0.5 and 0.75 as switching probabilities representing low, medium, and high switching respectively. 
+```{r}
 #***************************************************************
@@
 #merge with configuration context switching values
-require(reshape2)
 encounter_data <- merge(encounter_data, params[,c("cfg.id","network.0.cs","network.0.k","num.networks")], by="cfg.id")
@@
 
+  #export to pdf
+  pdf(paste("./pdf/"," context_switching_encounters_comp_kregular_groupedbynets_",n,".pdf",sep = ""), width=7, height=5)
+  print(plot)
+  dev.off()
+
 }
@@
 
-  #gets too messy with permeability data 
-  #perm_data <- dcast(perm_encounters, network.0.k + num.networks ~ variable, mean)
-  #colnames(perm_data) <- c("k","num-networks", "avg-encounters")
-
   plot <- ggplot(plot_data, aes(x=as.factor(plot_data$k), y=plot_data$"avg-encounters")) 
@@
   plot <- plot +  geom_line(aes(color=as.factor(plot_data$"num-networks"), group=as.factor(plot_data$"num-networks"), linetype=as.factor(plot_data$"num-networks")),size=1)
-
-  #add line for permeability
-  #plot <- plot +  geom_point(data=perm_data, aes(x=as.factor(perm_data$k), y=perm_data$"avg-encounters", shape="permeability", color=as.factor(perm_data$"num-networks")),size = 3.5)
-  #plot +  geom_line(data=perm_data, aes(x=as.factor(perm_data$k), y=perm_data$"avg-encounters",group=as.factor(perm_data$"num-networks"),linetype=as.factor(plot_data$"num-networks"),color=as.factor(perm_data$"num-networks")),size=1)
 
@@
    print(plot)
+
+  pdf(paste("./pdf/"," context_switching_encounters_comp_kregular_groupedbycs_",cs,".pdf",sep=""), width=7, height=5)
+  print(plot)
+  dev.off()
+}
+gc()
+```
+
+## Comparison for Scale-Free Networks ##
+
+First, we get the permeability results for scale-free networks for comparison.
+```{r}
+#**************************************************************************
+#   read encounter results for context permeability (for comparison)
+#**************************************************************************
+params <- "../data/context_permeability/scale-free_networks/param-space_2014-05-30_18:38:14experiment:1_.csv"
+encounters <- "../data/context_permeability/scale-free_networks/num_encounters.csv"
+
+params <- read.exp.parameters(param_file_name=params)
+
+encounter_data <- fread(encounters)
+encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
+#merge with configuration context switching values
+encounter_data <- merge(encounter_data, params[,c("cfg.id","network.0.d","num.networks")], by="cfg.id")
+head(encounter_data)
+#melt data to use cast
+melted_encounters <- melt(encounter_data,id.vars=c("cfg.id","run","network.0.d","num.networks"), measure.vars=c("total-encounters"))
+head(melted_encounters)
+permeability_encounters <- melted_encounters
+```
+
+We now create the plots to compare scale-free networks with context permeability. 
+```{r}
+#***************************************************************
+#   read encounter results for context switching
+#***************************************************************
+params <- "../data/context_switching/multiple_networks/scale-free_networks/param-space_2014-06-22_00:30:57experiment:10_.csv"
+
+encounters <- "../data/context_switching/multiple_networks/scale-free_networks/num_encounters.csv"
+
+params <- read.exp.parameters(param_file_name=params)
+
+encounter_data <- fread(encounters)
+encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
+head(encounter_data)
+
+#merge with configuration context switching values
+encounter_data <- merge(encounter_data, params[,c("cfg.id","network.0.cs","network.0.d","num.networks")], by="cfg.id")
+head(encounter_data)
+
+#melt data to use cast
+melted_encounters <- melt(encounter_data,id.vars=c("cfg.id","run","network.0.cs","network.0.d","num.networks"), measure.vars=c("total-encounters"))
+head(melted_encounters)
+
+```
+
+```{r}
+for(n in 2:5){
+  #plot for 2 networks
+  current_encounters<-melted_encounters[melted_encounters$"num.networks" == n,]
+  perm_encounters<-permeability_encounters[permeability_encounters$"num.networks" == n,]
+
+  plot_data <- dcast(current_encounters, network.0.d + network.0.cs ~ variable, mean)
+  colnames(plot_data) <- c("d","cs","avg-encounters")
+
+  perm_data <- dcast(perm_encounters, network.0.d ~ variable, mean)
+  colnames(perm_data) <- c("d","avg-encounters")
+
+  plot <- NULL
+
+  plot <- ggplot(plot_data, aes(x=as.factor(plot_data$d), y=plot_data$"avg-encounters")) 
+  plot <- plot +  geom_point(aes(shape=as.factor(plot_data$cs), color=as.factor(plot_data$cs)),size = 3.5)
+  plot <- plot +  geom_line(aes(color=as.factor(plot_data$cs), group=as.factor(plot_data$cs), linetype=as.factor(plot_data$cs)),size=1)   
+  #add line for permeability baseline
+  plot <- plot + geom_point(data=perm_data, aes(x=as.factor(perm_data$d), y=perm_data$"avg-encounters", shape="permeability", color="permeability"),size = 3.5)
+  plot <- plot + geom_line(data=perm_data, aes(x=as.factor(perm_data$d), y=perm_data$"avg-encounters", group="Permeability", linetype="permeability", color="permeability"),size=1)
+
+  plot <- plot + labs(color="CS", shape="CS", linetype="CS", y="Average Encounters", x="D",
+                       title=paste("Scale-Free Networks With Number of Networks =",n))
+
+  print(plot)
+
+  pdf(paste("./pdf/"," context_switching_encounters_comp_sf_groupedbynets_",n,".pdf", sep=""), width=7, height=5)
+  print(plot)
+  dev.off()
+
 }
@@
 ```
+
+```{r}
+
+for(cs in c(0.25,0.5,0.75)){
+  #plot for 2 networks
+  current_encounters<-melted_encounters[melted_encounters$"network.0.cs" == cs,]
+  #perm_encounters<-permeability_encounters[permeability_encounters$"num.networks" > 1,]
+
+  plot_data <- dcast(current_encounters, network.0.d + num.networks ~ variable, mean)
+  colnames(plot_data) <- c("d","num-networks","avg-encounters")
+
+  plot <- ggplot(plot_data, aes(x=as.factor(plot_data$d), y=plot_data$"avg-encounters")) 
+  plot <- plot +  geom_point(aes(shape=as.factor(plot_data$"num-networks"), color=as.factor(plot_data$"num-networks")),size = 3.5)
+  plot <- plot +  geom_line(aes(color=as.factor(plot_data$"num-networks"), group=as.factor(plot_data$"num-networks"), linetype=as.factor(plot_data$"num-networks")),size=1)
+
+  plot <- plot + labs(color="Num. Networks", shape="Num. Networks", linetype="Num. Networks", y="Average Encounters", x="D",
+                      title=paste("Scale-Free Networks With CS =",cs))
+
+   print(plot)
+
+  pdf(paste("./pdf/"," context_switching_encounters_comp_sf_groupedbycs_",cs,".pdf",sep=""), width=7, height=5)
+  print(plot)
+  dev.off()
+}
+gc()
+
+```

### 2014-08-18 analysis/correlation_test.Rmd
pre-proof-read version of the paper added; some correlation analysis added; other old analysis corrected

Context Permeability Convergence Correlation
============================================
In this report we will do a quick analysis of the correlation between simulation convergence and 
network properties. We will compute the **pearman's rank correlation coefficient** to analyse our data.

```{r}
source("../R/experiment_utils.R")
library(reshape)
library(reshape2)
library(data.table)

# Correlations with significance levels
library(Hmisc)

```

## K-Regular Networks ##
```{r}
#read the network properties
props <- read.table(file="../data/context_permeability/regular_networks/network_properties.csv", sep = ",", header = T)
head(props)

apl_data <- melt(props, id=c("k","networks","run"),measure.vars=c("average.path.length"))
clustering_data <- melt(props, id=c("k","networks","run"),measure.vars=c("clustering.coefficient"))

average_apl_data <- dcast(apl_data, k + networks ~ variable, mean)
average_clustering_data <- dcast(clustering_data, k + networks ~ variable, mean)
head(average_apl_data)
head(average_clustering_data)

#read the convergence data
params <- read.exp.parameters(param_file_name="../data/context_permeability/regular_networks/convergence/param-space_2014-08-01_00:09:09experiment:0_.csv")

#read the adata related to consensus was achieved before

convergence_data <- fread("../data/context_permeability/regular_networks/convergence/consensus_achieved.csv")
convergence_data <- as.data.frame(convergence_data)[,-ncol(convergence_data)]
convergence_data <- merge(convergence_data, params, by="cfg.id")

convergence_data <- melt(convergence_data,id.vars=c("cfg.id","run","num.networks","network.0.k"), measure.vars=c("consensus-achieved"))

convergence_data <- aggregate(data=convergence_data, convergence_data$value~convergence_data$num.networks + convergence_data$network.0.k, FUN=function(x) sum(x)/length(x)*100 )

colnames(convergence_data) <- c("networks", "k", "convergence")
head(convergence_data)

table <- cast(convergence_data, networks~k, value="convergence")
latex_table <- tabular.cast_df(table)

full_data <- merge(convergence_data,average_apl_data, by=c("networks","k"))
full_data <- merge(full_data, average_clustering_data, by=c("networks","k"))
head(full_data)
```

```{r}
pairs(full_data)

#Spearman's correlation applies to ranks and so provides a measure of a monotonic relationship between two continuous random variables. It is also useful with ordinal data and is robust to outliers (unlike Pearson's correlation).
apl_test <- cor.test(normal.range(full_data$convergence), normal.range(full_data$average.path.length), type="spearman", conf.level = 0.95)
library(ggplot2)
clustering_test <- cor.test(normal.range(full_data$convergence), normal.range(full_data$clustering.coefficient), type="spearman", conf.level = 0.95)
qplot(normal.range(full_data$convergence), normal.range(full_data$average.path.length)) +xlab("Convergence Ratio") + ylab("Normalised Average Path Length")

apl_test
clustering_test
```

## Scale-free Networks ##
```{r}
#read the network properties
props <- read.table(file="../data/context_permeability/scale-free_networks/network_properties.csv", sep = ",", header = T)
head(props)

apl_data <- melt(props, id=c("d","networks","run"),measure.vars=c("average.path.length"))
clustering_data <- melt(props, id=c("d","networks","run"),measure.vars=c("clustering.coefficient"))

average_apl_data <- dcast(apl_data, d + networks ~ variable, mean)
average_clustering_data <- dcast(clustering_data, d + networks ~ variable, mean)
head(average_apl_data)
head(average_clustering_data)

#read the convergence data
params <- read.exp.parameters(param_file_name="../data/context_permeability/scale-free_networks/convergence/param-space_2014-08-01_00:47:12experiment:0_.csv")

#read the adata related to consensus was achieved before

convergence_data <- fread("../data/context_permeability/scale-free_networks/convergence/consensus_achieved.csv")
convergence_data <- as.data.frame(convergence_data)[,-ncol(convergence_data)]
convergence_data <- merge(convergence_data, params, by="cfg.id")

convergence_data <- melt(convergence_data,id.vars=c("cfg.id","run","num.networks","network.0.d"), measure.vars=c("consensus-achieved"))
convergence_data <- aggregate(data=convergence_data, convergence_data$value~convergence_data$num.networks + convergence_data$network.0.d, FUN=function(x) sum(x)/length(x)*100)
colnames(convergence_data) <- c("networks", "d", "convergence")
head(convergence_data)

full_data <- merge(convergence_data,average_apl_data, by=c("networks","d"))
full_data <- merge(full_data, average_clustering_data, by=c("networks","d"))
head(full_data)
```

```{r}
pairs(full_data)

#Spearman's correlation applies to ranks and so provides a measure of a monotonic relationship between two continuous random variables. It is also useful with ordinal data and is robust to outliers (unlike Pearson's correlation).
apl_test <- cor.test(normal.range(full_data$convergence), normal.range(full_data$average.path.length), type="spearman",conf.level = 0.95)
library(ggplot2)
clustering_test <- cor.test(normal.range(full_data$convergence), normal.range(full_data$clustering.coefficient), type="spearman",conf.level = 0.95)
qplot(normal.range(full_data$convergence), normal.range(full_data$average.path.length)) +xlab("Convergence Ratio") + ylab("Normalised Average Path Length")

apl_test
clustering_test
```

### 2014-08-18 analysis/network_properties.Rmd
pre-proof-read version of the paper added; some correlation analysis added; other old analysis corrected

@@
 networks display when they are merged.
+
+Load the dependencies for this report.
+```{r}
+source("../R/experiment_utils.R")
+source("../R/network.utils.R")
+
+library(stargazer)
+library(reshape2)
+library(ggplot2)
+
+library(bigmemory)
+library(parallel)
+#to create a progress bar 
+library(BBmisc)
+
+```
 
@@
 ```{r results='asis',echo=FALSE}
-source("../R/experiment_utils.R")
-
 #shows the k values explored and the number of networks
-params <- read.exp.parameters("../data/context_permeability/regular_networks/param-space_2014-05-30_16:47:53experiment:0_.csv")
+params <- read.exp.parameters("../data/context_permeability/regular_networks/param-space_2014-07-23_11:40:44experiment:0_.csv")
 params <- params[,c("cfg.id","num.networks","network.0.k")]
@@
 
-require(stargazer)
 stargazer(t(k_values), type="html", summary = FALSE)
@@
 ```{r message=FALSE}
-source("../R/network.utils.R")
-require(bigmemory)
 network_data <- read.big.matrix(filename="../data/context_permeability/regular_networks/networks.csv", header=T, sep=";")
@@
 
+plot(network1,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="10-Regular 1")
+plot(network2,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="10-Regular 2")
+plot(combined_network,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="Combined 10-Regulars")
+
+#print to pdf
+pdf(paste("./pdf/","network_properties_merge_2_10regular.pdf"), width=15, height=5)
 par(mfrow=c(1,3))
@@
 plot(combined_network,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="Combined 10-Regulars")
+dev.off()
 
@@
 
+#print to report
 par(mfrow=c(1,1))
 plot(network_k_20,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="K-Regular with K=20")
+
+#print to pdf
+
+pdf(paste("./pdf/","network_properties_1_20regular.pdf"), width=7, height=5)
+par(mfrow=c(1,1))
+plot(network_k_20,vertex.size = 2, vertex.label=NA, layout =   layout.kamada.kawai, main="K-Regular with K=20")
+dev.off()
+
 ```
@@
 
-require(stargazer)
 stargazer(netprop.table, type="html", summary = FALSE)
@@
 #Collect the network data and create a data table to hold the network properties
-require(parallel)
 
@@
 
-require(BBmisc)#for progress bar
 pb <- makeProgressBar(min=0, max=(length(num_networks)*length(k_values)), label="network analysis")
@@
 
-require(ggplot2)
+#save this for later use
+write.table(props, "../data/context_permeability/regular_networks/network_properties.csv", quote = FALSE, sep = ",", row.names = FALSE)
 
@@
 plot <- plot + labs(fill="K", y="Average Path Length", x="Number of Networks")
+
+#print to report
 plot
+
+#print to pdf
+pdf(paste("./pdf/","network_properties_apl_kreg_12345.pdf"), width=7, height=5)
+par(mfrow=c(1,1))
+plot 
+dev.off()
 
@@
 
+#print to pdf
+pdf(paste("./pdf/","network_properties_apl_kreg_1020304050.pdf"), width=7, height=5)
+par(mfrow=c(1,1))
+plot 
+dev.off()
+
 #create clustering coefficient box plots for k = 1,2,3,4,5
@@
 
+#print to pdf
+pdf(paste("./pdf/","network_properties_cc_kreg_12345.pdf"), width=7, height=5)
+par(mfrow=c(1,1))
+plot 
+dev.off()
+
 #create clustering coefficient box plots for k = 10,20,30,40,50
@@
 plot
+
+#print to pdf
+pdf(paste("./pdf/","network_properties_cc_kreg_1020304050.pdf"), width=7, height=5)
+par(mfrow=c(1,1))
+plot 
+dev.off()
 ```
@@
 #aggregate run data by k and networks
-require(reshape2)
-
 apl_data <- melt(props, id=c("k","networks","run"),measure.vars=c("average-path-length"))
@@
 plot <- plot +  geom_line(aes(color=as.factor(net_props$k), group=as.factor(net_props$k), linetype=as.factor(net_props$k)),size=1)   
-plot <- plot + labs(color="K", shape="K", linetype="K", y="Average Path Length", x="Number of Networks")
+plot <- plot + labs(color="K", shape="K", linetype="K", y="Average of Average Path Length", x="Number of Networks")
 plot
+
+#print to pdf
+pdf(paste("./pdf/","network_properties_apl_line_kreg_12345.pdf"), width=7, height=5)
+par(mfrow=c(1,1))
+plot 
+dev.off()
 
@@
 plot <- plot +  geom_line(aes(color=as.factor(net_props$k), group=as.factor(net_props$k), linetype=as.factor(net_props$k)),size=1)   
-plot <- plot + labs(color="K", shape="K", linetype="K", y="Average Path Length", x="Number of Networks")
+plot <- plot + labs(color="K", shape="K", linetype="K", y="Average of Average Path Length", x="Number of Networks")
 plot
+
+#print to pdf
+pdf(paste("./pdf/","network_properties_apl_line_kreg_1020304050.pdf"), width=7, height=5)
+par(mfrow=c(1,1))
+plot 
+dev.off()
 
@@
 plot <- plot +  geom_line(aes(color=as.factor(net_props$k), group=as.factor(net_props$k), linetype=as.factor(net_props$k)),size=1)   
-plot <- plot + labs(color="K", shape="K", linetype="K", y="Clustering Coefficient", x="Number of Networks")
+plot <- plot + labs(color="K", shape="K", linetype="K", y="Average of Clustering Coefficient", x="Number of Networks")
 plot
+
+#print to pdf
+pdf(paste("./pdf/","network_properties_cc_line_kreg_12345.pdf"), width=7, height=5)
+par(mfrow=c(1,1))
+plot 
+dev.off()
 
@@
 plot <- plot +  geom_line(aes(color=as.factor(net_props$k), group=as.factor(net_props$k), linetype=as.factor(net_props$k)),size=1)   
-plot <- plot + labs(color="K", shape="K", linetype="K", y="Clustering Coefficient", x="Number of Networks")
+plot <- plot + labs(color="K", shape="K", linetype="K", y="Average of Clustering Coefficient", x="Number of Networks")
 plot
+
+#print to pdf
+pdf(paste("./pdf/","network_properties_cc_line_kreg_1020304050.pdf"), width=7, height=5)
+par(mfrow=c(1,1))
+plot 
+dev.off()
 
@@
 #read the network data
-require(bigmemory)
 network_data <- read.big.matrix(filename="../data/context_permeability/scale-free_networks/networks.csv", header=T, sep=";")
@@
 #Collect the network data and create a data table to hold the network properties
-require(parallel)
-
 ## Number of workers (R processes) to use:
@@
 
-require(BBmisc)#for progress bar
 pb <- makeProgressBar(min=0, max=(length(num_networks)*length(d_values)), label="network analysis")
@@
 props <- as.data.frame(props)
-
-require(ggplot2)
+#save this for later use
+write.table(props, "../data/context_permeability/scale-free_networks/network_properties.csv", quote = FALSE, sep = ",", row.names = FALSE)
 
@@
 
+#print to pdf
+pdf(paste("./pdf/","network_properties_apl_sf_12345.pdf"), width=7, height=5)
+par(mfrow=c(1,1))
+plot 
+dev.off()
+
 #create clustering coefficient box plots for d = 1,2,3,4,5
@@
 plot
+
+#print to pdf
+pdf(paste("./pdf/","network_properties_cc_sf_12345.pdf"), width=7, height=5)
+par(mfrow=c(1,1))
+plot 
+dev.off()
 ```
@@
 #aggregate run data by k and networks
-require(reshape2)
-
 apl_data <- melt(props, id=c("d","networks","run"),measure.vars=c("average-path-length"))
@@
 plot <- plot +  geom_line(aes(color=as.factor(net_props$d), group=as.factor(net_props$d), linetype=as.factor(net_props$d)),size=1)   
-plot <- plot + labs(color="D", shape="D", linetype="D", y="Average Path Length", x="Number of Networks")
+plot <- plot + labs(color="D", shape="D", linetype="D", y="Average of Average Path Length", x="Number of Networks")
 plot
+
+#print to pdf
+pdf(paste("./pdf/","network_properties_apl_line_sf_12345.pdf"), width=7, height=5)
+par(mfrow=c(1,1))
+plot 
+dev.off()
 
@@
 plot <- plot +  geom_line(aes(color=as.factor(net_props$d), group=as.factor(net_props$d), linetype=as.factor(net_props$d)),size=1)   
-plot <- plot + labs(color="D", shape="D", linetype="D", y="Clustering Coefficient", x="Number of Networks")
+plot <- plot + labs(color="D", shape="D", linetype="D", y="Average of Clustering Coefficient", x="Number of Networks")
 plot
+
+#print to pdf
+pdf(paste("./pdf/","network_properties_cc_line_sf_12345.pdf"), width=7, height=5)
+par(mfrow=c(1,1))
+plot 
+dev.off()
 
@@
 ```
+
+#Properties for Scale-free + Regular Configuration#
+
+```{r}
+#shows the d values explored and the number of networks
+params <- read.exp.parameters("../data/context_permeability/scale-free_regular/param-space_2014-05-30_18:40:41experiment:2_.csv")
+params <- params[,c("cfg.id","network.0.k","network.1.d")]
+
+#read the network data
+network_data <- read.big.matrix(filename="../data/context_permeability/scale-free_regular/networks.csv", header=T, sep=";")
+
+#Collect the network data and create a data table to hold the network properties
+## Number of workers (R processes) to use:
+numWorkers <- 8
+
+measure_parallel <- function(cfg,r){
+  data <- network_data
+  network <- read.big.network(data,cfg,r)
+  properties <- measure.network(network)
+  properties <- cbind(r,properties)
+  return(properties)
+}
+
+props <- NULL
+
+k_values <- c(1:5,seq(10,50,10))
+d_values <- c(1,2,3,4,5)
+
+runs <- sort(unique(network_data[,"run"]))
+
+pb <- makeProgressBar(min=0, max=(length(k_values)*length(d_values)), label="network analysis")
+
+#pre-alocate a matrix for the network properties
+props <- matrix(nrow=(length(k_values)*length(d_values)*length(runs)), ncol=7)
+i <- 0
+
+for(k in k_values){
+  #reads the properties for all the k-regular networks with the given k and num_networks 
+  for(d in d_values){
+    cfg <- params[params$"network.0.k" == k & params$"network.1.d" == d,][[1]]
+
+    properties <- mcmapply(cfg=cfg, r=runs, measure_parallel, mc.cores = numWorkers)
+    properties <- t(properties)
+
+    props[(i+1):(i+100),] <- cbind(d,k,properties)
+    i <- i + 100  
+    #some progress feddback
+    pb$inc(1,paste("reading k=",k,"d=",d,"\n"))
+    gc()
+  } 
+}
+pb$kill()
+
+colnames(props)<-c("d","k","run","nodes","edges","clustering-coefficient","average-path-length")
+
+#clean up
+rm(pb)
+gc()
+
+props <- as.data.frame(props)
+
+#save this for later use
+write.table(props, "../data/context_permeability/scale-free_regular/network_properties.csv", quote = FALSE, sep = ",", row.names = FALSE, append=FALSE)
+
+#props <- read.table("../data/context_permeability/scale-free_regular/network_properties.csv", sep = ",", header = T)
+
+#create average path length box plots for k = 1,2,3,4,5
+net_props <- props[props$k <= 5,]
+
+plot <- plot <- ggplot(net_props, aes(x=as.factor(net_props$d), y=net_props$"average-path-length",fill=as.factor(net_props$k)) ) 
+plot <- plot + geom_boxplot()
+plot <- plot + labs(fill="K", y="Average Path Length", x="D")
+
+#print to report
+plot
+
+pdf(paste("./pdf/","network_properties_apl_sf_kregular_12345.pdf"), width=7, height=5)
+plot
+dev.off()
+
+net_props <- props[props$k >5,]
+
+plot <- plot <- ggplot(net_props, aes(x=as.factor(net_props$d), y=net_props$"average-path-length",fill=as.factor(net_props$k)) ) 
+plot <- plot + geom_boxplot()
+plot <- plot + labs(fill="K", y="Average Path Length", x="D")
+
+#print to report
+plot
+
+pdf(paste("./pdf/","network_properties_apl_sf_kregular_1020304050.pdf"), width=7, height=5)
+plot
+dev.off()
+
+```
+
+Create box plots for clustering coefficient
+```{r}
+#create average path length box plots for k = 1,2,3,4,5
+net_props <- props[props$k <= 5,]
+
+plot <- plot <- ggplot(net_props, aes(x=as.factor(net_props$d), y=net_props$"clustering-coefficient",fill=as.factor(net_props$k)) ) 
+plot <- plot + geom_boxplot()
+plot <- plot + labs(fill="K", y="Clustering Coefficient", x="D")
+
+#print to report
+plot
+
+pdf(paste("./pdf/","network_properties_cc_sf_kregular_12345.pdf"), width=7, height=5)
+plot
+dev.off()
+
+net_props <- props[props$k >5,]
+
+plot <- plot <- ggplot(net_props, aes(x=as.factor(net_props$d), y=net_props$"clustering-coefficient",fill=as.factor(net_props$k)) ) 
+plot <- plot + geom_boxplot()
+plot <- plot + labs(fill="K", y="Clustering Coefficient", x="D")
+
+#print to report
+plot
+
+pdf(paste("./pdf/","network_properties_cc_sf_kregular_1020304050.pdf"), width=7, height=5)
+plot
+dev.off()
+
+```
+
+```{r}
+#aggregate run data by k and networks
+apl_data <- melt(props, id=c("k","d","run"),measure.vars=c("average-path-length"))
+clustering_data <- melt(props, id=c("k","d","run"),measure.vars=c("clustering-coefficient"))
+
+average_apl_data <- dcast(apl_data, k + d ~ variable, mean)
+average_clustering_data <- dcast(clustering_data, k + d ~ variable, mean)
+
+#plot average path length for k = 1,2,3,4,5
+net_props <- average_apl_data[average_apl_data$"k" <= 5,]
+plot <- ggplot(net_props, aes(x=as.factor(net_props$d), y=net_props$"average-path-length",)) 
+plot <- plot +  geom_point(aes(shape=as.factor(net_props$k), color=as.factor(net_props$k)),size = 3.5)
+plot <- plot +  geom_line(aes(color=as.factor(net_props$k), group=as.factor(net_props$k), linetype=as.factor(net_props$k)),size=1)   
+plot <- plot + labs(color="K", shape="K", linetype="K", y="Average of Average Path Length", x="D")
+plot
+
+#print to pdf
+pdf(paste("./pdf/","network_properties_apl_line_sf_kreg_12345.pdf"), width=7, height=5)
+par(mfrow=c(1,1))
+plot 
+dev.off()
+
+net_props <- average_apl_data[average_apl_data$"k" > 5,]
+plot <- ggplot(net_props, aes(x=as.factor(net_props$d), y=net_props$"average-path-length",)) 
+plot <- plot +  geom_point(aes(shape=as.factor(net_props$k), color=as.factor(net_props$k)),size = 3.5)
+plot <- plot +  geom_line(aes(color=as.factor(net_props$k), group=as.factor(net_props$k), linetype=as.factor(net_props$k)),size=1)   
+plot <- plot + labs(color="K", shape="K", linetype="K", y="Average of Average Path Length", x="D")
+plot
+
+#print to pdf
+pdf(paste("./pdf/","network_properties_apl_line_sf_kreg_1020304050.pdf"), width=7, height=5)
+par(mfrow=c(1,1))
+plot 
+dev.off()
+
+```
+
+```{r}
+#plot average path length for k = 1,2,3,4,5
+net_props <- average_clustering_data[average_clustering_data$"k" <= 5,]
+plot <- ggplot(net_props, aes(x=as.factor(net_props$d), y=net_props$"clustering-coefficient",)) 
+plot <- plot +  geom_point(aes(shape=as.factor(net_props$k), color=as.factor(net_props$k)),size = 3.5)
+plot <- plot +  geom_line(aes(color=as.factor(net_props$k), group=as.factor(net_props$k), linetype=as.factor(net_props$k)),size=1)   
+plot <- plot + labs(color="K", shape="K", linetype="K", y="Average of Clustering Coefficient", x="D")
+plot
+
+#print to pdf
+pdf(paste("./pdf/","network_properties_cc_line_sf_kreg_12345.pdf"), width=7, height=5)
+par(mfrow=c(1,1))
+plot 
+dev.off()
+
+net_props <- average_clustering_data[average_clustering_data$"k" > 5,]
+plot <- ggplot(net_props, aes(x=as.factor(net_props$d), y=net_props$"clustering-coefficient",)) 
+plot <- plot +  geom_point(aes(shape=as.factor(net_props$k), color=as.factor(net_props$k)),size = 3.5)
+plot <- plot +  geom_line(aes(color=as.factor(net_props$k), group=as.factor(net_props$k), linetype=as.factor(net_props$k)),size=1)   
+plot <- plot + labs(color="K", shape="K", linetype="K", y="Average of Clustering Coefficient", x="D")
+plot
+
+#print to pdf
+pdf(paste("./pdf/","network_properties_cc_line_sf_kreg_1020304050.pdf"), width=7, height=5)
+par(mfrow=c(1,1))
+plot 
+dev.off()
+
+#clean up
+rm(apl_data,average_apl_data)
+gc()
+```

### 2014-08-18 doc/appendix.tex
pre-proof-read version of the paper added; some correlation analysis added; other old analysis corrected

\renewcommand\thefigure{\thesection.\arabic{figure}}    
\setcounter{figure}{0}

\renewcommand\thetable{\thesection.\arabic{table}}    
\setcounter{table}{0}

\section{Overlapping Network Properties}

\subsection{Homogeneous Network Topology Configurations}
\begin{figure}[H]
\centering
\begin{subfigure}{.49\linewidth}
  \centering
 \includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_apl_kreg_12345"}
 \caption{}
 \label{append_fig:network_properties_apl_kreg_12345}
\end{subfigure}%
\begin{subfigure}{.49\linewidth}
  \centering
 \includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_apl_kreg_1020304050"}
 \caption{}
 \label{append_fig:network_properties_apl_kreg_1020304050}
\end{subfigure}
\begin{minipage}{0.9\linewidth}
\vspace{0.2cm}
\caption{\textit{Average path length} for 100 instances of overlapping \textit{k-regular} networks(containing 100 nodes each) with ~$k=\{1,2,3,4,5\}$~(\ref{append_fig:network_properties_apl_kreg_12345}), and  $k= \{10,20,30,40,50\}$ (\ref{append_fig:network_properties_apl_kreg_1020304050}). Since there is barely any variation in the property values for each configuration, the colours cannot be seen correctly, they are presented in the same order as the legend nonetheless.}
\label{append_fig:network_properties_apl_kreg}
\end{minipage}

\end{figure}

\begin{figure}[H]
\centering
\begin{subfigure}{.5\linewidth}
  \centering
 \includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_cc_kreg_12345"}
 \caption{}
 \label{append_fig:network_properties_cc_kreg_12345}
\end{subfigure}%
\begin{subfigure}{.5\linewidth}
  \centering
 \includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_cc_kreg_1020304050"}
 \caption{}
 \label{append_fig:network_properties_cc_kreg_1020304050}
\end{subfigure}
\begin{minipage}{0.9\linewidth}
\vspace{0.2cm}
\caption{\textit{Clustering coefficient} for 100 instances of overlapping \textit{k-regular} networks (containing 100 nodes each) with ~$k=\{1,2,3,4,5\}$~(\ref{append_fig:network_properties_cc_kreg_12345}) and  $k= \{10,20,30,40,50\}$ (\ref{append_fig:network_properties_cc_kreg_1020304050}). Note that the variation is bigger for networks with less connectivity. Also, for $k=50$, the network is fully connected.}
\label{append_fig:network_properties_cc_kreg}
\end{minipage}
\end{figure}

\begin{figure}[H]
\centering
\begin{subfigure}{.5\linewidth}
  \centering
 \includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_apl_sf_12345"}
 \caption{Average path length}
 \label{append_fig:network_properties_apl_sf_12345}
\end{subfigure}%
\begin{subfigure}{.5\linewidth}
  \centering
 \includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_cc_sf_12345"}
 \caption{Clustering Coefficient}
 \label{append_fig:network_properties_cc_sf_12345}
\end{subfigure}
\begin{minipage}{0.9\linewidth}
	\vspace{0.2cm}
	\caption{\textit{Average path length} and \textit{clustering coefficient} for 100 instances of overlapping \textit{scale-free} networks. D is a parameter used to construct the network. It dictates how many edges are added by preferential attachment each time a new node is added to the networks. For more details refer to \cite{Barabasi1999}.}
	\label{append_fig:network_properties_sf}
\end{minipage}
\end{figure}

\subsection{Heterogeneous Network Topology Configurations}
\begin{figure}[H]
\centering
\begin{subfigure}{.49\linewidth}
  \centering
 \includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_apl_sf_kregular_12345"}
 \caption{}
 \label{append_fig:network_properties_apl_sf_kreg_12345}
\end{subfigure}%
\begin{subfigure}{.49\linewidth}
  \centering
 \includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_apl_sf_kregular_1020304050"}
 \caption{}
 \label{append_fig:network_properties_apl_sf_kreg_1020304050}
\end{subfigure}

\begin{minipage}{0.9\linewidth}
\vspace{0.2cm}
\caption{\textit{Average path length} for 100 instances of two overlapping networks: 1 \textit{scale-free} with $d=\{1,2,3,4,5\}$ and 1 \textit{k-regular} network with ~$k=\{1,2,3,4,5\}$~(\ref{append_fig:network_properties_apl_sf_kreg_12345}), and  $k=\{10,20,30,40,50\}$ (\ref{append_fig:network_properties_apl_sf_kreg_1020304050}). Since there is barely any variation in the property values for each configuration, the colours cannot be seen correctly in some cases, they are presented in the same order as the legend nonetheless.}
\label{append_fig:network_properties_apl_sf_kreg}
\end{minipage}

\end{figure}

\begin{figure}[H]
\centering
\begin{subfigure}{.49\linewidth}
  \centering
 \includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_cc_sf_kregular_12345"}
 \caption{}
 \label{append_fig:network_properties_cc_sf_kreg_12345}
\end{subfigure}%
\begin{subfigure}{.49\linewidth}
  \centering
 \includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_cc_sf_kregular_1020304050"}
 \caption{}
 \label{append_fig:network_properties_cc_sf_kreg_1020304050}
\end{subfigure}

\begin{minipage}{0.9\linewidth}
\vspace{0.2cm}
\caption{\textit{Clustering coefficient} for 100 instances of two overlapping networks: 1 \textit{scale-free} with $d=\{1,2,3,4,5\}$ and 1 \textit{k-regular} network with ~$k=\{1,2,3,4,5\}$~(\ref{append_fig:network_properties_apl_sf_kreg_12345}), and  $k=\{10,20,30,40,50\}$ (\ref{append_fig:network_properties_apl_sf_kreg_1020304050}). Since there is barely any variation in the property values for each configuration, the colours cannot be seen correctly in some cases, they are presented in the same order as the legend nonetheless.}
\label{append_fig:network_properties_cc_sf_kreg}
\end{minipage}

\end{figure}
\clearpage

\renewcommand\thefigure{\thesection.\arabic{figure}}    
\setcounter{figure}{0}

\renewcommand\thetable{\thesection.\arabic{table}}    
\setcounter{table}{0}

\begin{landscape}
	\section{Context Permeability Analysis}
	\label{append_ctx_permeability}
	\vspace{-0.1cm}
\begin{table}[H]
	\centering
\begin{minipage}{0.9\linewidth}	
	\caption{Average number of meetings during a simulation run for 100 agents and a maximum of 2000 simulation cycles for different configuration of \textit{k-regular} networks.}
	\label{append_tab:enc_ctx_permeability_k}
\end{minipage}

\renewcommand{\arraystretch}{0.85}
\begin{tabular}{lcccccccccc}
	\toprule
	& \multicolumn{10}{c}{Number of Networks} \\ 
	& \multicolumn{2}{c}{1} & \multicolumn{2}{c}{2} & \multicolumn{2}{c}{3} & \multicolumn{2}{c}{4} & \multicolumn{2}{c}{5} \\

	k  & avg. & sd & avg. & sd & avg. & sd & avg. & sd & avg. & \multicolumn{1}{c}{sd} \\ 
\midrule
	1  & $200000$ & $\phantom{0000}0.0$ & $191237$ & $35780.6$ & $97770$ & $86648.0$ & $44827$ & $71714.8$ & $14210$ & $31633.6$ \\
	2  & $200000$ & $\phantom{0000}0.0$ & $\phantom{0}99744$ & $89096.9$ & $22690$ & $50813.5$ & $\phantom{0}7514$ & $21352.6$ & $\phantom{0}4602$ & $\phantom{0}6116.7$ \\
	3  & $198033$ & $19670.0$ & $\phantom{0}68555$ & $82808.5$ & $10217$ & $33963.1$ & $\phantom{0}6539$ & $22227.3$ & $\phantom{0}2828$ & $\phantom{0}2283.6$ \\
	4  & $198093$ & $19070.0$ & $\phantom{0}38359$ & $69305.4$ & $\phantom{0}5028$ & $10680.0$ & $\phantom{0}3710$ & $\phantom{0}4618.7$ & $\phantom{0}2678$ & $\phantom{0}2127.4$ \\
	5  & $196042$ & $27845.6$ & $\phantom{0}21287$ & $48141.1$ & $\phantom{0}3444$ & $\phantom{0}5144.0$ & $\phantom{0}2834$ & $\phantom{0}4334.5$ & $\phantom{0}2278$ & $\phantom{0}1921.5$ \\
	10  & $178207$ & $62301.7$ & $\phantom{00}8066$ & $28298.4$ & $\phantom{0}2894$ & $\phantom{0}6424.5$ & $\phantom{0}1800$ & $\phantom{0}1148.2$ & $\phantom{0}2180$ & $\phantom{0}2078.3$ \\
	20  & $\phantom{0}75541$ & $95871.3$ & $\phantom{00}2338$ & $\phantom{0}2739.9$ & $\phantom{0}2178$ & $\phantom{0}1588.3$ & $\phantom{0}1936$ & $\phantom{00}989.4$ & $\phantom{0}1802$ & $\phantom{00}823.6$ \\
	30  & $\phantom{0}11703$ & $43425.0$ & $\phantom{00}1952$ & $\phantom{0}1087.9$ & $\phantom{0}1726$ & $\phantom{00}936.6$ & $\phantom{0}1930$ & $\phantom{0}1096.3$ & $\phantom{0}1956$ & $\phantom{0}1273.5$ \\
	40  & $\phantom{00}1694$ & $\phantom{00}954.5$ & $\phantom{00}1646$ & $\phantom{00}821.9$ & $\phantom{0}1862$ & $\phantom{00}872.3$ & $\phantom{0}1806$ & $\phantom{00}884.6$ & $\phantom{0}1686$ & $\phantom{00}647.1$ \\
	50  & $\phantom{00}1788$ & $\phantom{00}786.9$ & $\phantom{00}1724$ & $\phantom{00}744.7$ & $\phantom{0}1776$ & $\phantom{00}827.7$ & $\phantom{0}1842$ & $\phantom{00}896.8$ & $\phantom{0}1896$ & $\phantom{00}911.4$ \\
\bottomrule
\end{tabular}

\end{table}

\begin{table}[H]
	\centering
	\begin{minipage}{0.9\linewidth}
		\caption{Average number of meetings during a simulation run for 100 agents and a maximum of 2000 simulation cycles for different configuration of \textit{scale-free} networks.}
		\label{append_tab:enc_ctx_permeability_d}
	\end{minipage}

	\renewcommand{\arraystretch}{0.85}
	\begin{tabular}{lcccccccccc}
		\toprule
		& \multicolumn{10}{c}{Number of Networks} \\ 
		& \multicolumn{2}{c}{1} & \multicolumn{2}{c}{2} & \multicolumn{2}{c}{3} & \multicolumn{2}{c}{4} & \multicolumn{2}{c}{5} \\

		d  & avg. & sd & avg. & sd & avg. & sd & avg. & sd & avg. & \multicolumn{1}{c}{sd} \\ 
		\midrule
		1  & $200000$ & $\phantom{0000}0$ & $141085$ & $83720$ & $66020$ & $82601$ & $17712$ & $42444$ & $14917$ & $38343.6$ \\
		2  & $150632$ & $78710$ & $\phantom{0}21654$ & $41341$ & $\phantom{0}7555$ & $21407$ & $\phantom{0}5890$ & $10889$ & $\phantom{0}3638$ & $\phantom{0}5127.0$ \\
		3  & $\phantom{0}37824$ & $64073$ & $\phantom{0}12309$ & $36441$ & $\phantom{0}5299$ & $20035$ & $\phantom{0}2804$ & $\phantom{0}3791$ & $\phantom{0}2618$ & $\phantom{0}2445.4$ \\
		4  & $\phantom{0}13751$ & $33295$ & $\phantom{00}4846$ & $\phantom{0}7921$ & $\phantom{0}2852$ & $\phantom{0}2766$ & $\phantom{0}2370$ & $\phantom{0}1441$ & $\phantom{0}2200$ & $\phantom{0}1433.4$ \\
		5  & $\phantom{00}8802$ & $18754$ & $\phantom{00}2536$ & $\phantom{0}1880$ & $\phantom{0}3204$ & $11008$ & $\phantom{0}2166$ & $\phantom{0}1269$ & $\phantom{0}1958$ & $\phantom{00}971.6$ \\
	\bottomrule
	\end{tabular}

\end{table}

\begin{table}[H]
\centering
\begin{minipage}{0.9\linewidth}	
	\caption{Average number of meetings during a simulation run for 100 agents and a maximum of 2000 simulation cycles for different configuration of 1 \textit{k-regular} and 1 \textit{scale-free} networks.}
	\label{append_tab:ctx_perm_kreg_sf_encounters}
\end{minipage}

\renewcommand{\arraystretch}{0.85}
\begin{tabular}{lcccccccccc}
\toprule
 & \multicolumn{10}{c}{d} \\ 
 & \multicolumn{2}{c}{1} & \multicolumn{2}{c}{2} & \multicolumn{2}{c}{3} & \multicolumn{2}{c}{4} & \multicolumn{2}{c}{5} \\ 
k  & avg. & sd & avg. & sd & avg. & sd & avg. & sd & avg. & \multicolumn{1}{c}{sd} \\ 
\midrule
1  & $173312$ & $61519$ & $100175$ & $88406$ & $63191$ & $81071$ & $73715$ & $84549$ & $51313$ & $67704$ \\
2  & $118591$ & $90107$ & $\phantom{0}72054$ & $86077$ & $43308$ & $70318$ & $31756$ & $58760$ & $43281$ & $72182$ \\
3  & $109155$ & $88722$ & $\phantom{0}38270$ & $66714$ & $34899$ & $65533$ & $26412$ & $55589$ & $23436$ & $49978$ \\
4  & $\phantom{0}80035$ & $88719$ & $\phantom{0}33339$ & $64075$ & $21289$ & $45725$ & $15575$ & $39516$ & $24034$ & $52407$ \\
5  & $\phantom{0}89179$ & $91823$ & $\phantom{0}31044$ & $62485$ & $13908$ & $36791$ & $14112$ & $39490$ & $\phantom{0}9252$ & $28404$ \\
10  & $\phantom{0}62416$ & $81036$ & $\phantom{0}11017$ & $35071$ & $\phantom{0}9095$ & $27266$ & $12182$ & $39798$ & $\phantom{0}5559$ & $20448$ \\
20  & $\phantom{0}61371$ & $81409$ & $\phantom{00}6680$ & $17900$ & $\phantom{0}6944$ & $27826$ & $\phantom{0}4721$ & $19832$ & $\phantom{0}2390$ & $\phantom{0}2313$ \\
30  & $\phantom{0}51559$ & $77468$ & $\phantom{00}4980$ & $12740$ & $\phantom{0}5095$ & $20028$ & $\phantom{0}2268$ & $\phantom{0}1355$ & $\phantom{0}2046$ & $\phantom{0}1225$ \\
40  & $\phantom{0}58625$ & $83049$ & $\phantom{00}5483$ & $20169$ & $\phantom{0}2726$ & $\phantom{0}3735$ & $\phantom{0}2346$ & $\phantom{0}1503$ & $\phantom{0}2412$ & $\phantom{0}1874$ \\
50  & $\phantom{0}48702$ & $74718$ & $\phantom{00}6568$ & $22611$ & $\phantom{0}2566$ & $\phantom{0}1716$ & $\phantom{0}2362$ & $\phantom{0}1619$ & $\phantom{0}1980$ & $\phantom{0}1081$ \\
\bottomrule
\end{tabular}
\end{table}

\end{landscape}
\clearpage

\renewcommand\thefigure{\thesection.\arabic{figure}}    
\setcounter{figure}{0}

\renewcommand\thetable{\thesection.\arabic{table}}    
\setcounter{table}{0}

\section{Context Switching Analysis}
\label{append_ctx_switching}

\begin{figure}[H]
	\centering
	\includegraphics[width=1\linewidth]{"../analysis/pdf/   context_switching_2_10_regular _switching_persp"}
	\begin{minipage}{0.9\textwidth}
		\caption{Perpective plot for the average number of meets during a simulation for 100 independent runs: 2 \textit{10-regular} networks ($k = 30$).}
		\label{append_fig:ctx_cs_2_10kreg}
	\end{minipage}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=1\linewidth]{"../analysis/pdf/   context_switching_2_30_regular _switching_persp"}
	\begin{minipage}{0.9\textwidth}
		\caption{Perpective plot for the average number of meets during a simulation for 100 independent runs: 2 \textit{30-regular} networks ($k = 30$).}
		\label{append_fig:ctx_cs_2_30kreg}
	\end{minipage}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=1\linewidth]{"../analysis/pdf/   context_switching_2_sf_d1 _switching_persp"}
	\begin{minipage}{0.9\textwidth}
		\caption{Perpective plot for the average number of meets during a simulation for 100 independent runs: 2 \textit{scale-free} networks with $d=1$.}
		\label{append_fig:ctx_cs_2_sd_d1}
	\end{minipage}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=1\linewidth]{"../analysis/pdf/   context_switching_2_sf_d5 _switching_persp"}
	\begin{minipage}{0.9\textwidth}
		\caption{Perpective plot for the average number of meets during a simulation for 100 independent runs: 2 \textit{scale-free} networks with $d=5$.}
		\label{append_fig:ctx_cs_2_sd_d5}
	\end{minipage}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_switching_sf_d5_d1 _switching_persp"}
	\begin{minipage}{0.9\textwidth}
		\caption{Perspective plot for the average number of meets during a simulation for 100 independent runs: 2 \textit{scale-free} networks, the first with $d=5$ and the second with $d=1$.}
		\label{append_fig:ctx_cs_sf_d5_d1}
	\end{minipage}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_switching_1_10regular_1_scale-free_d1 _switching_persp"}
	\begin{minipage}{0.9\textwidth}
		\caption{Perspective plot for the average number of meets during a simulation for 100 independent runs: 1 \textit{10-regular} network ($k=10$) and a scale-free network with $d=1$.
		}
		\label{append_fig:ctx_cs_kreg10_sfd1}
	\end{minipage}
\end{figure}

### 2014-08-18 doc/main.tex
pre-proof-read version of the paper added; some correlation analysis added; other old analysis corrected

@@
 \usepackage{multirow}
+\usepackage{amsthm}
+\usepackage{algorithmic}
+\usepackage{algorithm}
+\usepackage{graphicx}
+\usepackage{wrapfig}
+\usepackage{appendix}
+\usepackage{subcaption}
+\usepackage{siunitx}
+
+\usepackage{pdflscape}
+
+\usepackage[draft]{todonotes}
+\newcommand{\comment}[1]
+{\par {\bfseries \color{blue} #1 \par}} %comment showed
+
+%scientific notation setup
+\sisetup{
+	round-mode = places,
+	round-precision = 2,
+	scientific-notation = false}
+
+\usepackage{booktabs}
+
+\usepackage{float}
+\floatname{algorithm}{Model}
+\newcommand{\algorithmname}{Model}
+
+\newtheorem{mydef}{Definition}
 
@@
 We study the notion of context permeability using a consensus game in which agents try to achieve global consensus.
-We design and analyse models of permeability with three model different configurations.
+We design and analyse two different models of permeability.
 In the first model agents interact concurrently in multiple social networks.
@@
 They switch between the different networks spending more or less time in each network.
-Finally we use a strategic neighbourhood selection by segregation that acts as a regulatory mechanism in the societal self-organisation process to achieve consensus.
-We compare each model and analyse the influence of different social topologies in the speed of convergence to global consensus.
-%TODO abstract: brief strong conclusion
+We compare each model and analyse the influence of different social networks in the speed of convergence to consensus.
+We conduct a series of experiments that show the impact of coexisting social networks when designing simulation models.
+This approach unveils both the limitations of the current modelling approaches and possible research directions for complex social space simulations.
 		\end{abstract}
@@
 	\newpage
-%********************************************
+	%******************************************
 	%		INTRODUCTION
-%********************************************
-\section{Introduction and Related Work}
+	%******************************************
+	\section{Introduction}
 	\label{sec:introduction}
-%Social simulation view oever consensus
-\noindent In social simulation, studying models of consensus formation helps us to investigate real-world phenomena.
-This can be done not only by constructing data-driven simulation but also with the help of abstract models that permit the assembly of \textit{what-if-scenarios}.
-Examples of real-world target phenomena in this domain include: the joint assessments of social policies or, in the context of economics and politics, \textit{the voting problem}.
-Herbert Simon investigated this last problem in an early model described in~\cite{Simon1954}.
+	%******************************************
+	%		Research context
+	%******************************************
+	Studying simulation models of consensus formation can advance our understanding of real-world emergent social phenomena.
+Typically, we can construct models with different levels of abstraction.
+Simulation methods can range from data-driven paradigms to more abstract descriptions that allow us to create \textit{what-if-scenarios}.
+While most models are simplified descriptions of the real-world, many constitute complex systems themselves and thus the necessity of tools like simulation to explore their properties.
+In \cite{Emmeche1997}, Emmeche makes a distinction between two types of complexity.
+He characterises the complexity of real systems as \textit{``ontological complexity"} and the one of models as \textit{``descriptive complexity"}.
+Examples of real-world target phenomena for social simulation models include for instance the joint assessments of policies or, in the context of economics and politics, \textit{the voting problem}.
+Herbert Simon investigations on this problem were also one of the first stepping stones to the field of social simulation \cite{Simon1954}.
 
+	In agent-based \textit{opinion dynamics}, agent interactions are guided by \textit{social space} abstractions.
+In some models, dimensionality is irrelevant and any agent can interact with any other agents.
+	Other approaches use an underlying structure to create agent neighbourhoods.
+Axelrod for instance, in its model of \textit{dissemination of culture} \cite{Axelrod1997}, represents agents in a bi-dimensional grid.
+Finally, in an attempt to mimic real social systems, some simulation models make use of \textit{complex network models} (see \cite{Weisbuch2004}) to create the infrastructure that guides agent interaction.
+
+	%******************************************
+	%		Motivation 
+	%******************************************
+	%position, most agent-based models don't take into account  social relations and this is important
+	In real-world scenarios, actors engage in a multitude of social relations different in kind and quality.
+Most simulation models don't explore \textit{social space} designs that take into account the differentiation between coexisting social networks.
+Modelling multiple concomitant relations was an idea pioneered by Peter Albin in \cite{Albin1975} but without any further development.
+The complex social structures that results from interacting in these different dimensions forms the basis for the formation of social identity \cite{Roccas2002,Ellemers2002}.
+
+	%******************************************
+	%		Objectives
+	%******************************************
+	In this paper, we explore the possibility of modelling opinion dynamics with multiple social networks.
+We look at how the properties influence the convergence to opinion consensus.
+Starting with this premise of
+	using multiple social networks, we present a series of models that use these networks in different ways which creates distinct emergent dynamics.
+We want to observe the consequences of using multiple social networks at the same time ---while maintaining the model as simple and abstract as possible much like what happens with the current contributions on opinion dynamics present in the literature.
+
+	In our models agents can: interact at the same time in the multiple networks (choosing partners from any network) or switch between networks (choosing only partners from their current network).
+While our models seem quite simple, and are quite abstract, they generate quite complex outcomes and thus the need of simulation to understand their dynamics.
+
+	%******************************************
+	%		Paper Structure
+	%******************************************
+	\subsection{Paper Structure}
+	This paper is organised as follows.
+In the next section we present work related to, \textit{opinion dynamics}, \textit{social space} modelling and \textit{complex network models}.
+In the following section, we describe our game of consensus and introduce multiple model variations designed to study the notion of context permeability and the process of consensus formation in multiple social networks.
+Section \ref{sec:experimental-setup} describes the experimental set-up; the set of tool and methodologies followed to conduct our investigations.
+In section \ref{sec:results-discussion}, we present and discuss our results and compares the different simulation models.
+Finally we conclude by making a summary of what we learned from the simulation models and point out possible future research directions.
+
+	%******************************************
+	%		Related Work
+	%******************************************
+	\section{Related Work}
+	\label{sec:relatedwork}
+	%******************************************
+	%	Opinion Dynamics
+	%******************************************
+	\subsection{Opinion Dynamics and Consensus Formation}
 	Formal opinion dynamics models provide an understanding if not an analysis of opinion formation processes.
@@
 In particular, the work on consensus building in the context of decision-making was first studied by DeGroot \cite{Degroot74} and Lehrer \cite{Lehrer1975}.
-Empirical studies of opinion formation in large populations have methodological limitations, as such, we use simulation, in particular Multi-Agent Simulation (MAS), as a methodological framework to study such phenomena in a larger scale.
-Most opinion dynamics simulation models are based either on binary opinions \cite{Galam1997,Antunes2009} or on opinions with continuous values \cite{Deffuant2000,Deffuant2002}.
+Empirical studies of opinion formation in large populations have methodological limitations, as such, computational sociology arises with a set of tools to cope with those limitations.
+We use simulation, in particular \textit{multi-agent simulation (MAS)}, as a methodological framework to study such phenomena in a larger scale.
+Most opinion dynamics simulation models are based either on binary opinions \cite{Galam1997,Antunes2009} or continuous values \cite{Deffuant2000,Deffuant2002}.
 In these models, agents update their opinions either under social influence or according to their own experience.
@@
 
-In agent-based opinion dynamics models, agent interactions are guided by social space abstractions.
-In some models, dimensionality is irrelevant.
-Typically, all agents can participate in interactions with all other agents.
-Axelrod, takes a different approach in his model of dissemination of culture \cite{Axelrod1997} and represents agents in a bi-dimensional grid which provides the structure that shapes how they interact.
-In Weisbuch's bounded confidence model with social networks \cite{Weisbuch2004}, the agents are bound by network structures.
-A first definition for these types of bounded confidence models was given in \cite{Krause1997}.
-
-%position, most agent-based models don't take into account  social relations and this is important
-In real-world scenarios, actors engage in a multitude of social relations different in kind and quality.
-Most simulation models don't explore social space designs that take into account the differentiation between coexisting social networks.
-Modelling multiple concomitant relations was an idea pioneered by Peter Albin in \cite{Albin1975} but without significant further development.
-The complex social structures that result from interacting in these different dimensions form the basis for the formation of social identity \cite{Roccas2002,Ellemers2002}.
-
-%A broader view over consensus formation
-\subsection{On Consensus}
-Opinion dynamics models try to study under which circumstances convergence to consensus can be achieved.
-These agent-based models can have broader applications outside social simulation.
+	Opinion dynamics models try to study under which circumstances consensus or polarisation is reached.
+Agent-based models can have broader applications outside social simulation.
 In distributed systems in general, consensus is a means by which processes agree on some data value that is needed during computation, typically, this agreement is the result of a negotiation process often with the aid of a mediator.
@@
 Moreover, conventions typically originate from the necessity to resolve conflict.
-Mult-Agent Systems (MAS) can also benefit from being capable of produce emergent conventions as they might need to coordinate or cooperate in order to solve different problems \cite{Delgado2002}.
-
+MAS can also benefit from being capable of produce emergent conventions in coordination or cooperation problems \cite{Delgado2002}.
 The decentralised nature of these models of consensus is highly desirable for problems where dynamic control is needed.
@@
 Consequently, the guarantee of achieving a global consensus and the efficiency of convergence towards it has been a natural concerns in the design of local interaction behaviours.
-Shoham and Tennenholtz compared several strategy update rules in %paper urbano
 
-%TODO this was the last thing I wrote
+	Consensus models are also investigated as means to create conventions in MAS.
+Shoham and Tennenholtz \cite{Shoham1994} create a bridge between economic literature and machine learning by studying a series of models in which multiple agents are engaged in learning a particular convention.
+They call this process \textit{co-learning}.
+The complexity of these systems derives from the its concurrent nature: one agents adapts to the behaviour of another agent it has encountered, as these agents update their behaviour in a similar fashion, this results in a highly non-linear system dynamics.
+In their work, Shoham and Tennenholtz define the notion of \textit{stochastic social games} and compare different rules with the objective of establishing conventions in a decentralised fashion.
+In their stochastic games, they present one particular rule which we use in our models:
 
-. This explains the interest on the design of
-emergent conventions through a co-learning process [13]: individual agents occasionally meet and observe each
-other, and they may .
+	\begin{mydef}
+		\label{def:external-majority}
+		\textit{External Majority (EM)} update rule: adopt action $i$ if so far it was observed in other agents more often than other action and remain with your current action in the case of equality. 
+	\end{mydef}
 
-%TODO present the literature related to norms and consensus and motivate the problem
+	This EM was shown to coincide with \textit{Highest Cumulative Reward (HCR)} which is a simple rule that states that ``an agent should adopt an action that has yielded the highest cumulative reward to date".
+We chose to use EM in our simulation models for its simplicity and success in the evolution of conventions.
+We can see that there is an overlap between opinion dynamics from social simulation and agent based learning---or co-learning in this case.
 
-%TODO distributed systems need consensus to perform reliable sets of actions (tolerance to faults etc) such as transations
-%Agents that co-exist need to coordinate to perform certain tasks or choose appropriate strategies, science a particular behaviour can 
-%have an impact on the each agent not only on the environment, and even when agents have an impact on the environment, this is reflected
-%in the performance of other agents that co-habit the same environment.
+	%******************************************
+	%	Social Structure in Simulation Models
+	%******************************************
+	\subsection{Social Structure in Simulation Models}
+	One of the most widely used approaches to represent social spaces in abstract simulation models is using a  bi-dimensional gridd.
+This approach has its origins in the first \textit{“checkerboard”} model introduced in computational social sciences by Thomas Schelling \cite{Schelling1971} and Sakoda \cite{Sakoda1971}.
+Another famous example that uses bi-dimensional grids as social structure is the social simulation model of dissemination of culture from Axelrod \cite{Axelrod1997}.
 
-%TODO as in human societies, consensus is not an intentional end result but rather an emergent process which arises 
-%without a central authority
+	Cellular automata (CA) is an example from the are of artificial life that also makes use of bi-dimensional structures to model neighbourhood interactions.
+While these models are idealised frameworks, the exploration of simple computational models can bring us deeper insights than models with high levels descriptive complexity which would render their analysis, very difficult.
+The work of Flache and Hegselmann \cite{FlacheHegselmann2001} relaxes the standard CA assumptions about the regular bi-dimensional grids by considering irregular grid structures (Voronoi diagrams).
+This work presents results on the robustness of some important general properties in relation to variations in the typical grid structure.
+We can also find contributions that incorporate both the complexity of network models and the behaviour of dynamic processes.
+One example of this combination is the work in \cite{Sullivan2000} which explores a graph-based cellular automaton to study the relationship between spatial form of urban systems and the robustness of different process dynamics under spatial change.
+Moreover this allows for the integration of real geographical information to construct the graph-cellular automata.
+This fact makes so that while the models of dynamic processes are relatively abstract, they are tested in spatial structures based on data from real complex structures and thus making a connection between purely abstract models and data-driven models.
 
-%TODO see Emergent Conventions and the Structure of Multi{Agent Systems
-%TODO see On the synhesis of useful social laws for artificial agent societies
+	%******************************************
+	%	Complex Network Models
+	%******************************************
 
-In the field of Distributed Artificial Intelligence (DAI) in general and in Multi-Agent Systems (MAS) in particular, achieving a global agreement on some strategy, convention or norm is fundamental 
-\cite{Delgado2002}
+	Finally, another type social space models are the \textit{random graph / network models}.
+Networks with different properties can be built using network models.
+Each complex network or class of complex networks, presents specific topological features.
+These properties are typically found in---and the models inspired by---real-world network structures.
+One of the first complex network models is the random graph from Erdős and Renyi \cite{Erdos1959}.
+Other examples include the model of preferential attachment \cite{Barabasi1999} and the small-world network models \cite{Watts1998}.
+One common problem of these models is the fact that once generated, the network structure is static so these models are not really suitable for the description of highly dynamic groups or communities.
+An example of a model that takes these dynamics into account is the model of team formation~\cite{Gaston2005}.
+A more in-depth review of network models and their properties is given in~\cite{Nunes2012}.
 
-%Objective of this paper
-This paper is aimed at extending the line of research regarding the representation of social spaces by modelling these with explicit multiple networks.
+	\section{Multi-context Models}
+	\label{sec:multi-context-models}
+	In this section, we present our modelling approach to explore the concept of permeability between contexts.
+In our approach, we considers multiple social networks as a way to represent the complex social space of an agent.
+This setting can be seen in a simulation as a n-dimensional scenario where each dimension surface represents a different social relation (see figure \ref{img:multiple-relations}).
+Each relation is instantiated using a social network model.
+The word ``context" is used in many different senses and it is subjected to many analysis \cite{Hayes1997}.
+Here, we use the term \textit{social context} in a simpler and more strict way.
+Agents belong to distinct social contexts (neighbourhoods) in these multiple networks.
+The \textit{social context} of an agent is thus a set of neighbours currently available for interaction.
+\textit{Context Permeability} is the ability of a particular norm, strategy, opinion or trend to permeate from one social relation to another.
+Agents belonging to disjoint neighbourhoods in different networks foster the creation of bridges between subsets of the population that wouldn't otherwise be influenced by a consensus formed in a distant coalition or in a distinct context.
 
-%****************************************
-%			PAPER STRUCTURE
-%****************************************
-\subsection{Paper Structure}
-This paper is organised as follows.
-In the next section we define our modelling approach that uses multiple social networks.
-We describe our game of consensus and introduce multiple model variations designed to study the notion of context permeability and the process of consensus formation.
-Section \ref{sec:experimental-setup} describes the experimental set-up for our series of experiments.
-Finally, in section \ref{sec:results-discussion}, we discuss our results and compare the different simulation models.
+	\begin{figure}[h]
+		\centering
+		\includegraphics[width=0.7\linewidth]{./images/multi-context_model.pdf}
+		\begin{minipage}{0.9\linewidth}
+			\caption{Multiple social network structure that shapes the social space in our simulation models.}
+			\label{img:multiple-relations}
+		\end{minipage}
+	\end{figure}
+
+	%Consensus
+	We study the notion of context permeability in different simulation models in which agents interact using a simple consensus game.
+The society of agents has to adopt a binary \textquotedblleft option \textquotedblright according to a majority rule.
+We use the speed of consensus as a measure for self-organisation, exploring the relationship between different network topologies and this measure.
+
+	%Presenting 3 models
+	We partitioned the design space of our experiments using different simulation models.
+Each model is designed to analyse different aspects of social context permeability.
+In a first model \cite{Antunes2007, Antunes2010}, we study the notion of permeability by overlapping social networks.
+In a second model \cite{Antunes2009}, we analyse the dynamics introduced by switching between \textit{social contexts}(neighbourhoods in different networks), adding a temporal component to neighbourhoods within different social relations.
+
+	\subsection{Simulation and Consensus Game}
+	\label{sec:sim_consensus}
+	Our agent-based models are designed as \textit{discrete-event} models.
+On each simulation cycle, every agent executes a simulation step.
+The agents are selected in a random uniform fashion for execution.
+This is common practice in agent-based simulation and guarantees that there is no bias caused by the order in which the agents are executed.
+For each simulation model, we present a description of the individual agent behaviour.
+Every model we present can be seen as a binary opinion dynamics model or a consensus game.
+In this game, the society of agents tries to reach an arbitrary global consensus about two possible choices.
+Each agent keeps track of the number of choices observed from interaction partners throughout a simulation run.
+In each iteration, each agent selects an available neighbour to interact with and observes its current choice.
+The agent decides to switch its current choice if the observed option becomes the majority of the two possible choices.
+The objective of the game is to reach a global consensus, but the particular choice that gets collectively selected is irrelevant.
+What is important is that overall agreement is achieved.
+In the consensus game we consider, each agent uses the previously presented external majority (EM) rule to update its opinion value (see definition \ref{def:external-majority} in section \ref{sec:relatedwork}).
+
+	\newpage
+	\subsection{Context Permeability}
+	This first model of context permeability \cite{Antunes2007,Antunes2010} is designed to study our first setting for permeability.
+In most interesting applications, an agent is immersed in a complex social world where it engages in a multitude of relations with other agents (and even aggregate agents such as institutions or informal groups).
+In this model we consider that the \textit{context permeability} is created by agents that can belong simultaneously to several relations.
+As an example, two agents can be simultaneously family and co-workers, and while some links might not connect two agents directly, others can contain neighbourhoods in which they are related~(either directly or through a common neighbour).
+Model \ref{model:context_permeability} describes the behaviour of each agent for each simulated step.
+	%***************************************************
+	%	Context Permeability Model Description
+	%***************************************************
+	\begin{algorithm}[H]
+		\caption{Context Permeability}
+		\label{model:context_permeability}
+		\algsetup{indent=2em}
+		\begin{algorithmic}
+			\vspace{0.5em}
+			\STATE $M$ \COMMENT{Simulation Model / Environmnet}
+			\STATE $A$ \COMMENT{Current Agent in Execution}
+			\\ \hrulefill
+
+			\STATE\COMMENT{\textbf{Randomly select a network}}
+			\STATE $r$ $\leftarrow$ randomUniform(0,$ M.networks.length() $)
+			\STATE network $\leftarrow$ $M.networks[r]$
+
+			\STATE
+			\STATE \COMMENT{\textbf{Randomly select a neighbour}}
+			\STATE neighbours $\leftarrow$ network.neighboursOf($A$) 
+			\STATE $r$ $\leftarrow$ randomUniform(0,neighbours.length())
+			\STATE partner $\leftarrow$ neighbours[r]
+			\STATE
+			\STATE \COMMENT{\textbf{Update opinion and memory}}
+			\STATE \COMMENT{opinions take the values \{0,1\}--so they can be used as an index}
+			\STATE A.memory[partner.opinion]++
+			\IF {(A.memory[partner.opinion] $>$ A.memory[A.opinion])}
+			\STATE A.opinion $\leftarrow$ partner.opinion
+			\ENDIF
+		\end{algorithmic}
+	\end{algorithm}
+	In this model, on each time step, each agent selects a random neighbour from any 
+	social network available and updates its opinion based on the opinion of the selected partner using the \textit{external majority} rule.
+
+	\subsection{Context Switching}
+	\label{sec:models_cs}
+	In the context switching model \cite{Antunes2009}, agents are embedded in multiple relations represented as static social networks and they switch \textit{contexts} with some probability $\zeta_{C_i}$ associated with each context $C_i$.
+The switching probability value is the same in the same network.
+Each agent switches from its current neighbourhood to a its neighbourhood in another network (in which this agent was inactive).
+The agents are only active in one context at a time and can only perform encounters with neighbours in the same context.
+We can think of context switching as a temporary deployment in another place, such as what happens with temporary immigration.
+The network topology is static; when an agent switches from one network to another, they become inactive in one network and active in their destination.
+	%***************************************************
+	%	Context Switching Model Description
+	%***************************************************
+	\begin{algorithm}[H]
+		\caption{Context Switching}
+		\label{model:context_switching}
+		\algsetup{indent=2em}
+		\begin{algorithmic}
+			\vspace{0.5em}
+			\STATE $M$ \COMMENT{Simulation Model / Environmnet}
+			\STATE $A$ \COMMENT{Current Agent in Execution}
+			\\ \hrulefill
+
+			\STATE\COMMENT{\textbf{Get the current network (\textit{context} is a network index)}}
+			\STATE cNetwork $\leftarrow$ M.networks[A.context]
+			\STATE 
+			\STATE \COMMENT{\textbf{Get the neighbours for the current network}}
+			\STATE neighbours $\leftarrow$ cNetwork.neighboursOf($A$) 
+			\STATE \COMMENT {filter by agents active in the same network}
+			\STATE neighbours $\leftarrow$ \{n $|$ n $\in$ neighbours $\wedge$ (n.context = A.context)\}
+			\STATE
+			\STATE\COMMENT{\textbf{Randomly select a neighbour}} 
+			\STATE $r$ $\leftarrow$ randomUniform(0,neighbours.length())
+			\STATE partner $\leftarrow$ neighbours[r]
+			\STATE
+			\STATE \COMMENT{\textbf{Update opinion and memory}}
+			\STATE \COMMENT{opinions take the values \{0,1\}--so they can be used as an index}
+			\STATE A.memory[partner.opinion]++
+			\IF {(A.memory[partner.opinion] $>$ A.memory[A.opinion])}
+			\STATE A.opinion $\leftarrow$ partner.opinion
+			\ENDIF
+			\STATE
+			\STATE \COMMENT{\textbf{Switch to another network}}
+			\STATE switchingProb $\leftarrow$ M.params.switchingProb(A.context)
+			\STATE $r \leftarrow $ randomUniform(0,1)
+			\IF{($r < $ switchingProb)}
+			\STATE numNets $\leftarrow$ M.networks.length()
+			\STATE nextNetworks $\leftarrow$ \{i $|$ (i $\in$ [0,numNets[) $\wedge$ (M.networks[i] != A.context)\}
+			\STATE $r$ $\leftarrow$ randomUniform(0,nextNetworks.length())
+			\STATE A.context $\leftarrow$ nextNetworks[r]
+			\ENDIF
+		\end{algorithmic}
+	\end{algorithm}
+	\noindent In this model agents select an (active) partner from their current neighbourhood.
+If a partner is available the agents update their opinion value based on EM.
+At the end of the interaction, the agent switches \textit{from} the current context to a different one with a probability associated with its current network.
+
+	This model describes an abstract way to represent the time spent on each network using the switching probability $\zeta_{C_i}$.
+Here, the permeability between contexts is achieved using this temporal component.
+Context switching introduces one notion that has not been explored in the literature so far: the fact that, although some social contexts can be relatively stable if we consider short to moderate periods of time, our social peers are not always available at all times and spend different amounts of time in distinct social contexts.
 
@@
 	\label{sec:experimental-setup}
+	In this section we describe all the tools and processes necessary to produce the current research output.
+The experiments for our previously described simulation models were developed using the MASON~\cite{Luke2005} simulation framework written in Java.
+All the code for the simulation models can be found here \cite{Nunes:Software:11067}.
+Moreover, all the results presented in this paper were made reproducible by using the \textit{statistical computing language R} \cite{R2008} and the R package \textit{knitr} \cite{knitr2014}.
+Knitr is used for generating reports that contain the code, the results of its execution (plots and tables), and the textual description for such results.
+All the R code and the configuration files used to produce the analysed data can be found \textbf{in}...\todo{Archive the data, analysis and code used for the analysis, get a doi for it and cite it here}.
+
+%recap
+For each configuration in our experiments we performed 100 independent simulation runs.
+The results are thus analysed in terms of value distribution, average and standard deviation, or variance over the 100 runs.
+Like we described in section \ref{sec:sim_consensus}, our models are discrete-event models and each cycle agents execute
+a step in a random order : this is so that this dynamic system --our simulation model-- is not influenced by the order in which agents are executed.
+Simulations ends when total consensus is achieved or 2000 steps have passed.
+
+\subsection{Social Network Models}
+\label{sec:exp-setup_network_models}
+The social networks used in our models are \textit{k-regular} and \textit{scale-free}.
+A k-regular network is a network where each node has the same number of connections.
+These networks are constructed by arranging the nodes in a ring and connecting each node to their next $k$ neighbours.
+Each network has $2k$ edges per vertex.
+
+Scale-free networks \cite{Barabasi1999} are created with a model of preferential attachment proposed by Barab\'{a}si and colleagues \cite{Barabasi1999}.
+This model builds upon the perception of a common property of many large networks, a scale-free-power-law distribution of node connectivity.
+This feature was found to be a consequence of two generic mechanisms: networks expand continuously by the addition of new vertices, and new vertices attach preferentially to sites that are already well connected, being this mechanism more commonly known as ``preferential attachment''.
+In these networks, the probability $P(k)$ of two nodes being connected to each other decays as a power law, following $P(k) \sim k^{- \gamma}$.
+
+The network instances were generated using the \textit{b-have network library} \cite{Nunes:Software:11069}.
+This is a Java library which allows for the manipulation of Network/Graph data structures.
+It also includes the more commonly used random network models from the literature.
+
+\subsection{Measuring Network Properties}
+We measure two structural properties of our networks: the \textit{average path length} and the \textit{clustering coefficient}.
+The \textit{average path length} measures the typical separation between two vertices in the graph.
+The \textit{clustering coefficient} measures the average cliquishness of the graph neighbourhood.
+This measure quantifies how close the neighbours of a node are to forming a clique.
+Duncan J.
+Watts and Steven Strogatz \cite{Watts1998} introduced the measure to characterise a class of complex networks called small-world networks.
+The networks produced by the \textit{b-have network library} \cite{Nunes:Software:11069} were exported to files and analysed using the \textit{igraph R package} \cite{igraph2006}.
 
@@
 
-\section*{References}
+% Overview
+
+\subsection{Overlapping Network Properties}
+\label{sec:network_properties}
+In this first analysis, we investigate the properties of different network topologies that we use in our models. 
+One of the parameters in some experiments is the number of networks in which the agents interact. Adding more networks means adding more connections. 
+We show that what is important is not just the the number of connections, but the properties the resulting structure displays when these networks are merged.
+The way we look at the network properties is as follows.
+
+Each network is generated in such a way that the node positions are randomised.
+What this means is that we can have multiple networks with the same topology and yet, each node has a different neighbourhood on each network.
+Also, neighbourhoods do not necessarily overlap due to the node shuffling.
+Adding more networks to the social space is not the same as creating a single network with twice the number of connections.
+
+\noindent Consider figure \ref{fig:network_properties_merge_2_10regular}.
+We created two random k-regular networks with k=10 and merged them ignoring edges from common neighbours --in the simulation models this edge agglutination is not performed, we use it here for the purposes of network analysis.
+The common edges are highlighted in a different colour.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_merge_2_10regular"}
+	\begin{minipage}{0.9\textwidth}
+		\caption{Overlapping of two k-regular networks, each with k=10.}
+		\label{fig:network_properties_merge_2_10regular}
+	\end{minipage}
+\end{figure}
+
+\begin{table}
+	\centering
+	\begin{minipage}{0.9\textwidth}
+		\caption{Properties for overlapping of two k-regular networks, each with k=10.}
+		\label{tab:network_properties_merge_2_10regular}
+	\end{minipage}
+	\begin{tabular}{lcccc}
+		& Nodes &  Edges & Clustering Coef.	  &  Avg. Path Length \\ 
+		\hline  10-Regular 1 & 100 &  1,000  &  0.711 &  2.980 \\ 
+		\hline  10-Regular 2 & 100 & 1,000 & 0.711 &  2.980 \\ 
+		\hline  Combined & 100 & 1,790  & 0.512 &  1.638 \\ 
+		\hline 20-Regular & 100 & 2,000	& 0.731	& 1.788 \\
+		\hline 
+	\end{tabular} 
+\end{table}
+
+The networks are drawn using the \textit{Kamada-Kawai} Layout \cite{Kamada19897} which regards the desirable ``geometric" (Euclidean) distance between two vertices in the drawing as the ``graph theoretic" distance between them in the corresponding graph.
+We can see by the results of the layout in figure \ref{fig:network_properties_merge_2_10regular}, that the distance between nodes in the network has decreased, this is also confirmed by the reduced average path length of the combined networks (see table \ref{tab:network_properties_merge_2_10regular}).
+
+\begin{wrapfigure}{r}{0.45\linewidth}
+	\includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_1_20regular"}
+	\begin{minipage}{0.8\linewidth}
+		\caption{Single k-regular network with k=20. (Drawn using the Kamada-Kawai layout)}
+		\label{fig:network_properties_1_20regular}
+	\end{minipage}
+\end{wrapfigure}
+
+To illustrate our point we analysed one k-regular network with k = 20 (see figure \ref{fig:network_properties_1_20regular} --and the corresponding entry on table \ref{tab:network_properties_merge_2_10regular}).
+The clustering coefficient of a 20-Regular network is approximately the same as the one of a 10-regular network (higher than the combination of 10-regular networks).
+The average path length also decreases as there are more connections between the nodes.
+As we will show, these properties may vary.
+Since the nodes are subjected to random permutations, we can generate different overlaps which lead to distinct structural values.
+
+Since we model the agent social space as a multitude of networks, we need to investigate the properties resulting from the merging of these networks.
+We do this empirically by taking the network instances used in the simulation and analysing the distribution of clustering coefficient and average path length for the different configurations.
+
+\subsubsection{Properties of Overlapping K-Regular Networks}
+\label{sec:overlapping_kreg}
+We will now investigate, what kind of properties we can get from merging K-Regular networks.
+First, we analysed the distribution for the average path length and the clustering coefficient values over 100 network instances with 100 nodes each.
+Since this variation is negligible we use the average as a descriptor for different configurations of k values and number of overlapping networks.
+(The reader should refer to figures \ref{append_fig:network_properties_apl_kreg} and \ref{append_fig:network_properties_cc_kreg} in the appendix for the box plot preliminary analysis.)
+
+Figure~\ref{fig:network_properties_apl_line_kreg} shows the average value for the \textit{average path length} of 100 k-regular network instances, each with 100 nodes.
+We can see that the \textit{average path length} changes more drastically when we go from 1 to 2 networks this is precisely the effect we can see in figure \ref{fig:network_properties_merge_2_10regular}.
+What we are seeing is that merging these networks at random effectively creates multiple shortcuts between points that were not connected in the original k-regular topology.
+Beyond this point, adding more networks does not modify this structural property in a significant way.
+Note that, since each network has 100 nodes, with $k=50$ the network is fully connected (hence the average path length being 1).
+
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}{.5\linewidth}
+		\centering
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_apl_line_kreg_12345"}
+		\caption{}
+		\label{fig:network_properties_apl_line_kreg_12345}
+	\end{subfigure}%
+	\begin{subfigure}{.5\linewidth}
+		\centering
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_apl_line_kreg_1020304050"}
+		\caption{}
+		\label{fig:network_properties_apl_line_kreg_1020304050}
+	\end{subfigure}
+	\begin{minipage}{0.9\textwidth}
+		\vspace{0.2cm}
+		\caption{Average value for the \textit{average path length} of 100 instances of overlapping k-regular networks(containing 100 nodes each) with ~k=\{1,2,3,4,5\}~(\ref{fig:network_properties_apl_line_kreg_12345}), and k= ~\{10,20,30,40,50\} (\ref{fig:network_properties_apl_line_kreg_1020304050}).}
+		\label{fig:network_properties_apl_line_kreg}
+	\end{minipage}
+\end{figure}
+
+\noindent Figure~\ref{fig:network_properties_cc_line_kreg} shows the results for the average \textit{clustering coefficient} of 100 instances of overlapping k-regular networks.
+We can see that adding multiple networks changes the clustering coefficient of the resulting structure.
+We can see that for $k \le 20$ the clustering coefficient drops when we add a second network.
+This happens because when we merge these networks, their connectivity is not enough to generate shortcuts with tightly clustered neighbourhoods.
+The clustering coefficient is computed by taking the average local clustering coefficient of each node in the network.
+An initial highly clustered k-regular network (with all the nodes having the same structure) is affected when you modify the node neighbourhoods in such a way that some are more clustered than others.
+
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}{.5\linewidth}
+		\centering
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_cc_line_kreg_12345"}
+		\caption{}
+		\label{fig:network_properties_cc_line_kreg_12345}
+	\end{subfigure}%
+	\begin{subfigure}{.5\linewidth}
+		\centering
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_cc_line_kreg_1020304050"}
+		\caption{}
+		\label{fig:network_properties_cc_line_kreg_1020304050}
+	\end{subfigure}
+	\begin{minipage}{0.9\textwidth}
+		\vspace{0.2cm}
+		\caption{Average value for the \textit{clustering coefficient} of 100 instances of overlapping k-regular networks(containing 100 nodes each) with ~k=\{1,2,3,4,5\}~(\ref{fig:network_properties_cc_line_kreg_12345}), and  k = \{10,20,30,40,50\} (\ref{fig:network_properties_cc_line_kreg_1020304050}).}
+		\label{fig:network_properties_cc_line_kreg}
+	\end{minipage}
+\end{figure}
+
+The exception is when you merge networks with $k=1$.
+These have a ring-like structure so there are no nodes forming a clique\footnote{A clique is a group of nodes such that every two nodes are connected by an edge.} with their neighbours.
+
+\subsubsection{Properties of Overlapping Scale-free Networks}
+In a preliminary analysis we looked at the distribution of property values that results from merging scale-free networks (see figure \ref{append_fig:network_properties_sf}).
+Like in the previous results, the properties don't vary much between the 100 different instances of each overlapping network configuration.
+We can then say that specific configurations display a specific \textit{average path length} and \textit{clustering coefficient} both for \textit{k-regular} networks and \textit{scale-free} networks.
+Since the average of these measures is still a good descriptor, we ploted the average of the \textit{average path length} (figure \ref{fig:network_properties_apl_line_sf_12345}) and \textit{clustering coefficient} (figure \ref{append_fig:network_properties_cc_sf_12345}) for each overlapping network configuration.
+
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}{.5\linewidth}
+		\centering
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_apl_line_sf_12345"}
+		\caption{}
+		\label{fig:network_properties_apl_line_sf_12345}
+	\end{subfigure}%
+	\begin{subfigure}{.5\linewidth}
+		\centering
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_cc_line_sf_12345"}
+		\caption{}
+		\label{fig:network_properties_cc_line_sf_12345}
+	\end{subfigure}
+	\begin{minipage}{0.9\textwidth}
+		\vspace{0.2cm}
+		\caption{Average value for the \textit{average path length} (\ref{append_fig:network_properties_apl_sf_12345}) and \textit{clustering coefficient} (\ref{append_fig:network_properties_cc_sf_12345}) for 100 instances of overlapping \textit{scale-free} networks(containing 100 nodes each).}
+		\label{fig:network_properties_line_sf}
+	\end{minipage}
+\end{figure}
+
+The parameter $d$ in figure \ref{fig:network_properties_line_sf} dictates how many edges are added by preferential attachment (see sectino \ref{sec:exp-setup_network_models}) each time a new node is added to a network (during its construction).
+This means that for $d=1$, the resulting network is a \textit{forest}: a network composed of disjoint tree graphs.
+Figure~\ref{fig:network_properties_apl_line_sf_12345} shows us that the \textit{average path length} still decreases consistently when we more networks.
+One of the characteristics of \textit{scale-free} networks is its short average  path length, thus, for $d \ge 2$ we can see that adding more edges does not make so much difference.
+Scale-free networks also have a reduced \textit{clustering coefficient} which is evident in figure \ref{fig:network_properties_cc_line_sf_12345}.
+This is increased when we merge more networks.
+
+\subsubsection{Merging K-Regular with Scale-Free Networks}
+Finally, we look at what happens when we merge k-regular networks with \textit{scale-free} networks.
+We didn't make an exhaustive analysis for this configuration but we show what is the resulting structure of such merging.
+You can see in figure \ref{fig:network_properties_merge_regular_scale-free} that this results in a network with a lower \textit{average path length} due to the shortcuts created by the \textit{scale-free} network.
+It is also less dense than the structure with two 10-regular networks (figure \ref{fig:network_properties_merge_2_10regular}).
+In this analysis we consider only the merging of two networks.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_10regular_2scale-free"}
+	\begin{minipage}{0.9\textwidth}
+		\caption{Overlapping of a 10-regular with a \textit{scale-free} network with D=2.}
+		\label{fig:network_properties_merge_regular_scale-free}
+	\end{minipage}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}{.5\linewidth}
+		\centering
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_apl_line_sf_kreg_12345"}
+		\caption{}
+		\label{fig:network_properties_apl_line_sf__kreg_12345}
+	\end{subfigure}%
+	\begin{subfigure}{.5\linewidth}
+		\centering
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_apl_line_sf_kreg_1020304050"}
+		\caption{}
+		\label{fig:network_properties_apl_line_sf_kreg_1020304050}
+	\end{subfigure}
+	\begin{minipage}{0.9\textwidth}
+		\vspace{0.2cm}
+		\caption{Average \textit{average path  length} for 100 instances of heterogeneous network configurations:  1 \textit{scale-free} with $d=\{1,2,3,4,5\}$ and 1 \textit{k-regular} network with $k=\{1,2,3,4,5\}$ (\ref{fig:network_properties_apl_line_sf__kreg_12345}) and $k=\{10,20,30,40,50\}$ (\ref{fig:network_properties_apl_line_sf_kreg_1020304050}).
+(See the respective box plots in the appendix: figure \ref{append_fig:network_properties_apl_sf_kreg}).}
+		\label{fig:network_properties_line_apl_sf_kreg}
+	\end{minipage}
+\end{figure}
+
+Figure \ref{fig:network_properties_line_apl_sf_kreg} shows the \textit{average path length} of 100 independently generated instances of combinations of 1 \textit{k-regular} network and 1 \textit{scale-free} network with different values $k$ and $d$ respectively.
+We can see that for configurations where the \textit{k-regular} networks have low values of $k$ (figure \ref{fig:network_properties_apl_line_sf__kreg_12345}), adding a \textit{scale-free} network always decreases the \textit{average path length}.
+Moreover the higher the $d$ the lower the path length as more connections are formed between different nodes.
+Which higher values of $k$ (figure \ref{fig:network_properties_apl_line_sf_kreg_1020304050}) however, increasing the value of $d$ does not decrease the \textit{average path length}.
+This is not surprising given that with that level of connectivity having a more connected \textit{scale-free} doesn't make such an impact.
+The first network is already highly dense and connected so adding a few extra connections doesn't matte --what matters in this case is that there is a scale-free network creating the extra shortcuts between nodes that weren't connected before.
+
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}{.5\linewidth}
+		\centering
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_cc_line_sf_kreg_12345"}
+		\caption{}
+		\label{fig:network_properties_cc_line_sf__kreg_12345}
+	\end{subfigure}%
+	\begin{subfigure}{.5\linewidth}
+		\centering
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_cc_line_sf_kreg_1020304050"}
+		\caption{}
+		\label{fig:network_properties_cc_line_sf_kreg_1020304050}
+	\end{subfigure}
+	\begin{minipage}{0.9\textwidth}
+		\vspace{0.2cm}
+		\caption{Average \textit{clustering coefficient} for 100 instances of heterogeneous network configurations:  1 \textit{scale-free} with $d=\{1,2,3,4,5\}$ and 1 \textit{k-regular} network with $k=\{1,2,3,4,5\}$  (\ref{append_fig:network_properties_cc_sf_12345}) and $k=\{10,20,30,40,50\} $ (See the respective box plots in the appending: figure\ref{append_fig:network_properties_cc_sf_kreg}).}
+		\label{fig:network_properties_line_cc_sf_kreg}
+	\end{minipage}
+\end{figure}
+
+\noindent Figure \ref{fig:network_properties_line_cc_sf_kreg} show the results for the \textit{clustering coefficient}.
+These are similar to the results we get for \textit{k-regular} networks (see figure \ref{network_properties_cc_line_kreg}).
+the difference is that we are not adding more networks but rather increasing the parameter $d$ of the scale-free.
+Curiously in this case, the effects are qualitatively similar with the ones of merged \textit{k-regular} network with low value of $k$.
+With high values of $k$ (figure \ref{fig:network_properties_cc_line_sf_kreg_1020304050}) we can see that higher values of $d$ are not enough to make the network more clustered.
+This is because, scale-free networks are more sparse and have a very low number of triangles between nodes.
+
+%***************************************************
+%	Context Permeability 
+%***************************************************
+\subsection{Context Permeability}
+\label{sec:results:context_permeability}
+
+In this section, we discuss the results for various set of experiments on the first model we presented --the \textit{context permeability model} \cite{Antunes2007,Antunes2010}.
+In a first set of experiments, the agent space was structured using \textit{k-regular} and \textit{scale-free }social networks.
+Each network layer was configured with the same topology.
+We analyse the context permeability model in terms of convergence to consensus: the ratio of simulations that converged to total consensus over 3000 runs; and how many agent encounters were needed for this to happen.
+
+\subsubsection{Convergence Ratio}
+\label{sec:ctx_perm_convergence}
+In this section we analyse the ratio of convergence to consensus for different network configurations.
+We correlate this ratio with the properties that the combined network structure exhibits.
+As we have seen in section \ref{sec:network_properties}, the properties don't vary much for different random network instances so we use the average as the descriptor for these properties in this correlation.
+
+The following tables show the results of our simulations.
+Table ~\ref{tab:regular_convergence} show the percentage of total consensus achieved within 2000 cycles for 3000 runs.
+We can see that for k-regular networks with a small $k$, consensus is rarely achieved with a single network.
+However, as soon as we add more networks, consensus is achieved in a significantly greater number of occasions.
+These results are especially interesting for the \textit{scale-free }networks (table \ref{tab:scale-free_convergence}): as soon as we add more planes, for a \textit{scale-free} with $d\ge2$, we can achieve consensus in a lot of occasions.
+This is to show that achieving consensus is not just a matter of connectivity.
+With \textit{scale-free} networks, we can achieve consensus more often with less clustered networks.
+This convergence is achieved not because of the clustering coefficient but rather due to lower \textit{average path length}.
+This is difficult to visualise using only the tables and the previous plots so, to confirm this hypothesis, we measured the \textit{Spearman's correlation} between the ratio of convergences to consensus, the average of \textit{average path length} , and the average of \textit{clustering coefficient} for the corresponding network configurations (see table \ref{tab:convergence_correlation}).
+
+\begin{table}[H]
+	\centering		
+	\begin{minipage}{0.9\textwidth}
+		\caption{Ratio of convergence to total consensus in 3000 independent runs with with a number of concomitant networks ($\#$ nets.) equal in kind: k-regular networks with $k=\{1,2,3,4,5,10,20,30,40,50\}$.}
+		\label{tab:regular_convergence}
+	\end{minipage}
+
+	\setlength{\tabcolsep}{.30000em}
+	\begin{tabular}{c|SSSSSSSSSS}
+
+		\toprule
+		& \multicolumn{10}{c}{value for k} \\ 
+		\# nets.  & 1 & 2 & 3 & 4 & 5 & 10 & 20 & 30 & 40 & 50\\
+		\midrule
+		1  & 0.0000 & 0.0000 & 0.0006667 & 0.0050  & 0.01633 & 0.1830 & 0.6713 & 0.9673 & 1.0000 & 1.0000 \\
+		2  & 0.0770 & 0.5887 & 0.8136667 & 0.8967 & 0.93467 & 0.9817 & 0.9977 & 1.0000 & 1.0000 & 1.0000 \\
+		3  & 0.6560 & 0.9417 & 0.9780000 & 0.9920 & 0.99433 & 0.9997 & 1.0000 & 1.0000 & 1.0000 & 1.0000 \\
+		4  & 0.8780 & 0.9867 & 0.9966667 & 0.9993 & 1.00000 & 1.0000 & 1.0000 & 1.0000 & 1.0000 & 1.0000 \\
+		5  & 0.9497 & 0.9937 & 0.9993333 & 1.0000 & 1.00000 & 1.0000 & 1.0000 & 1.0000 & 1.0000 & 1.0000 \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+\begin{table}[H]
+	\centering
+	\begin{minipage}{0.9\textwidth}
+		\caption{Ratio of convergence to total consensus in 3000 independent runs with a number of concomitant networks ($\#$ nets.) equal in kind: \textit{scale-free} networks with $d=\{1,2,3,4,5\}$.}	
+		\label{tab:scale-free_convergence}
+	\end{minipage}
+
+	\setlength{\tabcolsep}{.30000em}
+	\begin{tabular}{c|SSSSS}
+		\toprule
+		& \multicolumn{5}{c}{value for d} \\ 
+		$\#$ nets.  & 1 & 2 & 3 & 4 & \multicolumn{1}{c}{5} \\ 
+		\midrule
+		1  &  0.0000  &  0.2903  &  0.8590  &  0.9573  &  0.9873  \\
+		2  &  0.2840  &  0.9287  &  0.9877  &  0.9973  &  0.9980  \\
+		3  &  0.7793  &  0.9850  &  0.9970  &  1.0000  &  1.0000  \\
+		4  &  0.9287  &  0.9977  &  0.9997  &  1.0000  &  1.0000  \\
+		5  &  0.9737  &  0.9997  &  1.0000  &  1.0000  &  1.0000  \\
+		\hline 
+	\end{tabular}
+\end{table}
+
+\begin{table}[H]
+	\caption{Spearman's correlation between convergence ratio (CR), average \textit{average path length} (APL) and \textit{clustering coefficient} (CC) along with the respective p-value and confidence interval, for a confidence level of 95\%.}
+	\label{tab:convergence_correlation}
+
+	\centering	
+	\begin{tabular}{r|cc|cll}
+
+		\toprule
+		network model & X & Y & Correlation & CI(95\%) & p-value \\
+		\midrule
+		k-regular & CR & APL & -0.726 & [-0.836, -0.561] & \num[scientific-notation = true]{2.437e-09} \\
+		k-regular & CR & CC & 0.264   &   [-0.015,  0.505]       &    \num[scientific-notation = true]{0.064}     \\
+		\midrule
+		scale-free & CR & APL &    -0.912     &  [-0.961, -0.808]       &   \num[scientific-notation = true]{2.28e-10} \\
+		scale-free & CR & CC & 0.633   &   [0.318, 0.823]  &   \num[scientific-notation = true]{0.0006776} \\
+		\hline
+
+		\hline
+	\end{tabular}
+\end{table}
+
+\subsubsection{Number of Encounters to Achieve Consensus}
+\label{sec:ctx_perm_encounters}
+We now analyse the convergence in terms of average number of meetings during a simulation run.
+Since the maximum number of simulation cycles is 2000, the maximum number of encounters is 2000000 (we have 100 agents and each one performs 1 encounter per cycle).
+We show that for some configurations, the average of encounters is not a good descriptor since it varies greatly from run to run.
+It is better to look at the distributions of these measures rather than considering the average.
+Nevertheless, we included the data with all the average number of encounters as well as the respective standard deviations for different network configurations.
+You can find this data in appendix \ref{append_ctx_permeability}.
+
+%boxplots for k-regular networks
+First, we present the results for k-regular networks.
+In the box plots To observe the distribution of the number of encounters consider the box plots for $k = \{1,2,3,4,5\}$ (figure \ref{fig:ctx_perm_kreg_12345}) and $k =\{10,20,30,40,50\}$ (figure \ref{fig:ctx_perm_kreg_1020304050}).
+In figure \ref{fig:ctx_perm_kreg}, we focus on configurations with a number of networks $\ge 3$ since less networks lead to much worse results in terms of convergence speed.
+These plots still present two types of situations: the typical runs in which the number of encounters doesn't vary that much and some ``outlier runs" which present some interesting dynamics as we will see later.
+
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}{.49\linewidth}
+		\centering
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_permeability_encounters_kregular_12345"}
+		\caption{}
+		\label{fig:ctx_perm_kreg_12345}
+	\end{subfigure}%
+	\begin{subfigure}{.49\linewidth}
+		\centering
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_permeability_encounters_kregular_1020304050"}
+		\caption{}
+		\label{fig:ctx_perm_kreg_1020304050}
+	\end{subfigure}
+	\begin{minipage}{0.9\linewidth}
+		\vspace{0.2cm}
+		\caption{Number of meetings over 100 independent simulation runs for multiple k-regular networks: $k=\{1,2,3,4,5\}$~(\ref{fig:ctx_perm_kreg_12345}) and $k=\{10,20,30,40,50\}$~(\ref{fig:ctx_perm_kreg_1020304050})).}
+		\label{fig:ctx_perm_kreg}
+	\end{minipage}
+\end{figure}
+
+\noindent Figure~\ref{fig:ctx_perm_kreg} shows us results that are qualitatively similar to what we previously observed for convergence ratios (see section \ref{sec:ctx_perm_convergence}).
+Networks with less connectivity and a greater average path length lead to total convergence less often.
+Moreover, the simulation outcomes vary much more in comparison with the other configurations ($k>1$ and $networks \ge 3$).
+
+Notice that for $k=3$ and $networks=3$ (\ref{fig:ctx_perm_kreg_1020304050}), we still have runs that deviate from what we consider the typical behaviour.
+Instead of disregarding this as a simple outlier, we show that this run allows us to gain an insight on the dynamics of our \textit{External Majority} consensus game.
+
+Before anything else we analysed the network structure from this run and observed that there were no distinct differences between the network instances from the ``outlier run" and the ones of the ``typical" run.
+This suggested that this can be a property of the game itself --and of the network structure that leads to this situation -- and what happens is that the agents reach a state from which converging towards consensus is significantly harder.
+Villatoro \cite{Villatoro2013}  found that some complex network models lead consensus games to form metastable sub-conventions.
+These are very difficult to break and reaching 100\% agreement is not as straightforward as assumed by previous researchers.
+We are not concerned with this difficulty but rather with what happens in similar cases.
+Figure~\ref{fig:ctx_perm_kreg_runs} shows the consensus progression for two simulation runs a typical case and the outlier.
+
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}{.49\linewidth}
+		\centering
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_permeability_simrun_kregular_k10_normal"}
+		\caption{Typical Run}
+		\label{fig:ctx_perm_kreg_run_normal}
+	\end{subfigure}%
+	\begin{subfigure}{.49\linewidth}
+		\centering
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_permeability_simrun_kregular_k10_outlier"}
+		\caption{Outlier Run}
+		\label{fig:ctx_perm_kreg_run_outlier}
+	\end{subfigure}
+
+	\begin{minipage}{0.9\linewidth}
+		\vspace{0.2cm}
+		\caption{Number of agents with each opinion during a simulation run: typical run in \ref{fig:ctx_perm_kreg_run_normal} and ``outlier run" in \ref{fig:ctx_perm_kreg_run_outlier}.}
+		\label{fig:ctx_perm_kreg_runs}
+	\end{minipage}
+\end{figure}
+
+\noindent In our case, we take the outlier in the configuration with $k=3$ and $networks=3$ and look at the memory that agents use in the consensus game.
+As we described previously, agents record the number of individuals encountered with each opinion value (two opinions in this case).
+We look at the average difference between the number of opinions observed for all the agents.
+We also look at the variance to see if the opinion observations evolve in an uniform fashion throughout the simulation.
+Figure~\ref{fig:ctx_perm_kreg_runs_diff} shows the average difference between opinion memory for the first 10 steps (which was when the simulation converged for the normal run).
+
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}{1\linewidth}
+		\centering
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/ cp-regular-normal-run-memory-diff"}
+		\caption{Typical Run}
+		\label{fig:ctx_perm_kreg_run_normal_diff}
+	\end{subfigure}%
+	\\
+	\begin{subfigure}{1\linewidth}
+		\centering
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/ cp-regular-outlier-run-memory-diff"}
+		\caption{Outlier Run}
+		\label{fig:ctx_perm_kreg_run_outlier_diff}
+	\end{subfigure}
+
+	\begin{minipage}{0.9\linewidth}
+		\vspace{0.2cm}
+		\caption{Average and variance of the difference between opinions observed for the 100 agents: typical run in figure \ref{fig:ctx_perm_kreg_run_normal_diff} and first steps of the``outlier run" in figure \ref{fig:ctx_perm_kreg_run_outlier_diff}.}
+		\label{fig:ctx_perm_kreg_runs_diff}
+	\end{minipage}
+\end{figure}
+
+We can see that both the average difference in the opinion memory and the variance, rise faster in the normal run than it does in the outlier run.
+This is not enough to establish that there is a significant difference between the two.
+Moreover, the memory differences are quite similar but the number of agents for each opinion was quite even.
+This happens due to the position of agents in the network and their initial opinion values.
+These circumstances led the agents to a initial stability.
+Note that the opinion difference continues to rise throughout the simulation along with the variance.
+The variance starts to increase more rapidly after 200 steps.
+The exponential growth reveals that the convergence to consensus is not done evenly throughout the network, this is one of the reasons why consensus takes more time to achieve.
+Also, the low variance in the first $200$ steps shows us that the opinion strength was evenly distributed --we have almost the same number of agents for each opinion but the memory differences are qualitatively the same for both opinions.
+As soon as this variance increases, one of the opinions breaks the stable state and the convergence towards global consensus begins.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=1\linewidth]{"../analysis/pdf/ cp-regular-outlier-fullrun-memory-diff"}
+	\begin{minipage}{0.9\textwidth}
+		\caption{Average and variance of the difference between opinions observed for the 100 agents throughout the outlier run.}
+		\label{fig:ctx_perm_kreg_run_outlier_diff_full}
+	\end{minipage}
+\end{figure}
+
+\noindent In other words, in some sections of the network, the agents converged towards one opinion and continue to reinforce each other (leading the opinion difference to grow) and the more regions converge, the faster the global convergence is.
+%boxplots for scale-free networks
+
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}{.49\linewidth}
+		\centering
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_permeability_encounters_sf"}
+		\caption{}
+		\label{fig:ctx_perm_sf_full}
+	\end{subfigure}%
+	\begin{subfigure}{.49\linewidth}
+		\centering
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/   context_permeability_encounters_sf_best"}
+		\caption{}
+		\label{fig:ctx_perm_sf_best}
+	\end{subfigure}
+	\begin{minipage}{0.9\linewidth}
+		\vspace{0.2cm}
+		\caption{Number of meetings over 100 independent simulation runs for multiple \textit{scale-free} networks: with d=\{1,2,3,4,5\} (\ref{fig:ctx_perm_sf_full}) with a zoom on the best configurations in \ref{fig:ctx_perm_sf_best}.}
+		\label{fig:ctx_perm_sf}
+	\end{minipage}
+\end{figure}
+
+\noindent Figure~\ref{fig:ctx_perm_sf} shows the average number of encounters during 100 independent simulation runs for \textit{scale-free} networks.
+(We don't include the configuration for 1 network and $d = 1$ because as we have seen in the convergence results, these never converge.
+The convergence ratio is very low for the configurations with 1 network $d = 2$ and 2 networks with $d = 1$; hence the high number of encounters~(see also table \ref{tab:scale-free_convergence}).
+
+These results are similar to those of \textit{k-regular} in that adding more networks speeds up the convergence to consensus.
+The difference is that more ``atypical" runs occur with multiple \textit{scale-free} networks.
+Again, this is the effect ot these types of topologies.
+As we discussed previously, in these less connected topologies, agents are more prone to be arranged in such a way that progression towards consensus is more difficult to attain due to bottlenecks to regions in the network that converged to different opinion values.
+
+%boxplots for k-regular + scale-free networks
+\subsubsection{Heterogeneous Network Configuration}
+We also performed experiments where we mixed the network topologies: in this case we used 1 \textit{scale-free} and 1 \textit{k-regular} networks.
+Table~\ref{tab:regular_scale-free_convergence} shows the convergence ratio for the heterogeneous network configuration with the multiple values for $d$ and $k$ for the \textit{scale-free} and \textit{k-regular} respectively.
+
+\begin{table}[H]
+	\centering
+	\begin{minipage}{0.9\textwidth}
+		\caption{Ratio of convergence to total consensus in 3000 independent runs with two networks: 1 \textit{k-regular} and 1 \textit{scale-free} network with different $k$ and $d$ values respectively.}	
+		\label{tab:regular_scale-free_convergence}
+	\end{minipage}
+	\setlength{\tabcolsep}{.30000em}
+	\begin{tabular}{c|SSSSSSSSSS}
+
+		\toprule
+		& \multicolumn{10}{c}{k} \\ 
+		d  & 1 & 2 & 3 & 4 & 5 & 10 & 20 & 30 & 40 & \multicolumn{1}{c}{50} \\ 
+		\midrule
+		1  & 0.18 & 0.47 & 0.55 & 0.67 & 0.61 & 0.76 & 0.77 & 0.81 & 0.75 & 0.82 \\
+		2  & 0.63 & 0.72 & 0.88 & 0.89 & 0.90 & 0.97 & 1.00 & 1.00 & 0.99 & 1.00 \\
+		3  & 0.77 & 0.86 & 0.87 & 0.97 & 0.98 & 0.99 & 0.98 & 0.99 & 1.00 & 1.00 \\
+		4  & 0.73 & 0.92 & 0.92 & 0.97 & 0.96 & 0.96 & 0.99 & 1.00 & 1.00 & 1.00 \\
+		5  & 0.87 & 0.85 & 0.94 & 0.94 & 0.98 & 0.99 & 1.00 & 1.00 & 1.00 & 1.00 \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+\noindent One of the differences lies in the configuration with $d=1$ and $k=1$.
+The convergence ratio is higher than with $2$ $1-regular$ networks (see table \ref{tab:regular_convergence}) --but not better than two \textit{scale-free} networks.
+This happens because, with $k=1$ the network is basically a ring and has the maximum possible average path length for a connected graph.
+Adding two rings, improves this but underlying structure is still very susceptible to self-reinforcing structures (a connected sub-graph is basically a line).
+Adding a \textit{scale-free} changes this drastically as we are mixing tree-like network components with this first circle.
+
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}{.49\linewidth}
+		\centering
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_permeability_encounters_sfreg_k1020304050"}
+		\caption{}
+		\label{fig:ctx_perm_sfkreg_1020304050full}
+	\end{subfigure}%
+	\begin{subfigure}{.49\linewidth}
+		\centering
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/  context_permeability_encounters_sfreg_k1020304050_best"}
+		\caption{}
+		\label{fig:ctx_perm_sfkreg_1020304050best}
+	\end{subfigure}
+	\begin{minipage}{0.9\linewidth}
+		\vspace{0.2cm}
+		\caption{Number of meetings over 100 independent simulation runs for heterogeneous configuration: 1 \textit{k-regular} network with  $k=\{1,2,3,4,5\}$ and 1 \textit{scale-free} network with $d\{1,2,3,4,5\}$.
+Figure \ref{fig:ctx_perm_sfkreg_1020304050best} shows a zoom on the best configurations.}
+		\label{fig:ctx_perm_sfkreg}
+	\end{minipage}
+\end{figure}
+
+Figure \ref{fig:ctx_perm_sfkreg} shows the results for the number of encounters necessary for the agents to achieve consensus.
+We focus on the \textit{k-regular} networks with higher values of $k$.
+We can see that with these two networks, the configurations with values of $d>=2$ for \textit{scale-free} networks produce drastically better results in terms of speed of convergence.
+
+The data for the average number of encounters, as well as the respective standard deviations referent to the results in figure \ref{fig:ctx_perm_sfkreg} can be found in appendix \ref{append_ctx_permeability}, table \ref{append_tab:ctx_perm_kreg_sf_encounters}.
+
+\subsection{Context Switching}
+In this section, we present the results relative to the context switching model.
+The difference between this model and the previous one is that the agents no longer interact in the multiple networks at the same time (being able to select any neighbour at a given simulation step).
+In this model, they become active in a single network at a time.
+Agents can switch to a different network at the end of each step.
+The switching mechanism uses a probability associated with the current network in which the agent is currently active.
+With this new idea of swapping contexts, we covered some space left undeveloped in Antunes and colleagues original work \cite{Antunes2007,Antunes2010}.
+
+As we discussed previously in section \ref{sec:models_cs} (see model \ref{model:context_switching}), the switching probability dictates the probability an agent has of switching \textit{from} the current network after an encounter has been performed.
+In an abstract manner, this allows us to model how much time agents spend on each network.
+A further development of this model will be to assign different preferences to different networks for each agent.
+This can help us model phenomena such as real-world agents that dedicate more or less time consuming content from different social networks.
+For now we attribute this probability to the network to contain the model complexity.
+
+\subsubsection{Exploring the Switching Probability}
+We first look at the influence of the new parameter (switching probability) in the convergence to consensus.
+We span the switching probability between $0$ and $1$ in intervals of $0.05$.
+We do this for 2 networks with \textit{k-regular} and \textit{scale-free} topologies.
+Figure \ref{fig:ctx_cs_2_kregular} shows the results for two \textit{k-regular} networks: one configuration with $k = 10$ and one configuration with $k = 30$.
+We use these two configurations to observe the relationship between the number of encounters to achieve consensus, the switching probability parameter and the connectivity of the networks.
+Remember that with $k=30$ the average path length is also lower (see section \ref{sec:overlapping_kreg}).
+
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}{0.49\linewidth}
+		\centering
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/  context_switching_2_10_regular _switching_contour"}
+		\caption{10-Regular Networks}
+		\label{fig:ctx_cs_2_10kreg}
+	\end{subfigure}%
+	\begin{subfigure}{0.49\linewidth}
+		\centering
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/  context_switching_2_30_regular _switching_contour"}
+		\caption{30-Regular Networks}
+		\label{fig:ctx_cs_2_30kreg}
+	\end{subfigure}
+
+	\begin{minipage}{0.9\linewidth}
+		\vspace{0.2cm}
+		\caption{Contour plot for the average number of meets during a simulation for 100 independent runs: 2 \textit{10-regular} networks (\ref{fig:ctx_cs_2_10kreg}) and \textit{30-regular} networks (\ref{fig:ctx_cs_2_30kreg}).
+See the perspective plots in appendix \ref{append_ctx_switching}.}
+		\label{fig:ctx_cs_2_kregular}
+	\end{minipage}
+\end{figure}
+
+\noindent We can see that with smaller values of $k$, symmetry in the context switching probability is more important (having the same probability in both networks) if the agent switches less from one of them.
+This is the case because switching less from one network means spending more time in that network.
+This means that switching more from other network can be disruptive to a neighbourhood that already converged to a sub-convention.
+This can be observed in configurations with \textit{k-regular} networks (figure \ref{fig:ctx_cs_2_10kreg}) but it is especially apparent in \textit{scale-free} networks (figure \ref{fig:ctx_cs_2_sf_d1}).
+
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}{0.49\linewidth}
+		\centering
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/  context_switching_2_sf_d1 _switching_contour"}
+		\caption{\textit{Scale-Free} $d=1$}
+		\label{fig:ctx_cs_2_sf_d1}
+	\end{subfigure}%
+	\begin{subfigure}{0.49\linewidth}
+		\centering
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/  context_switching_2_sf_d5 _switching_contour"}
+		\caption{\textit{Scale-Free} $d=5$}
+		\label{fig:ctx_cs_2_sf_d5}
+	\end{subfigure}
+
+	\begin{minipage}{0.9\linewidth}
+		\vspace{0.2cm}
+		\caption{Contour plot for the average number of meets during a simulation for 100 independent runs: 2 \textit{scale-free} networks with $d=1$ (\ref{fig:ctx_cs_2_sf_d1}) and $d=5$ (\ref{fig:ctx_cs_2_sf_d5}).
+See the perspective plots in  appendix \ref{append_ctx_switching}.}
+		\label{fig:ctx_cs_2_sf}
+	\end{minipage}
+\end{figure}
+
+When we increase the connectivity (and lower the average path length), both in \textit{k-regular} and \textit{scale-free} networks, the switching probability becomes ``irrelevant": in the sense that you can use any probability you want and the results in term of speed of convergence will be the same.
+The exception is obviously when considering the switching probability with value $0$.
+In this case, agents are isolated (they are initially equally distributed throughout the networks) and reaching consensus becomes very hard.
+--Especially hard since agents are active only in one network: being in all the networks creates the possibly of disconnected graphs in the networks they are not currently active.
+
+One major difference from the previous model is that the agents no longer can select a neighbour for interaction from any network.
+The selection has to be made from the network they are currently active in.
+This makes so that agents spending different amounts of time in distinct network topologies are influenced differently -- an agent can be very influential in one network being a very central node in that context, and marginally important in the other one: in a sense its opinion in one network can be more important to overall convergence than in other network due to its position in the network.
+
+To check the influence of topology and connectivity in the new switching dynamics we took the most susceptible network type (the \textit{scale-free} networks) and performed the following experiment.
+We setup 2 \textit{scale-free} networks; one with $d=1$ and the other with $d=5$.
+We then performed the
+same span of switching probability similarly to the previous experiments. The results can be seen in figure \ref{fig:ctx_cs_sf_d5_d1}.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_switching_sf_d5_d1 _switching_contour"}
+	\begin{minipage}{0.9\textwidth}
+		\caption{Contour plot for the average number of meets during a simulation for 100 independent runs: 2 \textit{scale-free} networks, the first with $d=5$ and the second with $d=1$.
+See the perspective plots in  appendix \ref{append_ctx_switching} (figure \ref{append_fig:ctx_cs_sf_d5_d1}).
+		}
+		\label{fig:ctx_cs_sf_d5_d1}
+	\end{minipage}
+\end{figure}
+
+We can see that in this case, its more important to switch \textit{from} the network with lower average path length and a forest-like composition ($d=1$) with a probability of least the same value or more than the one of the other network (with $d=5$).
+The same can be observed when we mix the two topologies (\textit{k-regular} with \textit{scale-free}) as we can see in figure \ref{fig:ctx_cs_kreg10_sfd1}.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_switching_1_10regular_1_scale-free_d1 _switching_contour"}
+	\begin{minipage}{0.9\textwidth}
+		\caption{Contour plot for the average number of meets during a simulation for 100 independent runs: 1 \textit{10-regular} network (k=10) and a \textit{scale-free} network with $d=1$.
+See the perspective plots in  appendix \ref{append_ctx_switching} (figure \ref{append_fig:ctx_cs_kreg10_sfd1}).
+		}
+		\label{fig:ctx_cs_kreg10_sfd1}
+	\end{minipage}
+\end{figure}
+
+It seems that basically switching less from the less connected network is bad in both cases: spending more time in the network with bigger neighbourhoods allows for a stabler convergence.
+Sub-conventions can emerge in \textit{scale-free} networks with $d=1$ because usually some network regions are isolated by a single node --the root of the sub-tree they belong to.
+
+\subsubsection{Comparison with Context Permeability}
+Finally, to compare the context switching model with the previous model of context permeability, we constructed the following experiment.
+We froze the switching probabilities in the values $\zeta={0.25,0.5,0.75}$ and varied the number of networks.
+(We considered these values because they conveniently characterise the probability in low, medium and high switching) We compare the results with the context permeability in terms of average number of encounters to achieve consensus.
+Note that we have seen that in some cases, due to the distribution of the number of encounters, the average is not an accurate descriptor for the convergence.
+Nonetheless, normally the configurations with highly variable outcomes also produce an average that is qualitatively distinct from the rest of the configurations (see for example figure \ref{fig:ctx_perm_kreg} in section \ref{sec:ctx_perm_encounters}).
+As such, we took the average number of encounters during the simulations to compare what happens in the context switching model with the context permeability model.
+
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}{.49\linewidth}
+		\centering
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_switching_encounters_comp_kregular_groupedbynets_2"}
+		\caption{}
+		\label{fig:ctx_switching_comp_kreg_2}
+	\end{subfigure}%
+	\begin{subfigure}{.5\linewidth}
+		\centering
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_switching_encounters_comp_kregular_groupedbynets_3"}
+		\caption{}
+		\label{fig:ctx_switching_comp_kreg_3}
+	\end{subfigure}\\
+	\begin{subfigure}{.49\linewidth}
+		\centering
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_switching_encounters_comp_kregular_groupedbynets_4"}
+		\caption{}
+		\label{fig:ctx_switching_comp_kreg_4}
+	\end{subfigure}
+	\begin{subfigure}{.5\linewidth}
+		\centering
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_switching_encounters_comp_kregular_groupedbynets_5"}
+		\caption{}
+		\label{fig:ctx_switching_comp_kreg_5}
+	\end{subfigure}
+	\begin{minipage}{0.9\textwidth}
+		\vspace{0.2cm}
+		\caption{Average number of encounters during a simulation for 100 independent runs with \textit{k-regular} topologies in all the network layers.
+We compare the results of context switching with context permeability with a $number of networks = \{2,3,4,5\}$.
+The switching probability is the same in all the networks.
+}
+		\label{fig:ctx_switching_comp_kreg}
+	\end{minipage}
+\end{figure}
+
+Figure \ref{fig:ctx_switching_comp_kreg} shows us that for 2 networks the results in terms of number of encounters for the context switching approximate those we got for context permeability.
+When we increase the number of networks ($n\ge3$) the configurations with higher switching probability lead the results to be more close to what happens in context permeability.
+This is no surprise since more switching makes agents switch more often between networks and consequently allows them too choose more often from different neighbourhoods.
+This is almost the same as having a larger neighbourhood to choose from, which is what happened in the context permeability model.
+
+The surprise was that for values of $k \ge 20$, the results where practically the same for both models independently of the switching probability --even when we increased the number of networks, the number of encounters remains around $2000$ on average for all the models.
+Above a certain level of neighbourhood size (and overlapping which causes the average path length to drop), the switching probability becomes less influential.
+It is still important that we get comparable results because we are introducing a temporal components that was never explored before in these types of opinion dynamics models.
+The fact that the agents can become active in different networks at different points in time.
+
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}{.49\linewidth}
+		\centering
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_switching_encounters_comp_sf_groupedbynets_2"}
+		\caption{}
+		\label{fig:ctx_switching_comp_sf_2}
+	\end{subfigure}%
+	\begin{subfigure}{.5\linewidth}
+		\centering
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_switching_encounters_comp_sf_groupedbynets_3"}
+		\caption{}
+		\label{fig:ctx_switching_comp_sf_3}
+	\end{subfigure}\\
+	\begin{subfigure}{.49\linewidth}
+		\centering
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_switching_encounters_comp_sf_groupedbynets_4"}
+		\caption{}
+		\label{fig:ctx_switching_comp_sf_4}
+	\end{subfigure}
+	\begin{subfigure}{.5\linewidth}
+		\centering
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_switching_encounters_comp_sf_groupedbynets_5"}
+		\caption{}
+		\label{fig:ctx_switching_comp_sf_5}
+	\end{subfigure}
+	\begin{minipage}{0.9\textwidth}
+		\vspace{0.2cm}
+		\caption{}
+		\label{fig:ctx_switching_comp_sf}
+	\end{minipage}
+\end{figure}
+
+For \textit{scale-free} networks, figure \ref{ctx_switching_comp_sf} shows us similar results.
+It seems that a switching with a higher probability displays results similar with those of context permeability.
+In this case, adding more networks makes so that lower switching probabilities display slightly worse results.
+This influence is due to the fact that the neighbourhoods are considerably smaller in \textit{scale-free} networks --even with values of $d=5$-- so the impact of low switching was bound to be noticed.
+
+One final remark is that with context switching, we always achieve consensus being for \textit{k-regular} or \textit{scale-free} networks.
+In addition, increasing the number of networks seems to always reduce the number of encounters to achieve consensus in both models, this happens due to what we called \textit{permeability}.
+Having multiple points of dissemination that permeate between different social networks enhances the overall convergence to consensus.
+More isolated nodes to be reached in sparsely connected networks such as scale-free networks.
+
+%******************************************
+%	Conclusion
+%******************************************
+\section{Conclusion}
+\label{sec:conclusion-future}
+In this paper, we analysed and discussed our modelling framework for multi-relational models of social spaces.
+These results show that not only contexts play an important role in the dissemination of consensus in artificial agent societies, but also that simple mechanisms can generate a great deal of complexity, especially in these scenarios where conventions are being co-learned by multiple agents.
+Adding more networks to our opinion dynamics model leads to outcomes where consensus was achieved not only more often but also faster.
+
+Future work includes the analysis of different complex network models, while \textit{k-regular} and \textit{scale-free} networks are two of the most pervasive network examples in these types of simulations.
+There has been a growing number of models with different properties inspired by real-world phenomena that can be considered.
+We can also analyse the networks according to different properties such as the present of nodes with high centrality in the network (hubs).
+Moreover, we are plan to apply what we learned with our consensus games to cooperation problems.
+Constructing agents that can learn both behaviour and coordination procedures is a difficult task especially when working with large distributed artificial societies.
+Consensus games such as this one can be used to reduce the search space in problems where agents need to cooperate or coordinate.
+
+Note that while the convergence and number of encounters seem to be correlated with the average path length as we have seen previously, this might not be the only property that plays a role in faster convergence to consensus.
+Correlation is just an informal tool to helps us assert if some monotonic relationship exists.
+More research is needed to assert, for instance, if self reinforced structures like the ones reported by \cite{Villatoro2013} exist in our multi-network scenarios.
+In particular we would be interested to see if permeability mitigates the effects of such structures.
+
+We have seen that context permeability by context overlapping or switching can provide a fairly straight forward modelling methodology that can be used to compose simulation scenarios for more complex social spaces.
+What remains to be done is to identify more precise contextual structures in real-world networks.
+While capturing the structure of real social network can be a daunting task, we do have pervasive records of networking activity between social actors: online social networks.
+Analysing these, can lead us to insights about complex structural properties that emerge from user activity, and context that can be identified within those networks.
+A difficult --but not impossible-- prospect for further research would be to track similar contexts between different real online social networks.
+
+We are just scratching the surface of multi-relational models in social simulation with the next step being the connection of our model to the reality.
+
+\newpage
+\begin{appendices}
+	\include{appendix}
+\end{appendices}
+
 \bibliographystyle{elsarticle-num}

### 2014-08-18 R/experiment_utils.R

@@ -10,6 +10,7 @@ normal.range <- function(x){
 #@param param_file_name: a string with the filename / path to the parameter file
 #*******************************************************************************
 read.exp.parameters <- function(param_file_name){
+  library(data.table)
   params <- read.csv(param_file_name, header=TRUE, sep=";")
   #remove empty column at the end
   params<- params[,-ncol(params)]
@@ -28,12 +29,12 @@ read.exp.parameters <- function(param_file_name){
 # @param parameters: a previously loaded parameter table
 #*******************************************************************************
 print.exp.parameters <- function(parameters){
-  require(stargazer)
+  library(stargazer)
 
   stargazer(params, title="Simulation Parameters", type="html", align=FALSE, summary = FALSE)
 }
 
-require(ggplot2)
+
 plot.exp.box <- function(data,
                          x_factor,
                          data_y,
@@ -41,6 +42,9 @@ plot.exp.box <- function(data,
                          fill_label,
                          y_label,
                          x_label){
+  
+  library(ggplot2)
+  
   .e <- environment()
   plot <- ggplot(aes(y=data_y,x=x_factor,fill=fill_factor), data=data, environment=.e)  
   plot <- plot + geom_boxplot()
@@ -54,8 +58,7 @@ plot.exp.box <- function(data,
 #
 #***********************************************************************
 plot_opinion <- function(opinion_data){
-  op_run <- as.data.frame(opinion_data)
-  r_op_data <- melt(op_run, id=(c("step")), measure.vars=(c("num.opinion.0","num.opinion.1")))
+  r_op_data <- melt(opinion_data, id=(c("step")), measure.vars=(c("num-opinion-0","num-opinion-1")))
   names(r_op_data)<- c("step", "opinion", "value")
   
   .e <- environment()
@@ -73,8 +76,10 @@ plot_opinion <- function(opinion_data){
 }
 
 read.opinion.progress <- function(filename){
-  opinion_data <- read.csv(filename, sep=";")
-  opinion_data<- opinion_data[,-ncol(opinion_data)]
+  library(data.table)
+  opinion_data <- fread(filename)
+  opinion_data <- as.data.frame(opinion_data)
+  opinion_data<- opinion_data[,-c(ncol(opinion_data))]
[…]

### 2014-09-26 analysis/context_permeability.Rmd
context_permeability Rmd modified

@@
 
-We will start by loading the dependencies for this report.
+We will start by loading the dependencies for this analysis.
 ```{r}
@@
 In this analysis we look at the convergence to consensus for simulations that use 
-regular networks only. We will analyse two things: the *percentage of convergence to total consensus* and the *number of encounters* necessary to achieve concensus.
+regular networks only. We will analyse two things: the *rate of convergence to total consensus* and the *number of encounters* necessary to achieve concensus.
 
-We first load the data related to convergence to consensus. In this first dataset, we can find a single boolean variable {1,0} that tells us wheather or not consensus was achieved. 
+We first load the data related to convergence to consensus.
+In this first dataset, we can find a single boolean variable {1,0} that tells us wheather or not consensus was achieved.
+Tipically in all our experiments, we perform 100 independent runs, since we felt 100 runs were not enough to give us an accurate convergence ratio, we run an additional experiment in this case, were each configuration was tested in 3000 independent simulation runs.
 ```{r results='asis',message=FALSE}
@@
 We can now create a table to display the percentage of convergences to total 
-consensus **for each value of k and number of networks**.
+consensus **for each value of k and number of networks**. We use the aggregate function to compute the convergence ratio.
 
@@
 As we have seen in the previous convergence results.
+We use the ggplot2 library to create the box plots in this case.
+(you can check the source at ../R/experiment_utils.R)
 ```{r}

### 2014-09-28 doc/main.tex
review1 started: review from Luis

@@
 
-%scientific notation setup
+%scientific notation for tables setup
 \sisetup{
@@
 
-		\address[ul]{Group of Studies in Social Simulation (GUESS), Laboratory of Agent Modelling, University of Lisbon, 1749-016 Lisbon, Portugal}
+		\address[ul]{Group of Studies in Social Simulation (GUESS), Laboratory of Agent Modelling, Faculdade de Ciências, Universidade de Lisboa, 1749-016 Lisboa, Portugal}
 		\title{Modelling Structured Societies: a Multi-relational Approach to Context Permeability}
@@
 It shapes the way actors interact and create their identity within overlapping social contexts.
-Each actor interacts in multiple contexts located within relations that constitute their social space.
+Each actor interacts in multiple contexts, located within relations that constitute their social space.
 We present a modelling approach to construct structured agent societies with multiple concomitant social networks.
-We study the notion of context permeability using a consensus game in which agents try to achieve global consensus.
+We study the notion of context permeability, using a game in which agents try to achieve global consensus.
 We design and analyse two different models of permeability.
-In the first model agents interact concurrently in multiple social networks.
+In the first model, agents interact concurrently in multiple social networks.
 The second model uses a context switching mechanism that adds temporal dynamics to agent interaction.
 They switch between the different networks spending more or less time in each network.
-We compare each model and analyse the influence of different social networks in the speed of convergence to consensus.
+We compare each model and analyse the influence of different social networks regarding the speed of convergence to consensus.
 We conduct a series of experiments that show the impact of coexisting social networks when designing simulation models.
@@
 Simulation methods can range from data-driven paradigms to more abstract descriptions that allow us to create \textit{what-if-scenarios}.
-While most models are simplified descriptions of the real-world, many constitute complex systems themselves and thus the necessity of tools like simulation to explore their properties.
+While most models are simplified descriptions of the real-world corresponding target phenomena, many constitute complex systems themselves and thus the need for tools and techniques like simulation to explore their properties.
 In \cite{Emmeche1997}, Emmeche makes a distinction between two types of complexity.
-He characterises the complexity of real systems as \textit{``ontological complexity"} and the one of models as \textit{``descriptive complexity"}.
+He characterises the complexity of real systems as \textit{``ontological complexity''} and the one of models as \textit{``descriptive complexity''}.
 Examples of real-world target phenomena for social simulation models include for instance the joint assessments of policies or, in the context of economics and politics, \textit{the voting problem}.
-Herbert Simon investigations on this problem were also one of the first stepping stones to the field of social simulation \cite{Simon1954}.
+Herbert Simon's investigations on this problem were also one of the first stepping stones to the field of social simulation \cite{Simon1954}.
 
 	In agent-based \textit{opinion dynamics}, agent interactions are guided by \textit{social space} abstractions.
-In some models, dimensionality is irrelevant and any agent can interact with any other agents.
+In some models, dimensionality and structure are irrelevant and any agent can interact with any other agent.
 	Other approaches use an underlying structure to create agent neighbourhoods.
@@
 
-	%******************************************
-	%		Motivation 
-	%******************************************
-	%position, most agent-based models don't take into account  social relations and this is important
 	In real-world scenarios, actors engage in a multitude of social relations different in kind and quality.
@@
 Modelling multiple concomitant relations was an idea pioneered by Peter Albin in \cite{Albin1975} but without any further development.
-The complex social structures that results from interacting in these different dimensions forms the basis for the formation of social identity \cite{Roccas2002,Ellemers2002}.
+The complex social structures that result from interacting in these different dimensions form the basis for the formation of social identity \cite{Roccas2002,Ellemers2002}.
 
@@
 Starting with this premise of
-	using multiple social networks, we present a series of models that use these networks in different ways which creates distinct emergent dynamics.
-We want to observe the consequences of using multiple social networks at the same time ---while maintaining the model as simple and abstract as possible much like what happens with the current contributions on opinion dynamics present in the literature.
+	using multiple social networks, we present a series of models that use these networks in different ways, which create distinct emergent dynamics.
+We want to observe the consequences of using multiple social networks at the same time --- while maintaining the model as simple and abstract as possible, much like what happens with the current contributions on opinion dynamics present in the literature.
 
@@
 	This paper is organised as follows.
-In the next section we present work related to, \textit{opinion dynamics}, \textit{social space} modelling and \textit{complex network models}.
-In the following section, we describe our game of consensus and introduce multiple model variations designed to study the notion of context permeability and the process of consensus formation in multiple social networks.
+In the next section, we present work related to, \textit{opinion dynamics}, \textit{social space} modelling and \textit{complex network models}.
+In the following section, we describe our game of consensus and introduce multiple model variations, designed to study the notion of context permeability and the process of consensus formation in multiple social networks.
 Section \ref{sec:experimental-setup} describes the experimental set-up; the set of tool and methodologies followed to conduct our investigations.
-In section \ref{sec:results-discussion}, we present and discuss our results and compares the different simulation models.
-Finally we conclude by making a summary of what we learned from the simulation models and point out possible future research directions.
+In section \ref{sec:results-discussion}, we present and discuss our results and compare the different simulation models.
+Finally, we conclude by making a summary of what we learned from the simulation models and point out possible future research directions.
 
@@
 	\label{sec:relatedwork}
+	In this section, we present work related to, \textit{opinion dynamics}, \textit{social space} modelling and \textit{complex network models}.	
 	%******************************************
@@
 	\subsection{Opinion Dynamics and Consensus Formation}
-	Formal opinion dynamics models provide an understanding if not an analysis of opinion formation processes.
+	Formal opinion dynamics models provide an understanding, if not an analysis, of opinion formation processes.
 An early formulation of these models was designed to comprehend complex phenomena found empirically in groups \cite{French1956}.
@@
 
-	Opinion dynamics models try to study under which circumstances consensus or polarisation is reached.
-Agent-based models can have broader applications outside social simulation.
-In distributed systems in general, consensus is a means by which processes agree on some data value that is needed during computation, typically, this agreement is the result of a negotiation process often with the aid of a mediator.
-In human societies, social conventions emerge to deal with coordination and subsequently with cooperation problems \cite{Lewis1969}, these conventions are regularities of behaviour that can turn normative with time due to their being persistent solutions to such problems.
+	§§§ ESTA ULTIMA FRASE ESTÁ ESTRANHA!!! falta uma vírgula antes de model? mesmo assim não se perceberia bem... Podes rever, pf?
+
+	Opinion dynamics models try to study under which circumstances consensus, or polarisation is reached.
+Agent-based models can have broader application outside social simulation.
+In distributed systems in general, consensus is a means by which processes agree on some data value that is needed during computation.
+Typically, this agreement is the result of a negotiation process often with the aid of a mediator.
+In human societies, social conventions emerge to deal with coordination and subsequently with cooperation problems \cite{Lewis1969}.
+These conventions are regularities of behaviour that can turn normative with time, due to there being persistent solutions to such problems.
 Moreover, conventions typically originate from the necessity to resolve conflict.
@@
 The decentralised nature of these models of consensus is highly desirable for problems where dynamic control is needed.
-In these scenarios, creating conventions before hand (off-line) or developing a central control mechanism for generating them can be a difficult and intractable task.
+In these scenarios, creating conventions before hand (off-line), or developing a central control mechanism for generating them, can be a difficult and intractable task.
 MAS can be designed to update their values and strategies based on this local information.
-Consequently, the guarantee of achieving a global consensus and the efficiency of convergence towards it has been a natural concerns in the design of local interaction behaviours.
+Consequently, the guarantee of achieving a global consensus and the efficiency of convergence towards it has been a natural concern in the design of local interaction behaviours.
 
 	Consensus models are also investigated as means to create conventions in MAS.
-Shoham and Tennenholtz \cite{Shoham1994} create a bridge between economic literature and machine learning by studying a series of models in which multiple agents are engaged in learning a particular convention.
+Shoham and Tennenholtz \cite{Shoham1994} create a bridge between economic literature and machine learning, by studying a series of models in which multiple agents are engaged in learning a particular convention.
 They call this process \textit{co-learning}.
-The complexity of these systems derives from the its concurrent nature: one agents adapts to the behaviour of another agent it has encountered, as these agents update their behaviour in a similar fashion, this results in a highly non-linear system dynamics.
+The complexity of these systems derives from its concurrent nature: one agent adapts to the behaviour of another agent it has encountered, and as these agents update their behaviour in a similar fashion, this results in a highly non-linear system dynamics.
 In their work, Shoham and Tennenholtz define the notion of \textit{stochastic social games} and compare different rules with the objective of establishing conventions in a decentralised fashion.
-In their stochastic games, they present one particular rule which we use in our models:
+In their stochastic games, they present one particular rule that we use in our models:
 
@@
 
-	This EM was shown to coincide with \textit{Highest Cumulative Reward (HCR)} which is a simple rule that states that ``an agent should adopt an action that has yielded the highest cumulative reward to date".
-We chose to use EM in our simulation models for its simplicity and success in the evolution of conventions.
-We can see that there is an overlap between opinion dynamics from social simulation and agent based learning---or co-learning in this case.
+	This EM was shown to coincide with \textit{Highest Cumulative Reward (HCR)}, which is a simple rule that states that ``an agent should adopt an action that has yielded the highest cumulative reward to date.'' We chose to use EM in our simulation models for its simplicity and success in the evolution of conventions.
+We can see that there is an overlap between opinion dynamics from social simulation and agent based learning---or co-learning, in this case.
 
@@
 	\subsection{Social Structure in Simulation Models}
-	One of the most widely used approaches to represent social spaces in abstract simulation models is using a  bi-dimensional gridd.
-This approach has its origins in the first \textit{“checkerboard”} model introduced in computational social sciences by Thomas Schelling \cite{Schelling1971} and Sakoda \cite{Sakoda1971}.
+	One of the most widely used approaches to represent social spaces in abstract simulation models is using a  bi-dimensional grid.
+This approach has its origins in the first \textit{‚Äúcheckerboard‚Äù}
+	§§§ VER AQUI
+	model introduced in computational social sciences by Thomas Schelling \cite{Schelling1971} and Sakoda \cite{Sakoda1971}.
 Another famous example that uses bi-dimensional grids as social structure is the social simulation model of dissemination of culture from Axelrod \cite{Axelrod1997}.
 
-	Cellular automata (CA) is an example from the are of artificial life that also makes use of bi-dimensional structures to model neighbourhood interactions.
-While these models are idealised frameworks, the exploration of simple computational models can bring us deeper insights than models with high levels descriptive complexity which would render their analysis, very difficult.
-The work of Flache and Hegselmann \cite{FlacheHegselmann2001} relaxes the standard CA assumptions about the regular bi-dimensional grids by considering irregular grid structures (Voronoi diagrams).
+	Cellular automata (CA) are an example from the area of artificial life that also makes use of bi-dimensional structures to model neighbourhood interactions.
+While these models are idealised frameworks, the exploration of simple computational models can bring us deeper insights than models with high level descriptive complexity, which would render their analysis very difficult.
+The work of Flache and Hegselmann \cite{FlacheHegselmann2001} relaxes the standard CA assumptions about the regular bi-dimensional grids, by considering irregular grid structures (Voronoi diagrams).
 This work presents results on the robustness of some important general properties in relation to variations in the typical grid structure.
 We can also find contributions that incorporate both the complexity of network models and the behaviour of dynamic processes.
-One example of this combination is the work in \cite{Sullivan2000} which explores a graph-based cellular automaton to study the relationship between spatial form of urban systems and the robustness of different process dynamics under spatial change.
-Moreover this allows for the integration of real geographical information to construct the graph-cellular automata.
-This fact makes so that while the models of dynamic processes are relatively abstract, they are tested in spatial structures based on data from real complex structures and thus making a connection between purely abstract models and data-driven models.
+One example of this combination is the work in \cite{Sullivan2000}, which explores a graph-based cellular automaton to study the relationship between spatial form of urban systems and the robustness of different process dynamics under spatial change.
+Moreover, this allows for the integration of real geographical information to construct the graph-cellular automata.
+This fact causes that, while the models of dynamic processes are relatively abstract, they are tested in spatial structures based on data from real complex structures and thus making a connection between purely abstract models and data-driven models.
 
@@
 	%******************************************	
-
-	Finally, another type social space models are the \textit{random graph / network models}.
+	Finally, another type of social space models are the \textit{random graph/network models}.
 Networks with different properties can be built using network models.
@@
 These properties are typically found in---and the models inspired by---real-world network structures.
-One of the first complex network models is the random graph from Erdős and Renyi \cite{Erdos1959}.
+One of the first complex network models is the random graph from §§§ VER Erd≈ës and Renyi \cite{Erdos1959}.
 Other examples include the model of preferential attachment \cite{Barabasi1999} and the small-world network models \cite{Watts1998}.
@@
 	In this section, we present our modelling approach to explore the concept of permeability between contexts.
-In our approach, we considers multiple social networks as a way to represent the complex social space of an agent.
-This setting can be seen in a simulation as a n-dimensional scenario where each dimension surface represents a different social relation (see figure \ref{img:multiple-relations}).
+In our approach, we consider multiple social networks as a way to represent the complex social space in which an agent is inserted.
+In a simulation, this setting can be seen as a n-dimensional scenario, where each dimension surface represents a different social relation (see figure \ref{img:multiple-relations}).
 Each relation is instantiated using a social network model.
-The word ``context" is used in many different senses and it is subjected to many analysis \cite{Hayes1997}.
+The word ``context'' is used in many different senses and it is subjected to many analysis \cite{Hayes1997}.
 Here, we use the term \textit{social context} in a simpler and more strict way.
@@
 	We study the notion of context permeability in different simulation models in which agents interact using a simple consensus game.
-The society of agents has to adopt a binary \textquotedblleft option \textquotedblright according to a majority rule.
+The society of agents has to adopt a binary \textquotedblleft option\textquotedblright according to a majority rule.
 We use the speed of consensus as a measure for self-organisation, exploring the relationship between different network topologies and this measure.
@@
 For each simulation model, we present a description of the individual agent behaviour.
-Every model we present can be seen as a binary opinion dynamics model or a consensus game.
+Every model we present can be seen as a binary opinion dynamics model, or a consensus game.
 In this game, the society of agents tries to reach an arbitrary global consensus about two possible choices.
 Each agent keeps track of the number of choices observed from interaction partners throughout a simulation run.
-In each iteration, each agent selects an available neighbour to interact with and observes its current choice.
+In each iteration, each agent selects an available neighbour to interact with, and observes its current choice.
 The agent decides to switch its current choice if the observed option becomes the majority of the two possible choices.
@@
 
+	§§§ TALVEZ ACRESCENTAR ISTO???
+The reason we are not really interested in which exact option gets selected is the same reason why we chose such a content-neutral game for the individual interactions.
+From the very beginning, our research questions were focused on the collective properties, the structure of the networks involved, and the dynamical outcomes of the simulations, thus leaving out issues related with individual motivations and desired results, either for any individual agent or the society.
+Granted, most applications of this research will often include such goals, for inquisition into complex social issues, including possibly policy design, in which the individual rationalities must be considered, and will have a very strong influence on the collective outcomes.
+We opted not to taint the simulation with such matters, leaving that very interesting approach for future work.
+
 	\newpage
@@
 	This first model of context permeability \cite{Antunes2007,Antunes2010} is designed to study our first setting for permeability.
-In most interesting applications, an agent is immersed in a complex social world where it engages in a multitude of relations with other agents (and even aggregate agents such as institutions or informal groups).
-In this model we consider that the \textit{context permeability} is created by agents that can belong simultaneously to several relations.
+In most interesting applications, an agent is immersed in a complex social world, where it engages in a multitude of relations with other agents (and even aggregated agents such as institutions or informal groups).
+In this model, we consider that the \textit{context permeability} is created by agents that can belong simultaneously to several relations.
 As an example, two agents can be simultaneously family and co-workers, and while some links might not connect two agents directly, others can contain neighbourhoods in which they are related~(either directly or through a common neighbour).
@@
 	\end{algorithm}
-	In this model, on each time step, each agent selects a random neighbour from any 
+	In this model, on each time step, each agent select a random neighbour from any 
 	social network available and updates its opinion based on the opinion of the selected partner using the \textit{external majority} rule.
@@
 	\label{sec:models_cs}
-	In the context switching model \cite{Antunes2009}, agents are embedded in multiple relations represented as static social networks and they switch \textit{contexts} with some probability $\zeta_{C_i}$ associated with each context $C_i$.
-The switching probability value is the same in the same network.
-Each agent switches from its current neighbourhood to a its neighbourhood in another network (in which this agent was inactive).
-The agents are only active in one context at a time and can only perform encounters with neighbours in the same context.
+	In the context switching model \cite{Antunes2009}, agents are embedded in multiple relations represented as static social networks and they switch \textit{contexts} with a given probability $\zeta_{C_i}$ associated with context $C_i$.
+The switching probability value is §§§VERIFICA SE É ISTO§§§ kept constant for any given network.§§§TIRAR  the same in the same network.§§§ Each agent switches from its current neighbourhood to a further §§§(vê pf se further está bem, fiquei na dúvida o que querias dizer) neighbourhood in another network (in which this agent was inactive).
+The agents are only active in one context at a time, and can only perform encounters with neighbours in the same context.
 We can think of context switching as a temporary deployment in another place, such as what happens with temporary immigration.
@@
 	\end{algorithm}
-	\noindent In this model agents select an (active) partner from their current neighbourhood.
-If a partner is available the agents update their opinion value based on EM.
+	\noindent In this model, agents select an (active) partner from their current neighbourhood.
+If a partner is available, the agents update their opinion value based on EM.
 At the end of the interaction, the agent switches \textit{from} the current context to a different one with a probability associated with its current network.
@@
 Context switching introduces one notion that has not been explored in the literature so far: the fact that, although some social contexts can be relatively stable if we consider short to moderate periods of time, our social peers are not always available at all times and spend different amounts of time in distinct social contexts.
+	§§§ ISTo É IMPROTANTE, INOVADOR, E DEVEMOS TALVEZ DAR-LHE MAIS ENFASE NAS CONCLUSOES
 
@@
 	\label{sec:experimental-setup}
-	In this section we describe all the tools and processes necessary to produce the current research output.
+	In this section, we describe all the tools and processes necessary to produce the current research output.
 The experiments for our previously described simulation models were developed using the MASON~\cite{Luke2005} simulation framework written in Java.
@@
 All the R code and the configuration files used to produce the analysed data can be found \textbf{in}...\todo{Archive the data, analysis and code used for the analysis, get a doi for it and cite it here}.
+§§§
 
 %recap
-For each configuration in our experiments we performed 100 independent simulation runs.
+For each configuration in our experiments, we performed 100 independent simulation runs.
 The results are thus analysed in terms of value distribution, average and standard deviation, or variance over the 100 runs.
-Like we described in section \ref{sec:sim_consensus}, our models are discrete-event models and each cycle agents execute
-a step in a random order : this is so that this dynamic system --our simulation model-- is not influenced by the order in which agents are executed.
-Simulations ends when total consensus is achieved or 2000 steps have passed.
+Like we described in section \ref{sec:sim_consensus}, our models are discrete-event models and in each cycle agents execute
+a step in a random order: this is so that this dynamical system --our simulation model-- is not influenced by the order in which agents are executed.
+Simulations end when total consensus is achieved or 2000 (§§§ including XXX agent-to-agent interactions) steps have passed.
 
@@
 The social networks used in our models are \textit{k-regular} and \textit{scale-free}.
-A k-regular network is a network where each node has the same number of connections.
+A k-regular network is a network where all the nodes have the same number of connections.
 These networks are constructed by arranging the nodes in a ring and connecting each node to their next $k$ neighbours.
 Each network has $2k$ edges per vertex.
+
+§§§acho que se devia explicar primeiro o que **são** scale-free networks, o que as define, e só depois dizer que se podem construir com o preferential attachment, aliás, não é a única maneira de as construir, nem sei se é a melhor, apenas á a mais usual e usada...§§§
 
@@
 
-The network instances were generated using the \textit{b-have network library} \cite{Nunes:Software:11069}.
-This is a Java library which allows for the manipulation of Network/Graph data structures.
+The network instances were generated using the \textit{b-have network library} §§§cita tb o paper do MABS 2013?
+\cite{Nunes:Software:11069}.
+This is a Java library that allows for the manipulation of Network/Graph data structures.
 It also includes the more commonly used random network models from the literature.
@@
 
+§§§ TALVEZ UM POUCO MAIS SOBRE O SIGNIFICADO DESSAS MEDIDAS, E DAÍ O SEU VALOR PARA OS ESTUDOS DE FENOMENOS SOCIAIS COMPLEXOS
+
 \section{Results and Discussion}
@@
 % Overview
+In this section, we bababa
+§§§
 
@@
 Each network is generated in such a way that the node positions are randomised.
-What this means is that we can have multiple networks with the same topology and yet, each node has a different neighbourhood on each network.
+This means that we can have multiple networks with the same topology and yet, each node has a different neighbourhood on each network.
 Also, neighbourhoods do not necessarily overlap due to the node shuffling.
@@
 		& Nodes &  Edges & Clustering Coef.	  &  Avg. Path Length \\ 
-		\hline  10-Regular 1 & 100 &  1,000  &  0.711 &  2.980 \\ 
-		\hline  10-Regular 2 & 100 & 1,000 & 0.711 &  2.980 \\ 
+		\hline  10-regular 1 & 100 &  1,000  &  0.711 &  2.980 \\ 
+		\hline  10-regular 2 & 100 & 1,000 & 0.711 &  2.980 \\ 
 		\hline  Combined & 100 & 1,790  & 0.512 &  1.638 \\ 
-		\hline 20-Regular & 100 & 2,000	& 0.731	& 1.788 \\
+		\hline 20-regular & 100 & 2,000	& 0.731	& 1.788 \\
 		\hline 
@@
 
-The networks are drawn using the \textit{Kamada-Kawai} Layout \cite{Kamada19897} which regards the desirable ``geometric" (Euclidean) distance between two vertices in the drawing as the ``graph theoretic" distance between them in the corresponding graph.
+The networks are drawn using the \textit{Kamada-Kawai} Layout \cite{Kamada19897} which regards the desirable ``geometric'' (Euclidean) distance between two vertices in the drawing as the ``graph theoretic'' distance between them in the corresponding graph.
 We can see by the results of the layout in figure \ref{fig:network_properties_merge_2_10regular}, that the distance between nodes in the network has decreased, this is also confirmed by the reduced average path length of the combined networks (see table \ref{tab:network_properties_merge_2_10regular}).
@@
 To illustrate our point we analysed one k-regular network with k = 20 (see figure \ref{fig:network_properties_1_20regular} --and the corresponding entry on table \ref{tab:network_properties_merge_2_10regular}).
-The clustering coefficient of a 20-Regular network is approximately the same as the one of a 10-regular network (higher than the combination of 10-regular networks).
+The clustering coefficient of a 20-regular network is approximately the same as the one of a 10-regular network (higher than the combination of 10-regular networks).
 The average path length also decreases as there are more connections between the nodes.
 As we will show, these properties may vary.
-Since the nodes are subjected to random permutations, we can generate different overlaps which lead to distinct structural values.
+Since the nodes are subjected to random permutations, we can generate different overlaps that lead to distinct structural values.
+
+§§§ regra== "xxx that" ou "xxx, which"
 
@@
 \label{sec:overlapping_kreg}
-We will now investigate, what kind of properties we can get from merging K-Regular networks.
+We will now investigate what kind of properties we can get from merging k-regular networks.
 First, we analysed the distribution for the average path length and the clustering coefficient values over 100 network instances with 100 nodes each.
-Since this variation is negligible we use the average as a descriptor for different configurations of k values and number of overlapping networks.
+Since this variation §§§qual variation???
+do average path length???§§§ is negligible, we use the average as a descriptor for different configurations of k values and number of overlapping networks.
 (The reader should refer to figures \ref{append_fig:network_properties_apl_kreg} and \ref{append_fig:network_properties_cc_kreg} in the appendix for the box plot preliminary analysis.)
@@
 Figure~\ref{fig:network_properties_apl_line_kreg} shows the average value for the \textit{average path length} of 100 k-regular network instances, each with 100 nodes.
-We can see that the \textit{average path length} changes more drastically when we go from 1 to 2 networks this is precisely the effect we can see in figure \ref{fig:network_properties_merge_2_10regular}.
+We can see that the \textit{average path length} changes more drastically when we go from 1 to 2 networks.
+This is precisely the effect we can see in figure \ref{fig:network_properties_merge_2_10regular}.
 What we are seeing is that merging these networks at random effectively creates multiple shortcuts between points that were not connected in the original k-regular topology.
@@
 		\vspace{0.2cm}
-		\caption{Average value for the \textit{average path length} of 100 instances of overlapping k-regular networks(containing 100 nodes each) with ~k=\{1,2,3,4,5\}~(\ref{fig:network_properties_apl_line_kreg_12345}), and k= ~\{10,20,30,40,50\} (\ref{fig:network_properties_apl_line_kreg_1020304050}).}
+		\caption{Average value for the \textit{average path length} of 100 instances of overlapping k-regular networks (containing 100 nodes each) with k=\{1,2,3,4,5\}~(\ref{fig:network_properties_apl_line_kreg_12345}), and k= ~\{10,20,30,40,50\} (\ref{fig:network_properties_apl_line_kreg_1020304050}).}
 		\label{fig:network_properties_apl_line_kreg}
@@
 We can see that adding multiple networks changes the clustering coefficient of the resulting structure.
-We can see that for $k \le 20$ the clustering coefficient drops when we add a second network.
-This happens because when we merge these networks, their connectivity is not enough to generate shortcuts with tightly clustered neighbourhoods.
+For $k \le 20$, the clustering coefficient drops when we add a second network.
+This happens because when we merge these networks, their connectivity is not high enough to generate shortcuts with tightly clustered neighbourhoods.
 The clustering coefficient is computed by taking the average local clustering coefficient of each node in the network.
@@
 		\vspace{0.2cm}
-		\caption{Average value for the \textit{clustering coefficient} of 100 instances of overlapping k-regular networks(containing 100 nodes each) with ~k=\{1,2,3,4,5\}~(\ref{fig:network_properties_cc_line_kreg_12345}), and  k = \{10,20,30,40,50\} (\ref{fig:network_properties_cc_line_kreg_1020304050}).}
+		\caption{Average value for the \textit{clustering coefficient} of 100 instances of overlapping k-regular networks (containing 100 nodes each) with ~k=\{1,2,3,4,5\}~(\ref{fig:network_properties_cc_line_kreg_12345}), and  k = \{10,20,30,40,50\} (\ref{fig:network_properties_cc_line_kreg_1020304050}).}
 		\label{fig:network_properties_cc_line_kreg}
@@
 The exception is when you merge networks with $k=1$.
-These have a ring-like structure so there are no nodes forming a clique\footnote{A clique is a group of nodes such that every two nodes are connected by an edge.} with their neighbours.
+These have a ring-like structure, so there are no nodes forming a clique\footnote{A clique is a group of nodes such that every two nodes are connected by an edge.} with their neighbours.
 
@@
 We can then say that specific configurations display a specific \textit{average path length} and \textit{clustering coefficient} both for \textit{k-regular} networks and \textit{scale-free} networks.
-Since the average of these measures is still a good descriptor, we ploted the average of the \textit{average path length} (figure \ref{fig:network_properties_apl_line_sf_12345}) and \textit{clustering coefficient} (figure \ref{append_fig:network_properties_cc_sf_12345}) for each overlapping network configuration.
+Since the average of these measures is still a good descriptor, we plotted the average of the \textit{average path length} (figure \ref{fig:network_properties_apl_line_sf_12345}) and \textit{clustering coefficient} (figure \ref{append_fig:network_properties_cc_sf_12345}) for each overlapping network configuration.
 
@@
 		\vspace{0.2cm}
-		\caption{Average value for the \textit{average path length} (\ref{append_fig:network_properties_apl_sf_12345}) and \textit{clustering coefficient} (\ref{append_fig:network_properties_cc_sf_12345}) for 100 instances of overlapping \textit{scale-free} networks(containing 100 nodes each).}
+		\caption{Average value for the \textit{average path length} (\ref{append_fig:network_properties_apl_sf_12345}) and \textit{clustering coefficient} (\ref{append_fig:network_properties_cc_sf_12345}) for 100 instances of overlapping \textit{scale-free} networks (containing 100 nodes each).}
 		\label{fig:network_properties_line_sf}
@@
 
-The parameter $d$ in figure \ref{fig:network_properties_line_sf} dictates how many edges are added by preferential attachment (see sectino \ref{sec:exp-setup_network_models}) each time a new node is added to a network (during its construction).
+The parameter $d$ in figure \ref{fig:network_properties_line_sf} dictates how many edges are added by preferential attachment (see section\ref{sec:exp-setup_network_models}) each time a new node is added to a network (during its construction).
 This means that for $d=1$, the resulting network is a \textit{forest}: a network composed of disjoint tree graphs.
-Figure~\ref{fig:network_properties_apl_line_sf_12345} shows us that the \textit{average path length} still decreases consistently when we more networks.
+Figure~\ref{fig:network_properties_apl_line_sf_12345} shows us that the \textit{average path length} still decreases consistently when we add more networks.
 One of the characteristics of \textit{scale-free} networks is its short average  path length, thus, for $d \ge 2$ we can see that adding more edges does not make so much difference.
@@
 Finally, we look at what happens when we merge k-regular networks with \textit{scale-free} networks.
-We didn't make an exhaustive analysis for this configuration but we show what is the resulting structure of such merging.
+We didn't make an exhaustive analysis for this configuration, but we show what is the resulting structure of such merging.
 You can see in figure \ref{fig:network_properties_merge_regular_scale-free} that this results in a network with a lower \textit{average path length} due to the shortcuts created by the \textit{scale-free} network.
@@
 		\vspace{0.2cm}
-		\caption{Average \textit{average path  length} for 100 instances of heterogeneous network configurations:  1 \textit{scale-free} with $d=\{1,2,3,4,5\}$ and 1 \textit{k-regular} network with $k=\{1,2,3,4,5\}$ (\ref{fig:network_properties_apl_line_sf__kreg_12345}) and $k=\{10,20,30,40,50\}$ (\ref{fig:network_properties_apl_line_sf_kreg_1020304050}).
+		\caption{Average \textit{average path  length} for 100 instances of heterogeneous network configurations:  one \textit{scale-free} with $d=\{1,2,3,4,5\}$ and one \textit{k-regular} network with $k=\{1,2,3,4,5\}$ (\ref{fig:network_properties_apl_line_sf__kreg_12345}) and $k=\{10,20,30,40,50\}$ (\ref{fig:network_properties_apl_line_sf_kreg_1020304050}).
 (See the respective box plots in the appendix: figure \ref{append_fig:network_properties_apl_sf_kreg}).}
@@
 
-Figure \ref{fig:network_properties_line_apl_sf_kreg} shows the \textit{average path length} of 100 independently generated instances of combinations of 1 \textit{k-regular} network and 1 \textit{scale-free} network with different values $k$ and $d$ respectively.
+Figure \ref{fig:network_properties_line_apl_sf_kreg} shows the \textit{average path length} of 100 independently generated instances of combinations of one \textit{k-regular} network and one \textit{scale-free} network with different values $k$ and $d$, respectively.
 We can see that for configurations where the \textit{k-regular} networks have low values of $k$ (figure \ref{fig:network_properties_apl_line_sf__kreg_12345}), adding a \textit{scale-free} network always decreases the \textit{average path length}.
-Moreover the higher the $d$ the lower the path length as more connections are formed between different nodes.
-Which higher values of $k$ (figure \ref{fig:network_properties_apl_line_sf_kreg_1020304050}) however, increasing the value of $d$ does not decrease the \textit{average path length}.
-This is not surprising given that with that level of connectivity having a more connected \textit{scale-free} doesn't make such an impact.
-The first network is already highly dense and connected so adding a few extra connections doesn't matte --what matters in this case is that there is a scale-free network creating the extra shortcuts between nodes that weren't connected before.
+Moreover, the higher the $d$, the lower the path length, as more connections are formed between different nodes.
+With higher values of $k$ (figure \ref{fig:network_properties_apl_line_sf_kreg_1020304050}) however, increasing the value of $d$ does not decrease the \textit{average path length}.
+This is not surprising given that with that level of connectivity, having a more connected \textit{scale-free} network does not make such an impact.
+The first network is already highly dense and connected, so adding a few extra connections doesn't matter --what does matter in this case is that there is a scale-free network creating the extra shortcuts between nodes that were not connected before.
 
@@
 		\vspace{0.2cm}
-		\caption{Average \textit{clustering coefficient} for 100 instances of heterogeneous network configurations:  1 \textit{scale-free} with $d=\{1,2,3,4,5\}$ and 1 \textit{k-regular} network with $k=\{1,2,3,4,5\}$  (\ref{append_fig:network_properties_cc_sf_12345}) and $k=\{10,20,30,40,50\} $ (See the respective box plots in the appending: figure\ref{append_fig:network_properties_cc_sf_kreg}).}
+		\caption{Average \textit{clustering coefficient} for 100 instances of heterogeneous network configurations:  one \textit{scale-free} with $d=\{1,2,3,4,5\}$ and one \textit{k-regular} network with $k=\{1,2,3,4,5\}$  (\ref{append_fig:network_properties_cc_sf_12345}) and $k=\{10,20,30,40,50\} $ (See the respective box plots in the appending: figure\ref{append_fig:network_properties_cc_sf_kreg}).}
 		\label{fig:network_properties_line_cc_sf_kreg}
@@
 
-\noindent Figure \ref{fig:network_properties_line_cc_sf_kreg} show the results for the \textit{clustering coefficient}.
+\noindent Figure \ref{fig:network_properties_line_cc_sf_kreg} shows the results for the \textit{clustering coefficient}.
 These are similar to the results we get for \textit{k-regular} networks (see figure \ref{network_properties_cc_line_kreg}).
-the difference is that we are not adding more networks but rather increasing the parameter $d$ of the scale-free.
-Curiously in this case, the effects are qualitatively similar with the ones of merged \textit{k-regular} network with low value of $k$.
+The difference is that we are not adding more networks but rather increasing the parameter $d$ of the scale-free.
+Curiously, in this case, the effects are qualitatively similar with the ones of merged \textit{k-regular} network with low value of $k$.
 With high values of $k$ (figure \ref{fig:network_properties_cc_line_sf_kreg_1020304050}) we can see that higher values of $d$ are not enough to make the network more clustered.
-This is because, scale-free networks are more sparse and have a very low number of triangles between nodes.
+This happens because scale-free networks are more sparse and have a very low number of triangles between nodes.
 
@@
 
-In this section, we discuss the results for various set of experiments on the first model we presented --the \textit{context permeability model} \cite{Antunes2007,Antunes2010}.
+In this section, we discuss the results for various sets of experiments on the first model we presented --the \textit{context permeability model} \cite{Antunes2007,Antunes2010}.
 In a first set of experiments, the agent space was structured using \textit{k-regular} and \textit{scale-free }social networks.
@@
 \label{sec:ctx_perm_convergence}
-In this section we analyse the ratio of convergence to consensus for different network configurations.
+We now analyse the ratio of convergence to consensus for different network configurations.
 We correlate this ratio with the properties that the combined network structure exhibits.
-As we have seen in section \ref{sec:network_properties}, the properties don't vary much for different random network instances so we use the average as the descriptor for these properties in this correlation.
+As we have seen in section \ref{sec:network_properties}, the properties don't vary much for different random network instances, so we use the average as the descriptor for these properties in this correlation.
 
 The following tables show the results of our simulations.
-Table ~\ref{tab:regular_convergence} show the percentage of total consensus achieved within 2000 cycles for 3000 runs.
+Table ~\ref{tab:regular_convergence} shows the percentage of total consensus achieved with 2000 cycles for 3000 runs.
 We can see that for k-regular networks with a small $k$, consensus is rarely achieved with a single network.
@@
 This is difficult to visualise using only the tables and the previous plots so, to confirm this hypothesis, we measured the \textit{Spearman's correlation} between the ratio of convergences to consensus, the average of \textit{average path length} , and the average of \textit{clustering coefficient} for the corresponding network configurations (see table \ref{tab:convergence_correlation}).
+
+§§§ talvez explicar o que significa a Spearman's correlation ???
 
@@
 We now analyse the convergence in terms of average number of meetings during a simulation run.
-Since the maximum number of simulation cycles is 2000, the maximum number of encounters is 2000000 (we have 100 agents and each one performs 1 encounter per cycle).
+Since the maximum number of simulation cycles is 2000, the maximum number of encounters is 2~000~000 (we have 100 agents and each one performs one encounter per cycle).
 We show that for some configurations, the average of encounters is not a good descriptor since it varies greatly from run to run.
 It is better to look at the distributions of these measures rather than considering the average.
-Nevertheless, we included the data with all the average number of encounters as well as the respective standard deviations for different network configurations.
+Nevertheless, we included the data with all the average number of encounters, as well as the respective standard deviations for different network configurations.
 You can find this data in appendix \ref{append_ctx_permeability}.
@@
 First, we present the results for k-regular networks.
-In the box plots To observe the distribution of the number of encounters consider the box plots for $k = \{1,2,3,4,5\}$ (figure \ref{fig:ctx_perm_kreg_12345}) and $k =\{10,20,30,40,50\}$ (figure \ref{fig:ctx_perm_kreg_1020304050}).
-In figure \ref{fig:ctx_perm_kreg}, we focus on configurations with a number of networks $\ge 3$ since less networks lead to much worse results in terms of convergence speed.
-These plots still present two types of situations: the typical runs in which the number of encounters doesn't vary that much and some ``outlier runs" which present some interesting dynamics as we will see later.
+To observe the distribution of the number of encounters consider the box plots for $k = \{1,2,3,4,5\}$ (figure \ref{fig:ctx_perm_kreg_12345}) and $k =\{10,20,30,40,50\}$ (figure \ref{fig:ctx_perm_kreg_1020304050}).
+In figure \ref{fig:ctx_perm_kreg}, we focus on configurations with a number of networks $\ge 3$, since less networks lead to much worse results in terms of convergence speed.
+These plots still present two types of situations: the typical runs, in which the number of encounters doesn't vary that much, and some ``outlier runs," which present some interesting dynamics, as we will see later on.
 
@@
 \noindent Figure~\ref{fig:ctx_perm_kreg} shows us results that are qualitatively similar to what we previously observed for convergence ratios (see section \ref{sec:ctx_perm_convergence}).
-Networks with less connectivity and a greater average path length lead to total convergence less often.
+Networks with lesser connectivity and a greater average path length lead to total convergence less often.
 Moreover, the simulation outcomes vary much more in comparison with the other configurations ($k>1$ and $networks \ge 3$).
@@
 Notice that for $k=3$ and $networks=3$ (\ref{fig:ctx_perm_kreg_1020304050}), we still have runs that deviate from what we consider the typical behaviour.
-Instead of disregarding this as a simple outlier, we show that this run allows us to gain an insight on the dynamics of our \textit{External Majority} consensus game.
-
-Before anything else we analysed the network structure from this run and observed that there were no distinct differences between the network instances from the ``outlier run" and the ones of the ``typical" run.
+Instead of disregarding this as a simple outlier, we show that this run allows us to gain an insight into the dynamics of our \textit{External Majority} consensus game.
+
+Before anything else, we analysed the network structure from this run and observed that there were no distinct differences between the network instances from the ``outlier run" and the ones of the ``typical" run.
 This suggested that this can be a property of the game itself --and of the network structure that leads to this situation -- and what happens is that the agents reach a state from which converging towards consensus is significantly harder.
@@
 
-\noindent In our case, we take the outlier in the configuration with $k=3$ and $networks=3$ and look at the memory that agents use in the consensus game.
+\noindent In our case, we take the outlier in the configuration with $k=3$ and $networks=3$, and look at the memory that agents use in the consensus game.
 As we described previously, agents record the number of individuals encountered with each opinion value (two opinions in this case).
@@
 
-We can see that both the average difference in the opinion memory and the variance, rise faster in the normal run than it does in the outlier run.
+We can see that both the average difference in the opinion memory and the variance rise faster in the normal run than in the outlier run.
 This is not enough to establish that there is a significant difference between the two.
-Moreover, the memory differences are quite similar but the number of agents for each opinion was quite even.
+Moreover, the memory differences are quite similar, but the number of agents for each opinion was quite even.
 This happens due to the position of agents in the network and their initial opinion values.
@@
 The variance starts to increase more rapidly after 200 steps.
-The exponential growth reveals that the convergence to consensus is not done evenly throughout the network, this is one of the reasons why consensus takes more time to achieve.
+The exponential growth reveals that the convergence to consensus is not done evenly throughout the network, this is one of the reasons why consensus takes more time to be achieved.
 Also, the low variance in the first $200$ steps shows us that the opinion strength was evenly distributed --we have almost the same number of agents for each opinion but the memory differences are qualitatively the same for both opinions.
@@
 
+§§§ ACHO QUE ESTAMOS A GASTAR UM BOCADO DE TEMPO/ESPAÇO A MAIS COM ESTE "OUTLIER RUN" OU ISSO CONDUZ A UMA CONCLUSÃO FORTE E IMPORTANTE, OU ESTAMOS SUJEITOS A ALGUMA CRÍTICA AQUI
+
 \begin{figure}[H]
@@
 \noindent In other words, in some sections of the network, the agents converged towards one opinion and continue to reinforce each other (leading the opinion difference to grow) and the more regions converge, the faster the global convergence is.
-%boxplots for scale-free networks
 
@@
 \noindent Figure~\ref{fig:ctx_perm_sf} shows the average number of encounters during 100 independent simulation runs for \textit{scale-free} networks.
-(We don't include the configuration for 1 network and $d = 1$ because as we have seen in the convergence results, these never converge.
-The convergence ratio is very low for the configurations with 1 network $d = 2$ and 2 networks with $d = 1$; hence the high number of encounters~(see also table \ref{tab:scale-free_convergence}).
+(We don't include the configuration for one network and $d = 1$ because, as we have seen in the convergence results, these never converge.
+The convergence ratio is very low for the configurations with one network $d = 2$ and 2 networks with $d = 1$; hence the high number of encounters~(see also table \ref{tab:scale-free_convergence}).
 
@@
 The difference is that more ``atypical" runs occur with multiple \textit{scale-free} networks.
-Again, this is the effect ot these types of topologies.
-As we discussed previously, in these less connected topologies, agents are more prone to be arranged in such a way that progression towards consensus is more difficult to attain due to bottlenecks to regions in the network that converged to different opinion values.
-
-%boxplots for k-regular + scale-free networks
+Again, this is the effect of these types of topologies.
+As we discussed previously, in these less connected topologies, agents are more prone to be arranged in such a way that progression towards consensus is more difficult to attain, due to bottlenecks to regions in the network that converged to different opinion values.
+
 \subsubsection{Heterogeneous Network Configuration}
-We also performed experiments where we mixed the network topologies: in this case we used 1 \textit{scale-free} and 1 \textit{k-regular} networks.
+We also performed experiments where we mixed the network topologies: in this case we used one \textit{scale-free} and one \textit{k-regular} networks.
 Table~\ref{tab:regular_scale-free_convergence} shows the convergence ratio for the heterogeneous network configuration with the multiple values for $d$ and $k$ for the \textit{scale-free} and \textit{k-regular} respectively.
@@
 	\begin{minipage}{0.9\textwidth}
-		\caption{Ratio of convergence to total consensus in 3000 independent runs with two networks: 1 \textit{k-regular} and 1 \textit{scale-free} network with different $k$ and $d$ values respectively.}	
+		\caption{Ratio of convergence to total consensus in 3000 independent runs with two networks: one \textit{k-regular} and one \textit{scale-free} network with different $k$ and $d$ values respectively.}
 		\label{tab:regular_scale-free_convergence}
@@
 
-\noindent One of the differences lies in the configuration with $d=1$ and $k=1$.
+\noindent One of the differences §§§entre quê e quê???, fica dificil sem as imagens no meio §§§ lies in the configuration with $d=1$ and $k=1$.
 The convergence ratio is higher than with $2$ $1-regular$ networks (see table \ref{tab:regular_convergence}) --but not better than two \textit{scale-free} networks.
-This happens because, with $k=1$ the network is basically a ring and has the maximum possible average path length for a connected graph.
-Adding two rings, improves this but underlying structure is still very susceptible to self-reinforcing structures (a connected sub-graph is basically a line).
+This happens because with $k=1$ the network is basically a ring and has the maximum possible average path length for a connected graph.
+Adding two rings improves §§§improves WHAT???§§§ this but the underlying structure is still very susceptible to self-reinforcing structures (a connected sub-graph is basically a line).
 Adding a \textit{scale-free} changes this drastically as we are mixing tree-like network components with this first circle.
@@
 		\vspace{0.2cm}
-		\caption{Number of meetings over 100 independent simulation runs for heterogeneous configuration: 1 \textit{k-regular} network with  $k=\{1,2,3,4,5\}$ and 1 \textit{scale-free} network with $d\{1,2,3,4,5\}$.
+		\caption{Number of meetings over 100 independent simulation runs for heterogeneous configuration: one \textit{k-regular} network with  $k=\{1,2,3,4,5\}$ and one \textit{scale-free} network with $d\{1,2,3,4,5\}$.
 Figure \ref{fig:ctx_perm_sfkreg_1020304050best} shows a zoom on the best configurations.}
@@
 
-The data for the average number of encounters, as well as the respective standard deviations referent to the results in figure \ref{fig:ctx_perm_sfkreg} can be found in appendix \ref{append_ctx_permeability}, table \ref{append_tab:ctx_perm_kreg_sf_encounters}.
+The data for the average number of encounters, as well as the respective standard deviations referent to the results in figure \ref{fig:ctx_perm_sfkreg}, can be found in appendix \ref{append_ctx_permeability}, table \ref{append_tab:ctx_perm_kreg_sf_encounters}.
 
@@
 
-As we discussed previously in section \ref{sec:models_cs} (see model \ref{model:context_switching}), the switching probability dictates the probability an agent has of switching \textit{from} the current network after an encounter has been performed.
+As we discussed previously in section \ref{sec:models_cs} (see model \ref{model:context_switching}), the switching probability dictates the frequency with which an agent switches \textit{from} the current network after an encounter has been performed.
 In an abstract manner, this allows us to model how much time agents spend on each network.
@@
 This can help us model phenomena such as real-world agents that dedicate more or less time consuming content from different social networks.
-For now we attribute this probability to the network to contain the model complexity.
+For now, we attribute this probability to the network to restrain the model complexity.
 
@@
 		\includegraphics[width=1\linewidth]{"../analysis/pdf/  context_switching_2_10_regular _switching_contour"}
-		\caption{10-Regular Networks}
+		\caption{10-regular Networks}
 		\label{fig:ctx_cs_2_10kreg}
@@
 		\includegraphics[width=1\linewidth]{"../analysis/pdf/  context_switching_2_30_regular _switching_contour"}
-		\caption{30-Regular Networks}
+		\caption{30-regular Networks}
 		\label{fig:ctx_cs_2_30kreg}
@@
 
-\noindent We can see that with smaller values of $k$, symmetry in the context switching probability is more important (having the same probability in both networks) if the agent switches less from one of them.
+\noindent We note that with smaller values of $k$, symmetry in the context switching probability is more important (having the same probability in both networks) if the agent switches less from one of them.
 This is the case because switching less from one network means spending more time in that network.
-This means that switching more from other network can be disruptive to a neighbourhood that already converged to a sub-convention.
+This means that switching more from the other network can be disruptive to a neighbourhood that has already converged to a sub-convention.
 This can be observed in configurations with \textit{k-regular} networks (figure \ref{fig:ctx_cs_2_10kreg}) but it is especially apparent in \textit{scale-free} networks (figure \ref{fig:ctx_cs_2_sf_d1}).
@@
 
-When we increase the connectivity (and lower the average path length), both in \textit{k-regular} and \textit{scale-free} networks, the switching probability becomes ``irrelevant": in the sense that you can use any probability you want and the results in term of speed of convergence will be the same.
+§§§ ATENçÂO QUE ``deve fechar com '' (duas plicas), não com " (aspas)
+
+When we increase the connectivity (and lower the average path length), both in \textit{k-regular} and \textit{scale-free} networks, the switching probability becomes ``irrelevant:'' in the sense that you can use any probability you want and the results in terms of speed of convergence will be the same.
 The exception is obviously when considering the switching probability with value $0$.
 In this case, agents are isolated (they are initially equally distributed throughout the networks) and reaching consensus becomes very hard.
---Especially hard since agents are active only in one network: being in all the networks creates the possibly of disconnected graphs in the networks they are not currently active.
+--Especially hard since agents are active only in one network: being active in all the networks creates the possibly of disconnected graphs in the networks they are not currently active.
 
@@
 The selection has to be made from the network they are currently active in.
-This makes so that agents spending different amounts of time in distinct network topologies are influenced differently -- an agent can be very influential in one network being a very central node in that context, and marginally important in the other one: in a sense its opinion in one network can be more important to overall convergence than in other network due to its position in the network.
-
-To check the influence of topology and connectivity in the new switching dynamics we took the most susceptible network type (the \textit{scale-free} networks) and performed the following experiment.
-We setup 2 \textit{scale-free} networks; one with $d=1$ and the other with $d=5$.
+This causes that agents spending different amounts of time in distinct network topologies are influenced differently -- an agent can be very influential in one network, being a very central node in that context, and marginally important in the other one: in a sense its opinion in one network can be more important to overall convergence than in other network,  due to its position in the network.
+
+To check the influence of topology and connectivity in the new switching dynamics we took the most susceptible (§§§TO WHAT???) network type (the \textit{scale-free} networks) and performed the following experiment.
+We setup two \textit{scale-free} networks; one with $d=1$ and the other with $d=5$.
 We then performed the
@@
 
-We can see that in this case, its more important to switch \textit{from} the network with lower average path length and a forest-like composition ($d=1$) with a probability of least the same value or more than the one of the other network (with $d=5$).
-The same can be observed when we mix the two topologies (\textit{k-regular} with \textit{scale-free}) as we can see in figure \ref{fig:ctx_cs_kreg10_sfd1}.
+We see that in this case it is more important to switch \textit{from} the network with lower average path length and a forest-like composition ($d=1$) with a probability of at least the same value or more than the one of the other network (with $d=5$).
+The same can be observed when we mix the two topologies (\textit{k-regular} with \textit{scale-free}), as we can see in figure \ref{fig:ctx_cs_kreg10_sfd1}.
 
@@
 	\begin{minipage}{0.9\textwidth}
-		\caption{Contour plot for the average number of meets during a simulation for 100 independent runs: 1 \textit{10-regular} network (k=10) and a \textit{scale-free} network with $d=1$.
+		\caption{Contour plot for the average number of meets during a simulation for 100 independent runs: one \textit{10-regular} network (k=10) and a \textit{scale-free} network with $d=1$.
 See the perspective plots in  appendix \ref{append_ctx_switching} (figure \ref{append_fig:ctx_cs_kreg10_sfd1}).
@@
 
-The surprise was that for values of $k \ge 20$, the results where practically the same for both models independently of the switching probability --even when we increased the number of networks, the number of encounters remains around $2000$ on average for all the models.
-Above a certain level of neighbourhood size (and overlapping which causes the average path length to drop), the switching probability becomes less influential.
-It is still important that we get comparable results because we are introducing a temporal components that was never explored before in these types of opinion dynamics models.
-The fact that the agents can become active in different networks at different points in time.
+The surprise was that for values of $k \ge 20$, the results where practically the same for both models independently of the switching probability --even when we increased the number of networks, the number of encounters remained around $2000$ on average for all the models.
+Above a certain level of neighbourhood size (and overlapping, which causes the average path length to drop), the switching probability becomes less influential.
+It is still important that we get comparable results because we are introducing a temporal component that was never explored before in these types of opinion dynamics models: the fact that the agents can become active in different networks at different points in time.
+§§§ mudei . para : na ultima frase, por favor valida
 
@@
 For \textit{scale-free} networks, figure \ref{ctx_switching_comp_sf} shows us similar results.
-It seems that a switching with a higher probability displays results similar with those of context permeability.
-In this case, adding more networks makes so that lower switching probabilities display slightly worse results.
+It seems that switching with a higher probability displays results similar with those of context permeability.
+In this case, adding more networks makes so that lowering switching probabilities displays slightly worse results.
 This influence is due to the fact that the neighbourhoods are considerably smaller in \textit{scale-free} networks --even with values of $d=5$-- so the impact of low switching was bound to be noticed.
 
-One final remark is that with context switching, we always achieve consensus being for \textit{k-regular} or \textit{scale-free} networks.
-In addition, increasing the number of networks seems to always reduce the number of encounters to achieve consensus in both models, this happens due to what we called \textit{permeability}.
+One final remark is that with context switching, we always achieve consensus §§§ não percebo este being, será de cortar?§§§ being for \textit{k-regular} or \textit{scale-free} networks.
+In addition, increasing the number of networks seems to always reduce the number of encounters to achieve consensus in both models.
+This happens due to what we have called \textit{permeability}.
 Having multiple points of dissemination that permeate between different social networks enhances the overall convergence to consensus.
-More isolated nodes to be reached in sparsely connected networks such as scale-free networks.
+§§§ acrescentei <<With permeability there are more previously >>§§§ With permeability there are more previously isolated nodes being reached in sparsely connected networks such as scale-free networks.
+
+§§§ não falaste de context switching induzido por razões, suponho que é intencional para deixar algo para um futuro paper, e também porque este já vai longo...
+§§§
 
@@
 In this paper, we analysed and discussed our modelling framework for multi-relational models of social spaces.
-These results show that not only contexts play an important role in the dissemination of consensus in artificial agent societies, but also that simple mechanisms can generate a great deal of complexity, especially in these scenarios where conventions are being co-learned by multiple agents.
+These results show that not only contexts play an important role in the dissemination of consensus in artificial agent societies, but also that simple mechanisms can generate a great deal of complexity, especially in those scenarios where conventions are being co-learned by multiple agents.
 Adding more networks to our opinion dynamics model leads to outcomes where consensus was achieved not only more often but also faster.
 
-Future work includes the analysis of different complex network models, while \textit{k-regular} and \textit{scale-free} networks are two of the most pervasive network examples in these types of simulations.
+Future work includes the analysis of different complex network models, §§§while???
+será although?
+§§§ while \textit{k-regular} and \textit{scale-free} networks are two of the most pervasive network examples in these types of simulations.
 There has been a growing number of models with different properties inspired by real-world phenomena that can be considered.
 We can also analyse the networks according to different properties such as the present of nodes with high centrality in the network (hubs).
-Moreover, we are plan to apply what we learned with our consensus games to cooperation problems.
+Moreover, we  plan to apply what we learned with our consensus games to cooperation problems.
 Constructing agents that can learn both behaviour and coordination procedures is a difficult task especially when working with large distributed artificial societies.
@@
 
-Note that while the convergence and number of encounters seem to be correlated with the average path length as we have seen previously, this might not be the only property that plays a role in faster convergence to consensus.
+Note that while the convergence and number of encounters seem to be correlated with the average path length, as we have seen previously, this might not be the only property that plays a role in faster convergence to consensus.
 Correlation is just an informal tool to helps us assert if some monotonic relationship exists.
-More research is needed to assert, for instance, if self reinforced structures like the ones reported by \cite{Villatoro2013} exist in our multi-network scenarios.
+More research is needed to assert, for instance, if self-reinforced structures like the ones reported by \cite{Villatoro2013} exist in our multi-network scenarios.
 In particular we would be interested to see if permeability mitigates the effects of such structures.
 
-We have seen that context permeability by context overlapping or switching can provide a fairly straight forward modelling methodology that can be used to compose simulation scenarios for more complex social spaces.
+We have seen that context permeability by context overlapping or switching can provide a fairly straightforward modelling methodology that can be used to compose simulation scenarios for more complex social spaces.
 What remains to be done is to identify more precise contextual structures in real-world networks.
 While capturing the structure of real social network can be a daunting task, we do have pervasive records of networking activity between social actors: online social networks.
-Analysing these, can lead us to insights about complex structural properties that emerge from user activity, and context that can be identified within those networks.
+Analysing these can lead us to insights about complex structural properties that emerge from user activity, and context that can be identified within those networks.
 A difficult --but not impossible-- prospect for further research would be to track similar contexts between different real online social networks.
+	§§§ isto vem na linha do que eu acrescentei acima sobre manter o jogo neutro, para nos concentrarmos na estrutura do problema, talvez seja de ir lá buscar umas frases, e acerescentá-las aqui, que justificam que não nos debruçámos sobre dados reais, porque nos interessava mais a estrutura matemática...
 
 We are just scratching the surface of multi-relational models in social simulation with the next step being the connection of our model to the reality.
+§§§ esta frase enfraquece um pouco as conclusões e o artigo, não achas???
 
@@
 
+§§§ é preciso rever a bibliografia, há muitas coisas sem data, ou DOI aparece em minúsculas (usa "{{DOI}}" se for preciso forçar as maiúsculas, etc
+
 \end{document}

### 2015-06-15 doc/main.tex
corrected some file names and added the generated images in pdf so that the doc can be built from the repo

@@
 		\author[ul]{Luis Antunes}
-		\ead{xarax@di.fc.ul.pt}
+		\ead{xarax@ciencias.ulisboa.pt}
 
@@
 	%******************************************
+
+\noindent In most simulations of complex social phenomena, agents are considered to inhabit a space in which structure is very simple, and has little resemblance with the social world it is supposed to depict, and for which the conclusions are supposed to be extrapolated.
+This simplicity does not come by chance, rather, it is somewhat necessary and desired by the researchers, since the problems to be approached are themselves so complex that whichever factors of complexity can be reduced, or at least postponed, are always welcome.
+So, as widely visible, geographical space is usually reduced to a two-dimensional grid composed by square patches, and all social relations between  agents are condensed into one abstract relation.
+Usually, approaches disregard the fact that in real world our relations are multiple, and, moreover, possess very diverse characteristics, including rich information about degree, intensity, frequency, methods associated, asymmetry, and so on.
+
+To explore the addition of multiple relations and its consequences for the dissemination of phenomena in social simulations, we put forward to reduce the emphasis given on the individual interactions, depicted as a theoretical game.
+We accomplished this by choosing a simple, and especially, neutral game to represent those interactions.
+Our main concern was that the game itself would not provide biases or trends in the collective phenomenon being studied, so we chose the consensus formation game, with a straightforward majority rule to decide the outcome of each individual move.
+
 	Studying simulation models of consensus formation can advance our understanding of real-world emergent social phenomena.
@@
 	%******************************************
-	In this paper, we explore the possibility of modelling opinion dynamics with multiple social networks.
+	In this article, we explore the possibility of modelling opinion dynamics with multiple social networks.
 We look at how the properties influence the convergence to opinion consensus.
@@
 	%******************************************
-	%		Paper Structure
-	%******************************************
-	\subsection{Paper Structure}
-	This paper is organised as follows.
-In the next section, we present work related to, \textit{opinion dynamics}, \textit{social space} modelling and \textit{complex network models}.
+	%		Article Structure
+	%******************************************
+	\subsection{article Structure}
+\noindent This article is organised as follows.
+In the next section, we present work related to \textit{opinion dynamics}, \textit{social space} modelling and \textit{complex network models}.
 In the following section, we describe our game of consensus and introduce multiple model variations, designed to study the notion of context permeability and the process of consensus formation in multiple social networks.
@@
 	\label{sec:relatedwork}
-	In this section, we present work related to, \textit{opinion dynamics}, \textit{social space} modelling and \textit{complex network models}.	
+\noindent In this section, we present work related to, \textit{opinion dynamics}, \textit{social space} modelling and \textit{complex network models}.	
 	%******************************************
@@
 	\subsection{Opinion Dynamics and Consensus Formation}
-	Formal opinion dynamics models provide an understanding, if not an analysis, of opinion formation processes.
+\noindent Formal opinion dynamics models provide an understanding, if not an analysis, of opinion formation processes.
 An early formulation of these models was designed to comprehend complex phenomena found empirically in groups \cite{French1956}.
@@
 In these models, agents update their opinions either under social influence or according to their own experience.
-For a detailed analysis over some opinion dynamics model analytical and simulation results, refer to \cite{Hegselmann2002}.
-
-	§§§ ESTA ULTIMA FRASE ESTÁ ESTRANHA!!! falta uma vírgula antes de model? mesmo assim não se perceberia bem... Podes rever, pf?
+For a detailed analysis over some opinion dynamics models, refer to \cite{Hegselmann2002}.
 
@@
 	\subsection{Social Structure in Simulation Models}
-	One of the most widely used approaches to represent social spaces in abstract simulation models is using a  bi-dimensional grid.
-This approach has its origins in the first \textit{‚Äúcheckerboard‚Äù}
-	§§§ VER AQUI
-	model introduced in computational social sciences by Thomas Schelling \cite{Schelling1971} and Sakoda \cite{Sakoda1971}.
+\noindent One of the most widely used approaches to represent social spaces in abstract simulation models is using a  bi-dimensional grid.
+This approach has its origins in the first \textit{``checkerboard''} model introduced in computational social sciences by Thomas Schelling \cite{Schelling1971} and Sakoda \cite{Sakoda1971}.
 Another famous example that uses bi-dimensional grids as social structure is the social simulation model of dissemination of culture from Axelrod \cite{Axelrod1997}.
@@
 These properties are typically found in---and the models inspired by---real-world network structures.
-One of the first complex network models is the random graph from §§§ VER Erd≈ës and Renyi \cite{Erdos1959}.
+One of the first complex network models is the random graph from Erd\H{o}s and Rényi \cite{Erdos1959}.
 Other examples include the model of preferential attachment \cite{Barabasi1999} and the small-world network models \cite{Watts1998}.
@@
 	\label{sec:multi-context-models} 
-	In this section, we present our modelling approach to explore the concept of permeability between contexts.
+\noindent In this section, we present our modelling approach to explore the concept of permeability between contexts.
 In our approach, we consider multiple social networks as a way to represent the complex social space in which an agent is inserted.
@@
 	\label{sec:sim_consensus}
-	Our agent-based models are designed as \textit{discrete-event} models.
+\noindent Our agent-based models are designed as \textit{discrete-event} models.
 On each simulation cycle, every agent executes a simulation step.
@@
 
-	§§§ TALVEZ ACRESCENTAR ISTO???
 	The reason we are not really interested in which exact option gets selected is the same reason why we chose such a content-neutral game for the individual interactions.
-From the very beginning, our research questions were focused on the collective properties, the structure of the networks involved, and the dynamical outcomes of the simulations, thus leaving out issues related with individual motivations and desired results, either for any individual agent or the society.
+From the very beginning, our research questions were focused on the collective properties, the structure of the networks involved, and the dynamical outcomes of the simulations: thus leaving out issues related with individual motivations and desired results, either for any individual agent or the society.
 Granted, most applications of this research will often include such goals, for inquisition into complex social issues, including possibly policy design, in which the individual rationalities must be considered, and will have a very strong influence on the collective outcomes.
@@
 
-	\newpage
+%	\newpage
 	\subsection{Context Permeability}
-	This first model of context permeability \cite{Antunes2007,Antunes2010} is designed to study our first setting for permeability.
+\noindent This first model of context permeability \cite{Antunes2007,Antunes2010} is designed to study our first setting for permeability.
 In most interesting applications, an agent is immersed in a complex social world, where it engages in a multitude of relations with other agents (and even aggregated agents such as institutions or informal groups).
@@
 	\label{sec:models_cs}
-	In the context switching model \cite{Antunes2009}, agents are embedded in multiple relations represented as static social networks and they switch \textit{contexts} with a given probability $\zeta_{C_i}$ associated with context $C_i$.
-The switching probability value is §§§VERIFICA SE É ISTO§§§ kept constant for any given network.§§§TIRAR  the same in the same network.§§§ Each agent switches from its current neighbourhood to a further §§§(vê pf se further está bem, fiquei na dúvida o que querias dizer) neighbourhood in another network (in which this agent was inactive).
+\noindent In the context switching model \cite{Antunes2009}, agents are embedded in multiple relations represented as static social networks and they switch \textit{contexts} with a given probability $\zeta_{C_i}$ associated with context $C_i$.
+The switching probability value is the same for every agent in a given network.
+Each agent switches from its current neighbourhood to another network (in which this agent was inactive).
 The agents are only active in one context at a time, and can only perform encounters with neighbours in the same context.
@@
 Context switching introduces one notion that has not been explored in the literature so far: the fact that, although some social contexts can be relatively stable if we consider short to moderate periods of time, our social peers are not always available at all times and spend different amounts of time in distinct social contexts.
-	§§§ ISTo É IMPROTANTE, INOVADOR, E DEVEMOS TALVEZ DAR-LHE MAIS ENFASE NAS CONCLUSOES
 
@@
 	\label{sec:experimental-setup}
-	In this section, we describe all the tools and processes necessary to produce the current research output.
+\noindent In this section, we describe all the tools and processes necessary to produce the current research output.
 The experiments for our previously described simulation models were developed using the MASON~\cite{Luke2005} simulation framework written in Java.
 All the code for the simulation models can be found here \cite{Nunes:Software:11067}.
-Moreover, all the results presented in this paper were made reproducible by using the \textit{statistical computing language R} \cite{R2008} and the R package \textit{knitr} \cite{knitr2014}.
+Moreover, all the results presented in this article were made reproducible by using the \textit{statistical computing language R} \cite{R2008} and the R package \textit{knitr} \cite{knitr2014}.
 Knitr is used for generating reports that contain the code, the results of its execution (plots and tables), and the textual description for such results.
-All the R code and the configuration files used to produce the analysed data can be found \textbf{in}...\todo{Archive the data, analysis and code used for the analysis, get a doi for it and cite it here}.
-§§§
+All the R code used  to produce the data analysis and the configuration files used to reproduce the data can be found in \cite{NunesAntunes2014:Analysis:11898}.
 
@@
 a step in a random order: this is so that this dynamical system --our simulation model-- is not influenced by the order in which agents are executed.
-Simulations end when total consensus is achieved or 2000 (§§§ including XXX agent-to-agent interactions) steps have passed.
+Simulations end when total consensus is achieved or 2000 steps have passed.
 
@@
 \label{sec:exp-setup_network_models}
-The social networks used in our models are \textit{k-regular} and \textit{scale-free}.
+\noindent The social networks used in our models are \textit{k-regular} and \textit{scale-free}.
 A k-regular network is a network where all the nodes have the same number of connections.
@@
 
-§§§acho que se devia explicar primeiro o que **são** scale-free networks, o que as define, e só depois dizer que se podem construir com o preferential attachment, aliás, não é a única maneira de as construir, nem sei se é a melhor, apenas á a mais usual e usada...§§§
-
-Scale-free networks \cite{Barabasi1999} are created with a model of preferential attachment proposed by Barab\'{a}si and colleagues \cite{Barabasi1999}.
+Scale-free networks are networks in which the degree distribution follows a power law, at least asymptotically.
+That is, the fraction $P(k)$ of nodes in the network having $k$ connections to other nodes goes for large values of $k$ as: $ P(k)  \sim  k^{-\gamma}$ where $\gamma$ is a parameter whose value is typically in the range $2 < \gamma < 3$.
+
+We use the method proposed in \cite{Barabasi1999} by Barab\'{a}si and Albert to construct the scale-free network instances using a preferential attachment.
 This model builds upon the perception of a common property of many large networks, a scale-free-power-law distribution of node connectivity.
@@
 
-The network instances were generated using the \textit{b-have network library} §§§cita tb o paper do MABS 2013?
-\cite{Nunes:Software:11069}.
+The network instances were generated using the \textit{b-have network library} \cite{Nunes:Software:11069}.
 This is a Java library that allows for the manipulation of Network/Graph data structures.
@@
 \subsection{Measuring Network Properties}
-We measure two structural properties of our networks: the \textit{average path length} and the \textit{clustering coefficient}.
+\noindent We measure two structural properties of our networks: the \textit{average path length} and the \textit{clustering coefficient}.
 The \textit{average path length} measures the typical separation between two vertices in the graph.
@@
 Watts and Steven Strogatz \cite{Watts1998} introduced the measure to characterise a class of complex networks called small-world networks.
+
+These properties are quite important to study social phenomena as they characterize structures that 
+can be found in the real scenarios.
+The small-world networks generated by the models of Watts and Strogatz for instance \cite{Watts1998}, tries to model real-world social networks with short average path length, generate local clustering, and triadic closures between the nodes.
+One shortcoming of this model, is the fact that these networks do not possess node hubs found in many real-world social networks.
+
+Since we construct scenarios where we overlap highly clustered k-regular networks and scale-free networks with node hubs, we are interested in what kind of properties emerge from merging these structures and how they are comparable to the existing models.
+
 The networks produced by the \textit{b-have network library} \cite{Nunes:Software:11069} were exported to files and analysed using the \textit{igraph R package} \cite{igraph2006}.
-
-§§§ TALVEZ UM POUCO MAIS SOBRE O SIGNIFICADO DESSAS MEDIDAS, E DAÍ O SEU VALOR PARA OS ESTUDOS DE FENOMENOS SOCIAIS COMPLEXOS
 
@@
 % Overview
-In this section, we bababa
-§§§
+\noindent In this section, we analyse and discuss the results for different experiments with both the
+context permeability and context switching models. We start by analysing the structural properties
+that arise from combining different networks while maintaining the same set of network nodes.
+We then perform multiple experiments where we observe the impact of different model configurations in the convergence to consensus.
+We correlate the outcomes of our context permeability model simulations with the structural properties of the multi-network structures.
+We also explore how the new dynamics introduced by the context switching model, affect the consensus building process.
 
@@
 \label{sec:network_properties}
-In this first analysis, we investigate the properties of different network topologies that we use in our models. 
+\noindent In this first analysis, we investigate the properties of different network topologies that we use in our models. 
 One of the parameters in some experiments is the number of networks in which the agents interact. Adding more networks means adding more connections. 
@@
 	\centering
-	\includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_merge_2_10regular"}
+	\includegraphics[width=1\linewidth]{"../analysis/pdf/network_properties_merge_2_10regular"}
 	\begin{minipage}{0.9\textwidth}
@@
 
+\begin{wrapfigure}[13]{r}{0.45\textwidth}
+	\includegraphics[width=1\linewidth]{"../analysis/pdf/network_properties_1_20regular"}
+	\begin{minipage}{0.7\linewidth}
+		\caption{Single k-regular network with k=20. (Kamada-Kawai layout)}
+		\label{fig:network_properties_1_20regular}
+	\end{minipage}
+\end{wrapfigure}
+
 The networks are drawn using the \textit{Kamada-Kawai} Layout \cite{Kamada19897} which regards the desirable ``geometric'' (Euclidean) distance between two vertices in the drawing as the ``graph theoretic'' distance between them in the corresponding graph.
 We can see by the results of the layout in figure \ref{fig:network_properties_merge_2_10regular}, that the distance between nodes in the network has decreased, this is also confirmed by the reduced average path length of the combined networks (see table \ref{tab:network_properties_merge_2_10regular}).
-
-\begin{wrapfigure}{r}{0.45\linewidth}
-	\includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_1_20regular"}
-	\begin{minipage}{0.8\linewidth}
-		\caption{Single k-regular network with k=20. (Drawn using the Kamada-Kawai layout)}
-		\label{fig:network_properties_1_20regular}
-	\end{minipage}
-\end{wrapfigure}
-
 To illustrate our point we analysed one k-regular network with k = 20 (see figure \ref{fig:network_properties_1_20regular} --and the corresponding entry on table \ref{tab:network_properties_merge_2_10regular}).
@@
 
-§§§ regra== "xxx that" ou "xxx, which"
-
 Since we model the agent social space as a multitude of networks, we need to investigate the properties resulting from the merging of these networks.
@@
 \label{sec:overlapping_kreg}
-We will now investigate what kind of properties we can get from merging k-regular networks.
+\noindent We will now investigate what kind of properties we can get from merging k-regular networks.
 First, we analysed the distribution for the average path length and the clustering coefficient values over 100 network instances with 100 nodes each.
-Since this variation §§§qual variation???
-do average path length???§§§ is negligible, we use the average as a descriptor for different configurations of k values and number of overlapping networks.
-(The reader should refer to figures \ref{append_fig:network_properties_apl_kreg} and \ref{append_fig:network_properties_cc_kreg} in the appendix for the box plot preliminary analysis.)
+From a box plot preliminary analysis (see figures \ref{append_fig:network_properties_cc_kreg} and \ref{append_fig:network_properties_apl_kreg}), we can see that the average path length does not vary much for the 100 instances, as such, we use the average as a descriptor for different configurations of k values and number of overlapping networks.
 
@@
 		\centering
-		\includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_apl_line_kreg_12345"}
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/network_properties_apl_line_kreg_12345"}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_apl_line_kreg_1020304050"}
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/network_properties_apl_line_kreg_1020304050"}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_cc_line_kreg_12345"}
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/network_properties_cc_line_kreg_12345"}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_cc_line_kreg_1020304050"}
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/network_properties_cc_line_kreg_1020304050"}
 		\caption{}
@@
 \subsubsection{Properties of Overlapping Scale-free Networks}
-In a preliminary analysis we looked at the distribution of property values that results from merging scale-free networks (see figure \ref{append_fig:network_properties_sf}).
+\noindent In a preliminary analysis we looked at the distribution of property values that results from merging scale-free networks (see figure \ref{append_fig:network_properties_sf}).
 Like in the previous results, the properties don't vary much between the 100 different instances of each overlapping network configuration.
@@
 		\centering
-		\includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_apl_line_sf_12345"}
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/network_properties_apl_line_sf_12345"}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_cc_line_sf_12345"}
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/network_properties_cc_line_sf_12345"}
 		\caption{}
@@
 \subsubsection{Merging K-Regular with Scale-Free Networks}
-Finally, we look at what happens when we merge k-regular networks with \textit{scale-free} networks.
+\noindent Finally, we look at what happens when we merge k-regular networks with \textit{scale-free} networks.
 We didn't make an exhaustive analysis for this configuration, but we show what is the resulting structure of such merging.
@@
 	\centering
-	\includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_10regular_2scale-free"}
+	\includegraphics[width=1\linewidth]{"../analysis/pdf/network_properties_10regular_2scale-free"}
 	\begin{minipage}{0.9\textwidth}
@@
 		\centering
-		\includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_apl_line_sf_kreg_12345"}
-		\caption{}
-		\label{fig:network_properties_apl_line_sf__kreg_12345}
-	\end{subfigure}%
-	\begin{subfigure}{.5\linewidth}
-		\centering
-		\includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_apl_line_sf_kreg_1020304050"}
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/network_properties_apl_line_sf_kreg_12345"}
+		\caption{}
+		\label{fig:network_properties_apl_line_sf_kreg_12345}
+	\end{subfigure}%
+	\begin{subfigure}{.5\linewidth}
+		\centering
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/network_properties_apl_line_sf_kreg_1020304050"}
 		\caption{}
@@
 		\vspace{0.2cm}
-		\caption{Average \textit{average path  length} for 100 instances of heterogeneous network configurations:  one \textit{scale-free} with $d=\{1,2,3,4,5\}$ and one \textit{k-regular} network with $k=\{1,2,3,4,5\}$ (\ref{fig:network_properties_apl_line_sf__kreg_12345}) and $k=\{10,20,30,40,50\}$ (\ref{fig:network_properties_apl_line_sf_kreg_1020304050}).
+		\caption{Average \textit{average path  length} for 100 instances of heterogeneous network configurations:  one \textit{scale-free} with $d=\{1,2,3,4,5\}$ and one \textit{k-regular} network with $k=\{1,2,3,4,5\}$ (\ref{fig:network_properties_apl_line_sf_kreg_12345}) and $k=\{10,20,30,40,50\}$ (\ref{fig:network_properties_apl_line_sf_kreg_1020304050}).
 (See the respective box plots in the appendix: figure \ref{append_fig:network_properties_apl_sf_kreg}).}
@@
 Figure \ref{fig:network_properties_line_apl_sf_kreg} shows the \textit{average path length} of 100 independently generated instances of combinations of one \textit{k-regular} network and one \textit{scale-free} network with different values $k$ and $d$, respectively.
-We can see that for configurations where the \textit{k-regular} networks have low values of $k$ (figure \ref{fig:network_properties_apl_line_sf__kreg_12345}), adding a \textit{scale-free} network always decreases the \textit{average path length}.
+We can see that for configurations where the \textit{k-regular} networks have low values of $k$ (figure \ref{fig:network_properties_apl_line_sf_kreg_12345}), adding a \textit{scale-free} network always decreases the \textit{average path length}.
 Moreover, the higher the $d$, the lower the path length, as more connections are formed between different nodes.
@@
 		\centering
-		\includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_cc_line_sf_kreg_12345"}
-		\caption{}
-		\label{fig:network_properties_cc_line_sf__kreg_12345}
-	\end{subfigure}%
-	\begin{subfigure}{.5\linewidth}
-		\centering
-		\includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_cc_line_sf_kreg_1020304050"}
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/network_properties_cc_line_sf_kreg_12345"}
+		\caption{}
+		\label{fig:network_properties_cc_line_sf_kreg_12345}
+	\end{subfigure}%
+	\begin{subfigure}{.5\linewidth}
+		\centering
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/network_properties_cc_line_sf_kreg_1020304050"}
 		\caption{}
@@
 \noindent Figure \ref{fig:network_properties_line_cc_sf_kreg} shows the results for the \textit{clustering coefficient}.
-These are similar to the results we get for \textit{k-regular} networks (see figure \ref{network_properties_cc_line_kreg}).
+These are similar to the results we get for \textit{k-regular} networks (see figure \ref{fig:network_properties_cc_line_kreg}).
 The difference is that we are not adding more networks but rather increasing the parameter $d$ of the scale-free.
@@
 
-In this section, we discuss the results for various sets of experiments on the first model we presented --the \textit{context permeability model} \cite{Antunes2007,Antunes2010}.
+\noindent In this section, we discuss the results for various sets of experiments on the first model we presented --the \textit{context permeability model} \cite{Antunes2007,Antunes2010}.
 In a first set of experiments, the agent space was structured using \textit{k-regular} and \textit{scale-free }social networks.
@@
 \label{sec:ctx_perm_convergence}
-We now analyse the ratio of convergence to consensus for different network configurations.
+\noindent We now analyse the ratio of convergence to consensus for different network configurations.
 We correlate this ratio with the properties that the combined network structure exhibits.
@@
 This convergence is achieved not because of the clustering coefficient but rather due to lower \textit{average path length}.
-This is difficult to visualise using only the tables and the previous plots so, to confirm this hypothesis, we measured the \textit{Spearman's correlation} between the ratio of convergences to consensus, the average of \textit{average path length} , and the average of \textit{clustering coefficient} for the corresponding network configurations (see table \ref{tab:convergence_correlation}).
-
-§§§ talvez explicar o que significa a Spearman's correlation ???
+This is difficult to visualise using only the tables and the previous plots so, to confirm this hypothesis, we measured the \textit{Spearman's correlation}\footnote{The Spearman's rank correlation coefficient is a nonparametric measure of statistical dependence between two variables.
+It assesses how well the relationship between two variables can be described using a monotonic function.} between the ratio of convergences to consensus, the average of \textit{average path length}, and the average of \textit{clustering coefficient} for the corresponding network configurations (see table \ref{tab:convergence_correlation}).
 
@@
 \label{sec:ctx_perm_encounters}
-We now analyse the convergence in terms of average number of meetings during a simulation run.
+\noindent We now analyse the convergence in terms of average number of meetings during a simulation run.
 Since the maximum number of simulation cycles is 2000, the maximum number of encounters is 2~000~000 (we have 100 agents and each one performs one encounter per cycle).
@@
 		\centering
-		\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_permeability_encounters_kregular_12345"}
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/context_permeability_encounters_kregular_12345"}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_permeability_encounters_kregular_1020304050"}
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/context_permeability_encounters_kregular_1020304050"}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_permeability_simrun_kregular_k10_normal"}
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/context_permeability_simrun_kregular_k10_normal"}
 		\caption{Typical Run}
@@
 		\centering
-		\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_permeability_simrun_kregular_k10_outlier"}
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/context_permeability_simrun_kregular_k10_outlier"}
 		\caption{Outlier Run}
@@
 		\centering
-		\includegraphics[width=1\linewidth]{"../analysis/pdf/ cp-regular-normal-run-memory-diff"}
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/cp-regular-normal-run-memory-diff"}
 		\caption{Typical Run}
@@
 		\centering
-		\includegraphics[width=1\linewidth]{"../analysis/pdf/ cp-regular-outlier-run-memory-diff"}
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/cp-regular-outlier-run-memory-diff"}
 		\caption{Outlier Run}
@@
 
-§§§ ACHO QUE ESTAMOS A GASTAR UM BOCADO DE TEMPO/ESPAÇO A MAIS COM ESTE "OUTLIER RUN" OU ISSO CONDUZ A UMA CONCLUSÃO FORTE E IMPORTANTE, OU ESTAMOS SUJEITOS A ALGUMA CRÍTICA AQUI
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=1\linewidth]{"../analysis/pdf/ cp-regular-outlier-fullrun-memory-diff"}
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=1\linewidth]{"../analysis/pdf/cp-regular-outlier-fullrun-memory-diff"}
 	\begin{minipage}{0.9\textwidth}
@@
 		\centering
-		\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_permeability_encounters_sf"}
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/context_permeability_encounters_sf"}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=1\linewidth]{"../analysis/pdf/   context_permeability_encounters_sf_best"}
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/context_permeability_encounters_sf_best"}
 		\caption{}
@@
 \subsubsection{Heterogeneous Network Configuration}
-We also performed experiments where we mixed the network topologies: in this case we used one \textit{scale-free} and one \textit{k-regular} networks.
+\noindent We also performed experiments where we mixed the network topologies: in this case we used one \textit{scale-free} and one \textit{k-regular} networks.
 Table~\ref{tab:regular_scale-free_convergence} shows the convergence ratio for the heterogeneous network configuration with the multiple values for $d$ and $k$ for the \textit{scale-free} and \textit{k-regular} respectively.
@@
 
-\noindent One of the differences §§§entre quê e quê???, fica dificil sem as imagens no meio §§§ lies in the configuration with $d=1$ and $k=1$.
+\noindent One of the outcome differences between this configuration and the previous ones can be observed in the simulations with $d=1$ and $k=1$.
 The convergence ratio is higher than with $2$ $1-regular$ networks (see table \ref{tab:regular_convergence}) --but not better than two \textit{scale-free} networks.
 This happens because with $k=1$ the network is basically a ring and has the maximum possible average path length for a connected graph.
-Adding two rings improves §§§improves WHAT???§§§ this but the underlying structure is still very susceptible to self-reinforcing structures (a connected sub-graph is basically a line).
+Adding two rings improves  the convergence ratio but the underlying structure is still very susceptible to self-reinforcing structures (a connected sub-graph is basically a line).
 Adding a \textit{scale-free} changes this drastically as we are mixing tree-like network components with this first circle.
@@
 		\centering
-		\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_permeability_encounters_sfreg_k1020304050"}
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/context_permeability_encounters_sfreg_k1020304050"}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=1\linewidth]{"../analysis/pdf/  context_permeability_encounters_sfreg_k1020304050_best"}
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/context_permeability_encounters_sfreg_k1020304050_best"}
 		\caption{}
@@
 \subsection{Context Switching}
-In this section, we present the results relative to the context switching model.
+\noindent In this section, we present the results relative to the context switching model.
 The difference between this model and the previous one is that the agents no longer interact in the multiple networks at the same time (being able to select any neighbour at a given simulation step).
@@
 \subsubsection{Exploring the Switching Probability}
-We first look at the influence of the new parameter (switching probability) in the convergence to consensus.
+\noindent We first look at the influence of the new parameter (switching probability) in the convergence to consensus.
 We span the switching probability between $0$ and $1$ in intervals of $0.05$.
@@
 		\centering
-		\includegraphics[width=1\linewidth]{"../analysis/pdf/  context_switching_2_10_regular _switching_contour"}
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/context_switching_2_10_regular_switching_contour"}
 		\caption{10-regular Networks}
@@
 		\centering
-		\includegraphics[width=1\linewidth]{"../analysis/pdf/  context_switching_2_30_regular _switching_contour"}
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/context_switching_2_30_regular_switching_contour"}
 		\caption{30-regular Networks}
@@
 		\centering
-		\includegraphics[width=1\linewidth]{"../analysis/pdf/  context_switching_2_sf_d1 _switching_contour"}
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/context_switching_2_sf_d1_switching_contour"}
 		\caption{\textit{Scale-Free} $d=1$}
@@
 		\centering
-		\includegraphics[width=1\linewidth]{"../analysis/pdf/  context_switching_2_sf_d5 _switching_contour"}
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/context_switching_2_sf_d5_switching_contour"}
 		\caption{\textit{Scale-Free} $d=5$}
@@
 \end{figure}
-
-§§§ ATENçÂO QUE ``deve fechar com '' (duas plicas), não com " (aspas)
 
@@
 
-To check the influence of topology and connectivity in the new switching dynamics we took the most susceptible (§§§TO WHAT???) network type (the \textit{scale-free} networks) and performed the following experiment.
-We setup two \textit{scale-free} networks; one with $d=1$ and the other with $d=5$.
-We then performed the
+To check the influence of connectivity in the new switching dynamics we setup two \textit{scale-free} networks; one with $d=1$ and the other with $d=5$. We then performed the 
 same span of switching probability similarly to the previous experiments. The results can be seen in figure \ref{fig:ctx_cs_sf_d5_d1}.
@@
 	\centering
-	\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_switching_sf_d5_d1 _switching_contour"}
+	\includegraphics[width=1\linewidth]{"../analysis/pdf/context_switching_sf_d5_d1_switching_contour"}
 	\begin{minipage}{0.9\textwidth}
@@
 
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_switching_1_10regular_1_scale-free_d1 _switching_contour"}
+It seems that basically switching less from the less connected network is bad in both cases: spending more time in the network with bigger neighbourhoods allows for a stabler convergence.
+Sub-conventions can emerge in \textit{scale-free} networks with $d=1$ because usually some network regions are isolated by a single node --the root of the sub-tree they belong to.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=1\linewidth]{"../analysis/pdf/context_switching_1_10regular_1_scale-free_d1_switching_contour"}
 	\begin{minipage}{0.9\textwidth}
@@
 
-It seems that basically switching less from the less connected network is bad in both cases: spending more time in the network with bigger neighbourhoods allows for a stabler convergence.
-Sub-conventions can emerge in \textit{scale-free} networks with $d=1$ because usually some network regions are isolated by a single node --the root of the sub-tree they belong to.
-
 \subsubsection{Comparison with Context Permeability}
-Finally, to compare the context switching model with the previous model of context permeability, we constructed the following experiment.
+\noindent Finally, to compare the context switching model with the previous model of context permeability, we constructed the following experiment.
 We froze the switching probabilities in the values $\zeta={0.25,0.5,0.75}$ and varied the number of networks.
@@
 		\centering
-		\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_switching_encounters_comp_kregular_groupedbynets_2"}
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/context_switching_encounters_comp_kregular_groupedbynets_2"}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_switching_encounters_comp_kregular_groupedbynets_3"}
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/context_switching_encounters_comp_kregular_groupedbynets_3"}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_switching_encounters_comp_kregular_groupedbynets_4"}
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/context_switching_encounters_comp_kregular_groupedbynets_4"}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_switching_encounters_comp_kregular_groupedbynets_5"}
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/context_switching_encounters_comp_kregular_groupedbynets_5"}
 		\caption{}
@@
 
-The surprise was that for values of $k \ge 20$, the results where practically the same for both models independently of the switching probability --even when we increased the number of networks, the number of encounters remained around $2000$ on average for all the models.
+The surprise was that for values of $k \ge 20$, the results where practically the same for both
+models independently of the switching probability -- even when we increased the number of networks, the number of encounters remained around $2000$ on average for all the models.
 Above a certain level of neighbourhood size (and overlapping, which causes the average path length to drop), the switching probability becomes less influential.
 It is still important that we get comparable results because we are introducing a temporal component that was never explored before in these types of opinion dynamics models: the fact that the agents can become active in different networks at different points in time.
-§§§ mudei . para : na ultima frase, por favor valida
 
@@
 		\centering
-		\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_switching_encounters_comp_sf_groupedbynets_2"}
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/context_switching_encounters_comp_sf_groupedbynets_2"}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_switching_encounters_comp_sf_groupedbynets_3"}
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/context_switching_encounters_comp_sf_groupedbynets_3"}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_switching_encounters_comp_sf_groupedbynets_4"}
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/context_switching_encounters_comp_sf_groupedbynets_4"}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_switching_encounters_comp_sf_groupedbynets_5"}
+		\includegraphics[width=1\linewidth]{"../analysis/pdf/context_switching_encounters_comp_sf_groupedbynets_5"}
 		\caption{}
@@
 
-For \textit{scale-free} networks, figure \ref{ctx_switching_comp_sf} shows us similar results.
-It seems that switching with a higher probability displays results similar with those of context permeability.
-In this case, adding more networks makes so that lowering switching probabilities displays slightly worse results.
-This influence is due to the fact that the neighbourhoods are considerably smaller in \textit{scale-free} networks --even with values of $d=5$-- so the impact of low switching was bound to be noticed.
-
-One final remark is that with context switching, we always achieve consensus §§§ não percebo este being, será de cortar?§§§ being for \textit{k-regular} or \textit{scale-free} networks.
-In addition, increasing the number of networks seems to always reduce the number of encounters to achieve consensus in both models.
+For \textit{scale-free} networks, figure \ref{fig:ctx_switching_comp_sf} shows us similar
+results. It seems that switching with a higher probability displays results similar with those of
+context permeability. In this case, adding more networks makes so that lowering switching
+probabilities displays slightly worse results. This influence is due to the fact that the
+neighbourhoods are considerably smaller in \textit{scale-free} networks -- even with values of $d=5$ -- so the impact of low switching was bound to be noticed.
+
+An increasing number of networks seems to always reduce the number of encounters to achieve consensus in both models.
 This happens due to what we have called \textit{permeability}.
 Having multiple points of dissemination that permeate between different social networks enhances the overall convergence to consensus.
-§§§ acrescentei <<With permeability there are more previously >>§§§ With permeability there are more previously isolated nodes being reached in sparsely connected networks such as scale-free networks.
-
-§§§ não falaste de context switching induzido por razões, suponho que é intencional para deixar algo para um futuro paper, e também porque este já vai longo...
-§§§
-
-%******************************************
+With permeability there are more previously isolated nodes being reached in sparsely connected networks such as scale-free networks.
+
+%*****************************************
 %	Conclusion
 %******************************************
-\section{Conclusion}
+\section{Conclusions}
 \label{sec:conclusion-future}
-In this paper, we analysed and discussed our modelling framework for multi-relational models of social spaces.
+\noindent In this article, we analysed and discussed our modelling framework for multi-relational models of social spaces.
 These results show that not only contexts play an important role in the dissemination of consensus in artificial agent societies, but also that simple mechanisms can generate a great deal of complexity, especially in those scenarios where conventions are being co-learned by multiple agents.
 Adding more networks to our opinion dynamics model leads to outcomes where consensus was achieved not only more often but also faster.
-
-Future work includes the analysis of different complex network models, §§§while???
-será although?
-§§§ while \textit{k-regular} and \textit{scale-free} networks are two of the most pervasive network examples in these types of simulations.
-There has been a growing number of models with different properties inspired by real-world phenomena that can be considered.
+In particular, our results show that achieving convergence (i.e.\ total consensus in a network) is not a matter of connectivity.
+With scale-free networks we managed to achieve consensus more often and quicker than with less clustered networks.
+This conclusion is especially important for application with real world social phenomena, many times represented with such networks: full dissemination of a phenomenon (say, gossip-dissemination of a new anti-virus software) may prove impossible with one network only, but is very much eased up by the use of concomitant connections.
+Moreover, some of the techniques we have rehearsed have proven to speed up even more this now-eased up convergence.
+
+The second innovation presented in this article was the fact that our model describes an abstract way to represent the time spent on each network using the switching probability.
+This temporal component introduces a new dynamic to the study of opinion dynamics.
+Considering that in agent neighbourhoods, agents might not be available at all times and spend distinct amounts of time in different neighbourhoods, is an important factor to be included in some simulations from a modelling perspective.
+
+Future work includes the analysis of different complex network models.
+While \textit{k-regular} and \textit{scale-free} networks are two of the most pervasive network examples in these types of simulations, there has been a growing number of models with different properties inspired by real-world phenomena that can be considered.
 We can also analyse the networks according to different properties such as the present of nodes with high centrality in the network (hubs).
@@
 A difficult --but not impossible-- prospect for further research would be to track similar contexts between different real online social networks.
-	§§§ isto vem na linha do que eu acrescentei acima sobre manter o jogo neutro, para nos concentrarmos na estrutura do problema, talvez seja de ir lá buscar umas frases, e acerescentá-las aqui, que justificam que não nos debruçámos sobre dados reais, porque nos interessava mais a estrutura matemática...
-
-We are just scratching the surface of multi-relational models in social simulation with the next step being the connection of our model to the reality.
-§§§ esta frase enfraquece um pouco as conclusões e o artigo, não achas???
+
+\section*{Acknowledgements}
+\noindent This work was supported by the Funda\c{c}\~ao para a Ci\^encia e a Tecnologia under the grant SFRH / BD / 86034 / 2012.
 
@@
 
-§§§ é preciso rever a bibliografia, há muitas coisas sem data, ou DOI aparece em minúsculas (usa "{{DOI}}" se for preciso forçar as maiúsculas, etc
-
 \end{document}

### 2015-06-15 doc/main.tex
abstract reviewed

@@
 		\begin{abstract}
-			The structure of social relations is fundamental for the construction of plausible simulation scenarios.
-It shapes the way actors interact and create their identity within overlapping social contexts.
-Each actor interacts in multiple contexts, located within relations that constitute their social space.
-We present a modelling approach to construct structured agent societies with multiple concomitant social networks.
-We study the notion of context permeability, using a game in which agents try to achieve global consensus.
-We design and analyse two different models of permeability.
-In the first model, agents interact concurrently in multiple social networks.
-The second model uses a context switching mechanism that adds temporal dynamics to agent interaction.
-They switch between the different networks spending more or less time in each network.
-We compare each model and analyse the influence of different social networks regarding the speed of convergence to consensus.
-We conduct a series of experiments that show the impact of coexisting social networks when designing simulation models.
-This approach unveils both the limitations of the current modelling approaches and possible research directions for complex social space simulations.
+                  The structure of social relations is fundamental for the construction of plausible
+                  simulation scenarios. It shapes the way actors interact and create their identity
+                  within overlapping social contexts. Each actor interacts in multiple contexts
+                  within different types of social relations that constitute their social space. In
+                  this article, we present an approach to model structured agent societies with
+                  multiple coexisting social networks. We study the notion of \textit{context
+                    permeability}, using a game in which agents try to achieve global consensus. We
+                  design and analyse two different models of permeability. In the first model,
+                  agents interact concurrently in multiple social networks. In the second, we
+                  introduce a \textit{context switching} mechanism which adds a dynamic temporal
+                  component to agent interaction in the model. Agents switch between the different
+                  networks spending more or less time in each one. We compare these models and
+                  analyse the influence of different social networks regarding the speed of
+                  convergence to consensus. We conduct a series of experiments that show the impact
+                  of different configurations for coexisting social networks. This approach unveils
+                  both the limitations of the current modelling approaches and possible research
+                  directions for complex social space simulations.
 		\end{abstract}

### 2015-06-20 doc/main.tex
Model description reviewed

@@
 
-\noindent In most simulations of complex social phenomena, agents are considered to inhabit a space in which structure is very simple, and has little resemblance with the social world it is supposed to depict, and for which the conclusions are supposed to be extrapolated.
-This simplicity does not come by chance, rather, it is somewhat necessary and desired by the researchers, since the problems to be approached are themselves so complex that whichever factors of complexity can be reduced, or at least postponed, are always welcome.
-So, as widely visible, geographical space is usually reduced to a two-dimensional grid composed by square patches, and all social relations between  agents are condensed into one abstract relation.
-Usually, approaches disregard the fact that in real world our relations are multiple, and, moreover, possess very diverse characteristics, including rich information about degree, intensity, frequency, methods associated, asymmetry, and so on.
-
-To explore the addition of multiple relations and its consequences for the dissemination of phenomena in social simulations, we put forward to reduce the emphasis given on the individual interactions, depicted as a theoretical game.
-We accomplished this by choosing a simple, and especially, neutral game to represent those interactions.
-Our main concern was that the game itself would not provide biases or trends in the collective phenomenon being studied, so we chose the consensus formation game, with a straightforward majority rule to decide the outcome of each individual move.
-
-	Studying simulation models of consensus formation can advance our understanding of real-world emergent social phenomena.
-Typically, we can construct models with different levels of abstraction.
-Simulation methods can range from data-driven paradigms to more abstract descriptions that allow us to create \textit{what-if-scenarios}.
-While most models are simplified descriptions of the real-world corresponding target phenomena, many constitute complex systems themselves and thus the need for tools and techniques like simulation to explore their properties.
-In \cite{Emmeche1997}, Emmeche makes a distinction between two types of complexity.
-He characterises the complexity of real systems as \textit{``ontological complexity''} and the one of models as \textit{``descriptive complexity''}.
-Examples of real-world target phenomena for social simulation models include for instance the joint assessments of policies or, in the context of economics and politics, \textit{the voting problem}.
-Herbert Simon's investigations on this problem were also one of the first stepping stones to the field of social simulation \cite{Simon1954}.
-
-	In agent-based \textit{opinion dynamics}, agent interactions are guided by \textit{social space} abstractions.
-In some models, dimensionality and structure are irrelevant and any agent can interact with any other agent.
-	Other approaches use an underlying structure to create agent neighbourhoods.
-Axelrod for instance, in its model of \textit{dissemination of culture} \cite{Axelrod1997}, represents agents in a bi-dimensional grid.
-Finally, in an attempt to mimic real social systems, some simulation models make use of \textit{complex network models} (see \cite{Weisbuch2004}) to create the infrastructure that guides agent interaction.
-
-	In real-world scenarios, actors engage in a multitude of social relations different in kind and quality.
-Most simulation models don't explore \textit{social space} designs that take into account the differentiation between coexisting social networks.
-Modelling multiple concomitant relations was an idea pioneered by Peter Albin in \cite{Albin1975} but without any further development.
-The complex social structures that result from interacting in these different dimensions form the basis for the formation of social identity \cite{Roccas2002,Ellemers2002}.
+        \noindent In most simulations of complex social phenomena, agents are considered to inhabit
+        a space in which structure is very simple. This space has little resemblance with the social
+        world it is supposed to depict and for which conclusions are supposed to be
+        extrapolated. This simplicity does not come by chance, rather, it is necessary and desired
+        by the researchers: the problems to be approached are themselves so complex that whichever
+        factors of complexity can be reduced (or at least postponed), the reduction is always
+        welcome. So, it is common practice that geographical space is reduced to a two-dimensional
+        grid, and all social relations between agents are condensed into one more or less structured
+        abstract relation. Most social simulation and modelling approaches disregard the fact that
+        we engage in multiple social relations. Moreover, each kind of social relation can possess
+        distinctive characteristics that include: rich information such as degree of connectivity,
+        centrality, trust, interactions frequency, asymmetry, and so on.
+
+        To explore the addition of multiple relations and its consequences for the dissemination of
+        phenomena in social simulations, we put forward to \textit{reduce} the emphasis given on
+        agent individual interactions. We accomplished this by choosing a simple -- and especially
+        neutral -- game to model those interactions. Our main concern was that the game itself would
+        not provide biases or trends in the collective phenomenon being studied, so we chose the
+        \textit{consensus formation game}, with a straightforward majority rule to decide the
+        outcome of each individual move.
+
+        While most models are simplified descriptions -- reductions -- of real-world phenomena, many
+        constitute complex systems themselves and thus, we need techniques such as simulation to
+        explore their properties. We can make a distinction between two types of complexity: the
+        complexity of real systems (\textit{ontological complexity}) and the complexity of models
+        (\textit{descriptive complexity})~\cite{Emmeche1997}. The levels of abstraction in a
+        simulation model can then range from data-driven paradigms to more abstract descriptions
+        that allow us to create \textit{what-if-scenarios}. The study of this abstract
+        \textit{descriptive complexity} in simulation models is as valuable as its
+        \textit{data-driven} counterpart. We may not be able to make predictions based on the direct
+        application of such models; but, their study can inspire the engineering of artificial
+        complex systems and reveal properties with applications beyond the explanation of observable
+        phenomena. Studying consensus formation can thus advance our understanding of related
+        real-world social phenomena.
+
+        Examples of thematic real-world phenomena in social simulation models include for instance
+        the joint assessments of policies or, in the context of economics and politics, \textit{the
+          voting problem}. Herbert Simon's investigations on this problem were one of the first
+        stepping stones to the field of social simulation \cite{Simon1954}; which then inspired
+        models (like the one we present in this article) related to evolution and dissemination of
+        opinions, which we call \textit{opinion dynamics}. In agent-based \textit{opinion dynamics},
+        agent interactions are guided by \textit{social space} abstractions. In some models, the
+        dimensionality and structure of this space is irrelevant (any agent can interact with any
+        other agent). Other models use an underlying artefact that structures agent
+        neighbourhoods. Axelrod for instance, represents agent neighbourhoods as a bi-dimensional
+        grid in its model of \textit{dissemination of culture} \cite{Axelrod1997}. In an attempt to
+        mimic real social systems, one can also make use of \textit{complex network models} to
+        create the infrastructure that guides agent interaction (see \cite{Weisbuch2004} for an
+        example).
+
+	In real-world scenarios, actors engage in a multitude of social relations different in kind
+        and quality. Most simulation models don't explore \textit{social space} designs that take
+        into account the differentiation between coexisting social networks. Modelling multiple
+        coexisting relations was an idea pioneered by Peter Albin in \cite{Albin1975} but without
+        further development. The process of interacting in these different complex social dimensions
+        can be seen as the basis for the formation of our social identity
+        \cite{Roccas2002,Ellemers2002}.
 
@@
 	%******************************************
-	In this article, we explore the possibility of modelling opinion dynamics with multiple social networks.
-We look at how the properties influence the convergence to opinion consensus.
-Starting with this premise of
-	using multiple social networks, we present a series of models that use these networks in different ways, which create distinct emergent dynamics.
-We want to observe the consequences of using multiple social networks at the same time --- while maintaining the model as simple and abstract as possible, much like what happens with the current contributions on opinion dynamics present in the literature.
-
-	In our models agents can: interact at the same time in the multiple networks (choosing partners from any network) or switch between networks (choosing only partners from their current network).
-While our models seem quite simple, and are quite abstract, they generate quite complex outcomes and thus the need of simulation to understand their dynamics.
+	In this article, we explore the of modelling opinion dynamics with multiple social
+        networks. We look at how the properties of different network models influence the
+        convergence to opinion consensus. We present a series of models that use these networks in
+        different ways: which create distinct emergent dynamics. We want to study the consequences
+        of using multiple social networks at the same time while maintaining the interaction model
+        as simple and abstract as possible (following the methodology in most opinion dynamics
+        literature). We present two models where agents can: interact at the same time in the
+        multiple networks (choosing partners from any network); or switch between networks (choosing
+        only partners from their current network).
 
@@
 	%******************************************
-	\subsection{article Structure}
-\noindent This article is organised as follows.
-In the next section, we present work related to \textit{opinion dynamics}, \textit{social space} modelling and \textit{complex network models}.
-In the following section, we describe our game of consensus and introduce multiple model variations, designed to study the notion of context permeability and the process of consensus formation in multiple social networks.
-Section \ref{sec:experimental-setup} describes the experimental set-up; the set of tool and methodologies followed to conduct our investigations.
-In section \ref{sec:results-discussion}, we present and discuss our results and compare the different simulation models.
-Finally, we conclude by making a summary of what we learned from the simulation models and point out possible future research directions.
+	\subsection{Article Structure}
+        \noindent This article is organised as follows. In the next section, we present the work
+        related to \textit{opinion dynamics}, \textit{social space} modelling and \textit{complex
+          network models}. In the following section, we describe our game of consensus and introduce
+        our multiple model variations. These are designed to study the notion of \textit{context
+          permeability} and consensus formation in multiple social networks. Section
+        \ref{sec:experimental-setup} describes the experimental setup; the set of tool and
+        methodologies followed to conduct our investigations. In section
+        \ref{sec:results-discussion}, we present and discuss our results and compare the different
+        simulation models. Finally, we summarise what we learned from our experiments and point out
+        future research directions.
 
@@
 	\label{sec:relatedwork}
-\noindent In this section, we present work related to, \textit{opinion dynamics}, \textit{social space} modelling and \textit{complex network models}.	
+        \noindent In this section, we present work related to \textit{opinion dynamics},
+        \textit{social space} modelling, and \textit{complex network models}.
 	%******************************************
@@
 	\subsection{Opinion Dynamics and Consensus Formation}
-\noindent Formal opinion dynamics models provide an understanding, if not an analysis, of opinion formation processes.
-An early formulation of these models was designed to comprehend complex phenomena found empirically in groups \cite{French1956}.
-In particular, the work on consensus building in the context of decision-making was first studied by DeGroot \cite{Degroot74} and Lehrer \cite{Lehrer1975}.
-Empirical studies of opinion formation in large populations have methodological limitations, as such, computational sociology arises with a set of tools to cope with those limitations.
-We use simulation, in particular \textit{multi-agent simulation (MAS)}, as a methodological framework to study such phenomena in a larger scale.
-Most opinion dynamics simulation models are based either on binary opinions \cite{Galam1997,Antunes2009} or continuous values \cite{Deffuant2000,Deffuant2002}.
-In these models, agents update their opinions either under social influence or according to their own experience.
-For a detailed analysis over some opinion dynamics models, refer to \cite{Hegselmann2002}.
-
-	Opinion dynamics models try to study under which circumstances consensus, or polarisation is reached.
-Agent-based models can have broader application outside social simulation.
-In distributed systems in general, consensus is a means by which processes agree on some data value that is needed during computation.
-Typically, this agreement is the result of a negotiation process often with the aid of a mediator.
-In human societies, social conventions emerge to deal with coordination and subsequently with cooperation problems \cite{Lewis1969}.
-These conventions are regularities of behaviour that can turn normative with time, due to there being persistent solutions to such problems.
-Moreover, conventions typically originate from the necessity to resolve conflict.
-MAS can also benefit from being capable of produce emergent conventions in coordination or cooperation problems \cite{Delgado2002}.
-The decentralised nature of these models of consensus is highly desirable for problems where dynamic control is needed.
-In these scenarios, creating conventions before hand (off-line), or developing a central control mechanism for generating them, can be a difficult and intractable task.
-MAS can be designed to update their values and strategies based on this local information.
-Consequently, the guarantee of achieving a global consensus and the efficiency of convergence towards it has been a natural concern in the design of local interaction behaviours.
-
-	Consensus models are also investigated as means to create conventions in MAS.
-Shoham and Tennenholtz \cite{Shoham1994} create a bridge between economic literature and machine learning, by studying a series of models in which multiple agents are engaged in learning a particular convention.
-They call this process \textit{co-learning}.
-The complexity of these systems derives from its concurrent nature: one agent adapts to the behaviour of another agent it has encountered, and as these agents update their behaviour in a similar fashion, this results in a highly non-linear system dynamics.
-In their work, Shoham and Tennenholtz define the notion of \textit{stochastic social games} and compare different rules with the objective of establishing conventions in a decentralised fashion.
-In their stochastic games, they present one particular rule that we use in our models:
+        \noindent Formal opinion dynamics models provide an understanding, if not an analysis, of
+        opinion formation processes. An early formulation of such models was created as a way to
+        understand complex phenomena found empirically in groups \cite{French1956}. The work on
+        consensus building (in the context of decision-making) was first studied by DeGroot
+        \cite{Degroot74} and Lehrer \cite{Lehrer1975}. Empirical studies of opinion formation in
+        large populations have methodological limitations. Computational sociology arises with a set
+        of tools -- simulation models in particular -- to cope with such limitations. We use
+        \textit{multi-agent simulation (MAS)} as a methodological framework to study such social
+        phenomena in a larger scale. Most opinion dynamics models make use of binary opinion values
+        \cite{Galam1997,Antunes2009}, or continuous values \cite{Deffuant2000,Deffuant2002}. For a
+        detailed analysis over some opinion dynamics models, refer to \cite{Hegselmann2002}.
+
+	Opinion dynamics models allow us to discover under which circumstances a population of
+        agents reaches consensus or polarisation. Agent-based models can have broader application
+        outside social simulation though. In computational distributed systems, consensus is a means
+        by which processes agree on some data~value needed during computation. Typically, this
+        agreement is the result of a negotiation process (often with the aid of a mediator). In
+        human societies, social conventions emerge to deal with coordination and subsequently with
+        cooperation problems \cite{Lewis1969}. These conventions are regularities of behaviour that
+        can turn normative if they come to be persistent solutions to recurrent problems. MAS are
+        also capable of producing emergent conventions in coordination or cooperation problems
+        \cite{Delgado2002}. The decentralised nature of these computational models of consensus is
+        highly desirable for dynamic control problems. In these scenarios, creating conventions
+        before hand (off-line), or developing a central control mechanism for generating them, can
+        be a difficult and intractable task: either due to the uncertainty and complexity associated
+        with the environment, or due to the system scale and heterogeneity (which makes it very
+        difficult to handcraft each component).
+
+	Consensus models are also investigated as means to create conventions in MAS. Shoham and
+        Tennenholtz create a bridge between economic literature and machine learning by studying a
+        series of models in which multiple agents are engaged in learning a particular convention
+        \cite{Shoham1994}. They call this process \textit{co-learning}. The complexity of these
+        systems comes from its concurrent nature: one agent adapts to the behaviour of another
+        agents it has encountered, these other agents update their behaviour in a similar fashion,
+        which results in a highly non-linear system dynamics. In their work, Shoham and Tennenholtz
+        define the notion of \textit{stochastic social games} and compare different rules with the
+        objective of establishing conventions in a decentralised fashion. In their stochastic games,
+        they present one particular rule that we use in our models:
 
@@
 		\label{def:external-majority}
-		\textit{External Majority (EM)} update rule: adopt action $i$ if so far it was observed in other agents more often than other action and remain with your current action in the case of equality. 
+		\textit{External Majority (EM)} update rule: adopt action $i$ if so far it was
+                observed in other agents more often than other action and remain with your current
+                action in the case of equality.
 	\end{mydef}
 
-	This EM was shown to coincide with \textit{Highest Cumulative Reward (HCR)}, which is a simple rule that states that ``an agent should adopt an action that has yielded the highest cumulative reward to date.'' We chose to use EM in our simulation models for its simplicity and success in the evolution of conventions.
-We can see that there is an overlap between opinion dynamics from social simulation and agent based learning---or co-learning, in this case.
+	This EM rule was shown to coincide with \textit{Highest Cumulative Reward (HCR)}, which is a
+        simple rule that states that ``an agent should adopt an action that has yielded the highest
+        cumulative reward to date.'' We use the EM rule in our simulation models for its simplicity
+        and success in the evolution of conventions.
 
@@
 	\subsection{Social Structure in Simulation Models}
-\noindent One of the most widely used approaches to represent social spaces in abstract simulation models is using a  bi-dimensional grid.
-This approach has its origins in the first \textit{``checkerboard''} model introduced in computational social sciences by Thomas Schelling \cite{Schelling1971} and Sakoda \cite{Sakoda1971}.
-Another famous example that uses bi-dimensional grids as social structure is the social simulation model of dissemination of culture from Axelrod \cite{Axelrod1997}.
-
-	Cellular automata (CA) are an example from the area of artificial life that also makes use of bi-dimensional structures to model neighbourhood interactions.
-While these models are idealised frameworks, the exploration of simple computational models can bring us deeper insights than models with high level descriptive complexity, which would render their analysis very difficult.
-The work of Flache and Hegselmann \cite{FlacheHegselmann2001} relaxes the standard CA assumptions about the regular bi-dimensional grids, by considering irregular grid structures (Voronoi diagrams).
-This work presents results on the robustness of some important general properties in relation to variations in the typical grid structure.
-We can also find contributions that incorporate both the complexity of network models and the behaviour of dynamic processes.
-One example of this combination is the work in \cite{Sullivan2000}, which explores a graph-based cellular automaton to study the relationship between spatial form of urban systems and the robustness of different process dynamics under spatial change.
-Moreover, this allows for the integration of real geographical information to construct the graph-cellular automata.
-This fact causes that, while the models of dynamic processes are relatively abstract, they are tested in spatial structures based on data from real complex structures and thus making a connection between purely abstract models and data-driven models.
+        \noindent The usage of a bi-dimensional grid to represent abstract social spaces in
+        simulation models, is one of the most widely used approaches in the agent-based simulation
+        and modelling literature. This has its origins in the \textit{``checkerboard''} model
+        introduced in computational social sciences by Schelling and Sakoda
+        \cite{Schelling1971,Sakoda1971}. Another famous example that uses bi-dimensional grids as
+        social structure is the social simulation model of dissemination of culture from Axelrod
+        \cite{Axelrod1997}.
+
+	Cellular automata (CA) are an example from the area of \textit{artificial life} that also
+        makes use of bi-dimensional structures to model neighbourhood interactions. While these
+        models are idealised frameworks, their exploration can bring us deeper insights than models
+        with high level of descriptive complexity (which would render their analysis very
+        difficult). The work of Flache and Hegselmann relaxes the standard CA assumptions about the
+        regular bi-dimensional grids by considering irregular grid structures (Voronoi diagrams)
+        \cite{FlacheHegselmann2001}. They present results on the robustness of some important
+        general properties in relation to variations in the typical grid structure. There are also
+        contributions that incorporate both the complexity of network models and the behaviour of
+        dynamic processes. One example is the work in \cite{Sullivan2000}, which explores a
+        graph-based cellular automaton to study the relationship between spatial forms of urban
+        systems and the robustness of different process dynamics under spatial change. Moreover,
+        this shows how we can use real geographical information to construct graph-based cellular
+        automata (thus making a connection between purely abstract models and data-driven models).
 
@@
 	%******************************************	
-	Finally, another type of social space models are the \textit{random graph/network models}.
-Networks with different properties can be built using network models.
-Each complex network or class of complex networks, presents specific topological features.
-These properties are typically found in---and the models inspired by---real-world network structures.
-One of the first complex network models is the random graph from Erd\H{o}s and Rényi \cite{Erdos1959}.
-Other examples include the model of preferential attachment \cite{Barabasi1999} and the small-world network models \cite{Watts1998}.
-One common problem of these models is the fact that once generated, the network structure is static so these models are not really suitable for the description of highly dynamic groups or communities.
-An example of a model that takes these dynamics into account is the model of team formation~\cite{Gaston2005}.
-A more in-depth review of network models and their properties is given in~\cite{Nunes2012}.
+	Finally, another type of social space models are the \textit{random graph/network
+          models}. Each complex network -- or \textit{class} of complex networks -- captures
+        specific topological properties. These properties are found in real-world network
+        structures. One of the first complex network models is the random graph from Erd\H{o}s and
+        Rényi \cite{Erdos1959}. Other examples include the model of preferential attachment
+        \cite{Barabasi1999}, and the small-world networks \cite{Watts1998}. One common issue of
+        these models is the fact that once generated, the network structure is static. The models
+        are not really suitable for the description of highly dynamic groups or communities. An
+        example of a model that takes such dynamics into account is the model of team
+        formation in~\cite{Gaston2005}. A more in-depth review of network models (and their properties)
+        is given in~\cite{Nunes2012}.
 
@@
 	\label{sec:multi-context-models} 
-\noindent In this section, we present our modelling approach to explore the concept of permeability between contexts.
-In our approach, we consider multiple social networks as a way to represent the complex social space in which an agent is inserted.
-In a simulation, this setting can be seen as a n-dimensional scenario, where each dimension surface represents a different social relation (see figure \ref{img:multiple-relations}).
-Each relation is instantiated using a social network model.
-The word ``context'' is used in many different senses and it is subjected to many analysis \cite{Hayes1997}.
-Here, we use the term \textit{social context} in a simpler and more strict way.
-Agents belong to distinct social contexts (neighbourhoods) in these multiple networks.
-The \textit{social context} of an agent is thus a set of neighbours currently available for interaction.
-\textit{Context Permeability} is the ability of a particular norm, strategy, opinion or trend to permeate from one social relation to another.
-Agents belonging to disjoint neighbourhoods in different networks foster the creation of bridges between subsets of the population that wouldn't otherwise be influenced by a consensus formed in a distant coalition or in a distinct context.
+        \noindent In this section, we present our modelling approach to explore the concept of
+        permeability between contexts. We use multiple social networks to represent the complex
+        social space in which an agent is inserted. In a simulation model, this setting can be seen
+        as a n-dimensional scenario where each dimension contains a network that represents a
+        different social relation (see figure \ref{img:multiple-relations}). The word ``context'' is
+        used in many different senses and it is by itself subjected to many analysis
+        \cite{Hayes1997}. Here, we use the term \textit{social context} in a simpler and more strict
+        way. Agents belong to distinct social contexts which are their neighbourhoods in these
+        multiple networks. The \textit{social context} of an agent is thus a set of neighbours
+        currently available for interaction at a particular network or set of
+        networks. \textit{Context permeability} is the ability of a particular norm, strategy,
+        opinion, or trend, to permeate from one social relation to another. Agents belonging to
+        disjoint neighbourhoods in different networks serve as bridges between subsets of the
+        population that wouldn't otherwise be influenced by a consensus formed in a distant
+        coalition.
 
@@
           \begin{minipage}{0.9\linewidth}
-			\caption{Multiple social network structure that shapes the social space in our simulation models.}
+            \caption{Multiple social network structure that shapes the social space in our
+              simulation models.}
             \label{img:multiple-relations}
@@
 	%Consensus
-	We study the notion of context permeability in different simulation models in which agents interact using a simple consensus game.
-The society of agents has to adopt a binary \textquotedblleft option\textquotedblright according to a majority rule.
-We use the speed of consensus as a measure for self-organisation, exploring the relationship between different network topologies and this measure.
-
-	%Presenting 3 models
-	We partitioned the design space of our experiments using different simulation models.
-Each model is designed to analyse different aspects of social context permeability.
-In a first model \cite{Antunes2007, Antunes2010}, we study the notion of permeability by overlapping social networks.
-In a second model \cite{Antunes2009}, we analyse the dynamics introduced by switching between \textit{social contexts}(neighbourhoods in different networks), adding a temporal component to neighbourhoods within different social relations.
+	We study the notion of context permeability in different simulation models in which agents
+        interact using a simple consensus game. The society of agents has to adopt a binary opinion
+        value according to a majority rule. We use the speed of consensus as a measure for
+        self-organisation and explore the relationship between different network topologies and this
+        measure.
+
+	%Presenting 2 models
+	We partitioned the design space of our experiments using different simulation models. Each
+        model is designed to analyse different aspects of context permeability. In a first model
+        \cite{Antunes2007, Antunes2010}, we study the notion of permeability by overlapping social
+        networks. In a second model \cite{Antunes2009}, we analyse the dynamics introduced by
+        switching between \textit{social contexts}(neighbourhoods in different networks). This adds
+        a temporal component that changes the dynamics of the game: agents can only perform
+        encounters with neighbours that are active in their current context. (It also adds the
+        chance for some agents to be isolated during the simulation.)
 
@@
 	\label{sec:sim_consensus}
-\noindent Our agent-based models are designed as \textit{discrete-event} models.
-On each simulation cycle, every agent executes a simulation step.
-The agents are selected in a random uniform fashion for execution.
-This is common practice in agent-based simulation and guarantees that there is no bias caused by the order in which the agents are executed.
-For each simulation model, we present a description of the individual agent behaviour.
-Every model we present can be seen as a binary opinion dynamics model, or a consensus game.
-In this game, the society of agents tries to reach an arbitrary global consensus about two possible choices.
-Each agent keeps track of the number of choices observed from interaction partners throughout a simulation run.
-In each iteration, each agent selects an available neighbour to interact with, and observes its current choice.
-The agent decides to switch its current choice if the observed option becomes the majority of the two possible choices.
-The objective of the game is to reach a global consensus, but the particular choice that gets collectively selected is irrelevant.
-What is important is that overall agreement is achieved.
-In the consensus game we consider, each agent uses the previously presented external majority (EM) rule to update its opinion value (see definition \ref{def:external-majority} in section \ref{sec:relatedwork}).
-
-	The reason we are not really interested in which exact option gets selected is the same reason why we chose such a content-neutral game for the individual interactions.
-From the very beginning, our research questions were focused on the collective properties, the structure of the networks involved, and the dynamical outcomes of the simulations: thus leaving out issues related with individual motivations and desired results, either for any individual agent or the society.
-Granted, most applications of this research will often include such goals, for inquisition into complex social issues, including possibly policy design, in which the individual rationalities must be considered, and will have a very strong influence on the collective outcomes.
-We opted not to taint the simulation with such matters, leaving that very interesting approach for future work.
-
-%	\newpage
+        \noindent Our agent-based models are designed as \textit{discrete-event} models. On each
+        simulation cycle, every agent executes a simulation step. The agents are selected in a
+        random uniform fashion for execution. This is common practice in agent-based simulation and
+        guarantees that there is no bias caused by the order in which the agents are executed. For
+        each simulation model, we present a description of the individual agent behaviour. Every
+        model we present can be seen as a binary opinion dynamics model, or a consensus game. In
+        this game, the society of agents tries to reach an arbitrary global consensus about two
+        possible choices or opinion values. During a simulation run, each agent keeps track of the
+        number of each opinion value of their interaction partners. In each iteration, each agent
+        selects an available neighbour to interact with and observes its current opinion value. The
+        agent decides to switch its current opinion choice if the observed opinion value becomes the
+        majority of the two possible choices. The goal of the game is to reach a global consensus,
+        but the particular choice that gets collectively selected is irrelevant. What is important
+        is that overall agreement is achieved. In the consensus game we consider, each agent uses
+        the previously presented external majority (EM) rule to update its opinion value (see
+        definition \ref{def:external-majority} in section \ref{sec:relatedwork}).
+
+	The reason we are not interested in which exact option gets selected is the same reason why
+        we chose such a content-neutral game for the individual interactions. From the very
+        beginning, our research questions were focused on the collective properties, the structure
+        of the networks involved, and the dynamical outcomes of the simulations: thus leaving out
+        issues related with individual motivations and desired results (either for any individual
+        agent or the society). Granted, most applications of this research will often include such
+        goals, for inquisition into complex social issues, including possibly policy design, in
+        which the individual rationality must be considered, and will have a very strong influence
+        on the collective outcomes.
+
 	\subsection{Context Permeability}
-\noindent This first model of context permeability \cite{Antunes2007,Antunes2010} is designed to study our first setting for permeability.
-In most interesting applications, an agent is immersed in a complex social world, where it engages in a multitude of relations with other agents (and even aggregated agents such as institutions or informal groups).
-In this model, we consider that the \textit{context permeability} is created by agents that can belong simultaneously to several relations.
-As an example, two agents can be simultaneously family and co-workers, and while some links might not connect two agents directly, others can contain neighbourhoods in which they are related~(either directly or through a common neighbour).
-Model \ref{model:context_permeability} describes the behaviour of each agent for each simulated step.
+        \noindent The first model of context permeability \cite{Antunes2007,Antunes2010} is designed
+        to study the setting where an agent is immersed in a complex social world: where it engages
+        in a multitude of relations with other agents. In this model, we consider that the
+        \textit{context permeability} is created by agents that can belong \textit{simultaneously}
+        to several relations. As an example, two agents can be simultaneously family and
+        co-workers. While some links might not connect two agents directly, others can contain
+        neighbourhoods in which they are related~(either directly or through a common
+        neighbour). Model \ref{model:context_permeability} describes the behaviour of each agent for
+        each simulated step.
 	%***************************************************
@@
 			\vspace{0.5em}
-			\STATE $M$ \COMMENT{Simulation Model / Environmnet}
+			\STATE $M$ \COMMENT{Simulation Model / Environment}
 			\STATE $A$ \COMMENT{Current Agent in Execution}
@@
 	\label{sec:models_cs}
-\noindent In the context switching model \cite{Antunes2009}, agents are embedded in multiple relations represented as static social networks and they switch \textit{contexts} with a given probability $\zeta_{C_i}$ associated with context $C_i$.
-The switching probability value is the same for every agent in a given network.
-Each agent switches from its current neighbourhood to another network (in which this agent was inactive).
-The agents are only active in one context at a time, and can only perform encounters with neighbours in the same context.
-We can think of context switching as a temporary deployment in another place, such as what happens with temporary immigration.
-The network topology is static; when an agent switches from one network to another, they become inactive in one network and active in their destination.
+        \noindent In the context switching model \cite{Antunes2009}, agents are embedded in multiple
+        relations represented as static social networks and they switch \textit{contexts} with a
+        probability $\zeta_{C_i}$ associated with context $C_i$. The switching probability is the
+        same for every agent in a given network.  Each agent switches from its current neighbourhood
+        to another network. The agents are only active in one context at a time, and can only
+        perform encounters with neighbours in the same context. We can think of context switching as
+        a temporary deployment in another place, such as what happens with temporary
+        immigration. The network topology is static; when an agent switches from one network to
+        another, they become inactive in one network and active in their destination.
+
 	%***************************************************
@@
 	\end{algorithm}
-	\noindent In this model, agents select an (active) partner from their current neighbourhood.
-If a partner is available, the agents update their opinion value based on EM.
-At the end of the interaction, the agent switches \textit{from} the current context to a different one with a probability associated with its current network.
-
-	This model describes an abstract way to represent the time spent on each network using the switching probability $\zeta_{C_i}$.
-Here, the permeability between contexts is achieved using this temporal component.
-Context switching introduces one notion that has not been explored in the literature so far: the fact that, although some social contexts can be relatively stable if we consider short to moderate periods of time, our social peers are not always available at all times and spend different amounts of time in distinct social contexts.
+	\noindent In this model, agents select an (active) partner from their current
+        neighbourhood. If a partner is available, the agents update their opinion value based on
+        EM. At the end of the interaction, the agent switches \textit{from} the current context to a
+        different one with a probability associated with its current context.
+
+	This model describes an abstract way to represent the time spent on each network using the
+        switching probability $\zeta_{C_i}$. Here, the permeability between contexts is achieved
+        using this temporal component. Context switching introduces a notion that has not been
+        explored in the literature so far: the fact that, although some social contexts can be
+        relatively stable, our social peers are not always available for interaction and spend
+        different amounts of time in distinct social contexts.
 

### 2015-06-20 doc/main.tex
Experimental Setup reviewed

@@
 	\label{sec:experimental-setup}
-\noindent In this section, we describe all the tools and processes necessary to produce the current research output.
-The experiments for our previously described simulation models were developed using the MASON~\cite{Luke2005} simulation framework written in Java.
-All the code for the simulation models can be found here \cite{Nunes:Software:11067}.
-Moreover, all the results presented in this article were made reproducible by using the \textit{statistical computing language R} \cite{R2008} and the R package \textit{knitr} \cite{knitr2014}.
-Knitr is used for generating reports that contain the code, the results of its execution (plots and tables), and the textual description for such results.
-All the R code used  to produce the data analysis and the configuration files used to reproduce the data can be found in \cite{NunesAntunes2014:Analysis:11898}.
-
-%recap
-For each configuration in our experiments, we performed 100 independent simulation runs.
-The results are thus analysed in terms of value distribution, average and standard deviation, or variance over the 100 runs.
-Like we described in section \ref{sec:sim_consensus}, our models are discrete-event models and in each cycle agents execute
-a step in a random order: this is so that this dynamical system --our simulation model-- is not influenced by the order in which agents are executed.
-Simulations end when total consensus is achieved or 2000 steps have passed.
+        \noindent In this section, we present all the tools and processes necessary to produce the
+        current research output. The experiments were developed using the MASON~\cite{Luke2005}
+        simulation framework written in Java. All the code for the simulation models can be found
+        here \cite{Nunes:Software:11067}. Moreover, all the results presented in this article were
+        made reproducible by using the \textit{statistical computing language R} \cite{R2008} and
+        the R package \textit{knitr} \cite{knitr2014}. Knitr is used for generating reports that
+        contain the code, the results of its execution (plots and tables), and the textual
+        description for such results. All the R code used to produce the data analysis and the
+        configuration files used to reproduce the data can be found in
+        \cite{NunesAntunes2014:Analysis:11898}.
+
+        % recap
+        For each configuration in our experiments, we performed 100 independent simulation runs. The
+        results are analysed in terms of value distribution, average and standard deviation, or
+        variance over the 100 runs. Like we described in section \ref{sec:sim_consensus}, our models
+        are discrete-event models. In each cycle agents execute a step in a random order: this is so
+        that this dynamical system --our simulation model-- is not influenced by the order in which
+        agents are executed. Simulations end when total consensus is achieved or 2000 steps have
+        passed.
 
@@
         \label{sec:exp-setup_network_models}
-\noindent The social networks used in our models are \textit{k-regular} and \textit{scale-free}.
-A k-regular network is a network where all the nodes have the same number of connections.
-These networks are constructed by arranging the nodes in a ring and connecting each node to their next $k$ neighbours.
-Each network has $2k$ edges per vertex.
-
-Scale-free networks are networks in which the degree distribution follows a power law, at least asymptotically.
-That is, the fraction $P(k)$ of nodes in the network having $k$ connections to other nodes goes for large values of $k$ as: $ P(k)  \sim  k^{-\gamma}$ where $\gamma$ is a parameter whose value is typically in the range $2 < \gamma < 3$.
-
-We use the method proposed in \cite{Barabasi1999} by Barab\'{a}si and Albert to construct the scale-free network instances using a preferential attachment.
-This model builds upon the perception of a common property of many large networks, a scale-free-power-law distribution of node connectivity.
-This feature was found to be a consequence of two generic mechanisms: networks expand continuously by the addition of new vertices, and new vertices attach preferentially to sites that are already well connected, being this mechanism more commonly known as ``preferential attachment''.
-In these networks, the probability $P(k)$ of two nodes being connected to each other decays as a power law, following $P(k) \sim k^{- \gamma}$.
-
-The network instances were generated using the \textit{b-have network library} \cite{Nunes:Software:11069}.
-This is a Java library that allows for the manipulation of Network/Graph data structures.
-It also includes the more commonly used random network models from the literature.
+        \noindent The social networks used in our models are \textit{k-regular} and
+        \textit{scale-free}. A k-regular network is a network where all the nodes have the same
+        number of connections. These networks are constructed by arranging the nodes in a ring and
+        connecting each node to their next $k$ neighbours. Each network has $2k$ edges per vertex.
+
+        Scale-free networks are networks in which the degree distribution follows a power law, at
+        least asymptotically. That is, the fraction $P(k)$ of nodes in the network having $k$
+        connections to other nodes goes for large values of $k$ as: $ P(k) \sim k^{-\gamma}$ where
+        $\gamma$ is a parameter whose value is typically in the range $2 < \gamma < 3$.
+
+        We use the method proposed in \cite{Barabasi1999} by Barab\'{a}si and Albert to construct
+        the scale-free network instances using a preferential attachment. This model builds upon the
+        perception of a common property of many large networks: a scale-free-power-law distribution
+        of node connectivity. This feature was found to be a consequence of two generic mechanisms:
+        networks expand continuously by the addition of new vertices, and new vertices attach
+        preferentially to sites that are already well connected (more commonly known as
+        ``preferential attachment''). In these networks, the probability $P(k)$ of two nodes being
+        connected to each other decays as a power law, following $P(k) \sim k^{- \gamma}$.
+
+        The network instances were generated using the \textit{b-have network library}
+        \cite{Nunes:Software:11069}. This is a Java library that allows the creation and
+        manipulation of network/graph data structures. It also includes the more commonly used
+        random network models from the literature.
 
         \subsection{Measuring Network Properties}
-\noindent We measure two structural properties of our networks: the \textit{average path length} and the \textit{clustering coefficient}.
-The \textit{average path length} measures the typical separation between two vertices in the graph.
-The \textit{clustering coefficient} measures the average cliquishness of the graph neighbourhood.
-This measure quantifies how close the neighbours of a node are to forming a clique.
-Duncan J.
-Watts and Steven Strogatz \cite{Watts1998} introduced the measure to characterise a class of complex networks called small-world networks.
-
-These properties are quite important to study social phenomena as they characterize structures that 
-can be found in the real scenarios.
-The small-world networks generated by the models of Watts and Strogatz for instance \cite{Watts1998}, tries to model real-world social networks with short average path length, generate local clustering, and triadic closures between the nodes.
-One shortcoming of this model, is the fact that these networks do not possess node hubs found in many real-world social networks.
-
-Since we construct scenarios where we overlap highly clustered k-regular networks and scale-free networks with node hubs, we are interested in what kind of properties emerge from merging these structures and how they are comparable to the existing models.
-
-The networks produced by the \textit{b-have network library} \cite{Nunes:Software:11069} were exported to files and analysed using the \textit{igraph R package} \cite{igraph2006}.
+        \noindent We measure two structural properties of our networks: the \textit{average path
+          length} and the \textit{clustering coefficient}. The \textit{average path length} measures
+        the typical separation between two vertices in the graph. The \textit{clustering
+          coefficient} measures the average cliquishness of the graph neighbourhood. This measure
+        quantifies how close the neighbours of a node are to forming a clique. Duncan J. Watts and
+        Steven Strogatz \cite{Watts1998} introduced the measure to characterise a class of complex
+        networks called small-world networks.
+
+        These properties characterise structures that can be found in the real scenarios. The
+        small-world networks generated by the models of Watts and Strogatz for instance, model
+        real-world social networks with short average path length, local clustering structures, and
+        triadic closures between the nodes \cite{Watts1998}. One shortcoming of this model, is the
+        fact that these networks do not possess node hubs found in many real-world social
+        networks. (Nevertheless, these models are designed to create networks with specific
+        properties, not as general models for all kinds of real social networks)
+
+        Since we construct scenarios where we overlap highly clustered k-regular networks and
+        scale-free networks with node hubs, we are interested in the kind of properties that emerge
+        from merging these structures -- and if/how they are comparable to the existing models
+        --. The networks were produced by the \textit{b-have network library}
+        \cite{Nunes:Software:11069}, exported to files, and analysed using the \textit{igraph R
+          package} \cite{igraph2006}.
 

### 2015-06-21 doc/main.tex
overlapping network properties reviewed

@@
         \cite{Nunes:Software:11069}, exported to files, and analysed using the \textit{igraph R
-          package} \cite{igraph2006}.
+          package}~\cite{igraph2006}.
 
@@
         % Overview
-\noindent In this section, we analyse and discuss the results for different experiments with both the
-context permeability and context switching models. We start by analysing the structural properties
-that arise from combining different networks while maintaining the same set of network nodes.
-We then perform multiple experiments where we observe the impact of different model configurations in the convergence to consensus.
-We correlate the outcomes of our context permeability model simulations with the structural properties of the multi-network structures.
-We also explore how the new dynamics introduced by the context switching model, affect the consensus building process.
+        \noindent In this section, we analyse and discuss the results for different experiments with
+        both the context permeability and context switching models. We start by analysing the
+        structural properties that arise from combining different networks. We then observe the
+        impact of different model configurations in the convergence to consensus. We correlate the
+        outcomes of our context permeability model simulations with the structural properties of the
+        multi-network structures. We also explore how the new dynamics introduced by the context
+        switching mechanism affects the consensus building process.
 
@@
         \label{sec:network_properties}
-\noindent In this first analysis, we investigate the properties of different network topologies that we use in our models. 
-One of the parameters in some experiments is the number of networks in which the agents interact. Adding more networks means adding more connections. 
-We show that what is important is not just the the number of connections, but the properties the resulting structure displays when these networks are merged.
-The way we look at the network properties is as follows.
-
-Each network is generated in such a way that the node positions are randomised.
-This means that we can have multiple networks with the same topology and yet, each node has a different neighbourhood on each network.
-Also, neighbourhoods do not necessarily overlap due to the node shuffling.
-Adding more networks to the social space is not the same as creating a single network with twice the number of connections.
-
-\noindent Consider figure \ref{fig:network_properties_merge_2_10regular}.
-We created two random k-regular networks with k=10 and merged them ignoring edges from common neighbours --in the simulation models this edge agglutination is not performed, we use it here for the purposes of network analysis.
-The common edges are highlighted in a different colour.
+        \noindent In this first analysis, we investigate the properties of different network
+        topologies used in our models. One of the parameters in some experiments is the number of
+        networks in which the agents interact. Adding more networks implies the addition of more
+        connections. We show that what is important is \textit{not just} the the number of
+        connections, but the properties of the resulting structure (when we merge the networks). We
+        analyse the networks as follows.
+
+        Each network is generated in such a way that the node indexes are randomised. This means
+        that we can have multiple networks with the same topology and each node can have different
+        neighbourhoods in different networks. Also, neighbourhoods do not necessarily overlap due to
+        the node shuffling. Adding more networks to the social space is not the same as creating a
+        single network with twice the number of connections.
+
+        \noindent Consider figure \ref{fig:network_properties_merge_2_10regular}. We created two
+        random k-regular networks with k=10 and merged them ignoring edges from common neighbours.
+        (In the simulation models this edge agglutination is not performed, we use it here for the
+        purposes of network analysis.) Common edges are highlighted with a different colour.
 
@@
 
-The networks are drawn using the \textit{Kamada-Kawai} Layout \cite{Kamada19897} which regards the desirable ``geometric'' (Euclidean) distance between two vertices in the drawing as the ``graph theoretic'' distance between them in the corresponding graph.
-We can see by the results of the layout in figure \ref{fig:network_properties_merge_2_10regular}, that the distance between nodes in the network has decreased, this is also confirmed by the reduced average path length of the combined networks (see table \ref{tab:network_properties_merge_2_10regular}).
-To illustrate our point we analysed one k-regular network with k = 20 (see figure \ref{fig:network_properties_1_20regular} --and the corresponding entry on table \ref{tab:network_properties_merge_2_10regular}).
-The clustering coefficient of a 20-regular network is approximately the same as the one of a 10-regular network (higher than the combination of 10-regular networks).
-The average path length also decreases as there are more connections between the nodes.
-As we will show, these properties may vary.
-Since the nodes are subjected to random permutations, we can generate different overlaps that lead to distinct structural values.
-
-Since we model the agent social space as a multitude of networks, we need to investigate the properties resulting from the merging of these networks.
-We do this empirically by taking the network instances used in the simulation and analysing the distribution of clustering coefficient and average path length for the different configurations.
+        The networks are drawn using the \textit{Kamada-Kawai} Layout \cite{Kamada19897} which
+        treats the ``geometric'' (Euclidean) distance between two vertices in the drawing as the
+        ``graph theoretic'' distance between them in the corresponding graph. We can see by the
+        results of the layout in figure \ref{fig:network_properties_merge_2_10regular}, that the
+        distance between nodes in the network has decreased, this is also confirmed by the reduced
+        average path length of the combined networks (see table
+        \ref{tab:network_properties_merge_2_10regular}). To illustrate our point, we analysed one
+        k-regular network with k = 20 (see figure \ref{fig:network_properties_1_20regular} and the
+        corresponding entry on table \ref{tab:network_properties_merge_2_10regular}). The clustering
+        coefficient of a 20-regular network is approximately the same as the one of a 10-regular
+        network (higher than the combination of two 10-regular networks). The average path length
+        also decreases as there are more connections between previously distant nodes. As we will
+        show, these properties may vary due to the node indexes being subjected to random
+        permutations.
+
+        Since we model the agent social space as a multitude of networks, we need to investigate the
+        properties resulting from the merging of these networks. We do this empirically by taking
+        the network instances used in the simulations, and analysing the distribution of clustering
+        coefficient and average path length for the different configurations.
 
@@
         \label{sec:overlapping_kreg}
-\noindent We will now investigate what kind of properties we can get from merging k-regular networks.
-First, we analysed the distribution for the average path length and the clustering coefficient values over 100 network instances with 100 nodes each.
-From a box plot preliminary analysis (see figures \ref{append_fig:network_properties_cc_kreg} and \ref{append_fig:network_properties_apl_kreg}), we can see that the average path length does not vary much for the 100 instances, as such, we use the average as a descriptor for different configurations of k values and number of overlapping networks.
-
-Figure~\ref{fig:network_properties_apl_line_kreg} shows the average value for the \textit{average path length} of 100 k-regular network instances, each with 100 nodes.
-We can see that the \textit{average path length} changes more drastically when we go from 1 to 2 networks.
-This is precisely the effect we can see in figure \ref{fig:network_properties_merge_2_10regular}.
-What we are seeing is that merging these networks at random effectively creates multiple shortcuts between points that were not connected in the original k-regular topology.
-Beyond this point, adding more networks does not modify this structural property in a significant way.
-Note that, since each network has 100 nodes, with $k=50$ the network is fully connected (hence the average path length being 1).
-
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}{.5\linewidth}
-		\centering
+        \noindent We will now investigate what kind of properties we can get from merging k-regular
+        networks. First, we analysed the distribution for the average path length and the clustering
+        coefficient values over 100 network instances (each with 100 nodes). From a box plot
+        preliminary analysis (see figures \ref{append_fig:network_properties_cc_kreg} and
+        \ref{append_fig:network_properties_apl_kreg}), we can see that the average path length does
+        not vary much for the 100 instances, as such, the average makes a good descriptor for these
+        properties.
+
+        Figure~\ref{fig:network_properties_apl_line_kreg} shows the average value for the
+        \textit{average path length} of 100 k-regular network instances (each with 100 nodes). We
+        can see that the \textit{average path length} changes more drastically when we go from 1 to
+        2 networks. This is precisely the effect we can see in figure
+        \ref{fig:network_properties_merge_2_10regular}. Merging these networks at random effectively
+        creates multiple shortcuts between points that were not connected in the original k-regular
+        topology. Beyond this point, adding more networks does not modify this structural property
+        in a significant way. Note that, since each network has 100 nodes, with $k=50$ the network
+        is fully connected (hence the average path length being 1).
+
+        \begin{figure}[H] \centering
+          \begin{subfigure}{.5\linewidth} \centering
             \includegraphics[width=1\linewidth]{"../analysis/pdf/network_properties_apl_line_kreg_12345"}
@@
           \end{subfigure}%
-	\begin{subfigure}{.5\linewidth}
-		\centering
+          \begin{subfigure}{.5\linewidth} \centering
             \includegraphics[width=1\linewidth]{"../analysis/pdf/network_properties_apl_line_kreg_1020304050"}
@@
           \end{subfigure}
-	\begin{minipage}{0.9\textwidth}
-		\vspace{0.2cm}
-		\caption{Average value for the \textit{average path length} of 100 instances of overlapping k-regular networks (containing 100 nodes each) with k=\{1,2,3,4,5\}~(\ref{fig:network_properties_apl_line_kreg_12345}), and k= ~\{10,20,30,40,50\} (\ref{fig:network_properties_apl_line_kreg_1020304050}).}
+
+     \begin{minipage}{0.9\textwidth} \vspace{0.2cm}
+            \caption{Average value for the \textit{average path length} of 100 instances of
+              overlapping k-regular networks (containing 100 nodes each) with
+              k=\{1,2,3,4,5\}~(\ref{fig:network_properties_apl_line_kreg_12345}), and k=
+              ~\{10,20,30,40,50\} (\ref{fig:network_properties_apl_line_kreg_1020304050}).}
 		\label{fig:network_properties_apl_line_kreg}
               \end{minipage}
-\end{figure}
-
-\noindent Figure~\ref{fig:network_properties_cc_line_kreg} shows the results for the average \textit{clustering coefficient} of 100 instances of overlapping k-regular networks.
-We can see that adding multiple networks changes the clustering coefficient of the resulting structure.
-For $k \le 20$, the clustering coefficient drops when we add a second network.
-This happens because when we merge these networks, their connectivity is not high enough to generate shortcuts with tightly clustered neighbourhoods.
-The clustering coefficient is computed by taking the average local clustering coefficient of each node in the network.
-An initial highly clustered k-regular network (with all the nodes having the same structure) is affected when you modify the node neighbourhoods in such a way that some are more clustered than others.
+
+        \end{figure}
+
+        \noindent Figure~\ref{fig:network_properties_cc_line_kreg} shows the results for the average
+        \textit{clustering coefficient} of 100 instances of overlapping k-regular networks. Adding
+        multiple networks changes the clustering coefficient of the resulting structure. For
+        $k \le 20$, the clustering coefficient drops when we add a second network. This happens
+        because when we merge these networks, their connectivity is not high enough to generate
+        shortcuts with tightly clustered neighbourhoods. The clustering coefficient is computed by
+        taking the average local clustering coefficient of each node in the network. An initial
+        highly clustered k-regular network (with all the nodes having the same structure) is
+        affected when you modify the node neighbourhoods in such a way that some are more clustered
+        than others. Networks with $k=1$ have a ring-like structure, so there are no nodes forming a
+        clique\footnote{A clique is a group of nodes such that every two nodes are connected by an
+          edge.} with their neighbours.
 
@@
 
-The exception is when you merge networks with $k=1$.
-These have a ring-like structure, so there are no nodes forming a clique\footnote{A clique is a group of nodes such that every two nodes are connected by an edge.} with their neighbours.
-
         \subsubsection{Properties of Overlapping Scale-free Networks}
-\noindent In a preliminary analysis we looked at the distribution of property values that results from merging scale-free networks (see figure \ref{append_fig:network_properties_sf}).
-Like in the previous results, the properties don't vary much between the 100 different instances of each overlapping network configuration.
-We can then say that specific configurations display a specific \textit{average path length} and \textit{clustering coefficient} both for \textit{k-regular} networks and \textit{scale-free} networks.
-Since the average of these measures is still a good descriptor, we plotted the average of the \textit{average path length} (figure \ref{fig:network_properties_apl_line_sf_12345}) and \textit{clustering coefficient} (figure \ref{append_fig:network_properties_cc_sf_12345}) for each overlapping network configuration.
+        \noindent We also looked at the properties that result from merging scale-free networks (see
+        figure \ref{append_fig:network_properties_sf}). Like the previous results, the properties
+        don't vary much between the 100 different instances. We can then say that specific
+        configurations display a specific \textit{average path length} and \textit{clustering
+          coefficient} both for \textit{k-regular} networks and \textit{scale-free} networks. We
+        plotted the average of the \textit{average path length} (figure
+        \ref{fig:network_properties_apl_line_sf_12345}) and \textit{clustering coefficient} (figure
+        \ref{append_fig:network_properties_cc_sf_12345}) for each overlapping network configuration.
 
@@
 
-The parameter $d$ in figure \ref{fig:network_properties_line_sf} dictates how many edges are added by preferential attachment (see section\ref{sec:exp-setup_network_models}) each time a new node is added to a network (during its construction).
-This means that for $d=1$, the resulting network is a \textit{forest}: a network composed of disjoint tree graphs.
-Figure~\ref{fig:network_properties_apl_line_sf_12345} shows us that the \textit{average path length} still decreases consistently when we add more networks.
-One of the characteristics of \textit{scale-free} networks is its short average  path length, thus, for $d \ge 2$ we can see that adding more edges does not make so much difference.
-Scale-free networks also have a reduced \textit{clustering coefficient} which is evident in figure \ref{fig:network_properties_cc_line_sf_12345}.
-This is increased when we merge more networks.
+        The parameter $d$ (figure \ref{fig:network_properties_line_sf}) dictates how many edges are
+        added by preferential attachment (see section\ref{sec:exp-setup_network_models}). For $d=1$,
+        the resulting network is a \textit{forest}: a network composed of disjoint tree
+        graphs. Figure~\ref{fig:network_properties_apl_line_sf_12345} shows us that the
+        \textit{average path length} still decreases consistently when we add more networks. One of
+        the characteristics of \textit{scale-free} networks is its short average path length, thus,
+        for $d \ge 2$, adding more edges does not make a significant difference. Scale-free networks
+        also have a reduced \textit{clustering coefficient} (see figure
+        \ref{fig:network_properties_cc_line_sf_12345}). When we add more networks the
+        \textit{clustering coefficient} increases.
 
         \subsubsection{Merging K-Regular with Scale-Free Networks}
-\noindent Finally, we look at what happens when we merge k-regular networks with \textit{scale-free} networks.
-We didn't make an exhaustive analysis for this configuration, but we show what is the resulting structure of such merging.
-You can see in figure \ref{fig:network_properties_merge_regular_scale-free} that this results in a network with a lower \textit{average path length} due to the shortcuts created by the \textit{scale-free} network.
-It is also less dense than the structure with two 10-regular networks (figure \ref{fig:network_properties_merge_2_10regular}).
-In this analysis we consider only the merging of two networks.
+        \noindent Finally, we look at what happens when we merge k-regular networks with
+        \textit{scale-free} networks. We didn't make an exhaustive analysis for this configuration,
+        but we show what is the resulting structure of such merging. You can see in figure
+        \ref{fig:network_properties_merge_regular_scale-free} that this results in a network with a
+        lower \textit{average path length} due to the shortcuts created by the \textit{scale-free}
+        network. It is also less dense than the structure with two 10-regular networks (figure
+        \ref{fig:network_properties_merge_2_10regular}). We consider only the merging of two
+        networks.
 
@@
             \vspace{0.2cm}
-		\caption{Average \textit{average path  length} for 100 instances of heterogeneous network configurations:  one \textit{scale-free} with $d=\{1,2,3,4,5\}$ and one \textit{k-regular} network with $k=\{1,2,3,4,5\}$ (\ref{fig:network_properties_apl_line_sf_kreg_12345}) and $k=\{10,20,30,40,50\}$ (\ref{fig:network_properties_apl_line_sf_kreg_1020304050}).
-(See the respective box plots in the appendix: figure \ref{append_fig:network_properties_apl_sf_kreg}).}
+            \caption{Average \textit{average path length} for 100 instances of heterogeneous network
+              configurations: one \textit{scale-free} with $d=\{1,2,3,4,5\}$ and one
+              \textit{k-regular} network with $k=\{1,2,3,4,5\}$
+              (\ref{fig:network_properties_apl_line_sf_kreg_12345}) and $k=\{10,20,30,40,50\}$
+              (\ref{fig:network_properties_apl_line_sf_kreg_1020304050}). (See the respective box
+              plots in the appendix: figure \ref{append_fig:network_properties_apl_sf_kreg}).}
             \label{fig:network_properties_line_apl_sf_kreg}
@@
 
-Figure \ref{fig:network_properties_line_apl_sf_kreg} shows the \textit{average path length} of 100 independently generated instances of combinations of one \textit{k-regular} network and one \textit{scale-free} network with different values $k$ and $d$, respectively.
-We can see that for configurations where the \textit{k-regular} networks have low values of $k$ (figure \ref{fig:network_properties_apl_line_sf_kreg_12345}), adding a \textit{scale-free} network always decreases the \textit{average path length}.
-Moreover, the higher the $d$, the lower the path length, as more connections are formed between different nodes.
-With higher values of $k$ (figure \ref{fig:network_properties_apl_line_sf_kreg_1020304050}) however, increasing the value of $d$ does not decrease the \textit{average path length}.
-This is not surprising given that with that level of connectivity, having a more connected \textit{scale-free} network does not make such an impact.
-The first network is already highly dense and connected, so adding a few extra connections doesn't matter --what does matter in this case is that there is a scale-free network creating the extra shortcuts between nodes that were not connected before.
+        Figure \ref{fig:network_properties_line_apl_sf_kreg} shows the \textit{average path length}
+        of 100 independently generated instances of combinations of one \textit{k-regular} network
+        and one \textit{scale-free} network with different values $k$ and $d$ respectively. For
+        configurations where the \textit{k-regular} networks have low values of $k$ (figure
+        \ref{fig:network_properties_apl_line_sf_kreg_12345}), adding a \textit{scale-free} network
+        always decreases the \textit{average path length}. Moreover, the higher the $d$, the lower
+        the path length (as more connections are formed between different nodes). With higher values
+        of $k$ (figure \ref{fig:network_properties_apl_line_sf_kreg_1020304050}) however, increasing
+        the value of $d$ does not decrease the \textit{average path length}. This is not surprising
+        given the level of connectivity of this structure. The first network is already highly dense
+        and connected, so adding a few extra connections doesn't matter; what does matter is that we
+        have a scale-free network creating shortcuts between nodes that were not previously
+        connected.
 
@@
             \vspace{0.2cm}
-		\caption{Average \textit{clustering coefficient} for 100 instances of heterogeneous network configurations:  one \textit{scale-free} with $d=\{1,2,3,4,5\}$ and one \textit{k-regular} network with $k=\{1,2,3,4,5\}$  (\ref{append_fig:network_properties_cc_sf_12345}) and $k=\{10,20,30,40,50\} $ (See the respective box plots in the appending: figure\ref{append_fig:network_properties_cc_sf_kreg}).}
+            \caption{Average \textit{clustering coefficient} for 100 instances of heterogeneous
+              network configurations: one \textit{scale-free} with $d=\{1,2,3,4,5\}$ and one
+              \textit{k-regular} network with $k=\{1,2,3,4,5\}$
+              (\ref{append_fig:network_properties_cc_sf_12345}) and $k=\{10,20,30,40,50\} $ (See the
+              respective box plots in the appending:
+              figure\ref{append_fig:network_properties_cc_sf_kreg}).}
 		\label{fig:network_properties_line_cc_sf_kreg}
@@
 
-\noindent Figure \ref{fig:network_properties_line_cc_sf_kreg} shows the results for the \textit{clustering coefficient}.
-These are similar to the results we get for \textit{k-regular} networks (see figure \ref{fig:network_properties_cc_line_kreg}).
-The difference is that we are not adding more networks but rather increasing the parameter $d$ of the scale-free.
-Curiously, in this case, the effects are qualitatively similar with the ones of merged \textit{k-regular} network with low value of $k$.
-With high values of $k$ (figure \ref{fig:network_properties_cc_line_sf_kreg_1020304050}) we can see that higher values of $d$ are not enough to make the network more clustered.
-This happens because scale-free networks are more sparse and have a very low number of triangles between nodes.
-
-%***************************************************
+        \noindent Figure \ref{fig:network_properties_line_cc_sf_kreg} shows the results for the
+        \textit{clustering coefficient}. These are similar to the results we get for
+        \textit{k-regular} networks (see figure \ref{fig:network_properties_cc_line_kreg}). The
+        difference is that we are not adding more networks but rather increasing the parameter $d$
+        of the scale-free (number of connections added by preferential attachment for each
+        note). In this case, the effects are qualitatively similar with the ones of merged
+        \textit{k-regular} network with low value of $k$. In contrast, for high values of $k$
+        (figure \ref{fig:network_properties_cc_line_sf_kreg_1020304050}), a higher value of $d$ is
+        not enough to make the network more clustered. This happens because scale-free networks are
+        more sparse and have a very low number of triangles between nodes.
+
+        % *************************************************** 
         %           Context Permeability
-%***************************************************
+        % ***************************************************
         \subsection{Context Permeability}

### 2015-06-21 doc/main.tex
results for context permeability reviewed

@@
 
-\noindent In this section, we discuss the results for various sets of experiments on the first model we presented --the \textit{context permeability model} \cite{Antunes2007,Antunes2010}.
-In a first set of experiments, the agent space was structured using \textit{k-regular} and \textit{scale-free }social networks.
-Each network layer was configured with the same topology.
-We analyse the context permeability model in terms of convergence to consensus: the ratio of simulations that converged to total consensus over 3000 runs; and how many agent encounters were needed for this to happen.
+        \noindent In this section, we discuss the results for various sets of experiments on the
+        \textit{context permeability model} \cite{Antunes2007,Antunes2010}. First, we used
+        \textit{k-regular} and \textit{scale-free} networks with our model. Each network layer was
+        configured with the same topology. We analyse the context permeability model in terms of
+        convergence to consensus: the ratio of simulations that converged to total consensus over
+        3000 runs; and how many agent encounters were needed for this to happen.
 
@@
         \label{sec:ctx_perm_convergence}
-\noindent We now analyse the ratio of convergence to consensus for different network configurations.
-We correlate this ratio with the properties that the combined network structure exhibits.
-As we have seen in section \ref{sec:network_properties}, the properties don't vary much for different random network instances, so we use the average as the descriptor for these properties in this correlation.
-
-The following tables show the results of our simulations.
-Table ~\ref{tab:regular_convergence} shows the percentage of total consensus achieved with 2000 cycles for 3000 runs.
-We can see that for k-regular networks with a small $k$, consensus is rarely achieved with a single network.
-However, as soon as we add more networks, consensus is achieved in a significantly greater number of occasions.
-These results are especially interesting for the \textit{scale-free }networks (table \ref{tab:scale-free_convergence}): as soon as we add more planes, for a \textit{scale-free} with $d\ge2$, we can achieve consensus in a lot of occasions.
-This is to show that achieving consensus is not just a matter of connectivity.
-With \textit{scale-free} networks, we can achieve consensus more often with less clustered networks.
-This convergence is achieved not because of the clustering coefficient but rather due to lower \textit{average path length}.
-This is difficult to visualise using only the tables and the previous plots so, to confirm this hypothesis, we measured the \textit{Spearman's correlation}\footnote{The Spearman's rank correlation coefficient is a nonparametric measure of statistical dependence between two variables.
-It assesses how well the relationship between two variables can be described using a monotonic function.} between the ratio of convergences to consensus, the average of \textit{average path length}, and the average of \textit{clustering coefficient} for the corresponding network configurations (see table \ref{tab:convergence_correlation}).
+        \noindent To analyse the ratio of convergence to consensus for different network
+        configurations, we correlate this ratio with the properties that the combined network
+        structure exhibits. As we have seen in section \ref{sec:network_properties}, the properties
+        don't vary much for different random instances, so we use the average as the descriptor for
+        these properties.
+
+        The following tables show the results of our simulations. Table
+        ~\ref{tab:regular_convergence} shows the percentage of total consensus achieved with 2000
+        cycles for 3000 runs. For k-regular networks with a small $k$, consensus is rarely achieved
+        with a single network. However, as soon as we add more networks, consensus is achieved in a
+        significantly greater number of occasions. These results are especially interesting for the
+        \textit{scale-free} networks (table \ref{tab:scale-free_convergence}): as soon as we add
+        more networks, for a \textit{scale-free} with $d\ge2$, we can achieve consensus in a lot of
+        occasions. This is to show that achieving consensus is not just a matter of
+        connectivity. With \textit{scale-free} networks, we can achieve consensus more often with
+        less clustered networks. This convergence is achieved not because of the clustering
+        coefficient but rather due to lower \textit{average path length}. This is difficult to
+        visualise using only the tables and the previous plots so, to confirm this hypothesis, we
+        measured the \textit{Spearman's correlation}\footnote{The Spearman's rank correlation
+          coefficient is a non-parametric measure of statistical dependence between two variables. It
+          assesses how well the relationship between two variables can be described using a
+          monotonic function.} between the ratio of convergences to consensus, the average
+        \textit{average path length}, and the average \textit{clustering coefficient} for the
+        corresponding network configurations (see table \ref{tab:convergence_correlation}).
 
@@
           \begin{minipage}{0.9\textwidth}
-		\caption{Ratio of convergence to total consensus in 3000 independent runs with with a number of concomitant networks ($\#$ nets.) equal in kind: k-regular networks with $k=\{1,2,3,4,5,10,20,30,40,50\}$.}
+            \caption{Ratio of convergence to total consensus in 3000 independent runs with with a
+              number of concomitant networks ($\#$ nets.) equal in kind: k-regular networks with
+              $k=\{1,2,3,4,5,10,20,30,40,50\}$.}
 		\label{tab:regular_convergence}
@@
               \begin{minipage}{0.9\textwidth}
-		\caption{Ratio of convergence to total consensus in 3000 independent runs with a number of concomitant networks ($\#$ nets.) equal in kind: \textit{scale-free} networks with $d=\{1,2,3,4,5\}$.}	
+		\caption{Ratio of convergence to total consensus in 3000 independent runs with a
+                  number of concomitant networks ($\#$ nets.) equal in kind: \textit{scale-free}
+                  networks with $d=\{1,2,3,4,5\}$.}
 		\label{tab:scale-free_convergence}
@@
       \label{sec:ctx_perm_encounters}
-\noindent We now analyse the convergence in terms of average number of meetings during a simulation run.
-Since the maximum number of simulation cycles is 2000, the maximum number of encounters is 2~000~000 (we have 100 agents and each one performs one encounter per cycle).
-We show that for some configurations, the average of encounters is not a good descriptor since it varies greatly from run to run.
-It is better to look at the distributions of these measures rather than considering the average.
-Nevertheless, we included the data with all the average number of encounters, as well as the respective standard deviations for different network configurations.
-You can find this data in appendix \ref{append_ctx_permeability}.
-
-%boxplots for k-regular networks
-First, we present the results for k-regular networks.
-To observe the distribution of the number of encounters consider the box plots for $k = \{1,2,3,4,5\}$ (figure \ref{fig:ctx_perm_kreg_12345}) and $k =\{10,20,30,40,50\}$ (figure \ref{fig:ctx_perm_kreg_1020304050}).
-In figure \ref{fig:ctx_perm_kreg}, we focus on configurations with a number of networks $\ge 3$, since less networks lead to much worse results in terms of convergence speed.
-These plots still present two types of situations: the typical runs, in which the number of encounters doesn't vary that much, and some ``outlier runs," which present some interesting dynamics, as we will see later on.
+      \noindent We now analyse the convergence in terms of average number of meetings during a
+      simulation run. Since the maximum number of simulation cycles is 2000, the maximum number of
+      encounters is 2~000~000 (we have 100 agents and each one performs one encounter per cycle). We
+      show that for some configurations, the average of encounters is not a good descriptor since it
+      varies greatly from run to run. Rather than considering the average, it is better to look at
+      the distributions of these measures. Nevertheless, we included the data with all the average
+      number of encounters, as well as the respective standard deviations for different network
+      configurations. You can find this data in appendix \ref{append_ctx_permeability}.
+
+      % boxplots for k-regular networks
+      First, we present the results for k-regular networks. To observe the distribution of the
+      number of encounters, consider the box plots for $k = \{1,2,3,4,5\}$ (figure
+      \ref{fig:ctx_perm_kreg_12345}) and $k =\{10,20,30,40,50\}$ (figure
+      \ref{fig:ctx_perm_kreg_1020304050}). Figure \ref{fig:ctx_perm_kreg} shows the results for
+      configurations with a number of networks $\ge 3$ (since less networks lead to much worse
+      results in terms of convergence speed). These plots reveal two types of situations: the
+      typical runs, in which the number of encounters doesn't vary much, and some ``outlier runs,"
+      which present some interesting dynamics, as we will see later on.
 
@@
 		\vspace{0.2cm}
-		\caption{Number of meetings over 100 independent simulation runs for multiple k-regular networks: $k=\{1,2,3,4,5\}$~(\ref{fig:ctx_perm_kreg_12345}) and $k=\{10,20,30,40,50\}$~(\ref{fig:ctx_perm_kreg_1020304050})).}
+		\caption{Number of meetings over 100 independent simulation runs for multiple
+                  k-regular networks: $k=\{1,2,3,4,5\}$~(\ref{fig:ctx_perm_kreg_12345}) and
+                  $k=\{10,20,30,40,50\}$~(\ref{fig:ctx_perm_kreg_1020304050})).}
 		\label{fig:ctx_perm_kreg}
@@
 
-\noindent Figure~\ref{fig:ctx_perm_kreg} shows us results that are qualitatively similar to what we previously observed for convergence ratios (see section \ref{sec:ctx_perm_convergence}).
-Networks with lesser connectivity and a greater average path length lead to total convergence less often.
-Moreover, the simulation outcomes vary much more in comparison with the other configurations ($k>1$ and $networks \ge 3$).
-
-Notice that for $k=3$ and $networks=3$ (\ref{fig:ctx_perm_kreg_1020304050}), we still have runs that deviate from what we consider the typical behaviour.
-Instead of disregarding this as a simple outlier, we show that this run allows us to gain an insight into the dynamics of our \textit{External Majority} consensus game.
-
-Before anything else, we analysed the network structure from this run and observed that there were no distinct differences between the network instances from the ``outlier run" and the ones of the ``typical" run.
-This suggested that this can be a property of the game itself --and of the network structure that leads to this situation -- and what happens is that the agents reach a state from which converging towards consensus is significantly harder.
-Villatoro \cite{Villatoro2013}  found that some complex network models lead consensus games to form metastable sub-conventions.
-These are very difficult to break and reaching 100\% agreement is not as straightforward as assumed by previous researchers.
-We are not concerned with this difficulty but rather with what happens in similar cases.
-Figure~\ref{fig:ctx_perm_kreg_runs} shows the consensus progression for two simulation runs a typical case and the outlier.
+      \noindent Figure~\ref{fig:ctx_perm_kreg} shows us results qualitatively similar to what we
+      previously observed for convergence ratios (see section
+      \ref{sec:ctx_perm_convergence}). Networks with lesser connectivity and a greater average path
+      length lead to total convergence less often. The simulation outcomes also vary much more in
+      comparison with the other configurations ($k>1$ and $networks \ge 3$).
+
+      Notice that for $k=3$ and $networks=3$ (\ref{fig:ctx_perm_kreg_1020304050}), we still have
+      runs that deviate from what we consider the typical behaviour. Instead of disregarding this as
+      an outlier, we explore this behaviour to better understand the dynamics of our
+      \textit{External Majority} consensus game.
+
+      We analysed the network structure from this run and observed that there were \textit{no
+        distinct differences} between the network instances from the ``outlier run" and the ones of
+      the ``typical" run. This pointed to the consensus game itself as a possible cause for the
+      irregular behaviour -- not to the network structure --. What happens is that the agents reach
+      a state from which converging towards consensus is significantly harder. Villatoro
+      \cite{Villatoro2013} found that some complex network models lead consensus games to form
+      metastable sub-conventions. These are very difficult to break and reaching 100\% agreement is
+      not as straightforward as assumed by previous researchers. We are not concerned with this
+      difficulty, instead, we want to explore how to describe what happens in similar
+      cases. Figure~\ref{fig:ctx_perm_kreg_runs} shows the consensus progression for two simulation
+      runs a typical case and the outlier.
 
@@
           \vspace{0.2cm}
-		\caption{Number of agents with each opinion during a simulation run: typical run in \ref{fig:ctx_perm_kreg_run_normal} and ``outlier run" in \ref{fig:ctx_perm_kreg_run_outlier}.}
+          \caption{Number of agents with each opinion during a simulation run: typical run in
+            \ref{fig:ctx_perm_kreg_run_normal} and ``outlier run" in
+            \ref{fig:ctx_perm_kreg_run_outlier}.}
 		\label{fig:ctx_perm_kreg_runs}
@@
 
-\noindent In our case, we take the outlier in the configuration with $k=3$ and $networks=3$, and look at the memory that agents use in the consensus game.
-As we described previously, agents record the number of individuals encountered with each opinion value (two opinions in this case).
-We look at the average difference between the number of opinions observed for all the agents.
-We also look at the variance to see if the opinion observations evolve in an uniform fashion throughout the simulation.
-Figure~\ref{fig:ctx_perm_kreg_runs_diff} shows the average difference between opinion memory for the first 10 steps (which was when the simulation converged for the normal run).
+      \noindent We take the outlier in the configuration with $k=3$ and $networks=3$, and look at
+      the memory that agents use in the consensus game. As we described previously, agents record
+      the number of individuals encountered with each opinion value (two possible values in this
+      case). We look at the average difference between the number of values observed for all the
+      agents. We also look at the variance to find how the opinion observations evolve throughout
+      the simulation. Figure~\ref{fig:ctx_perm_kreg_runs_diff} shows the average difference between
+      opinion memory for the first 10 steps (which was when the simulation converged for the normal
+      run).
 
@@
           \vspace{0.2cm}
-		\caption{Average and variance of the difference between opinions observed for the 100 agents: typical run in figure \ref{fig:ctx_perm_kreg_run_normal_diff} and first steps of the``outlier run" in figure \ref{fig:ctx_perm_kreg_run_outlier_diff}.}
+          \caption{Average and variance of the difference between opinions observed for the 100
+            agents: typical run in figure \ref{fig:ctx_perm_kreg_run_normal_diff} and first steps of
+            the``outlier run" in figure \ref{fig:ctx_perm_kreg_run_outlier_diff}.}
 		\label{fig:ctx_perm_kreg_runs_diff}
@@
 
-We can see that both the average difference in the opinion memory and the variance rise faster in the normal run than in the outlier run.
-This is not enough to establish that there is a significant difference between the two.
-Moreover, the memory differences are quite similar, but the number of agents for each opinion was quite even.
-This happens due to the position of agents in the network and their initial opinion values.
-These circumstances led the agents to a initial stability.
-Note that the opinion difference continues to rise throughout the simulation along with the variance.
-The variance starts to increase more rapidly after 200 steps.
-The exponential growth reveals that the convergence to consensus is not done evenly throughout the network, this is one of the reasons why consensus takes more time to be achieved.
-Also, the low variance in the first $200$ steps shows us that the opinion strength was evenly distributed --we have almost the same number of agents for each opinion but the memory differences are qualitatively the same for both opinions.
-As soon as this variance increases, one of the opinions breaks the stable state and the convergence towards global consensus begins.
+      We can see that both the average difference in the opinion memory and the variance grow faster
+      in the normal run than in the outlier run. This is not enough to establish a significant
+      difference between the two. Moreover, the memory differences are quite similar, but the number
+      of agents for each opinion was quite even. This happens due to the position of agents in the
+      network and their initial opinion values. These circumstances led the agents to a initial
+      stability. Note that the opinion difference continues to rise throughout the simulation along
+      with the variance. The variance starts to increase more rapidly after 200 steps. The
+      exponential growth reveals that the convergence to consensus is not done evenly throughout the
+      network, this is one of the reasons why consensus takes more time to be achieved. Also, the
+      low variance in the first $200$ steps shows us that the opinion strength was evenly
+      distributed: we have almost the same number of agents for each opinion but the memory
+      differences are qualitatively the same for both opinions. As soon as this variance increases,
+      one of the opinions breaks the stable state and convergence towards global consensus begins.
 
@@
 	\begin{minipage}{0.9\textwidth}
-		\caption{Average and variance of the difference between opinions observed for the 100 agents throughout the outlier run.}
+          \caption{Average and variance of the difference between opinions observed for the 100
+            agents throughout the outlier run.}
           \label{fig:ctx_perm_kreg_run_outlier_diff_full}
@@
 
-\noindent In other words, in some sections of the network, the agents converged towards one opinion and continue to reinforce each other (leading the opinion difference to grow) and the more regions converge, the faster the global convergence is.
+      \noindent In other words, different neighbourhoods in the network lead to different opinion
+      observation configurations (possibly even creating self-reinforcing structures). Thus, the
+      influence of heterogeneous connectivity is reflected on the growth of opinion difference
+      variance.
 
@@
 		\vspace{0.2cm}
-		\caption{Number of meetings over 100 independent simulation runs for multiple \textit{scale-free} networks: with d=\{1,2,3,4,5\} (\ref{fig:ctx_perm_sf_full}) with a zoom on the best configurations in \ref{fig:ctx_perm_sf_best}.}
+		\caption{Number of meetings over 100 independent simulation runs for multiple
+                  \textit{scale-free} networks: with d=\{1,2,3,4,5\} (\ref{fig:ctx_perm_sf_full})
+                  with a zoom on the best configurations in \ref{fig:ctx_perm_sf_best}.}
 		\label{fig:ctx_perm_sf}
@@
 
-\noindent Figure~\ref{fig:ctx_perm_sf} shows the average number of encounters during 100 independent simulation runs for \textit{scale-free} networks.
-(We don't include the configuration for one network and $d = 1$ because, as we have seen in the convergence results, these never converge.
-The convergence ratio is very low for the configurations with one network $d = 2$ and 2 networks with $d = 1$; hence the high number of encounters~(see also table \ref{tab:scale-free_convergence}).
-
-These results are similar to those of \textit{k-regular} in that adding more networks speeds up the convergence to consensus.
-The difference is that more ``atypical" runs occur with multiple \textit{scale-free} networks.
-Again, this is the effect of these types of topologies.
-As we discussed previously, in these less connected topologies, agents are more prone to be arranged in such a way that progression towards consensus is more difficult to attain, due to bottlenecks to regions in the network that converged to different opinion values.
+      \noindent Figure~\ref{fig:ctx_perm_sf} shows the average number of encounters during 100
+      independent simulation runs for \textit{scale-free} networks. (We don't include the
+      configuration for one network and $d = 1$ because these never converge.) The convergence ratio
+      is very low for the configurations with one network $d = 2$ and 2 networks with $d = 1$; hence
+      the high number of encounters~(see also table \ref{tab:scale-free_convergence}).
+
+      These results are similar to those of \textit{k-regular} in that adding more networks speeds
+      up the convergence to consensus. The difference is that more ``atypical" runs occur with
+      multiple \textit{scale-free} networks. Again, this is the effect of these types of
+      topologies. As we discussed previously, in these less connected topologies, agents are more
+      prone to be arranged in such a way that progression towards consensus is more difficult to
+      attain due to bottlenecks. Different regions in the network might converge towards different
+      opinion values.
 
       \subsubsection{Heterogeneous Network Configuration}
-\noindent We also performed experiments where we mixed the network topologies: in this case we used one \textit{scale-free} and one \textit{k-regular} networks.
-Table~\ref{tab:regular_scale-free_convergence} shows the convergence ratio for the heterogeneous network configuration with the multiple values for $d$ and $k$ for the \textit{scale-free} and \textit{k-regular} respectively.
+      \noindent We also performed experiments with mixed network topologies: we used one
+      \textit{scale-free} and one \textit{k-regular}
+      networks. Table~\ref{tab:regular_scale-free_convergence} shows the convergence ratio for the
+      heterogeneous network configuration with the multiple values for $d$ and $k$ for the
+      \textit{scale-free} and \textit{k-regular} respectively.
 
@@
 	\begin{minipage}{0.9\textwidth}
-		\caption{Ratio of convergence to total consensus in 3000 independent runs with two networks: one \textit{k-regular} and one \textit{scale-free} network with different $k$ and $d$ values respectively.}
+          \caption{Ratio of convergence to total consensus in 3000 independent runs with two
+            networks: one \textit{k-regular} and one \textit{scale-free} network with different $k$
+            and $d$ values respectively.}
           \label{tab:regular_scale-free_convergence}
@@
 
-\noindent One of the outcome differences between this configuration and the previous ones can be observed in the simulations with $d=1$ and $k=1$.
-The convergence ratio is higher than with $2$ $1-regular$ networks (see table \ref{tab:regular_convergence}) --but not better than two \textit{scale-free} networks.
-This happens because with $k=1$ the network is basically a ring and has the maximum possible average path length for a connected graph.
-Adding two rings improves  the convergence ratio but the underlying structure is still very susceptible to self-reinforcing structures (a connected sub-graph is basically a line).
-Adding a \textit{scale-free} changes this drastically as we are mixing tree-like network components with this first circle.
+      \noindent One of the differences between this configuration and the previous ones can be
+      observed in the simulations with $d=1$ and $k=1$. The convergence ratio is higher than with
+      $2$ $1-regular$ networks (see table \ref{tab:regular_convergence}) -- but not better than two
+      \textit{scale-free} networks. This happens because with $k=1$ the network is basically a ring
+      and has the maximum possible average path length for a connected graph. Adding two rings
+      improves the convergence ratio but the underlying structure is still very susceptible to
+      self-reinforcing structures (a connected sub-graph is basically a line). Adding a
+      \textit{scale-free} changes this drastically as we are mixing tree-like network components
+      with a ring.
 
@@
 		\vspace{0.2cm}
-		\caption{Number of meetings over 100 independent simulation runs for heterogeneous configuration: one \textit{k-regular} network with  $k=\{1,2,3,4,5\}$ and one \textit{scale-free} network with $d\{1,2,3,4,5\}$.
-Figure \ref{fig:ctx_perm_sfkreg_1020304050best} shows a zoom on the best configurations.}
+		\caption{Number of meetings over 100 independent simulation runs for heterogeneous
+                  configuration: one \textit{k-regular} network with $k=\{1,2,3,4,5\}$ and one
+                  \textit{scale-free} network with $d\{1,2,3,4,5\}$. Figure
+                  \ref{fig:ctx_perm_sfkreg_1020304050best} shows a zoom on the best configurations.}
 		\label{fig:ctx_perm_sfkreg}
@@
 
-Figure \ref{fig:ctx_perm_sfkreg} shows the results for the number of encounters necessary for the agents to achieve consensus.
-We focus on the \textit{k-regular} networks with higher values of $k$.
-We can see that with these two networks, the configurations with values of $d>=2$ for \textit{scale-free} networks produce drastically better results in terms of speed of convergence.
-
-The data for the average number of encounters, as well as the respective standard deviations referent to the results in figure \ref{fig:ctx_perm_sfkreg}, can be found in appendix \ref{append_ctx_permeability}, table \ref{append_tab:ctx_perm_kreg_sf_encounters}.
+      Figure \ref{fig:ctx_perm_sfkreg} shows the results for the number of encounters necessary for
+      the agents to achieve consensus. We focus on the \textit{k-regular} networks with higher
+      values of $k$. We can see that with these two networks, the configurations with values of
+      $d>=2$ for \textit{scale-free} networks produce drastically better results in terms of speed
+      of convergence. The data for the average number of encounters, as well as the respective
+      standard deviations referent to the results in figure \ref{fig:ctx_perm_sfkreg}, can be found
+      in appendix \ref{append_ctx_permeability}, table \ref{append_tab:ctx_perm_kreg_sf_encounters}.
 

### 2015-06-21 doc/main.tex
results for context switching reviewed

@@
 
+      % ***************************************************
+      % Context Switching
+      % ***************************************************
+
       \subsection{Context Switching}
-\noindent In this section, we present the results relative to the context switching model.
-The difference between this model and the previous one is that the agents no longer interact in the multiple networks at the same time (being able to select any neighbour at a given simulation step).
-In this model, they become active in a single network at a time.
-Agents can switch to a different network at the end of each step.
-The switching mechanism uses a probability associated with the current network in which the agent is currently active.
-With this new idea of swapping contexts, we covered some space left undeveloped in Antunes and colleagues original work \cite{Antunes2007,Antunes2010}.
-
-As we discussed previously in section \ref{sec:models_cs} (see model \ref{model:context_switching}), the switching probability dictates the frequency with which an agent switches \textit{from} the current network after an encounter has been performed.
-In an abstract manner, this allows us to model how much time agents spend on each network.
-A further development of this model will be to assign different preferences to different networks for each agent.
-This can help us model phenomena such as real-world agents that dedicate more or less time consuming content from different social networks.
-For now, we attribute this probability to the network to restrain the model complexity.
+      \noindent In this section, we present the results relative to the context switching model. The
+      difference between this model and the previous one is that the agents no longer interact in
+      multiple networks at the same time (being able to select any neighbour at a given simulation
+      step). In this model, they become active in a single network at a time. Agents can switch to a
+      different network at the end of each step. The switching mechanism uses a probability
+      associated with each network. With this new idea of swapping contexts, we covered some space
+      left undeveloped in Antunes and colleagues original work \cite{Antunes2007,Antunes2010}.
+
+      As we discussed in section \ref{sec:models_cs} (see model \ref{model:context_switching}), the
+      switching probability dictates the frequency with which an agent switches \textit{from} the
+      current network \textit{after} an encounter has been performed. In an abstract manner, this
+      allows us to model how much time agents spend on each network. A further development of this
+      model will be to assign different preferences to different networks for each agent. This can
+      help us model phenomena such as real-world agents that dedicate more or less time consuming
+      content from different social networks. For now, we attribute this probability to the network
+      to restrain the model complexity.
 
       \subsubsection{Exploring the Switching Probability}
-\noindent We first look at the influence of the new parameter (switching probability) in the convergence to consensus.
-We span the switching probability between $0$ and $1$ in intervals of $0.05$.
-We do this for 2 networks with \textit{k-regular} and \textit{scale-free} topologies.
-Figure \ref{fig:ctx_cs_2_kregular} shows the results for two \textit{k-regular} networks: one configuration with $k = 10$ and one configuration with $k = 30$.
-We use these two configurations to observe the relationship between the number of encounters to achieve consensus, the switching probability parameter and the connectivity of the networks.
-Remember that with $k=30$ the average path length is also lower (see section \ref{sec:overlapping_kreg}).
+      \noindent We first look at the influence of the new parameter (switching probability) in the
+      convergence to consensus. We span the switching probability between $0$ and $1$ in intervals
+      of $0.05$. We do this for 2 networks with \textit{k-regular} and \textit{scale-free}
+      topologies. Figure \ref{fig:ctx_cs_2_kregular} shows the results for two \textit{k-regular}
+      networks: one configuration with $k = 10$ and one configuration with $k = 30$. We use these
+      two configurations to study the relationship between the number of encounters, the switching
+      probability parameter, and the connectivity of the networks. Remember that with $k=30$ the
+      average path length is also lower (section \ref{sec:overlapping_kreg}).
 
@@
           \vspace{0.2cm}
-		\caption{Contour plot for the average number of meets during a simulation for 100 independent runs: 2 \textit{10-regular} networks (\ref{fig:ctx_cs_2_10kreg}) and \textit{30-regular} networks (\ref{fig:ctx_cs_2_30kreg}).
-See the perspective plots in appendix \ref{append_ctx_switching}.}
+          \caption{Contour plot for the average number of meets during a simulation for 100
+            independent runs: 2 \textit{10-regular} networks (\ref{fig:ctx_cs_2_10kreg}) and
+            \textit{30-regular} networks (\ref{fig:ctx_cs_2_30kreg}). See the perspective plots in
+            appendix \ref{append_ctx_switching}.}
           \label{fig:ctx_cs_2_kregular}
@@
 
-\noindent We note that with smaller values of $k$, symmetry in the context switching probability is more important (having the same probability in both networks) if the agent switches less from one of them.
-This is the case because switching less from one network means spending more time in that network.
-This means that switching more from the other network can be disruptive to a neighbourhood that has already converged to a sub-convention.
-This can be observed in configurations with \textit{k-regular} networks (figure \ref{fig:ctx_cs_2_10kreg}) but it is especially apparent in \textit{scale-free} networks (figure \ref{fig:ctx_cs_2_sf_d1}).
+      \noindent For smaller values of $k$, symmetry in the context switching probability (having the
+      same probability in both networks) is more important if the agent switches less from one of
+      the networks. Switching less from one network means spending more time in that network. This
+      means that switching more from the other network can be disruptive to a neighbourhood that has
+      already converged to a sub-convention. This can be observed in configurations with
+      \textit{k-regular} networks (figure \ref{fig:ctx_cs_2_10kreg}) but it is especially apparent
+      in \textit{scale-free} networks (figure \ref{fig:ctx_cs_2_sf_d1}).
 
@@
           \vspace{0.2cm}
-		\caption{Contour plot for the average number of meets during a simulation for 100 independent runs: 2 \textit{scale-free} networks with $d=1$ (\ref{fig:ctx_cs_2_sf_d1}) and $d=5$ (\ref{fig:ctx_cs_2_sf_d5}).
-See the perspective plots in  appendix \ref{append_ctx_switching}.}
+          \caption{Contour plot for the average number of meets during a simulation for 100
+            independent runs: 2 \textit{scale-free} networks with $d=1$ (\ref{fig:ctx_cs_2_sf_d1})
+            and $d=5$ (\ref{fig:ctx_cs_2_sf_d5}). See the perspective plots in appendix
+            \ref{append_ctx_switching}.}
           \label{fig:ctx_cs_2_sf}
@@
 
-When we increase the connectivity (and lower the average path length), both in \textit{k-regular} and \textit{scale-free} networks, the switching probability becomes ``irrelevant:'' in the sense that you can use any probability you want and the results in terms of speed of convergence will be the same.
-The exception is obviously when considering the switching probability with value $0$.
-In this case, agents are isolated (they are initially equally distributed throughout the networks) and reaching consensus becomes very hard.
---Especially hard since agents are active only in one network: being active in all the networks creates the possibly of disconnected graphs in the networks they are not currently active.
-
-One major difference from the previous model is that the agents no longer can select a neighbour for interaction from any network.
-The selection has to be made from the network they are currently active in.
-This causes that agents spending different amounts of time in distinct network topologies are influenced differently -- an agent can be very influential in one network, being a very central node in that context, and marginally important in the other one: in a sense its opinion in one network can be more important to overall convergence than in other network,  due to its position in the network.
-
-To check the influence of connectivity in the new switching dynamics we setup two \textit{scale-free} networks; one with $d=1$ and the other with $d=5$. We then performed the 
-same span of switching probability similarly to the previous experiments. The results can be seen in figure \ref{fig:ctx_cs_sf_d5_d1}.
+      When we increase the connectivity (and lower the average path length), both in
+      \textit{k-regular} and \textit{scale-free} networks, the switching probability becomes
+      ``irrelevant'' --for any probability value, the speed of convergence will be the same--. The
+      exception is obviously when considering the switching probability with value $0$. In this
+      case, agents are isolated (they are initially equally distributed throughout the networks) and
+      reaching consensus becomes very hard. (Especially because agents are active only in one network
+      and this can create disconnected graphs.)
+
+      One major difference from the previous model is that the agents no longer interact with a
+      neighbour from any network at any time. The neighbour selection has to be made from the
+      network they are currently active in. This causes the agents to spend different amounts of
+      time in different networks. An agent can be very influential in one network -- being a very
+      central node in that context -- and marginally important in another: in a sense its opinion in
+      one network can be more important to overall convergence than in other network, due to its
+      position in the network.
+
+      To explore the contribution of connectivity to the new context switching dynamics, we setup
+      two \textit{scale-free} networks; one with $d=1$ and the other with $d=5$. We then spanned the
+      switching probability in increments of $0.05$. The results can be seen in figure
+      \ref{fig:ctx_cs_sf_d5_d1}.
 
@@
 	\begin{minipage}{0.9\textwidth}
-		\caption{Contour plot for the average number of meets during a simulation for 100 independent runs: 2 \textit{scale-free} networks, the first with $d=5$ and the second with $d=1$.
-See the perspective plots in  appendix \ref{append_ctx_switching} (figure \ref{append_fig:ctx_cs_sf_d5_d1}).
-		}
+          \caption{Contour plot for the average number of meets during a simulation for 100
+            independent runs: 2 \textit{scale-free} networks, the first with $d=5$ and the second
+            with $d=1$. See the perspective plots in appendix \ref{append_ctx_switching} (figure
+            \ref{append_fig:ctx_cs_sf_d5_d1}).  }
 		\label{fig:ctx_cs_sf_d5_d1}
@@
 
-We see that in this case it is more important to switch \textit{from} the network with lower average path length and a forest-like composition ($d=1$) with a probability of at least the same value or more than the one of the other network (with $d=5$).
-The same can be observed when we mix the two topologies (\textit{k-regular} with \textit{scale-free}), as we can see in figure \ref{fig:ctx_cs_kreg10_sfd1}.
-
-It seems that basically switching less from the less connected network is bad in both cases: spending more time in the network with bigger neighbourhoods allows for a stabler convergence.
-Sub-conventions can emerge in \textit{scale-free} networks with $d=1$ because usually some network regions are isolated by a single node --the root of the sub-tree they belong to.
+      In this case it is more important (to convergence speed) to switch \textit{from} the network
+      with lower average path length and a forest-like composition (and a probability of at least
+      the same value or more than the one of the other network with $d=5$). The same can be observed
+      when we mix \textit{k-regular} with \textit{scale-free} networks (see figure
+      \ref{fig:ctx_cs_kreg10_sfd1}).
+
+      Switching less from the less connected network is bad in both cases: it is possible that
+      spending more time in the network with bigger neighbourhoods allows for a stabler
+      convergence. Sub-conventions can emerge in \textit{scale-free} networks with $d=1$ because
+      usually some network regions are isolated by a single node -- the root of the sub-tree they
+      belong to.
 
@@
 	\begin{minipage}{0.9\textwidth}
-		\caption{Contour plot for the average number of meets during a simulation for 100 independent runs: one \textit{10-regular} network (k=10) and a \textit{scale-free} network with $d=1$.
-See the perspective plots in  appendix \ref{append_ctx_switching} (figure \ref{append_fig:ctx_cs_kreg10_sfd1}).
-		}
+          \caption{Contour plot for the average number of meets during a simulation for 100
+            independent runs: one \textit{10-regular} network (k=10) and a \textit{scale-free}
+            network with $d=1$. See the perspective plots in appendix \ref{append_ctx_switching}
+            (figure \ref{append_fig:ctx_cs_kreg10_sfd1}).  }
           \label{fig:ctx_cs_kreg10_sfd1}
@@
       \subsubsection{Comparison with Context Permeability}
-\noindent Finally, to compare the context switching model with the previous model of context permeability, we constructed the following experiment.
-We froze the switching probabilities in the values $\zeta={0.25,0.5,0.75}$ and varied the number of networks.
-(We considered these values because they conveniently characterise the probability in low, medium and high switching) We compare the results with the context permeability in terms of average number of encounters to achieve consensus.
-Note that we have seen that in some cases, due to the distribution of the number of encounters, the average is not an accurate descriptor for the convergence.
-Nonetheless, normally the configurations with highly variable outcomes also produce an average that is qualitatively distinct from the rest of the configurations (see for example figure \ref{fig:ctx_perm_kreg} in section \ref{sec:ctx_perm_encounters}).
-As such, we took the average number of encounters during the simulations to compare what happens in the context switching model with the context permeability model.
+      \noindent Finally, to compare the context switching model with the previous model of context
+      permeability, we froze the switching probabilities with values $\zeta={0.25,0.5,0.75}$ and
+      varied the number of networks. (We considered these values because they conveniently
+      characterise the probability in low, medium and high switching.) We compare the results with
+      the context permeability in terms of average number of encounters to achieve consensus. Note
+      that in some cases, due to the distribution of the number of encounters, the average is not an
+      accurate descriptor for the convergence. Nonetheless, configurations with highly variable
+      outcomes usually produce an average that is qualitatively distinct from the rest (see figure
+      \ref{fig:ctx_perm_kreg} in section \ref{sec:ctx_perm_encounters}). We took the average number
+      of encounters during the simulations to compare the context switching model with the context
+      permeability model.
 
@@
           \vspace{0.2cm}
-		\caption{Average number of encounters during a simulation for 100 independent runs with \textit{k-regular} topologies in all the network layers.
-We compare the results of context switching with context permeability with a $number of networks = \{2,3,4,5\}$.
-The switching probability is the same in all the networks.
-}
+          \caption{Average number of encounters during a simulation for 100 independent runs with
+            \textit{k-regular} topologies in all the network layers. We compare the results of
+            context switching with context permeability with a $number of networks =
+            \{2,3,4,5\}$. The switching probability is the same in all the networks. }
 		\label{fig:ctx_switching_comp_kreg}
@@
 
-Figure \ref{fig:ctx_switching_comp_kreg} shows us that for 2 networks the results in terms of number of encounters for the context switching approximate those we got for context permeability.
-When we increase the number of networks ($n\ge3$) the configurations with higher switching probability lead the results to be more close to what happens in context permeability.
-This is no surprise since more switching makes agents switch more often between networks and consequently allows them too choose more often from different neighbourhoods.
-This is almost the same as having a larger neighbourhood to choose from, which is what happened in the context permeability model.
-
-The surprise was that for values of $k \ge 20$, the results where practically the same for both
-models independently of the switching probability -- even when we increased the number of networks, the number of encounters remained around $2000$ on average for all the models.
-Above a certain level of neighbourhood size (and overlapping, which causes the average path length to drop), the switching probability becomes less influential.
-It is still important that we get comparable results because we are introducing a temporal component that was never explored before in these types of opinion dynamics models: the fact that the agents can become active in different networks at different points in time.
+      Figure \ref{fig:ctx_switching_comp_kreg} shows that for 2 networks the results in terms of
+      number of encounters for the context switching approximate those for context
+      permeability. When we increase the number of networks ($n\ge3$), the configurations with
+      higher switching probability lead the results to be closer to what happens in context
+      permeability. This is no surprise since more switching makes agents switch more often between
+      networks and consequently allows them too choose more often from different
+      neighbourhoods. This is almost the same as having a larger neighbourhood to choose from, which
+      is what happened in the context permeability model.
+
+      The surprise was that for values of $k \ge 20$, the results where practically the same for
+      both models independently of the switching probability -- even when we increased the number of
+      networks, the number of encounters remained around $2000$ on average for all the models. Above
+      a certain level of neighbourhood size (and overlapping, which causes the average path length
+      to drop), the switching probability becomes less influential. It is still important that we
+      get comparable results because we are introducing a temporal component that was never explored
+      before in these types of opinion dynamics models: the fact that the agents can become active
+      in different networks at different points in time.
 
@@
       For \textit{scale-free} networks, figure \ref{fig:ctx_switching_comp_sf} shows us similar
-results. It seems that switching with a higher probability displays results similar with those of
-context permeability. In this case, adding more networks makes so that lowering switching
-probabilities displays slightly worse results. This influence is due to the fact that the
-neighbourhoods are considerably smaller in \textit{scale-free} networks -- even with values of $d=5$ -- so the impact of low switching was bound to be noticed.
-
-An increasing number of networks seems to always reduce the number of encounters to achieve consensus in both models.
-This happens due to what we have called \textit{permeability}.
-Having multiple points of dissemination that permeate between different social networks enhances the overall convergence to consensus.
-With permeability there are more previously isolated nodes being reached in sparsely connected networks such as scale-free networks.
-
-%*****************************************
+      results. Switching with a higher probability displays results similar with those of context
+      permeability. In this case, adding more networks makes so that lowering switching
+      probabilities displays slightly worse results. This influence comes from the neighbourhoods
+      being considerably smaller in \textit{scale-free} networks -- even with values of $d=5$ -- so
+      the impact of low switching was bound to be noticed.
+
+      An increasing number of networks seems to always reduce the number of encounters to achieve
+      consensus in both models. This happens due to what we called \textit{permeability}. Having
+      multiple points of dissemination that permeate between different social networks enhances the
+      overall convergence to consensus. With permeability there are more previously isolated nodes
+      being reached in sparsely connected networks such as scale-free networks.
+
+      % *****************************************
       % Conclusion
-%******************************************
+      % ******************************************
       \section{Conclusions}

### 2015-06-21 doc/main.tex
conclusion reviewed

@@
       \label{sec:conclusion-future}
-\noindent In this article, we analysed and discussed our modelling framework for multi-relational models of social spaces.
-These results show that not only contexts play an important role in the dissemination of consensus in artificial agent societies, but also that simple mechanisms can generate a great deal of complexity, especially in those scenarios where conventions are being co-learned by multiple agents.
-Adding more networks to our opinion dynamics model leads to outcomes where consensus was achieved not only more often but also faster.
-In particular, our results show that achieving convergence (i.e.\ total consensus in a network) is not a matter of connectivity.
-With scale-free networks we managed to achieve consensus more often and quicker than with less clustered networks.
-This conclusion is especially important for application with real world social phenomena, many times represented with such networks: full dissemination of a phenomenon (say, gossip-dissemination of a new anti-virus software) may prove impossible with one network only, but is very much eased up by the use of concomitant connections.
-Moreover, some of the techniques we have rehearsed have proven to speed up even more this now-eased up convergence.
-
-The second innovation presented in this article was the fact that our model describes an abstract way to represent the time spent on each network using the switching probability.
-This temporal component introduces a new dynamic to the study of opinion dynamics.
-Considering that in agent neighbourhoods, agents might not be available at all times and spend distinct amounts of time in different neighbourhoods, is an important factor to be included in some simulations from a modelling perspective.
-
-Future work includes the analysis of different complex network models.
-While \textit{k-regular} and \textit{scale-free} networks are two of the most pervasive network examples in these types of simulations, there has been a growing number of models with different properties inspired by real-world phenomena that can be considered.
-We can also analyse the networks according to different properties such as the present of nodes with high centrality in the network (hubs).
-Moreover, we  plan to apply what we learned with our consensus games to cooperation problems.
-Constructing agents that can learn both behaviour and coordination procedures is a difficult task especially when working with large distributed artificial societies.
-Consensus games such as this one can be used to reduce the search space in problems where agents need to cooperate or coordinate.
-
-Note that while the convergence and number of encounters seem to be correlated with the average path length, as we have seen previously, this might not be the only property that plays a role in faster convergence to consensus.
-Correlation is just an informal tool to helps us assert if some monotonic relationship exists.
-More research is needed to assert, for instance, if self-reinforced structures like the ones reported by \cite{Villatoro2013} exist in our multi-network scenarios.
-In particular we would be interested to see if permeability mitigates the effects of such structures.
-
-We have seen that context permeability by context overlapping or switching can provide a fairly straightforward modelling methodology that can be used to compose simulation scenarios for more complex social spaces.
-What remains to be done is to identify more precise contextual structures in real-world networks.
-While capturing the structure of real social network can be a daunting task, we do have pervasive records of networking activity between social actors: online social networks.
-Analysing these can lead us to insights about complex structural properties that emerge from user activity, and context that can be identified within those networks.
-A difficult --but not impossible-- prospect for further research would be to track similar contexts between different real online social networks.
+      \noindent In this article, we analysed and discussed our modelling framework for
+      multi-relational models of social spaces. These results show that not only contexts play an
+      important role in the dissemination of consensus in artificial agent societies, but also that
+      simple mechanisms can generate a great deal of complexity (especially in those scenarios where
+      conventions are being co-learned by multiple agents). Adding more networks to our opinion
+      dynamics model leads to outcomes where consensus was achieved not only more often but also
+      faster. In particular, our results show that achieving convergence (i.e. total consensus in a
+      network) is not a matter of connectivity. With scale-free networks we managed to achieve
+      consensus more often and quicker than with less clustered networks. This conclusion is
+      especially important for application (or models) dealing with real-world social phenomena,
+      many times represented with such networks.
+
+      The second innovation presented in this article was the fact that our model describes an
+      abstract way to represent the time spent on each network using the switching probability. This
+      temporal component introduces a new dynamic to the study of opinion dynamics. Considering that
+      in agent neighbourhoods, agents might not be available at all times -- and spend different
+      amounts of time in different neighbourhoods--, this is an important factor to be included in
+      simulation models (either representing real-world systems with different levels of
+      abstraction, or artificial agent societies for particular applications).
+
+      Future work includes the analysis of different complex network models. While
+      \textit{k-regular} and \textit{scale-free} networks are two of the most pervasive network
+      examples in social simulation, there has been a growing number of models with different
+      properties inspired by real-world phenomena that can be considered. We will also analyse the
+      networks according to different properties such as betweeness centrality of certain
+      nodes. Moreover, we plan to apply what we learned with our consensus games to cooperation
+      problems. Constructing agents that can learn both behaviour and coordination procedures is a
+      difficult task (especially when working with large distributed artificial
+      societies). Consensus games such as this one can be used to reduce the search space in
+      problems where agents need to cooperate or coordinate in a decentralised fashion.
+
+      While the convergence and number of encounters seem to be correlated with the average path
+      length, this might not be the only property that plays a role in faster convergence to
+      consensus. Correlation is just an informal tool that helps us assert if some monotonic
+      relationship exists. More research is needed to find out, for instance, if self-reinforced
+      structures --like the ones reported by \cite{Villatoro2013}-- exist in our multi-network
+      structures. In particular, we are interested in finding out if permeability mitigates the
+      effects of such phenomenon.
+
+      We have seen that context permeability by context overlapping or switching can provide a
+      fairly straightforward modelling methodology. This can be used to compose simulation scenarios
+      for more complex social spaces. What remains to be done is to identify more precise contextual
+      structures in real-world networks. While capturing the structure of real social network can be
+      a daunting task, we do have pervasive records of networking activity between social actors:
+      online social networks. Analysing these can lead us to insights about complex structural
+      properties that emerge from user activity, and contexts that can be identified within those
+      networks. A difficult --but not impossible-- prospect for further research would be to track
+      similar contexts between different real online social networks.
 
       \section*{Acknowledgements}
-\noindent This work was supported by the Funda\c{c}\~ao para a Ci\^encia e a Tecnologia under the grant SFRH / BD / 86034 / 2012.
+      \noindent This work was supported by the Funda\c{c}\~ao para a Ci\^encia e a Tecnologia under
+      the grant SFRH / BD / 86034 / 2012.
 

### 2015-06-28 doc/main.tex
Affiliation Corrected

@@
 
-		\address[ul]{Group of Studies in Social Simulation (GUESS), Laboratory of Agent Modelling, Faculdade de Ciências, Universidade de Lisboa, 1749-016 Lisboa, Portugal}
-		\title{Modelling Structured Societies: a Multi-relational Approach to Context Permeability}
+		\address[ul]{GUESS/BioISI - Instituto de Biosistemas e Ciências Integrativas,
+                  Faculdade de Ciências, Universidade de Lisboa, 1749-016 Lisboa, Portugal.}
+                \title{Modelling Structured Societies: a Multi-relational Approach to Context
+                  Permeability}
 
@@
       \section*{Acknowledgements}
-      \noindent This work was supported by the Funda\c{c}\~ao para a Ci\^encia e a Tecnologia under
-      the grant SFRH / BD / 86034 / 2012.
+      \noindent Work supported by the Funda\c{c}\~ao para a Ci\^encia e a Tecnologia under the grant
+      SFRH/BD/86034/2012 and by centre grant (to BioISI, Centre Reference:
+      UID/MULTI/04046/2013), from FCT/MCTES/PIDDAC, Portugal
 

### 2015-06-28 doc/rebuttal.tex

\documentclass[11pt]{letter}

\begin{document}

\textbf{Journal: Artificial Intelligence\\
Ref. No. ARTINT-D-13-00131R1\\
Title: Modelling Structured Societies: a Multi-relational Approach to Context Permeability\\
}

Answer to the reviewer's comments:

\begin{itemize}
\item Reviewer 1 is satisfied with the improvements we made over the first submitted version.

\item Reviewer 2 raises two very valid points:
\begin{itemize}
\item[--2a] s/he argues that our scenario is too specific and of little use for a general AI practitioner, the motivation needs to be stronger. 
\item[--2b] s/he misses a summary of results and explanation about their relevance.
\end{itemize}

\item Reviewer 3:
\begin{itemize}
\item[--3a] has doubts about applicability, and sustains that the models we use are too detached from reality, especially when concerning the understanding of human society.
\item [--3b] and mentions some typos and grammar errors.
\end{itemize}

\end{itemize}

In the new version of our paper we have included the following changes.

\begin{itemize}
\item[A:] In order to better explain the motivation of the paper and applicability of the work (that Reviewer 1 finds good, but Reviewers 2 and 3 still considered that required further clarification), and in this way to address comments 2a and 3a, we have made substantial changes to the introduction, namely in pointing that the emphasis is not really on the particular game the agents play, namely the consensus game, but rather on the structure and dynamics that considering multiple relations (afterwards called multiplex relations) induces. In fact, we wanted to keep the game as simple as possible, so that it would be quite neutral on the phenomenon at hands. To this purpose, the main motivation is just to consider more realistic accounts of social phenomena. Our proposal goes in that direction by suggesting and defending that the concomitant belonging to several relations is closer to reality than to consider a single relation in which the various social bonds are mixed together, summarised, and to a great extent simplified, since the nature and features of relations (family, friends, colleagues, etc.) is quite different and allows diverse explorations when we are considering options in our decisions concerning or influenced by social options. Essentially, we don't pretend that our results are of direct use for extrapolation to real societies any more than Schelling would claim that his model is an accurate model of human racial segregation. Or, making the same case, we acknowledge that the Prisoner's Dilemma game, widely used as an instance of Public Goods games, and with substantial potential for depicting real situations, is not a situation in which real people find themselves frequently. What we do argue is that our use of structured social networks that exhibit scale-free properties is quite common in real world, as thoroughly reported in the literature. Our use of scale-free networks in concomitancy with other networks tries to provide even more realism and increases the applicability of our results, be those networks regular (or lattices, e.g. a common situation in classrooms, football stadiums, etc) or scale-free themselves (seeking to represent the several but not coincidental relations found in true society, both on- and off-line). Possibly, some more types of relations should have been covered, but our commitment was to take this set and make the study as exhaustive as possible.

\item[B:] To answer 2b, we have rewritten the conclusions in order to best emphasize the contributions and the significance of the results we obtained.

\item[C:] Finally, to address 3b, we performed a thorough revision and hopefully have removed all the typos and grammatical mistakes.
\end{itemize}

\end{document}

### 2015-06-28 doc/appendix.tex

@@
   \centering
- \includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_apl_kreg_12345"}
+ \includegraphics[width=1\linewidth]{"../analysis/pdf/network_properties_apl_kreg_12345"}
  \caption{}
@@
   \centering
- \includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_apl_kreg_1020304050"}
+ \includegraphics[width=1\linewidth]{"../analysis/pdf/network_properties_apl_kreg_1020304050"}
  \caption{}
@@
   \centering
- \includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_cc_kreg_12345"}
+ \includegraphics[width=1\linewidth]{"../analysis/pdf/network_properties_cc_kreg_12345"}
  \caption{}
@@
   \centering
- \includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_cc_kreg_1020304050"}
+ \includegraphics[width=1\linewidth]{"../analysis/pdf/network_properties_cc_kreg_1020304050"}
  \caption{}
@@
   \centering
- \includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_apl_sf_12345"}
+ \includegraphics[width=1\linewidth]{"../analysis/pdf/network_properties_apl_sf_12345"}
  \caption{Average path length}
@@
   \centering
- \includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_cc_sf_12345"}
+ \includegraphics[width=1\linewidth]{"../analysis/pdf/network_properties_cc_sf_12345"}
  \caption{Clustering Coefficient}
@@
   \centering
- \includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_apl_sf_kregular_12345"}
+ \includegraphics[width=1\linewidth]{"../analysis/pdf/network_properties_apl_sf_kregular_12345"}
  \caption{}
@@
   \centering
- \includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_apl_sf_kregular_1020304050"}
+ \includegraphics[width=1\linewidth]{"../analysis/pdf/network_properties_apl_sf_kregular_1020304050"}
  \caption{}
@@
   \centering
- \includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_cc_sf_kregular_12345"}
+ \includegraphics[width=1\linewidth]{"../analysis/pdf/network_properties_cc_sf_kregular_12345"}
  \caption{}
@@
   \centering
- \includegraphics[width=1\linewidth]{"../analysis/pdf/ network_properties_cc_sf_kregular_1020304050"}
+ \includegraphics[width=1\linewidth]{"../analysis/pdf/network_properties_cc_sf_kregular_1020304050"}
  \caption{}
@@
 	\centering
-	\includegraphics[width=1\linewidth]{"../analysis/pdf/   context_switching_2_10_regular _switching_persp"}
+	\includegraphics[width=1\linewidth]{"../analysis/pdf/context_switching_2_10_regular_switching_persp"}
 	\begin{minipage}{0.9\textwidth}
@@
 	\centering
-	\includegraphics[width=1\linewidth]{"../analysis/pdf/   context_switching_2_30_regular _switching_persp"}
+	\includegraphics[width=1\linewidth]{"../analysis/pdf/context_switching_2_30_regular_switching_persp"}
 	\begin{minipage}{0.9\textwidth}
@@
 	\centering
-	\includegraphics[width=1\linewidth]{"../analysis/pdf/   context_switching_2_sf_d1 _switching_persp"}
+	\includegraphics[width=1\linewidth]{"../analysis/pdf/context_switching_2_sf_d1_switching_persp"}
 	\begin{minipage}{0.9\textwidth}
@@
 	\centering
-	\includegraphics[width=1\linewidth]{"../analysis/pdf/   context_switching_2_sf_d5 _switching_persp"}
+R	\includegraphics[width=1\linewidth]{"../analysis/pdf/context_switching_2_sf_d5_switching_persp"}
 	\begin{minipage}{0.9\textwidth}
@@
 	\centering
-	\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_switching_sf_d5_d1 _switching_persp"}
+	\includegraphics[width=1\linewidth]{"../analysis/pdf/context_switching_sf_d5_d1_switching_persp"}
 	\begin{minipage}{0.9\textwidth}
@@
 	\centering
-	\includegraphics[width=1\linewidth]{"../analysis/pdf/ context_switching_1_10regular_1_scale-free_d1 _switching_persp"}
+	\includegraphics[width=1\linewidth]{"../analysis/pdf/context_switching_1_10regular_1_scale-free_d1_switching_persp"}
 	\begin{minipage}{0.9\textwidth}

### 2015-06-28 doc/main.tex

@@
 
-		\address[ul]{GUESS/BioISI - Instituto de Biosistemas e Ciências Integrativas,
-                  Faculdade de Ciências, Universidade de Lisboa, 1749-016 Lisboa, Portugal.}
+		\address[ul]{GUESS/BioISI--Instituto de Biosistemas e Ciências Integrativas,
+                  Faculdade de Ciências, Universidade de Lisboa, 1749-016 Lisboa, Portugal.}
                 \title{Modelling Structured Societies: a Multi-relational Approach to Context
